### 2016-08-18 draft/BOSSAP.tex
updates

%%% On-going present
%%
%% Beginning of file 'sample.tex'
%%
%% Modified 2005 December 5
%%
%% This is a sample manuscript marked up using the
%% AASTeX v5.x LaTeX 2e macros.

%% The first piece of markup in an AASTeX v5.x document
%% is the \documentclass command. LaTeX will ignore
%% any data that comes before this command.

%% The command below calls the preprint style  
%% which will produce a one-column, single-spaced document.
%% Examples of commands for other substyles follow. Use
%% whichever is most appropriate for your purposes.
%%
%%\documentclass[12pt,preprint]{aastex}

%% manuscript produces a one-column, double-spaced document:

%%\documentclass[manuscript]{aastex}

%% preprint2 produces a double-column, single-spaced document:

 %\documentclass[preprint2]{aastex}
%\documentclass[preprint2]{aastex}
%\documentclass[manuscript]{aastex}
\documentclass[iop]{emulateapj}
\renewcommand{\baselinestretch}{0.95}
%% Sometimes a paper's abstract is too long to fit on the
%% title page in preprint2 mode. When that is the case,
%% use the longabstract style option.

%% \documentclass[preprint2,longabstract]{aastex}

%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
%% If you are submitting to a journal that translates manuscripts
%% into SGML, you need to follow certain guidelines when preparing
%% your macros. See the AASTeX v5.x Author Guide
%% for information.

\usepackage{enumitem}

\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$~}\fi}} 
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}

%% You can insert a short comment on the title page using the command below.

%\slugcomment{Not to appear in Nonlearned J., 45.}

%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
%% The left head contains a list of authors,
%% usually a maximum of three (otherwise use et al.).  The right
%% head is a modified title of up to roughly 44 characters.
%% Running heads will not print in the manuscript style.

%\title[]
%{}

\shorttitle{Reshift Dependent Alcock-Paczynski effect from SDSS-III DR12}
\shortauthors{X.-D. Li, C. Park, C.G. Sabiu, H. Park, D.H. Weinberg, J. Kim, S.E. Hong}

%% This is the end of the preamble.  Indicate the beginning of the
%% paper itself with \begin{document}.

\begin{document}

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire.

\title{Cosmological constraints from the redshift dependence of the Alcock-Paczynski effect: application to the SDSS-III BOSS DR12 galaxies}

%\author{Xiao-Dong~Li\altaffilmark{1}, Changbom~Park\altaffilmark{1}, J.~E.~Forero-Romero\altaffilmark{2} and Juhan Kim%\altaffilmark{3}}
%\affil{\altaffilmark{1}School of Physics, Korea Institute for Advanced Study, Heogiro 85, Seoul 130-722, Korea }
%\affil{\altaffilmark{2}Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, %Colombia}
%\affil{\altaffilmark{3}Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-%gu, Seoul 130-722, Korea }
%\affil{\it (xiaodongli@kias.re.kr, cbp@kias.re.kr, je.forero@uniandes.edu.co, kjhan@kias.re.kr)}

%\author[Xiao-Dong~Li, Changbom~Park, Cristiano G. Sabiu, Juhan Kim and Sungwook E. Hong]
%{ Xiao-Dong Li$^{1,\dagger}$, Changbom Park$^{1}$, Cristiano G. Sabiu$^{2}$, Juhan Kim$^{3,1,\star}$, Sungwook E. Hong$^{1}$\\
%$^1$School of Physics, Korea Institute for Advanced Study, 85 Heogi-ro, Dongdaemun-gu, Seoul 130-722, Korea\\
%$^2$Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 305-348, Korea\\
%$^3$Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea\\
%$^{\dagger}$xiaodongli@kias.re.kr\\
%$\star$Corresponding Author: ***@kasi.re.kr}

\author{Xiao-Dong Li, Changbom Park,}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\author{Cristiano G. Sabiu, Hyunbae Park,}
\affil{Korea Astronomy and Space Science Institute, Daejeon 305-348, Korea}
\author{David H. Weinberg,}
\affil{Department of Astronomy and CCAPP, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA}
\author{Donald P. Schneider,}
\affil{Department of Astronomy and Astrophysics, The Pennsylvania State University, 
University Park, PA 16802 }
\affil{Institute for Gravitation and the Cosmos, The Pennsylvania State University, 
University Park, PA 16802 }
\author{Juhan Kim\altaffilmark{1},}
\affil{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\and
\author{Sungwook E. Hong}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}

%\altaffiltext{1}{xiaodongli@kias.re.kr}
%\altaffiltext{2}{cbp@kias.re.kr}
%\altaffiltext{3}{csabiu@kasi.re.kr}
%\altaffiltext{4}{\bf Hyunbae: your email}
\altaffiltext{1}{Corresponding Author: kjhan@kias.re.kr}

% \email{xiaodongli@kias.re.kr}
% \email{cbp@kias.re.kr}
% \email{je.forero@uniandes.edu.co}

% \author{S. Djorgovski\altaffilmark{1,2,3} and Ivan R. King\altaffilmark{1}}
% \affil{Astronomy Department, University of California,
%     Berkeley, CA 94720}
%
% \author{C. D. Biemesderfer\altaffilmark{4,5}}
% \affil{National Optical Astronomy Observatories, Tucson, AZ 85719}
% \email{aastex-help@aas.org}
%
% \and
%
% \author{R. J. Hanisch\altaffilmark{5}}
% \affil{Space Telescope Science Institute, Baltimore, MD 21218}
%
% %% Notice that each of these authors has alternate affiliations, which
% %% are identified by the \altaffilmark after each name.  Specify alternate
% %% affiliation information with \altaffiltext, with one command per each
% %% affiliation.
%
% \altaffiltext{1}{Visiting Astronomer, Cerro Tololo Inter-American Observatory.
% CTIO is operated by AURA, Inc.\ under contract to the National Science
% Foundation.}
% \altaffiltext{2}{Society of Fellows, Harvard University.}
% \altaffiltext{3}{present address: Center for Astrophysics,
%     60 Garden Street, Cambridge, MA 02138}
% \altaffiltext{4}{Visiting Programmer, Space Telescope Science Institute}
% \altaffiltext{5}{Patron, Alonso's Bar and Grill}

%% Mark off your abstract in the ``abstract'' environment. In the manuscript
%% style, abstract will output a Received/Accepted line after the
%% title and affiliation information. No date will appear since the author
%% does not have this information. The dates will be filled in by the
%% editorial office after submission.

\begin{abstract}
We apply the methodology developed in \cite{Li2014,Li2015} to BOSS DR12 galaxies and 
derive cosmological constraints from the redshift dependence of the Alcock-Paczynski (AP) effect.
The apparent anisotropy in the distribution of observed galaxies arise from two main sources,
the redshift-space distortion (RSD) effect due to the galaxy peculiar velocities,
and the geometric distortion when incorrect cosmological models are assumed for 
%the coordinate transformation from redshift space to comoving space, 
transforming redshift to comoving distance,
known as the AP effect.
%We focus on the redshift dependence of the anisotropic clustering of galaxies to constrain cosmological parameters.
Anisotropies produced by the RSD effect are, although large,
maintaining a nearly uniform magnitude over a large range of redshift,
while the degree of anisotropies from the AP effect varies with redshift by much larger magnitude. 
%We found that the redshift dependence of the anisotropy introduced by RSD is much less significant compared with the anisotropy caused by AP.
%We focus on the redshift dependence of the anisotropic clustering of galaxies to constrain cosmological parameters 
%which is less sensitive to RSD contamination.
We split the DR12 galaxies into six redshift bins, measure the 2-point correlation function in each bin,
and assess the redshift evolution of anisotropies.
%Assuming a flat Universe consisting of a pressure-less dark matter component 
%with current ratio $\Omega_m$, and a dark energy component with constant equation of state $w$,
We obtain constraints of $\Omega_m=0.314 \pm 0.038,\ \ w = -1.09 \pm 0.14$,
which are tighter than the current constraints from other cosmological probes
such as type Ia supernovae, cosmic microwave background, and baryon acoustic oscillation (BAO).
Combining these cosmological probes with our method yield tight constraints of 
$\Omega_m = 0.304 \pm 0.007,\ w=-1.04 \pm 0.03$.
Our method is complementary to the other large scale structure probes like BAO and topology.
%We discuss the caveats and possibilities for improving upon our methodology.
We expect this technique will play an important role in deriving cosmological constraints from
large scale structure surveys.
\end{abstract}

%% Keywords should appear after the \end{abstract} command. The uncommented
%% example has been keyed in ApJ style. See the instructions to authors
%% for the journal to which you are submitting your paper to determine
%% what keyword punctuation is appropriate.

\keywords{large-scale structure of Universe --- dark energy --- cosmological parameters}

%% From the front matter, we move on to the body of the paper.
%% In the first two sections, notice the use of the natbib \citep
%% and \citet commands to identify citations.  The citations are
%% tied to the reference list via symbolic KEYs. The KEY corresponds
%% to the KEY in the \bibitem in the reference list below. We have
%% chosen the first three characters of the first author's name plus
%% the last two numeral of the year of publication as our KEY for
%% each reference.

%% Authors who wish to have the most important objects in their paper
%% linked in the electronic edition to a data center may do so by tagging
%% their objects with \objectname{} or \object{}.  Each macro takes the
%% object name as its required argument. The optional, square-bracket
%% argument should be used in cases where the data center identification
%% differs from what is to be printed in the paper.  The text appearing
%% in curly braces is what will appear in print in the published paper.
%% If the object name is recognized by the data centers, it will be linked
%% in the electronic edition to the object data available at the data centers
%%
%% Note that for sources with brackets in their names, e.g. [WEG2004] 14h-090,
%% the brackets must be escaped with backslashes when used in the first
%% square-bracket argument, for instance, \object[\[WEG2004\] 14h-090]{90}).
%%  Otherwise, LaTeX will issue an error.

\section{Introduction}

The current standard model of cosmology has been highly successful at reproducing the Universe on large scales. %large scale observations of the Universe. 
From the temperature fluctuations in the cosmic microwave background (CMB), 
to the late time clustering of galaxies, 
the vacuum energy dominated cold dark matter model ($\Lambda$CDM) fits the data surprisingly well \citep{Planck2015,Anderson2013}. 
This result is all the more impressive considering both the underlying assumptions, 
such as homogeneity, isotropy, scale invariance of the primordial fluctuations, 
and the minimal set of cosmological parameters that are required.

Nonetheless, these models produce the unsatisfactory prospect that we must include within our ontology both a vacuum energy 
that is much smaller than that predicted from  quantum mechanics, 
or alternatively a new scalar field (dark energy) that has negative pressure
\citep{SW1989,Riess1998,Perl1999,PR2003,Li2011}, 
and a new matter component, which is not contained within the standard $SU(3)\times SU(2) \times U(1)$ formulation of particle physics.

With an over-abundance of models for both dark energy-like accelerated expansion and dark matter, 
it is crucial to obtain precise and model-independent measurements of the cosmic evolution, usually referred to as background observables. 
Two such observables are the angular diameter distance, $D_A$, and the Hubble factor, $H$.  
If these quantities can be measured at various redshifts and to a high degree of accuracy then our ability to differentiate between various competing models will be greatly increased.

In the last few years there has been increasing interest in using the Alcock-Paczynski (AP) effect \citep{AP1979} 
in the large-scale clustering of galaxies to obtain constraints on $D_A$ and $H$ \citep{Guzzo2008,topology}. 
Assuming an incorrect cosmological model for the coordinate transformation from redshift space to comoving space produces residual geometric distortions. 
These distortions are induced by the fact that measured distances along and perpendicular to the line of sight are fundamentally different. 
Measuring the ratio of galaxy clustering in the radial and transverse directions provides a probe of this AP effect.

There have been several methods proposed for applying the AP test to the large scale structure (LSS).
The most widely adopted one uses anisotropic clustering \citep{Ballinger1996,Matsubara1996},
which has been used for the 2 degree Field Quasar Survey \citep{Outram2004},
the WiggleZ dark energy survey \citep{Blake2011}, 
the Sloan Digital Sky Survey-I/II (SDSS-I/II) Luminous Red Galaxy (LRG) survey \citep{Eisenstein et al. 2011,ChuangWang2012},
and the SDSS-III Baryon Oscillation Spectroscopic Survey (BOSS) 
%\citep{Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, 2014ApJ...781...96L}.
\citep{Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, 2014ApJ...781...96L,
Alam2016, Beutler2016, Sanchez2016}
The main caveat of this method is that,
because the radial distances of galaxies are inferred from redshifts,
AP tests are inevitably limited by redshift-space distortions (RSD) \citep{Ballinger1996},
which leads to apparent anisotropy even if the adopted cosmology is correct.
The RSDs must be accurately modeled for the 2-point statistics of galaxy clustering.

\cite{Marinoni2010} proposed using the symmetry properties of galaxy pairs.
Unfortunately this method is also seriously limited by RSD.
The peculiar velocity distorts the redshift and changes the apparent tilt angles of galaxy pairs.
The effect depends on both redshift and underlying cosmology, and is rather difficult to model accurately \citep{Jennings2011}.
\cite{Ryden1995} and \cite{LavausWandelt1995} proposed another method using the apparent stretching of voids.
This approach has the advantage that the void regions are easier to model compared with dense regions,
but has limitations in that it utilizes only low density regions of the LSS
and requires large samples.

\cite{Li2014} proposed another method utilizing the redshift dependence of AP effect to overcome the RSD problem.
The anisotropies produced by RSD effect are, although very large,
close to uniform in magnitude over a large range of redshift.
Conversely, if cosmological parameters are incorrectly chosen, the LSS
appear anisotropic and the degree of anisotropy varies with redshift. 
%We found that the redshift dependence of the anisotropy introduced by RSD is much less significant compared with the anisotropy caused by AP.
%Thus we can focus on the redshift dependence of the galaxy density gradient field, 
%which is less affected by RSD, but still sensitive to cosmological parameters.
We used the {\it galaxy density gradient field} 
to characterize the anisotropies in LSS and tested the idea on Horizon Run 3 (HR3) N-body simulations \citep{horizonrun},
demonstrating that the method leads to unbiased estimation of the density parameter $\Omega_m$ and the dark energy equation of state (EoS) $w$.

The same topic was revisited in \cite{Li2015}, but using the {\it galaxy two-point correlation function} (2pCF) as the statistical tool.
The 2pCF as a function of angle, $\xi(\mu)$, is measured at different redshifts.
Similar to \cite{Li2014}, we found that the RSD effect, although significantly distorting $\xi(\mu)$, 
exhibits much less redshift evolution compared to the amount of change in $\xi(\mu)$ due to incorrectly adopted cosmologies.
When incorrect cosmological parameters are adopted, 
the shape of $\xi(\mu)$ appears anisotropic due to the AP effect, 
and the amplitude is shifted by the change in comoving volume;
both effects have significant redshift dependence.
%By focusing on the redshift dependence of $\xi(\mu)$, we can correctly recover the cosmological parameters despite the contamination of RSD.
We test the method using the 2pCF on mock surveys drawn from HR3
%we measuring the redshift evolution of 2pCF also leads to unbiased estimation of cosmological parameters 
and find the constraints obtained are tighter than those from the methodology of \cite{Li2014}.

The change of the comoving volume size is another consequence of an incorrectly adopted cosmology, 
and has motivated investigations constraining cosmological parameters from number counting of 
galaxy clusters \citep{PS1974,VL1996}. 
An obstacle in using the comoving volume for cosmological tests is the evolution of the number of target objects.
The essential need for reducing the evolution effects in applying the test led \cite{topology} to propose a new method
using the topology of LSS. 
Since the topology is a measure of intrinsic connectivity of structures,
it is expected to be insensitive to non-linear gravitational evolution, type of density tracers,
and RSD on large scales.
This method has been applied to the WiggleZ Dark Energy Survey data by \cite{WiggleZtopoloy},
and to simulated BOSS samples \citep{Speare2015}.

In this paper we apply our methodology to SDSS-III BOSS Data Release 12 (DR12) galaxies \citep{Reidetal:2016}.
%We split the DR12 samples of CMASS and LOWZ into six redshift bins (three in each) and measure the redshift evolution of 
%anisotropy therein to determine the correct cosmological parameters leading to least redshift evolution of anisotropy.
We take the 2pCF as statistical tool characterizing the anisotropic clustering and follow the procedure of \cite{Li2015} to conduct the analysis.
We assume a flat Universe and constrain parameters of $\Omega_m$ and $w$.
2pCF is a mature statistic in cosmology and its optimal estimation and statistical properties are well understood.
Compared with the density gradient field statistic, it leads to tighter constraints and is less affected by survey geometry.

The outline of this paper is as follows. 
In Sec. 2 we describe the observational data used in this paper.
In Sec. 3 we discuss the N-body simulations and mock galaxy catalogues that are used in this analysis.
In Sec. 4 we briefly review the nature and consequences of the AP effect when performing coordinate transforms in a cosmological context. 
In Sec. 5 and Sec. 6, we describe our analysis method and present the cosmological constraints obtained from BOSS DR12 galaxies. 
We conclude in Sec. 7.

%{\bf AMTB: Please chose one kind of tense of verbs. It changes from sentences to sentences!}
%{\bf AMTB: How many mock BOSS samples are made from HR4?}

\section{The Observational Data}\label{sec:data}

The Sloan Digital Sky Survey (SDSS; York et al. 2000) %DANGEROUS
imaged approximately 7\,606 $\rm deg^2$
of the Northern Galactic Hemisphere and 
3\,172 $\rm deg^2$ of the Southern Galactic Hemisphere in the {\it ugriz} bands \citep{Fukugita1996,Gunn1998}.
The survey was performed using the 
2.5m Sloan telescope \citep{Gunn et al. 2006}
at the Apache Point Observatory in New Mexico.
%BOSS, as part of the SDSS-III survey \citep{Eisenstein et al. 2011},
%has obtained additional imaging,
%increasing the region of the south to 3\,172 $\rm deg^2$.
BOSS \citep{Dawson et al. 2012,Smee2013}, as a part of the SDSS-III survey \citep{Eisenstein et al. 2011},
has obtained spectra and redshifts 
of 1.37 million galaxies selected from the SDSS imaging,
covering a region of 9\,376 $\rm deg^2$.
The galaxy redshifts were measured by an automated pipeline \citep{Bolton2012}.

\begin{figure*}
   \centering{
   %\includegraphics[width=7cm]{Tpcf--contour.eps}
   %\includegraphics[width=16cm]{Tpcf--contour-others.eps}
   %\includegraphics[width=7.5cm,natwidth=8.3,natheight=9]{maskdr12v1lowres.png}
   %\includegraphics[width=7.5cm,natwidth=8.3,natheight=9]{maskdr12v1lowzlowres.png}
   %\includegraphics[width=8.5cm,natwidth=8.3,natheight=5]{Tpcf--gal_LN.jpg}
   %\includegraphics[width=8.5cm,natwidth=8.3,natheight=5]{Tpcf--gal_LS.jpg}
   %\includegraphics[width=8.5cm,natwidth=8.3,natheight=5]{Tpcf--gal_CN.jpg}
   %\includegraphics[width=8.5cm,natwidth=8.3,natheight=5]{Tpcf--gal_CS.jpg}
   \includegraphics[width=8.5cm]{fig1_0.eps}
   \includegraphics[width=8.5cm]{fig1_1.eps}
   \includegraphics[width=8.5cm]{fig1_2.eps}
   \includegraphics[width=8.5cm]{fig1_3.eps}
   }
   \caption{\label{fig_radec}
   The sky coverage of the LOWZ and CMASS samples in the north and south Galactic caps. 
   The individual points mark position of galaxies in the survey coordinate frame.
   The solid lines mark the right ascension and declination.
   The mean completeness is 97.2\% for the LOWZ sample, shown in the upper panels,
   and 98.8\% for the CMASS sample in the lower panels.
   The effective sky coverage is 8,337 $\rm deg^2$ for LOWZ and 9,376 $\rm deg^2$ for CMASS.
   %Each patch corresponds to a plate,
   %with the color determined by the completeness of that plate.
   See \cite{Reidetal:2016} for more details.
   }
\end{figure*}

The spectroscopic sample of BOSS has two primary catalogues.
%the LOWZ at $z\leq0.4$, and CMASS covering $0.4\leq z \leq 0.7$. %of galaxies.
The LOWZ sample is designed to extend the SDSS-I/II LRG sample to $z\approx 0.4$ and fainter luminosities,
in order to increase the number density of the sample by a factor of 3.
The CMASS sample covers a higher redshift ($0.4\lesssim z \lesssim 0.7$).
It was targeted to be an approximately stellar mass limited sample of massive, luminous galaxies.
The final data release (DR12) samples are described in \cite{Reidetal:2016},
where the details of targeting algorithms and the catalogues are provided.
%The full targeting algorithms used and the method for calculating the galaxy and random catalogues are presented in \citet{Reidetal:2016}, 
%Full details of targeting algorithms and the catalogues are provided in \citep{}, 
%and we do not replicate this here.

%The galaxy survey used two primary target algorithms, 
%selecting samples called LOWZ, with 361\,759 galaxies in the final data release DR12 \citep{dr12} between $0.15<z <0.43$ and CMASS, 
%with 771\,567 galaxies in DR12 between $0.43< z < 0.70$. 
%The full targeting algorithms used and the method for calculating the galaxy and random catalogues are presented in \citet{Reidetal:2016}, 
%which also shows that the samples jointly cover a large cosmic volume $V_{\rm eff}=7.4\,{\rm Gpc}^3$.
%with a number density of galaxies as a function of observed redshift, 
%that ensures that the shot noise does not dominate at BAO (baryon acoustic oscillation) scales. 
%The full targeting algorithms used and the method for calculating the galaxy and random catalogues are presented in \citet{Reidetal:2016}, 
%Full details of the catalogues are provided in \citet{Reidetal:2016}, 
%and we do not replicate this here.

%BOSS is designed to obtain 
%spectra and redshifts of $\sim$1.35 million galaxies 
%(together with 160\,000 quasars and approximately 100\,000 ancillary targets)
%selected from the SDSS imaging.
%The SDSS-I/II data \citep{York et al. 2000}

%CMASS and LOWZ\,

%We use data from the Sloan Digital Sky Survey \citep[SDSS; ][]{2000AJ....120.1579Y}. 
%SDSS has mapped over one quarter of the sky in five photometric bands down to a limiting magnitude of $r\sim 22.5$. 
%The photometric data is reduced and from it are selected targets for followup spectroscopy. 
%The spectroscopic survey, known as the Baryon Oscillation Spectroscopic Survey (BOSS), 
%is charged with obtaining spectra for 1.35 million galaxies over a 10,000 square degree footprint.

\begin{figure*}
   \centering{
   \includegraphics[width=19cm]{fig2.eps}
   }
   \caption{\label{fig_nbar}
      The redshift density distribution of the BOSS DR12 galaxy samples, assuming a $\Lambda$CDM cosmology with $\Omega_m=0.31$.
      The blue and green solid histograms show the distribution of LOWZ and CMASS galaxies respectively. 
      The vertical dashed lines define the six redshift bins that are used to cut the samples.
      Their redshift ranges are listed.
      The number of LOWZ (CMASS) galaxies in the three low (high) redshift bins are presented in the brackets.
      }
\end{figure*}

Figure \ref{fig_radec} presents the sky coverage of the BOSS DR12 samples used in this analysis. 
%The light grey shaded region shows the expected total footprint of the BOSS survey. 
%Colors indicate the spectroscopic completeness.
The mean completeness is 97.2\% for the LOWZ sample, in the upper panels, and 98.8\% for the CMASS sample shown in the lower panels.
   %Each patch of different color corresponds to a plate,
   %with the color determined by the completeness of that plate..
Figure \ref{fig_nbar} shows the galaxy number density of the two samples.
In this analysis we use 361\,759 LOWZ galaxies at $0.15<z <0.43$ and 
771\,567 CMASS galaxies at $0.43< z < 0.693$.
%in total galaxies.
We split the galaxies into six redshift bins: 
three bins in LOWZ ($0.150<z_1<0.274<z_2<0.351<z_3<0.430$), 
and three in CMASS ($0.430<z_4<0.511<z_5<0.572<z_6<0.693$), 
as illustrated in Figure \ref{fig_nbar}.

\begin{figure*}
   \centering{
   \includegraphics[width=19cm]{fig3.eps}
   }
   \caption{\label{fig_mock}
      Creation of mock galaxy samples for BOSS.
      Using an all-sky mock survey from the HR4 or HR3 simulations,
       we are able to produce four sets of NGC samples or eight sets of SGC samples with non-overlapping sky coverage.
      The individual points are the right ascension and declination of 1\% galaxies drawn from the CMASS samples.
      }
\end{figure*}

Each spectroscopically observed galaxy is assigned several weights to account for observational effects. 
The galaxy weights are constructed from three distinct effects.
%redshift failure, $w_{fail}$, minimum variance, $w_{FKP}$, and angular variation, $w_{sys}$. 
%These weights are described in more detail in \cite{2012MNRAS.427.3435A} and \cite{2012MNRAS.424..564R}. 
Firstly, galaxies lacking a redshift due to fiber collisions 
\footnote{Fiber collisions occur when two objects are close enough together such that two fibers cannot be placed.
In BOSS, the collision radius is 62 $''$.}
or inadequate spectral information are accounted for by reweighting
the nearest galaxy by a weight $w_{\rm fail}=(1+n)$, 
where $n$ is the number of close neighbors without a measured redshift. 
Secondly, all galaxies are assigned `FKP' weights \citep{1994ApJ...426...23F}
%as a function of redshift depending on the number density.
as a function of number density,
to optimize the clustering measurements in the face of shot-noise and cosmic variance.
%according to,
%\begin{equation}
%w^i_{FKP}=\frac{1}{1+n_i(z)P_0},
%\end{equation}
%where $n_i(z)$ is the comoving space density at redshift $z$ and $P_0 \sim P(k=0.1~{\rm $h^{-1}$Mpc}) \sim 2\times 10^{4}h^{-3}{\rm Mpc^3}$, 
%as in \cite{2012MNRAS.427.3435A}. 
The third weight corrects for angular variations of survey completeness and the systematics 
related to the angular variations in stellar density that make detection of
galaxies difficult in over-crowded regions of the sky. %\citep{2012MNRAS.424..564R}. 
The total weight for each galaxy is the product of these three weights, $w_{\rm total}=w_{\rm fail}w_{\rm FKP}w_{\rm sys}$.

For the statistical analyses, 
random catalogues having the same angular and redshift selection functions as the data 
are provided along with the data \citep{Reidetal:2016}.
%Each random point is assigned with a redshift of measured galaxy randomly drawed from galaxies.
%and a weight given by the $w_{\rm tot}$ of the measured galaxy.
The random points are also weighted but they only include the minimum variance `FKP' weight. 
%50 times as many random points as we have galaxies

\section{The Mock Galaxy Data}
\label{sec:mocks}
%We use HR3 and HR4...
%We use HR4 J08 ...

%Shape of $\\xi$ measured in HR4 very similar to data...
%Shape of

For LSS studies mock survey samples created from simulations are crucial
for the correction of systematics and covariance estimation.
The Horizon Run simulations are a suite of large volume N-body simulations that 
have resolutions and volumes capable of accurately reproducing the observational statistics of the current major redshift surveys like 
SDSS-III BOSS \citep{park 2005,2009ApJ...701.1547K,horizonrun}.
The HR3 \citep{horizonrun} and HR4 \citep{hr4} simulations are used in our analysis.

From the HR3 and HR4 simulations we have generated all-sky light cone mock galaxy catalogues.
The all-sky spherical mocks are then incorporated with the same fiber collision effect, 
angular masks, and radial selection function with the real observational data,
creating mock surveys of BOSS DR12.

We impose a minimum mass limit varying along with redshift to match the radial density of BOSS samples.
The galaxies of the BOSS DR12 samples do not cleanly distribute above some particular mass boundary;
they always have a fuzzy, blur boundary extending to relatively small values (as an example, see Figure 3 of 
Parihar et al. 2014). %DANGEROUS
%rather than shaprly lying above a certain mass cut, 
Galaxies in the mock samples are systematically more massive than those from observations;
We will discuss the effect of this discrepancy in Sec. \ref{sec:caveats}.

\subsection{Horizon Run 4}

The HR4 simulation  \citep{hr4} used a box size $L={3150}$ $h^{-1}$Mpc, 
and $N=6300^3$ particles.  
The simulation used the second order Lagrangian perturbation theory (2LPT) initial conditions at $z_{i}=100$ and a WMAP5 cosmology
$(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96) \citep[]{komatsu 2011}, 
yielding a particle mass of $m_{p} \simeq 9.02 \times 10^9 \hMsun$.
This starting redshift, combined  with 2LPT initial conditions, ensures an accurate mass function and power spectrum \citep{2014NewA...30...79L}.

Mock galaxy samples are produced from the HR4 simulation by using a modified version of the one-to-one correspondence scheme \citep{hong2016}. 
The most bound member particles (MBPs) of simulated halos are adopted as the tracer of galaxies rather than the subhalos,
and the merger timescale is taken into account in the lifetime of merged halos.
We built the merger trees of simulated halos by tracking their MBPs from $z = 12$ to 0.
When a merger event occurs, we calculate the merger timescale described in \cite{jiang2008} (hereafter J08)
to determine when a satellite galaxy is completely disrupted.
%We modeled the position and the velocity of a galaxy from the position and velocity of its corresponding MBP.
By using the abundance matching, 
we modeled the luminosity of a central/isolated galaxies from their current mass
and of satellite galaxies 
from their mass at the time of infall.

\cite{hong2016} compared the 2pCF of our mock galaxy sample at $z = 0$ to the SDSS DR7 volume-limited galaxy sample \citep{zehavi2011}.
%When a typical subhalo-galaxy correspondence scheme is applied, 
%the 2pCF from our simulation is smaller than the observation and does not show a proper Finger-of-God (FOG) feature in our simulation resolution. 
%We found that %the %2pCF of our galaxy sample agrees well with the observation.
The simulated 2pCF shows a similar finger of god (FOG) feature \citep{FOG} as the observation in the contour map, 
and the projected 2pCF agrees with the observation within 1$\sigma$ deviation on scales greater than 1 ${h^{-1}}$Mpc.

%As will be introduced in the next section, 
The HR4 simulation yield one all-sky light cone mock galaxy catalogue reaching $r=3\,150$ ${h^{-1}}$Mpc.
As shown in Figure \ref{fig_mock},
from one all-sky survey, 
we are able to create four sets of non-overlapping north Galactic cap (NGC) samples for CMASS and LOWZ, 
or eight sets of non-overlapping south Galactic cap (SGC) samples.
In this paper we use these simulated galaxies for the estimation of the systematics in the 2pCF of the observed galaxies.
%We create four north

\begin{figure*}
   \centering{
   \includegraphics[height=8cm]{fig4_0.eps}
   \includegraphics[height=8cm]{fig4_1.eps}
   %\includegraphics[height=7cm]{FVol.eps}
   %\includegraphics[height=8cm]{xy.eps}
   %\includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_xy}
   %Apparent distortion of objects in four wrongly assumed cosmologies, assuming a true cosmology of .
   The redshift dependence of the AP effect in four incorrect cosmologies,
   assuming that the true cosmology is $\Omega_m=0.31$, $w=-1$.
   The left panel shows the apparent distortion of four perfect squares,
   measured by an observer located at the origin.
   The apparently distorted shapes are plotted in red solid lines.
   The underlying true shapes are indicated in blue dashed lines.
   The right panel displays the degree of the shape distortion, as described by Equations (\ref{eq:stretch}).
   The BOSS DR12 galaxies used in our analysis have a redshift coverage of $0.15 < z < 0.693$ (marked 
   by the gray vertical lines). Clearly, the magnitude of the shape distortion due to AP changes with redshift.
   %measured by an observer located at the origin.
   %For reference, blue dashed squares show their shapes and positions in the true cosmology.
   }
\end{figure*}

\subsection{Horizon Run 3}
%In our analysis we also mock surveys constructed from one of the Horizon Run simulations, HR3.

As in HR4, HR3 also adopts a flat-space $\Lambda$CDM cosmology with the WMAP 5 year parameters.
The simulation was made in a cube of volume $(10.815\  h^{-1}{\rm{Gpc}})^3$
using $7120^3$ particles with particle mass of $1.25\times 10^{11}$\hMsun.
The simulations were integrated from $z=27$ and reached $z=0$ after making $N_{\rm step}=600$ global timesteps.
The collapsed high-density regions were identified using the Friend-of-Friend algorithm with the linking length of 0.2 times the mean particle separation.
The physically self-bound (PSB) subhalos that are gravitationally self-bound and tidally stable \citep{kim and park 2006} 
are identified and used as galaxy proxies.
The PSB halo finder is a group-finding algorithm which can efficiently identify halos located even in crowded regions. 
This method combines two physical criteria such as the tidal radius of a halo and the total energy of each particle to find member particles.
The group velocity of member particles is adopted as the peculiar velocity of each PSB subhalo.

%This provides a substantial increase in the similarity between simulation and observational data,
%as these dark matter subhalos are sites for galaxy formation.
%LRG (Xiao: is it OK to change all the ``LRG'' to ``galaxy''?) formation.

To simulate the SDSS survey,
HR3 places 27 observers evenly within its cubical volume and allows
each observer to survey out to a redshift of 0.7
\footnote{In the analysis we choose the maximal redshift as 0.693 rather than 0.7. 
%The lightcone data created from HR3 simulations have cosmological redshift limit of $z<0.7$. 
The outer boundary of the mock survey becomes fuzzy due to the peculiar velocity effect 
on the galaxy redshifts (Eq. (\ref{eq:zvpeu})).
A population of galaxies, that are expected to enter the $z<0.7$ region from the outside, is missing.
%(these $z>0.7$ galaxies have a peculiar velocity toward us and 
%their observed redshfits become lower than 0.7).
To avoid this problem we set the maximal redshift at 0.693, 
23.3 $h^{-1}{\rm Mpc}$ away from $z=0.7$.}, 
creating 27 samples of independent, non-overlapping spherical regions.
From the 27 spherical light cone `galaxy' catalogues, 
we created 72 non-overlapping survey samples 
\footnote{Using the 27 spherical light cones, we create 72 sets of NGC samples from 18 light cones, 
and 72 sets of SGC samples from the other 9 light cones.}
simulating BOSS DR12 within the redshift range of $0.15< z< 0.693$.
%As will be described in the next section, 
These mock surveys are used to estimate the covariance of the 2pCF in our analysis.

\section{AP Effect in Incorrect Cosmologies}
\label{sec:APeffect}

%Considering we are Let us consider an object in the Universe with certain size and shape.
%Its observed redshift span $\Delta z$ and angular size $\Delta \theta$ are related with the comoving sizes by
This section illustrates the AP effect when an incorrect cosmological model is used to calculate the distances of galaxies. Similar illustrations have been provided in \cite{Li2014,Li2015}.

Suppose that we probe the shape and volume of an object in the Universe,
which spans $\Delta z$ in redshift and $\Delta \theta$ in angle.
Its comoving sizes in the radial and transverse directions are given by
\begin{eqnarray}\label{eq:distance}
& &\Delta r_{\parallel} = \frac{c}{H(z)}\Delta z,\nonumber\\
& &\Delta r_{\bot}=(1+z)D_A(z)\Delta \theta,
\end{eqnarray}
where $H$ is the Hubble parameter and $D_A$ the proper angular diameter distance.
In the particular case of a flat Universe with constant dark energy EoS, they take the forms of
\begin{eqnarray}\label{eq:HDA}
& &H(z) = H_0\sqrt{\Omega_ma^{-3}+(1-\Omega_m)a^{-3(1+w)}},\nonumber\\
& &D_A(z) = \frac{c}{1+z}r(z)=\frac{c}{1+z}\int_0^z \frac{dz^\prime}{H(z^\prime)},
\end{eqnarray}
where $a=1/(1+z)$ is the cosmic scale factor,
$H_0$ is the present value of Hubble parameter and $r(z)$ is the comoving distance.

In case we adopted an incorrect set of cosmological parameters in Equation (\ref{eq:HDA}),
the inferred $\Delta r_{\parallel}$ and $\Delta r_{\bot}$ are also incorrect,
resulting in distorted shape (AP effect) and wrongly estimated volume (volume effect).
The degree of variations in shape and volume are
\begin{equation}\label{eq:stretch}
 %{\rm Degree\ of\ LOS\ stretch\equiv}
 %{\rm rat}_{\rm LOS\ stretch}\equiv
 \frac{[\Delta r_{\parallel}/\Delta r_{\perp}]_{\rm wrong}}{[\Delta r_{\parallel}/\Delta r_{\perp}]_{\rm true}} =
  \frac{[D_A(z)H(z)]_{\rm true}}{[D_A(z)H(z)]_{\rm wrong}} 
\end{equation}
\begin{equation}\label{eq:volume}
 %{\rm Degree\ of\ volume\ magnification \equiv}
 %{\rm rat}_{\rm volume\ mag}\equiv
 \frac{{\rm Volume}_{\rm wrong}}{{\rm Volume}_{\rm true}}
 = \frac{[\Delta r_{\parallel}(\Delta r_{\perp})^{2}]_{\rm wrong}}{[\Delta r_{\parallel}(\Delta r_{\perp})^{2}]_{\rm true}}
 = \frac{[D_A(z)^2/H(z)]_{\rm wrong}}{[D_A(z)^2 / H(z)]_{\rm true}},
\end{equation}
where ``true'' and ``wrong'' denote the values of quantities in the true cosmology and incorrectly assumed cosmology.
From the AP and volume effects, we can constrain  $D_A(z)H(z)$ and $D_A(z)^2 / H(z)$, respectively.

The apparent distortion of objects due to incorrect cosmological parameters is illustrated in the left panel of Figure \ref{fig_xy}.
Suppose that the true cosmology is a flat $\Lambda$CDM model with the present density parameter $\Omega_m=0.31$
and standard dark energy EoS $w=-1$ \citep[the best $\Lambda$CDM model determined by Planck 2015 results][]{Planck2015}.
%(the best $\Lambda$CDM model determined by Planck 2015 results \citep{Planck2015}).
If we distributed three square objects at various distances from 500 to 2,000 $h^{-1}$Mpc,
and had an observer located at the origin measure their redshifts and compute their positions and shapes 
using redshift-distance relations of four incorrect cosmologies:
\begin{enumerate}[label=(\roman*)]
\item $\Omega_m=0.4$, $w=-1$,
\item $\Omega_m=0.1$, $w=-1$,
\item $\Omega_m=0.31$, $w=-0.3$,
\item $\Omega_m=0.31$, $w=-2.5$,
\end{enumerate}
the mismatch between the true and assumed cosmology will cause the shapes of the squares appear distorted.
In the cosmological models (ii) and (iv) the squares are stretched in the line of sight (LOS) direction (hereafter ``LOS shape stretch''),
%and magnification of the volume (hereafter ``volume magnification''), 
while in the models (i) and (iii) we see opposite effects of LOS shape compression.

The right panel of Figure \ref{fig_xy} presents the degree of shape distortion as a function of redshift. 
In cosmology (i) and (iii), $\frac{[D_A(z)H(z)]_{\rm true}}{[D_A(z)H(z)]_{\rm wrong}}$ have values less than 1, 
indicating LOS shape compression,
while in cosmology (ii) the curve lies above 1, 
corresponding to an LOS shape stretch.
The effect in cosmology (iv) is more subtle. 
There is a transition from LOS shape stretch to compression at $z \approx 0.65$.

More importantly, Figure \ref{fig_xy} highlights the redshift dependence of the AP effect. 
If the conversion of redshift to the comoving distance was correctly made,
there would be no shape distortion at any redshift.
Conversely, the four cases with incorrectly chosen cosmological parameters illustrated 
in Figure \ref{fig_xy} 
show characteristic dependence of the shape distortion on redshift.
Our method utilizes this redshift dependence to constrain cosmological parameters
governing the expansion history of the Universe.
%For example, in cosmology (i), %with $\Omega_m=0.4$, 
%the LOS shape stretch become more significant with increasing redshift.
%In cosmology (iv), not only the magnitude of the effect evolves with redshift,
%but there is also a turnover from LOS shape stretch to compression.
%The magnitude of anisotropies produced by AP evolves with redshift.
%We can search for such pattern in the LSS statistic to see whether there exists distortions produced by AP effect,
%thus determine the correctness of the cosmological model.% adopted for the computation of $r(z)$.

\section{Methodology}\label{sec:methodology}

We measure the 2pCF in redshift bins of BOSS DR12 galaxies and 
determine cosmological parameters by examining the redshift evolution of clustering anisotropy.
Mock survey samples are used to correct the results for the systematics and to estimate the covariance.
%Our procedure is as follows.

\subsection{Grid of cosmology parameters}

The observed coordinates ({\it RA, Dec, z}) of galaxies
need to be converted to comoving coordinates ({\it x, y, z}) for the 2pCF analysis.
The dependence of clustering anisotropy on cosmology enters through the conversion from redshift to comoving distance,
i.e. the distance-redshift relation $r(z)$.
We consider the case of a flat Universe dominated by matter and dark energy,
so our $r(z)$ is governed by two parameters, $\Omega_m$ and $w$, as presented in Equation (\ref{eq:HDA})	.

To constrain these two parameters we examine the parameter space of 
$0.06\leq \Omega_m\leq 0.41$ and $-1.5 \leq w \leq -0.4$ with intervals of 
$\delta \Omega_m = 0.005$ and $\delta w = 0.025$,
forming a 71$\times$45 grid.
%This coverage and step size shall be enough for us to determine the 95\% confidence level (CL) region with satisfactory precision.
For each set of ($\Omega_m$, $w$), 
the comoving coordinates of all galaxies are computed, 
%the 2pCF of these galaxies in six redshift bins are measured,
%and a $\chi^2$ value is then obtained by requiring least redshift evolution of anisotropy.
%This enables us to infer the values and underlying distributions of $\Omega_m$ and $w$ through Bayesian analysis.
and the 2pCF is ready to be calculated.

\begin{figure*}
   \centering{
   \includegraphics[width=14cm]{fig5.eps}
   %\includegraphics[width=14cm]{Tpcf--contour.eps}
   }
   \caption{
    \label{fig_2pcfcon} 
    2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples 
      in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
    The black dashed lines mark the scales 6\ $h^{-1}$Mpc $\leq s\leq$ 40\ $h^{-1}$Mpc.
    %The correlation functions have rather large values on small sales such as $s=5$ $h^{-1}$Mpc,
    %  and monotonically decreases to smaller values on larger scales due to weaker clustering.
    The contour lines are not horizontal due to the effects of peculiar velocity.
    The FOG and Kaiser effects clearly manifest themselves through the tilting of contour 
     lines where $1-\mu \rightarrow 0$ and $1-\mu \gtrsim0.1$, respectively.
    The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$.
   }
      %The redshift density distribution of the BOSS DR12 galaxy samples, assuming a $\Lambda$CDM cosmology with $\Omega_m=0.31$.
      %The blue and green solid histograms show the distribution of LOWZ and CMASS galaxies respectively. 
      %The vertical dashed lines define the 6 redshift bins that are used to cut the samples.   }
\end{figure*}

\subsection{Measuring the correlation function}

%We probe the Alcock-Paczynski effects using the 2pCF. 
%The 2pCF is a mature statistic in cosmology and its optimal estimation considers minimal variance 
%while dealing with complicated masks and selection functions. 
%The most commonly adopted formulation is that of the 
We adopt the Landy-Szalay estimator~\citep{1993ApJ...412...64L} to calculate the 2pCF,
\begin{equation}
\xi(s,\mu)=\frac{DD-2DR+RR}{RR}\ ,
\end{equation}
where $DD$ is the number of galaxy--galaxy pairs, 
$DR$ the number of galaxy-random pairs, 
and $RR$ is the number of random--random pairs, 
all separated by a distance defined by $s\pm\Delta s$ and $\mu\pm\Delta\mu$, 
where $s$ is the distance between the pair and $\mu=\cos(\theta)$, 
with $\theta$ being the angle between the line joining the pair of galaxies and the LOS direction to the target galaxy. 
This statistic captures the anisotropy of the clustering signal.

The random catalogue consists of unclustered points whose number density in redshift space mimics the radial selection function of the observational data. 
To reduce the statistical variance of the estimator we use 50 times as many random points as we have galaxies.
The galaxies and random points are weighted as described in Sec. \ref{sec:data}.

Figure \ref{fig_2pcfcon} shows the 2D contour of measured $\xi$ as a function of $\mu$ and $s$,
from the six redshift bins of LOWZ and CMASS samples 
in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
%The correlation functions have rather large values on small sales such as $s=5$ $h^{-1}$Mpc,
%and monotonically decrease to smaller values on larger scales due to weaker clustering.
Due to the peculiar velocity effect, the contour lines are not horizontal.
The FOG \citep{FOG} and Kaiser \citep{Kaiser1987} effects 
clearly manifest themselves through the tilting of contour lines in regions of $\mu \rightarrow 1$ and $1-\mu \gtrsim0.1$, respectively.
A visual inspection of the contour maps from the six redshift bins 
reveals that they all have a similar appearance,
implying small redshift evolution of $\xi$.

\subsection{Probing the anisotropy through 2pCF}

The 2pCF is measured as a function of the separation $s$ and the angular direction $\mu$.
To probe the anisotropy we are more interested in the dependence of the 2pCF on $\mu$.
We follow the procedure of \cite{Li2015} and integrate the $\xi$ over the interval $s_{\rm max} \leq s \leq s_{\rm min}$.
We evaluate
\begin{equation}\label{eq:xideltas}
\xi_{\Delta s} (\mu) \equiv \int_{s_{\rm min}}^{s_{\rm max}} \xi (s,\mu)\ ds.%,\ \ \ {\rm at\ particular\ binned\ direction\ }\mu_i
\end{equation}
The integration is limited at both small and large scales.
At small scales the value of $\xi$ is seriously affected by the FOG effect \citep{FOG}
which depends on the galaxies bias.
This may introduce a redshift evolution in $\xi_{\Delta s}(\mu)$ that is relatively difficult to model.
At large scales the measurement is dominated by noise due to poor statistics.
\cite{Li2015} found that $s_{\rm min}=6-10$ $h^{-1}$Mpc and $s_{\rm max}=40-70$ $h^{-1}$Mpc are reasonable choices 
which provide consistent, tight and unbiased constraints on cosmological parameters.
In this analysis we choose $s_{\rm min}=6$ $h^{-1}$Mpc and $s_{\rm max}=40$ $h^{-1}$Mpc.

The redshift evolution of the bias of observed galaxies leads to redshift evolution of the strength of clustering,
which is difficult to accurately model.
To mitigate this systematic uncertainty we rely on the shape of $\xi_{\Delta s}(\mu)$, rather than its amplitude,
\begin{equation}\label{eq:norm}
 \hat\xi_{\Delta s}(\mu) \equiv \frac{\xi_{\Delta s}(\mu)}{\int_{0}^{\mu_{\rm max}}\xi_{\Delta s}(\mu)\ d\mu}.
\end{equation}
We impose a cut $\mu<\mu_{\rm max}$ to reduce the fiber collision and FOG effects which are stronger toward the LOS ($\mu\rightarrow1$) direction.

\begin{figure*}
   \centering{
   \includegraphics[width=16cm]{fig6.eps}
   }
   \caption{\label{fig_datamock}
   %Apparent distortion of objects in four wrongly assumed cosmologies, assuming a true cosmology of .
   $\hat\xi_{\Delta s}(\mu)$ measured from BOSS DR12 CMASS NGC sample 
    (consists of $\approx 565\,000$ galaxies at $0.15 < z < 0.693$)
    and one realization from the HR4 N-body simulation, in the WMAP5 cosmology.
   The lower panel shows the difference between the results of observational data and mock galaxies.
   $\hat\xi_{\Delta s}(\mu)$ are obtained by integrating $\xi (s,\mu)$ within the range {\rm 6\ $h^{-1}$Mpc}$\leq s\leq${\rm 40\ $h^{-1}$Mpc} 
      and normalizing the amplitude, 
    i.e., Eq. (\ref{eq:xideltas}) and Eq. (\ref{eq:norm}).
   To produce a clear view of the FOG effect, we split the angular range of $0.01\leq \mu \leq 1$ into as many as 40 bins.
   Using the HR4 mock galaxies, the enhancement near $\theta=0^\circ$ caused by the FOG effect
    and the tilt of the shape in $20^\circ\lesssim\theta\lesssim90^\circ$ 
    as a result of the large-scale flow,
    are all very well reproduced.
%    Thw lo
   This verifies the ability of our galaxies assignment method \citep{hong2016} 
    to reproduce the properties of galaxy distributions from large scale surveys.
   %Conversely, the HR3 PSB halo mock can not 
   %reproduce the shape of $\hat\xi_{\Delta s}(\mu)$.
   We use the HR4 mock galaxies to correct the systematics effects produced by the RSD.
   %The 72 sets of PSB mocks from HR3 are used to compute covariance.
   %measured by an observer located at the origin.
   %For reference, blue dashed squares show their shapes and positions in the true cosmology.
   }
\end{figure*}

The clustering properties may be affected by various properties of the galaxy sample, 
such as, for example the mass, morphology, color, concentration. 
In our simulation, using the merger tree, 
we identify ``galaxies'', therefore we only use the galaxy mass building history to simulate BOSS galaxies. 
Therefore, it is necessary for us to test if our mock galaxies can accurately 
reproduce the $\hat\xi_{\Delta s}(\mu)$ of observed galaxies.

%The clustering properties may be affected by the redshift evolution of properties of the galaxy sample, 
%such as the mass, morphology, color, concentration, and so on. 
%In our simulation, using the merger tree, we identify 'galaxies' so that we only use the galaxy mass to simulate BOSS galaxies. Therefore, it was necessary for us to test if our mock galaxies can accurately reproduce the shape of $\xi_{\Delta s}(\mu)$ of observed galaxies.

%As shown by Figure 6, the mock galaxies from our HR4 simulation can well reproduce the 
%$\hat\xi_{\Delta s}(\mu)$ of the observed galaxies.
Figure \ref{fig_datamock}  compares the shape of $\hat\xi_{\Delta s}(\mu)$ measured from observational data and mock survey samples.
It is clear that $\hat \xi_{\Delta s}(\mu)$ from mock galaxies identified in the HR4 simulation (green dotted line) agrees well with the observation.
%The HR4 galaxy mock can well reproduce the result from observational measurement.
The enhancement near $\theta=0^\circ$ is caused by the FOG effect,
and the characteristic shape in $20^\circ\lesssim\theta\lesssim90^\circ$ 
produced from the large-scale flow
are all very well reproduced.
This result verifies the ability of our mock galaxies to reproduce the clustering properties of the observed galaxies.
The small overestimate (underestimate) of $\hat\xi_{\Delta s}$ at large (small) $\mu$ could be due to 
that our mocks galaxies are more massive than those in the observations.
%methodology. (AMTB: need some good expression; need consult SW)
%Conversely, the HR3 PSB halo galaxies do not accurately reproduce the observations.
We use the HR4 galaxy mocks to correct the systematics.
%The HR3 PSB mock galaxies are used to estimate the covariance of 2pCF since 72 mock survey samples are available.

\begin{figure*}
   \centering{
   \includegraphics[width=16cm]{fig7.eps}
   %\includegraphics[height=9cm]{Tpcf-sys.eps}
   }
   \caption{\label{fig_sys}
   %Apparent distortion of objects in four wrongly assumed cosmologies, assuming a true cosmology of .
   Systematics in $\delta \hat \xi_{\Delta s}$, measured from the HR4 mock galaxy samples.
   The redshift evolution of RSD effect and properties of samples can lead to non-zero values of $\delta \hat\xi_{\Delta s}(z_i,z_1)$.
   For the 1st to 5th redshift bins, $\delta\hat\xi_{\Delta s, \rm sys}(z_i,z_1)\lesssim0.02$,
    indicating a small redshift evolution of the RSD effect and properties of galaxies.
   For the 6th redshift bin, the values of $\delta\hat\xi_{\Delta s, \rm sys}(z_6,z_1)$ are relatively large,
   because galaxies in that highest redshift bin are significantly more massive than those at lower redshifts.
   % so the measured $\hat\xi_{\Delta s}(\mu)$ has larger (smaller) values at $\mu\rightarrow1$ ($\mu\rightarrow0$) 
   % compared with the others.
   See Sec. \ref{sec:syscor} for details.
   %The values are estimated from the HR4 mock galaxies. % and subtract its contribution.
   }
\end{figure*}

%It is impossible to probe $\hat\xi_{\Delta s}(\mu)$ as a continuous function with infinite degrees of freedom. 
We divide the full angular range $0\leq\mu\leq\mu_{\rm max}$ into $n_{\mu}$ bins and measure its value in each bin.
Since we are free to choose $\mu_{\rm max}$ and $n_{\mu}$,
they are varied to optimize the S/N of our results.
This topic will be discussed in Sec. \ref{sec:binningscheme}.

\subsection{Characterizing the redshift evolution}

As shown in Figure \ref{fig_nbar}, we split the BOSS DR12 galaxies into six redshift bins, three in LOWZ and three in CMASS.
To study the redshift evolution of the clustering anisotropy 
we use the {\it first redshift bin} as the reference and compare the measurements in other bins with that in the first.
We define
\begin{equation} \label{eq:deltahatxi}
\delta \hat\xi_{\Delta s}(z_i,z_1,\mu_j)\ \equiv\ \hat\xi_{\Delta s}(z_i,\mu_j) - \hat\xi_{\Delta s}(z_1,\mu_j)
\end{equation}
where $\hat\xi_{\Delta s}(z_i,\mu_j)$ is $\hat\xi_{\Delta s}$ measured in the $i$th redshift bin and $j$th $\mu$ bin,
where $1\leq i \leq 6$ and $1\leq j \leq n_{\mu}$.
To characterize the shape of the curve well $n_\mu \gtrsim5$ is required.

\subsection{Correction for systematics}\label{sec:syscor}

Other than the AP effect, there are additional effects 
which may produce redshift-dependent anisotropy and affect the results.

The observational artifacts, such as fiber collisions, redshift failures, 
and the non-cosmological density fluctuations with stellar density and seeing,
are accounted for in the galaxy weights \citep{Reidetal:2016}.
Fiber collisions and redshift failures may affect the value of $\hat\xi(\mu)$ in the region close to LOS;
%We correct them by reweighting galaxies, include fiber collisions in the construction of mock surveys,
we abandon the angular region of $1-\mu<0.01$, 
to avoid possible systematics (see Appendix \ref{sec:RBtest} for more discussion).

%The SGC catalogues have higher target density than NGC and 
%thus a higher galaxy number density, known as the north/south asymmetry.
The non-contiguous NGC and SGC are less well cross-calibrated with respect to each other 
than they are internally calibrated \citep{Schlafly2010,SF2011,Parejko2013}.
We construct the NGC and SGC mock surveys separately to avoid possible systematics.
The 2pCF analysis is also carried out for the NGC and SGC independently.
%Also, in this analysis we only look at the radial evolution of clustering properties. 
The result should be robust as long as each catalogue is well calibrated internally.

%The variation in the density of catalogues is not expected to have large effect on our analysis.

%The redshift evolution of AP effect, RSD effect and properties of samples all may lead to non-zero values of $\delta \hat\xi_{\Delta s}$.
%To measure the signal from the redshift evolution of the AP effect,
%we estimate the value of $\delta \hat\xi_{\Delta s}$ from the other effects and subtract their contribution
%(hereafter $\delta\hat\xi_{\Delta s, \rm sys}$) from the total variation.

The apparent anisotropy introduced by RSD is, 
although greatly reduced by focusing on the redshift evolution, 
still the most significant systematic effect.

We estimate the value of $\delta \hat\xi_{\Delta s}$ from the systematic effects and subtract their contribution
(hereafter $\delta\hat\xi_{\Delta s, \rm sys}$) from the total variation.
The quantity $\delta\hat\xi_{\Delta s, \rm sys}$ is estimated from the HR4 mock galaxies.
The mock survey sample imitates the SDSS BOSS sample by mimicking
the survey as close as possible and includes past light cone effects.
The observational systematics such as the RSD, survey geometry, and shot noise
are included in the exactly same way as the observation.
The peculiar velocity perturbs the observed redshift through the relation
\begin{equation}\label{eq:zvpeu}
\Delta z = (1+z) \frac{v_{{\rm LOS}}}{c},
\end{equation}
where $v_{\rm LOS}$ is the LOS component of the peculiar velocity of galaxies.
The redshift evolution of galaxy peculiar velocities, 
resulting from growth of structure,
causes the anisotropy produced by RSD to have a small redshift evolution; 
this is the main source of systematic uncertainty in our results.

We take the HR4 mock galaxy samples and compute $r(z)$ of galaxies in the cosmology under which the simulation is based.
In this case there is no AP effect. 
Thus, the measured $\delta \hat\xi_{\Delta s}$ are the redshift evolution purely created by systematics effects.
They are adopted as the estimation of $\delta\hat\xi_{\Delta s, \rm sys}$,
and the results are illustrated in Figure \ref{fig_sys}. %shows $\delta\hat\xi_{\Delta s, \rm sys}(z_i,z_1)$ measured from the HR4 mock galaxy samples.
%Measurements of $\hat\xi_{\Delta s}$ in the 2th to 6th redshift bins are compared with that in the first bin.

For the 1st to 5th redshift bins, $\delta\hat\xi_{\Delta s, \rm sys}(z_i,z_1)\lesssim0.02$,
indicating a small redshift evolution of the RSD effect and properties of galaxies.
The only exception is the 6th redshift bin where the values of $\delta\hat\xi_{\Delta s, \rm sys}(z_6,z_1)$ are relatively large.
The reason for the large values is that the galaxies in that highest redshift bin are significantly more massive than those at lower redshifts,
so the measured high redshift $\hat\xi_{\Delta s}(\mu)$ has larger (smaller) values at $\mu\rightarrow1$ ($\mu\rightarrow0$) 
compared with the others
(an investigation of the dependence of $\hat\xi_{\Delta s}(\mu)$ on galaxy mass is provided in Sec. \ref{sec:caveats}).

%This should be the reason why .

\subsection{The caveats}\label{sec:caveats}

%The biggest systematic of our method, like all other applications of AP, is still the RSD problem.
\cite{Li2014,Li2015} found the RSD effect exhibits a small redshift dependence of $\hat \xi_{\Delta s}(\mu)$, 
mainly due to the structure growth and the selection effect
(different galaxy bias at different redshifts).
In this analysis we use the mock galaxy sample from HR4 to correct this systematics.
The galaxy assignment scheme of \cite{hong2016} applied to HR4 is very successful in modeling both the 
large scale Kaiser effect and the small scale FOG effect in nonlinear regions.
%After correcting the systematic effect of RSD, we obtain reasonable cosmological constraint consistent with all other cosmological probes.

There are two possible caveats in our procedure of the modeling of the RSD effect.

1) The RSD effect is estimated from mock survey samples created in a particular cosmology, 
i.e., the $\Omega_m=0.26$ $\Lambda$CDM model. %model from WMAP5 observations with .
If this adopted cosmology is different from the truth, then there could be a systematic bias in the estimation. %of RSD
We believe that this will not seriously affect our cosmological constraints.
\cite{Li2014} shows that the redshift dependence of RSD is not sensitive to cosmological parameters.
Also, the cosmologies adopted in the HR3 and HR4 simulations are consistent with our best-fit cosmological parameters within 1$\sigma$,
therefore our inferred cosmological constraints should be fairly accurate.
In a future analysis,
we will estimate the redshift evolution of the RSD effect from a set of cosmological simulations 
covering the relevant part of the parameter space.
This approach will remove the remaining uncertainty associated with the RSD effect, 
which is already a minor effect in our analysis.
%the statistical uncertainty of this method could be much smaller,
%and modeling the RSD effect in a cosmological dependent manner would be necessary.

\begin{figure*}
   \centering{
   \includegraphics[width=14cm]{fig8.eps}
   %\includegraphics[width=14cm]{Tpcf--contour.eps}
   }
   \caption{
    \label{fig_2pcf_masscut} 
    $\hat \xi_{\Delta s}(\mu)$ measured from a small HR4 mock galaxy sample with different minimal mass cuts.
    The mock galaxies are taken from the $z=0$ snapshot data within the radius $r<600$ $h^{-1}$Mpc.
    Only small variations of $\hat\xi_{\Delta s}(\mu)$ are produced when changing the minimal mass cuts.
    Higher mass cuts result in larger (smaller) $\hat\xi_{\Delta s}(\mu)$ at $\mu\rightarrow1$ ($\mu\rightarrow0$).
    Considering the large variation of mass cuts, the variation of $\hat\xi_{\Delta s}(\mu)$ is not significant.
   }
      %The redshift density distribution of the BOSS DR12 galaxy samples, assuming a $\Lambda$CDM cosmology with $\Omega_m=0.31$.
      %The blue and green solid histograms show the distribution of LOWZ and CMASS galaxies respectively. 
      %The vertical dashed lines define the 6 redshift bins that are used to cut the samples.   }
\end{figure*}

2) The selection effect, i.e., the evolution of galaxy bias with redshifts, 
can introduce redshift evolution in the clustering properties of the observed galaxies.
%If that is not accurately modeled, people may worry about systematics. %may suffer from systematic errors.
%Again, we believe this is not a serious problem for our analysis.
In our analysis the amplitude of the 2pCF is normalized and only its angular information, 
the function $\hat \xi_{\Delta s}(\mu)$, is used.
This function is rather insensitive to the galaxy bias,
which mainly affects the strength of clustering.

As a test, Figure \ref{fig_2pcf_masscut} shows $\hat \xi_{\Delta s}(\mu)$ measured from a small HR4 galaxy sample with different minimal mass cuts.
The mock galaxies are taken from the $z=0$ snapshot data within the radius $r<600$ $h^{-1}$Mpc.
Applying the minimal mass cuts of $1,2,4\times 10^{13} h^{-1} M_{\odot}$, 
we created three sets of subsamples with number density of 
$\bar n=4.56,\ 2.10,\ 0.91 \times 10^{-4} ( h^{-1} \rm Mpc)^{-3}$, 
which roughly covers the scatter of the number density of BOSS DR12 galaxies at $0.15<z<0.7$
\footnote{The BOSS LOWZ and CMASS galaxies reside in massive haloes 
with a mean halo mass of $5.2 \times 10^{13} h^{-1} M_{\odot}$ and $2.6 \times 10^{13} h^{-1} M_{\odot}$ \citep{Parejko2013,White2011,Reidetal:2016},
respectively.
For CMASS galaxies, when the redshift changes from $z=0.43$ to $0.7$,
the mean stellar mass varies from $10^{11.6} {M_{\odot}}$ to $10^{11.9} {M_{\odot}}$ \citep{CMASSLSS2014}.}.

For subsamples with higher mass cuts the $\hat\xi_{\Delta s}(\mu)$
has larger (smaller) values at $\mu\rightarrow1$ ($\mu\rightarrow0$).
More massive samples result in less tilted $\hat\xi_{\Delta s}(\mu)$ in the region of $1-\mu\gtrsim0.1$
\footnote{This phenomenon is understandable.
The tilt of $\hat\xi_{\Delta s}(\mu)$ is related to the RSD effect, 
and also the overall amplitude of the 2pCF (the denominator of Eq. (\ref{eq:norm})).
The slope should be roughly proportional to $(v/b_g)^2$, 
where the peculiar velocity term $v^2$ denotes the effect of RSD, 
and the galaxy bias term $b_g^2$ represents the amplitude of the 2pCF. 
For the more massive sample, $b_g$ is much larger while $v$ is still close to the peculiar velocity of dark matter field,
%So their curves are less tilted.
therefore the slope is smaller.
}.
This explains the relative large value of $\hat \xi_{\Delta s,\rm sys}(z_6, z_1)$.
In particular, comparing the subsamples with mass cuts $4\times 10^{13}h^{-1} M_{\odot}$ and $1\times 10^{13}h^{-1} M_{\odot}$, 
we find the red dotted curve is higher (lower) than the blue solid line at $\mu\rightarrow1$ ($\mu\rightarrow0$),
with a difference of $\approx$0.1 (0.05),
consistent with the value of $\hat \xi_{\Delta s,\rm sys}(z_6, z_1)$ shown in Figure \ref{fig_sys}.

In addition, this result also explains the small discrepancy between the $\hat\xi_{\Delta s}(\mu)$ measured from the 
observational data and the HR4 simulations (Figure \ref{fig_datamock}).
The mock galaxies could be systematically more massive than the observed ones.
These systematics could be most significant in the 6th redshift bin
where mock galaxies are most massive, 
leading to possible overestimation of $\delta\hat\xi_{\Delta s,{\rm sys}}$.
We discuss the impact of this effect in Sec. 6.1.

Considering the large variation of mass cuts, the change of $\hat\xi_{\Delta s}(\mu)$ is not significant,
so we conclude that $\hat\xi_{\Delta s}(\mu)$ is relatively insensitive to the galaxy bias.

%In addition, Figure 5 of \cite{Li2015} also shows that the peculiar velocities of the halos (PSB halos from HR3) are very insensitive to their masses. 
%This means the RSD effect coming from galaxies with different biases are similar.
%So the modeling of RSD effect does not require accurate modeling of the biases of the observed galaxies.

\subsection{$\chi^2$ function}\label{sec:likelihood}

We define a $\chi^2$ function to quantify the redshift evolution of clustering anisotropy
\begin{equation}\label{eq:chisq1}
\chi^2\equiv \sum_{i=2}^{6} \sum_{j_1=1}^{n_{\mu}} \sum_{j_2=1}^{n_{\mu}} {\bf p}(z_i,\mu_{j_1}) ({\bf Cov}_{i}^{-1})_{j_1,j_2}  {\bf p}(z_i,\mu_{j_2}),
\end{equation}
where ${\bf p}(z_i,\mu_{j})$ is the redshift evolution of clustering, 
$\hat \xi_{\Delta s}$, with systematic effects subtracted
\begin{eqnarray}\label{eq:bfp}
 {\bf p}(z_i,\mu_{j}) \equiv&\ \delta \hat\xi_{\Delta s}(z_i,z_1,\mu_j) - \delta \hat\xi_{\Delta s, \rm sys}(z_i,z_1,\mu_j)
\end{eqnarray}
${\bf Cov}_i$ is the covariance matrix estimated from the 72 sets of PSB mock galaxies identified from HR3 N-body simulation.

\subsection{Averaging a set of replicate measurements to increase the S/N}\label{sec:binningscheme}

The angular cut, $\mu_{\rm max}$, and number of bins, $n_\mu$, is chosen freely.
%The cut $\mu_{\rm max}$ and the number of bins $n_\mu$ can be chosen freely in our analysis.
Different choices for these parameters yield slightly different results and different statistical uncertainties.
To suppress the statistical noise we adopt a large number of binning schemes and average their $\chi^2$s.

A value $\mu_{\rm max} = 0.99$ is sufficient to remove the fiber collision effect.
We have checked that our results are statistically robust against the choice of $\mu_{\rm max}$.

A larger $n_\mu$ tightens the constraint 
in the cost of more noise, 
while $n_\mu$ should be smaller than the number of mock samples used for covariance estimation.
We find $n_\mu \gtrsim 5$ gives relative tight constraints, 
and $n_\mu = 40$ is the limit we can reach given the size of the sample and the number of mock samples.

We run through the range $\mu_{\rm max} = 0.85, 0.86, ... 0.99$ at steps of 0.01 and $n_\mu = 5, 6, ... 40$, in total 540 binning schemes.
%\footnote{In fact we only use 381 schemes.
%In some cases the estimation of covariance is not very successful, leading to singular matrix or very noisy $\chi^2$;
%We reject these cases.}.
We compute $\chi^2$ according to Equation (\ref{eq:chisq1}) for these choices and take an average of these $\chi^2$s.
This approach suppresses the statistical noise quite effectively. %in the contour map of $\chi^2(\Omega_m,w)$.

%We find noise in the $\chi^2$ probably due to the low statistic caused by the limited size of the sample and the covmat due to small size of mocks ...
%So we compute many values of $\chi^2$ using different $n_\mu$ and $\mu_{\rm max}$...
%The noise in $\chi^2$ shall be statistically random and by taking an average it is suppressed while the physical signal is preserved...
%We tested the dependence of the result on $\mu_{\rm max}$ and find the result is rather stable within the range $\mu_{\rm max}=0.85 - 0.99$...
%So we use $\mu_{\rm max} = 0.85, 0.86, ... 0.99$...
%Increasing $n_\mu$ tighens the constraintm, but in cost of larger noise in the result...
%Also $n_\mu$ shall be smaller than the number of mocks to compute covmat...
%So we use $n_\mu = 5, 6, ... 40$...
%So we define...
%\begin{equation}\label{eq:chisq2}
%\bar\chi^2\equiv \frac{ \sum \chi^2(n_\mu,\ \mu_{\rm max}) } {\rm Number\ of\ \chi^2} ... (find a proper way to illustrate this equation)
%\end{equation}

%{\bf AMTB: We need to give some results on the systematic effects. }

\begin{figure*}
   \centering{
   \includegraphics[width=18cm]{fig9_0.eps}
   \includegraphics[width=18cm]{fig9_1.eps}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_TpCF}
   Upper panels: $\hat \xi_{\Delta s}(\mu)$ measured for the BOSS DR12 galaxies,
   which are divided into six redshift bins.
   Measurements from the three bins in LOWZ are indicated in solid lines, 
   while those from CMASS are the dashed lines.
   We present the measurements in three cosmologies,
   the $\Omega_m=0.31$ $\Lambda$CDM (left), the $\Omega_m=0.1$ $\Lambda$CDM (middle),
   and a cosmology with $\Omega_m=0.31$, $w=-2.5$ (right).   
   %We adopt $s_{\rm min}=6$ $h^{-1}$Mpc and $s_{\rm max}=40$ $h^{-1}$Mpc for the integral over the scale of 2pCF.
   The angular dependence of 2pCF is measured in 10 bins within the range $0.01\leq1-\mu\leq1$.
   In the middle and right panels, the redshift dependence of AP distortions leads to clear redshift evolution of $\hat \xi_{\Delta s}(\mu)$.
   Lower panels: The redshift evolution of the $\hat\xi_{\Delta s}$ after systematics correction,  
   $\delta\hat \xi_{\Delta s}(z_i,z_1)-\delta\hat \xi_{\Delta s,\rm sys}(z_i,z_1)$
   (for details of their definitions, see Eq. (\ref{eq:deltahatxi}) and Sec. \ref{sec:syscor}).
   For clarity we combine the curves of $z_2$ and $z_3$, which fluctuate
   due to the relatively small sample sizes.
   The statistical significance is indicated by the 1$\sigma$ error bars of $\delta\hat \xi_{\Delta s}(z_6,z_1)-\delta\hat \xi_{\Delta s,\rm sys}(z_6,z_1)$.
   The curves are statistically consistent with 0 in the $\Omega_m=0.31$ $\Lambda$CDM cosmology,
    while they deviate from 0 at significant confidence levels in the $\Omega_m=0.1$ cosmology and the $w=-2.5$ cosmology.
   %showing the redshift dependence of AP effect.
   Applying the likelihood analysis described in Sec. \ref{sec:likelihood},
    the two latter models disfavored at 5.3$\sigma$ and 7.5$\sigma$ CL compared to the $\Omega_m=0.31$ $\Lambda$CDM cosmology.
   }
\end{figure*}

\section{Result}

We apply our method to the BOSS DR12 CMASS and LOWZ galaxies.
We present the results in this section.

\subsection{Redshift evolution in wrong cosmologies}\label{sec:redevolvxi}

%{\bf Figure: $\xi$ curves, in different cosmologies, without and with RSD}

The upper panels of Figure \ref{fig_TpCF} present the $\hat \xi_{\Delta s}$ measured for BOSS galaxies in three different cosmologies.
In the left panel we adopt the Planck cosmology, i.e., $\Lambda$CDM with $\Omega_m=0.31$;
%which should be {\it close to the truth}.
In the other two panels, we choose two sets of parameters ---
the $\Omega_m=0.1$ $\Lambda$CDM cosmology (middle) and the cosmology with $\Omega_m=0.31$ and $w=-2.5$ (right).
We split the BOSS DR12 galaxies into six redshift bins,
construct their 3D distribution in these three cosmologies
and then measure $\hat \xi_{\Delta s}(\mu)$ according to the procedure of the last section.

For a sample of galaxies with homogeneous, isotropic spatial distribution, 
the measured $\hat \xi_{\Delta s}(\mu)$ is statistically uniform.
The distortion in $\hat \xi_{\Delta s}(\mu)$ introduced by RSD is large.
There are two distinct features in this distortion.
At $0\lesssim 1-\mu \lesssim 0.1$, $\hat \xi_{\Delta s}(\mu)$ turns up as $\mu\rightarrow1$
due to the large FOG effect.
In other directions, the anisotropic clustering produced by the large scale flow creates a monotonic angle dependence of $\hat\xi_{\Delta s}(\mu)$. %a slope in the curve.
These patterns are evident in all cosmologies.

%\subsubsection{AP effect}

The additional angular dependence of $\hat \xi_{\Delta s}(\mu)$ introduced by AP is not as strong as RSD;
However, it is still visible. 
In the middle and right panels, % of Figure \ref{fig_TpCF},
%where there is clear redshift evolution of $\hat \xi_{\Delta s}$.
the choice of two incorrect cosmologies results in an enhancement of  $\hat \xi_{\Delta s}(\mu)$ due to the 
apparent stretch of non-linear structures in the LOS direction
%As a result, near LOS the value of $\hat \xi_{\Delta s}$ is enhanced 
\footnote{{\it Stretch of structure enhances the value of $\xi_{\Delta s}$}.
On relatively small scales, the strong clustering produces large values of $\xi$.
The apparent stretch of structure means the strong clustering on small scales are, apparently, shifted to larger scales:
at some fixed scale, we measured larger $\xi$ if there is apparent stretch.
The value of $\xi_{\Delta s}$, which is the integral of $\xi$ within fixed range of $s$, is also enhanced.}.
This effect is evident when we compare  $\hat \xi_{\Delta s}(\mu)$ in these two panels to that in the left panel.

More importantly, in incorrect cosmologies the redshift dependence of the AP effect results in a redshift evolution of $\hat \xi_{\Delta s}$.
This unique feature makes the AP effect detectable even with the existence of the large RSD effect. %distinguishable from the RDS distortion.
When $\Omega_m=0.1$ and $w=-1$ are adopted, 
the LOS stretch of structure becomes stronger at higher redshift (see Figure \ref{fig_xy});
as a result, the enhancement of $\hat \xi_{\Delta s}$ along the LOS 
becomes more significant at higher redshifts.
The opposite behavior is seen for the choice of $\Omega_m=0.31$ and $w=-2.5$.
%We see very evident redshift evolution of $\hat \xi_{\Delta s}$.
%I.e., the redshift dependence of AP effect results in redshift evolution of $\hat \xi_{\Delta s}$.
However, we do not see such obvious redshift evolution in the Planck cosmology, % is not so obvious.
 indicating that the cosmological parameters of the Planck cosmology are close to the correct ones.
%The Planck cosmology is widely accepted as to be close to the true cosmology parameters of our Universe and 
%There the AP effect is not strong enough to produce an evident redshift evolution.

The lower panels of Figure \ref{fig_TpCF} show the redshift evolution of $\hat\xi_{\Delta s}$ after systematics correction, 
i.e., the quantity $\delta\hat \xi_{\Delta s}-\delta\hat \xi_{\Delta s,\rm sys}$.
The result is statistically consistent to 0 in Planck cosmology -- 
In the four curves, almost all points are consistent with 0 at $\lesssim1\sigma$ confidence level (CL).
The only exception is the leftmost point of $\delta\hat \xi_{\Delta s}(z_6,z_1)-\delta\hat \xi_{\Delta s,\rm sys}(z_6,z_1)$,
 which is negative at $\sim$2 $\sigma$ CL.
This result could be due to the overestimation of $\delta\hat\xi_{\Delta s, \rm sys}(z_6,z_1)$ as discussed in Sec. \ref{sec:syscor}.
This behavior will not affect our derived cosmological constraints:
Dropping this measurement by imposing a cut $\mu<0.9$
  does not shift the constrained on $\Omega_m$-$w$ (the pink contour of Figure \ref{fig_contours}).

In the $\Omega_m=0.1$ cosmology and the $w=-2.5$ cosmologies, however,
the measured $\delta\hat \xi_{\Delta s}-\delta\hat \xi_{\Delta s,\rm sys}$ deviates 
from zero at significant confidence levels.
Applying the likelihood analysis described in Sec. \ref{sec:likelihood},
 they are disfavored at 5.3$\sigma$ and 7.5$\sigma$ CL compared to the Planck cosmology.
Since these two cosmologies deviates from the $\Omega_m=0.31$ $\Lambda$CDM cosmology with $\Delta \Omega_m = 0.21$ and $\Delta w = 1.5$,
roughly speaking, we expect our method able to constrain $\Omega_m$ and $w$ with 1$\sigma$ uncertainties of 0.04 and 0.2, respectively.

%Overall, the effect of RSD on the 2pCF is large but its redshift dependence is small.
%The correct cosmology corresponds to the case with the lowest change of $\hat \xi_{\Delta s}$ with $z$.
%Even with RSD, we can still correctly determine the true cosmology by using the relative change of $\hat \xi_{\Delta s}$ with redshift.

\subsection{Cosmological constraint}\label{sec:constraint}

We constrain $\Omega_m$ and $w$ through Bayesian analysis \citep{Bayesian},
which derives the probability distribution function (PDF) of some parameters $\bf \theta$ (=($\Omega_m,w$) in this paper)
given observational data $\bf D$, 
according to Bayes' theorem:
\begin{equation}
 P({\bf \theta}|{\bf D}) = \frac{P({\bf \theta})P({\bf D}|{\bf \theta})}{m({\bf D})}.
\end{equation}
Here $P(\bf \theta)$, the prior distribution of the parameters,
contains all the information about the parameters known from substantive knowledge 
and expert opinion {\it before} observing the data.
The marginal PDF of $\bf D$, 
$m({\bf D})=\int P({\bf D|\theta})P({\bf \theta})d{\bf \theta}$, 
is a normalization constant independent of $\theta$.
All the information about the parameter $\bf \theta$ that stems from the experiment
is contained in the function $P({\bf D}|{\bf \theta})$, 
the conditional PDF of the observation $\bf D$ given the value of parameter.

\begin{figure*}
   \centering{
   %\includegraphics[width=7cm]{Tpcf--contour.eps}
   %\includegraphics[width=16cm]{Tpcf--contour-others.eps}
   %\includegraphics[width=16cm,natwidth=52,natheight=40]{fig10.eps}
   \includegraphics[width=16cm]{fig10.eps}
   }
   \caption{\label{fig_contours}
   Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method and other cosmological probes.
   %obtained from the BOSS DR12 CMASS and LOWZ samples.
   Using the BOSS DR12 galaxies within the redshift range $0.15< z< 0.693$, our method achieves tight cosmological constraints on $\Omega_m$ and $w$.
   The area of the 1$\sigma$ contour of our method is smaller than all other probes.
   Constraints from various probes are consistent with each other.
   See Sec. \ref{sec:constraint} for details.
   %in very good consistent with the other methods.
   }
\end{figure*}

In this analysis we simply assume flat priors for $\Omega_m$ and $w$,
and approximate $P({\bf D}|{\bf \theta})$ by a likelihood function $\mathcal{L}$
satisfying  $-2 \ln \mathcal{L}=\chi^2$;
the PDF of $\theta$ derived from our AP method takes the form
%The PDF cu is approximated by the {\it likelihood} function of $\mathcal{L}\propto \exp\left(-\frac{\chi^2}{2}\right)$.
%It is approximated by the {\it likelihood} function.
%So we have
\begin{equation}
 P({\bf \theta}|{\bf D}) \propto \mathcal{L} \propto \exp\left[-\frac{\chi^2}{2}\right].
\end{equation}
We use the {\texttt {COSMOMC}} software \citep{LB2002}
to obtain the Markov Chain Monte Carlo (MCMC) samples of $\theta$ following the PDF of $P({\bf \theta}|{\bf D})$.
Constraints on $\Omega_m$ and $w$ are derived from these samples.

The 68\% and 95\% likelihood contours of $\Omega_m$ and $w$ 
obtained from this analysis are shown in Figure \ref{fig_contours} (pink areas).
%For comparison, results from some other cosmological probes are also plotted.
Our AP method yields tight constraints on $\Omega_m$ and $w$ .
The mean values and 68\% CL are
\begin{equation}
 \Omega_m=0.314 \pm 0.038,\ \ w = -1.09 \pm 0.14.
\end{equation}
This result is consistent with the Planck $\Lambda$CDM cosmology within 1$\sigma$ \citep{Planck2015}.

We find the expected negative degeneracy between $\Omega_m$ and $w$.
At low redshift, increasing $\Omega_m$ and increasing $w$ have a similar effect on the cosmic expansion.
When one parameter is increased the other parameter can be decreased to counteract the AP effect
\footnote{At high redshift the direction of degeneracy completely changes. 
There the effect of $w$ is less important and the cosmic expansion is mainly governed by $\Omega_m$.
This behavior is why \cite{Li2015} obtained a positive degeneracy between $\Omega_m$ and $w$ from mock surveys 
spanning a wide range of $0< z < 1.5$.
The degeneracy direction between $\Omega_m$ and $w$ depends on the redshift range of the sample used in the analysis.
}.

For comparison, additional likelihood contours from other cosmological probes are displayed in Figure \ref{fig_contours}:
the JLA SNIa sample (green area, \cite{JLA}),
the BAO measurement from BOSS DR11 galaxies (bright yellow, \cite{Anderson2013}),
%\footnote{The CMASS and LOWZ samples from BOSS DR11 have a sky coverage of 8\,377 $\rm deg^2$ and a completeness of 97\%.
%They are very close to the DR12 samples.},
a combination of the BOSS DR11 BAO and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ (dark yellow, \cite{Riess2011,E14H0}),
and the full-mission Planck observations of temperature and polarization anisotropies, released in 2015 (blue, \cite{Planck2015}).

%
The SNIa contours occupy a region similar to ours, but provide much weaker constraints. %has similar degeneracy to our method.% to us while the contour size is larger.
The direction of degeneracy is also similar.
%This is expectable.
By measuring the apparent magnitudes of type Ia supernovae distributed at different redshifts, 
 cosmologists can infer the luminosity distance $d_L$ as a function of redshift.
The JLA sample has similar redshift coverage to the BOSS DR12 galaxies,
which could be the reason for the similarity between the contours of the SNIa and our AP method.
%This is to some extent similar to our method, 
%which probes the redshift evolution of geometric distortion.
%which maybe the reason of the similarity 
%So the shapes and the positions of the contours from these two methods are a kind of close to each other.
%Comparing these two methods, we find our method has better constraining power.
%For SNIa probe, the degeneracy between $\Omega_m$ and $w$ is more serious and the contour extends to $\Omega_m=0$.

%The BOSS DR11 galaxies BAO measurements yields $D_V(z=0.32) = (1264 \pm 25 {\rm Mpc})(r_d /r_{d,\rm fid})$,
%$D_A(z=0.57) = (1421 \pm 20 {\rm Mpc})(r_d /r_{d,\rm fid})$, 
%and $H(z=0.57) = (96.8 \pm 3.4 {\rm km/s/Mpc})(r_{d,\rm fid} /r_d )$.
%Here $r_d$ is the drag epoch,
%$D_V(z)$ is the spherically averaged 2-point measurement of the BAO position, defined as $\left[cz(1+z)^2D_A(z)^2H^{-1}(z)\right]^{1/3}$, 
%and all measurements are presented as the ratio of the distance priors to their values in the fiducial cosmology \citep{Anderson2013}.
%At $z=0.57$, separating the clustering along and transverse to the LOS enables measurement of the sizes of the BAO ring in these two directions.

BAO itself can not effectively constrain $\Omega_m$ and $w$, 
since these parameters are highly degenerate with $H_0$ in determining the length scale.
Combining BAO with the $H_0$ measurements to break the degeneracy yields better constraint on the parameter space.
%The contour size is a bit larger than ours.
The direction of degeneracy of the combined constraint is roughly orthogonal to ours.
%This means we can combine these two LSS probes to break the degeneracy and significantly strengthen the constraining power.

CMB measurements provide a powerful probe of the geometry of the Universe,
but can not effectively constrain $\Omega_m$ and $w$ due to the strong degeneracy of the parameters.
%But combining CMB with the other probes can significantly shrink the volume of parameter space and tightens the constraint.
The CMB contour is almost orthogonal to the AP contour. 
%Contours from the two probes nicely overlapped with each other.
%In particular, our contour is well consistent with the Planck 2015 $\Lambad$CDM with $\Omega_m=0.308$.

Among all the individual cosmological probes, our method yields the most stringent 
constraint on $\Omega_m$ and $w$.
Our result is consistent with those of all other probes.
%Also, the degeneracy of our contour is different from most the other probes.
%We can take the advantage of this fact and tighten the constraint by combing them together.

Assuming that the five different cosmological probes of CMB, BAO, SNIa, $H_0$ and our method are 
statistically independent,
we combine the results by simply multiplying their likelihoods,
resulting in the total likelihood function
\begin{equation}\label{eq:likelihood}
\mathcal{L}_{\rm total} = \mathcal{L}_{\rm CMB} \times \mathcal{L}_{\rm BAO} \times \mathcal{L}_{\rm SNIa}\times \mathcal{L}_{\rm H_0}
 \times \mathcal{L}_{\rm Our\ AP}.
\end{equation}
The Planck team has released the {\texttt {COSMOMC}} outputs of MCMC samples
using CMB+BAO+JLA+$H_0$
\footnote{http://pla.esac.esa.int/pla/\#cosmology; 
Their BAO datasets include three sets of measurements from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS}}.
We modify their MCMC samples (by changing the values of sample weight and likelihood)
 to include the likelihood of our method,
creating samples following the PDF of Eq. (\ref{eq:likelihood}).
The joint constraint from all five cosmological probes is
\begin{equation}
 \Omega_m = 0.304 \pm 0.007,\ w=-1.04 \pm 0.03.
\end{equation}
%{\bf which are the strongest constraints on these parameters obtained so far}
%{\bf AMTB: 
Our AP method plays an important role in strengthening the constraints on $\Omega_m$ and $w$.
As a comparison, combining CMB and our method yields $\Omega_m = 0.302 \pm 0.011,\ w=-1.05 \pm 0.04$,
while a combination of CMB and BAO yields $\Omega_m = 0.306 \pm 0.013,\ w=-1.03 \pm 0.06$.
%by combining the CMB and BAO measurements, %while .
In the absence of our method, a combination of SNIa, CMB, BAO and $H_0$
yields $\Omega_m = 0.306 \pm 0.009,\ w=-1.03 \pm 0.04$ \citep{Planck2015}.
% }

%\bibitem[Blake et al. (2011)]{WiggleZB}
%Blake, C., Kazin, E.A., Beutler, F., et al.
%2011, MNRAS, 418, 1707
%\bibitem[Kazin et al. (2014)]{WiggleZK}
%Kazin, E.A., Koda, J., Blake, C., et al.
%2014, MNRAS, 441, 352

\section{Concluding Remarks}

We apply the methodology developed in \cite{Li2014,Li2015} to BOSS DR12 galaxies.
In LSS surveys, the observed galaxy distribution appears anisotropic due to two reasons:
the contamination of galaxy redshifts due to the galaxy peculiar velocities, known as the RSD effect, 
and the error in the distance due to inaccurate cosmological parameters. %incorrectly assumed cosmological model for the coordinate transformation from redshift space to comoving space, known as the AP effect.
\cite{Li2014} reported that anisotropies produced by RSD effect are, although large,
close to uniform in magnitude over a large range of redshift,
while the degree of anisotropies introduced by AP varies with redshift. 
%We found that the redshift dependence of the anisotropy introduced by RSD is much less significant compared with the anisotropy caused by AP.
Thus we can use the redshift dependence of the anisotropic clustering of galaxies to constrain cosmological parameters without 
being much affected by RSD.

%The methodology developed in \cite{Li2015} was applied.
As in \cite{Li2015}, we investigate the redshift-dependence of clustering anisotropy by examining the 2pCF.
The 2pCF measured along different angular directions was characterized by the function $\hat \xi_{\Delta s}(\mu)$.
%In incorrectly adopted cosmological models, 
When the cosmological parameters governing the expansion history of the universe are incorrectly chosen,
the shape of this function evolves with redshift.
We split the DR12 galaxies into six redshift bins, measure the 2pCF in each redshift bin,
and search for the underlying true values of $\Omega_m$ and $w$ of our Universe % (assuming flat Universe)
by requiring minimal redshift evolution of $\hat \xi_{\Delta s}(\mu)$ across the six redshift bins.
We obtain tight constraints of $\Omega_m=0.314 \pm 0.038,\ \ w = -1.09 \pm 0.14$ from our method alone.

The constraints on $\Omega_m$ and $w$ from our AP method are tighter % in constraining the parameter space of $\Omega_m$ and $w$ 
than the other cosmological probes of SNIa, CMB, BAO, and $H_0$.
For the direction of degeneracy, %between $\Omega_m$ and $w$ in the constrained parameter space,
our method is similar to SNIa and orthogonal to CMB and BAO+$H_0$.
Combining the results of our method with those of other cosmological probes, 
we obtain tight constraints $ \Omega_m = 0.304 \pm 0.007,\ w=-1.04 \pm 0.03$.

\subsection{Comparison with other LSS probes}

Our method uses the anisotropic galaxy on scales from 6 to 40 $h^{-1}$Mpc.
%a novel analysis method extracting physical information encoded in LSS. % compared with the others.
%We look at the geometric distortion of LSS due to AP effect 
%clustering created by AP exhibits redshift evolution.
%Here the clustering scales we choose to look at in this analysis is 
Constrains on cosmological parameters are obtained from the redshift dependence of $D_A(z) H(z)$.

As a comparison, the BAO method uses the BAO feature in the 
clustering of galaxies on scales of 100-150 $h^{-1}$Mpc 
created by the oscillation of the baryon-photon plasma in the early Universe.
Measuring the BAO feature in 1D or 2D yields measurements of $D_V$ or $D_A$ and $H$ at some representative redshifts.
%So the principles and the physical information probed in these two methods are fundamentally different.

The AP methods proposed to date, such as those using 
galaxy pairs and voids, measure the rate of geometric distortion and are sensitive to $D_A(z) H(z)$,
while our method uses its the redshift dependence.
These methods can be combined together to fully utilize the physics of AP test.
Also, reducing the RSD effect 
through the redshift dependence could be 
applicable to these methods.

The topology method proposed by \cite{topology} 
uses the redshift evolution of the volume effect and is sensitive to the quantity $D_A(z)^2 / H(z)$.
Combing this method with ours can yield separate constraints on $D_A$ and $H$ 
for the same observational sample.
Constraints from the other statistical measures,
such as the distribution function of size or richness of LSS,
can be also combined \citep{Park2012,Park2015}.
%Analyzing the distortion of apparent galaxies clustering due to RSD,
%people can constrain the growth rate, the clustering strength and the galaxy bias.

Recently, \cite{MS2016} developed a novel method 
constraining cosmological parameters based on the high-level similarity of the emission measure in the cluster outskirts.
In incorrect cosmologies, the emission measure from clusters exhibits redshift dependence.
%This leads to tight constraints on the redshift evolution of the cosmic length scale.
Utilizing a sample of 320 galaxy clusters ($0.056<z<1.24$) observed with Chandra,
they achieve tight cosmological constraints comparable to ours.
The idea of this novel technique is to some extent similar to our method 
(seeking for the conservation of geometric quantity with redshift),
and could have promising future.
%and can be combined with our method to

%The above LSS analysis methods, based on different concepts, 
%and probing different types of physical information, 
%are mutually complementary.
%It is worthy combining them together to comprehensively utilize the physical information encoded in the LSS 
%and derive tight constraints on parameters of cosmology. % and galaxy science.
%which is also fundamentally different from our method which is

\subsection{Room for improvements}

This paper is the first application of this redshift dependent AP test to observed LSS data.
There remains considerable opportunity for improving the analysis methodology,
e.g., the optimized schemes of redshift binning and 
optimized choices of the scales of clustering (the values $s_{\rm min}$ and $s_{\rm max}$).
In this paper, the 2pCF is characterized by $\hat \xi_{\Delta s}(\mu)$.
It should be more advantageous to use 
the redshift evolution of 2pCF in two dimensions, i.e., $\hat \xi(s,\mu)$, 
to capture the full information.
It is also necessary to combine the 
information in the higher-order
statistic beyond the two point functions.
As pointed out in Sec. \ref{sec:caveats},
more theoretical and numerical studies on the 
redshift evolution of the RSD effect 
will remove the remaining small 
uncertainties in our results.

To avoid the difficulty of modeling galaxy bias we dropped the information of strength of clustering
through normalizing the amplitude of $\xi$.
In the case that we have good knowledge of galaxy bias, one can utilize the amplitude of $\xi$ to probe the redshift dependence of volume effect 
and obtain much tighter constraints.
\cite{Li2015} showed that
the area of constraining regions in $\Omega_m$ and $w$ space from the redshift dependence of the volume effect is 3.5 times smaller 
than that from the redshift dependence of the AP effect alone.

In this analysis, by reducing the RSD effect, 
%through looking at the redshift evolution,
we are able to use the galaxy clustering down to 6 $h^{-1}$Mpc.
This is a major advance in extracting the cosmological information 
on small scales where galaxy clustering is strong
and there are a lot of independent structures.

To make sure that the derived cosmological constraint is robust, 
in the procedure of systematics correction, 
one should construct many mock surveys in which the RSD and other systematic effects are reliably modeled.
%It could be crucial to adopt a good galaxy assignment scheme, 
%such as the MBP-galaxy correspondence model developed in \citep{hong2016}.
%adopted in this analysis, could be crucial.
%So we can obtain an accurate estimation of systematic effect.

It would also be helpful to investigate the effect of galaxy properties.
For example, in case of a dense survey containing galaxies with various properties, 
one can split the galaxy sample into subsamples with different galaxy properties, 
derive cosmological constraints from these subsamples, 
and check the consistency of the results.

%Our method is to some extent very similar with the methods using the overall shape of 
%the power spectrum or correlation function Park \& Kim (2010) Shoji et al. 2009 {\bf AMTB: Read them and check }.
%But we have one addition that uses the shape in a set of redshift slices to reduce the RSD effect.

%This is one of the reasons why our method is powerful.
%for the strong power of our method -- the small scale galaxy clustering contains abundant information.
%In future the development of simulation technique may enable us to accurately modeling galaxy clusterings on even smaller scales 
%and makes our method more powerful.

\subsection{Synergies with future observations}

The constraining power of our method is proportional not only to the size, 
but also to the redshift coverage of the galaxy sample.
In this analysis we utilize 1\,133\,326 BOSS DR12 galaxies covering $0.15< z < 0.693$.
Future redshift surveys such as eBOSS \citep{eBOSS}, EUCLID \citep{EUCLID}, and DESI \citep{DESI}
will have larger sample sizes and wider redshift coverage.
Our method is expected to yield much tighter cosmological constraints
and can be applied to constrain wider classes of 
cosmological models when these data are available.
%In the future we will have LSS surveys of 
% having much wider redshift coverage and much larger number of observed galaxies.
%{\bf Introducing the redshift range and galaxy numbers of future surveys?: eBOSS, DESI, LSST, ...?}
%Being able to utilizing small scale clustering information a denser survey will be also helpful to improve the power of our method.
%Even for the regions already probed by the current SDSS-III survey, 
%there is still large potential to improve the power of constraint by conducting a deeper survey to increase the S/N.

In this analysis we assume a flat Universe to constrain $\Omega_m$ and $w$.
Our method should be sensitive to all other cosmological parameters governing the cosmic expansion history,
e.g., the curvature of the Universe, 
and the other dark energy parameters.

Overall, the future of our method is extremely promising. 
With the progressive development of LSS experiments, 
we expect it to play an important role in deriving cosmological constraints from LSS surveys.
%and yielding fruitful out-comings.

\section*{Acknowledgments}

We thank the Korea Institute for Advanced Study for providing computing resources (KIAS Center for Advanced Computation Linux Cluster System).
%We thank Seokcheon Lee and Graziano Rossi for many helpful discussions.
We would like to thank Ho Seong Hwang, Francisco-Shu Kitaura, Benjamin L'Huillier, Donghui Jeong, Teppei Okumura, Will Percival, Hyunmi Song 
and Yi Zheng for kind helps and helpful discussions.
This work was partially supported by the
Supercomputing Center/Korea Institute of Science and
Technology Information with supercomputing resources
including technical support (KSC-2013-G2-003).

Based on observations obtained with Planck (http://www.esa.int/Planck), 
an ESA science mission with instruments and contributions directly funded by 
ESA Member States, NASA, and Canada.

Funding for SDSS-III has been provided by the Alfred P. Sloan Foundation, the Participating Institutions, the
National Science Foundation, and the U.S. Department of Energy Office of Science. 
The SDSS-III web site is http://www.sdss3.org/. 
SDSS-III is managed by the Astrophysical Research Consortium for the Participating Institutions
of the SDSS-III Collaboration including the University of Arizona, the Brazilian Participation Group, Brookhaven
National Laboratory, Carnegie Mellon University, University of Florida, the French Participation Group, 
the German Participation Group, Harvard University, the Instituto de Astrofisica de Canarias, the Michigan State/Notre
Dame/JINA Participation Group, Johns Hopkins University, Lawrence Berkeley National Laboratory, Max Planck
Institute for Astrophysics, Max Planck Institute for Extraterrestrial Physics, New Mexico State University, New
York University, Ohio State University, Pennsylvania State
University, University of Portsmouth, Princeton University,
the Spanish Participation Group, University of Tokyo, University of Utah, Vanderbilt University, University of Virginia, 
University of Washington, and Yale University.

\appendix

\section{A. Robustness Tests}\label{sec:RBtest}

We conduct a series of tests to check the robustness of our results.

The cosmological constraints presented in Sec. \ref{sec:constraint} (hereafter the ``main results'') are derived using 
the following options (hereafter the ``default options''):
\begin{itemize}
 \item We adopt $s_{\rm min}=6 h^{-1} {\rm Mpc},\ s_{\rm max}=40 h^{-1} {\rm Mpc}$ in the integrated 2pCF
 ($\xi_{\Delta s} (\mu) \equiv \int_{s_{\rm min}}^{s_{\rm max}} \xi (s,\mu)\ ds$).
 \item The effects of systematics are estimated from the HR4 mock galaxies. 
 When constructing the mocks, to determine when a satellite galaxy is disrupted,
 we adopt the J08 model to calculate the satellite galaxy merger timescale.
 \item In total 72 sets of HR3 PSB mock surveys are used to construct the covariance matrix.
 \item We drop the angular region $1 - \mu < 0.01$, to mitigate the effects of fiber collisions and redshift failures.
\end{itemize}

\begin{figure*}
   \centering{
   \includegraphics[width=14cm]{fig11.eps}}
   %\includegraphics[width=5.9cm]{Tpcf--contour-nummock-36.eps}}
   \caption{ \label{fig_contour_RB}  
   Likelihood contours (68\%, 95.4\%) in the $\Omega_m$-$w$ plane, derived by applying our AP method to the BOSS DR12 galaxies.
   The upper-left panel displays the main results derived using the default options.
   %i.e. using $s_{\rm min}=6h^{-1}{\rm Mpc}$, $s_{\rm max}=40h^{-1}{\rm Mpc}$, $1 - \mu \ge 0.01$,
   %72 sets of HR3 PSB mocks for covariance estimation,
   %and J08 model to compute the merger timescale model in the construction of mock surveys.
   The other panels show the contours when the options are altered one by one.
   %We find good consistency among these contours. 
   }
\end{figure*}

We check whether the results are sensitive to these options.
We modify the above options one by one, 
derive the corresponding cosmological constraints, 
and check how much they deviate from the main results.
%and are compared with the constraints derived using the default option set.
We present this information in Figure \ref{fig_contour_RB}. %displays the many sets of cosmological constraints derived with various sets of modified options.
%The upper-left panel shows the result using the default options, 
%while the other many panels display the result after changing one of these options.

To be efficient, we adopt a coarser grid with $\delta \Omega_m=0.025,\ \delta w=0.05$ when covering the parameter space.
%Although the obtained contours look a little coarse, 
This resolution is high enough for the purpose of testing our methodology.

\subsection{$Different\ s_{\rm max}$}

The upper-panel of Figure \ref{fig_contour_RB} shows the main results, 
the cosmological constraint when the default options are adopted. %There we use $s_{\rm max}=40 h^{-1}{\rm Mpc}$. 
The results for $s_{\rm max}=30,\ 50 h^{-1}{\rm Mpc}$ are displayed in the middle and right panels of the first row.
%While the default choice of $s_{\rm max}=$ 40 $h^{-1}$Mpc gives the tightest constraint, 
The three choices of $s_{\rm max}$ results more or less similar to the main results.

\subsection{$Number\ of\ mocks\ for\ covariance\ estimation$}

In this analysis we use a set of 72 mock surveys sampled from HR3 to compute the covariance matrix.
We check whether the relative small number of mock surveys could produce significant bias in the derived cosmological constraint.

We take half of the mock surveys to compute the covariance matrix;
the result is presented in the second row of Figure \ref{fig_contour_RB}.
Our main result from 72 mocks gives slightly tighter constraint and less noisy contours than the results from 36 mocks.
The locations of contour center are similar, and statistically are quite close to each other.

Using 36 mocks we must adopt $n_\mu\lesssim20$ for the binning of $\xi_{\Delta s}(\mu)$,
so it is expected that the results are slightly weaker than the results of using 72 mocks (where we take $n_{\mu}\leq40$).

We further take the 2,000 sets of MultiDark PATCHY mock catalogues \citep{MDPATCHY} to compute the covaraince matrix.
%This set of mock surveys have been adopted for the error estimations of the 2pCF and power spectrum measurement of the BOSS galaxies \citep{Alam2016}.
Following Hartlap et al. (2006) and Percival et al. (2014), we correct the covariance matrix
for the statistical bias and scattering.
The obtained results are consistent with the main results.
The constrained area has a small extension in the upper-left corner, which will not affect the combined cosmological constraint.

%The constraints while using 36 mocks for covariance matrix appears a little weaker.
%The reason is that, the smaller number of mocks, the smaller number of binning allowed in the analysis. 
%As discussed in Sec. \ref{sec:binningscheme}, in our main analysis we are able to use as much as 40 bins in the region $0.01\leq\mu\leq1$.
%When using 36 mocks we limit the largest bin number to 20, which leads to slightly weaker constraint.

\subsection{$Mock\ galaxies\ for\ systematic\ correction$}

In the construction of HR4 mock galaxies \citep{hong2016}, 
the J08 model \citep{jiang2008}, a model derived from cosmological simulations, 
was adopted as the default option to calculate the merger timescale and to determine when a satellite galaxy is completely disrupted.

\cite{hong2016} also considered four alternative models for the calculation of merger timescale:
1) the LC93 model \citep{LC93} based on analytic calculation, 
2) the B08 \citep{B08} and 3) the V13 \citep{V13} models based on isolated simulations,
and 4) the M12 model \citep{M12} based on cosmological simulation.
%Among the five merger timescale models, 
%J08 was found to result in mock galaxies with properties and 2pCF best matching the observational data.
Among the five merger timescale models, 
J08 model produces mock galaxies having properties and 2pCF best agree with the observational data \citep{hong2016};
%So it was adopted in our main analysis.with
the LC93 model, having the shortest merger timescale among the five models,
produces galaxies with properties and 2pCF most deviated from the observations.

\begin{figure*}
   \centering{
   \includegraphics[width=16cm]{fig12.eps}
   %\includegraphics[height=9cm]{Tpcf-sys.eps}
   }
   \caption{\label{fig_sys_LC93}
   %Apparent distortion of objects in four wrongly assumed cosmologies, assuming a true cosmology of .
   Systematics in $\delta \hat \xi_{\Delta s}$, measured from the HR4 mock galaxies
   with the LC93 model adopted as the merger timescale model.
   Compared with the main result using the merger timescale model J08 (Figure \ref{fig_sys}), 
   there is a $\sim 25\%$ change in the amplitude of $\delta \hat \xi_{\Delta s}$.
   % so the measured $\hat\xi_{\Delta s}(\mu)$ has larger (smaller) values at $\mu\rightarrow1$ ($\mu\rightarrow0$) 
   % compared with the others.
   %See Sec. \ref{sec:syscor} for details.
   %The values are estimated from the HR4 mock galaxies. % and subtract its contribution.
   }
\end{figure*}

%To check whether our result is sensitive to these merger timescale models,
We adopt mock surveys created using the four alternative models to
measure the systematic correction $\delta \hat\xi_{\Delta s, {\rm sys}}$
and derive the cosmological constraints.
The difference between the $\delta \hat\xi_{\Delta s, {\rm sys}}$ estimated from the J08 model and the other models is $5\%-25\%$.
As an example, Figure \ref{fig_sys_LC93} presents the systematics correction estimated using LC93,
which has a $\sim25\%$ difference from the J08 estimation.

Nevertheless, Figure \ref{fig_contour_RB} shows that, 
when the alternative models adopted, 
the cosmological constraints are consistent with our main results;
the discrepancy is $\lesssim0.3\sigma$.

%In case of using the $z=0$ snapshot data rather than the lightcone galaxies to construct mock surveys,
%we find the contour slightly shifted to the upper-left direction.
%Statistically,

%Also, the shifts of contours mainly happens along the upper-left to lower-right diagonal.
%This means the joint constraint result, the constraint when combined with the other cosmological probes such as CMB, will not be very affected,
%since the CMB contour basically lies in the lower-left to upper-right diagonal.

\subsection{$Cut\ on\ \mu$}

%We checked whether the result is sensitive to the range of angular bins.
In our default options, we take $1 - \mu\ge0.01$.
For comparison, Figure \ref{fig_contour_RB} presents the cosmological constraints using the limits 
%0.02, 0.05, 0.07 and 0.1.
0.02, 0.05 and 0.07. 
A larger limit means we abandon more angular regions near the LOS.
%That will make the result less affected by the factors such as fiber collision.
We find that changing the cut has little effect on the cosmological constraints.
%Even for the case of $1 - \mu\ge0.1$,
%where 10\% of the angular region is dropped,
%the constraints are still fully consistent with the main results.
%This suggests that our main result is less affected by the fiber collision.

This test suggests that our result is not affected by the fiber collisions and redshift failures.
%In the observational data, these effects are taken into consideration by reweighting the nearest neighbor of the galaxy.
%Also, we add the fiber collision effect when constructing mock surveys.
If fiber collisions and redshift failures have any sizable effect,
since they mainly affect the angular region close to LOS,
one expects a systematic variation of the cosmological constraints when varying the limit on $1-\mu$.
%Such a variation was not detected in this test.
%so the fiber collision and redshift failure effects are certainly removed

\subsection{$Different\ s_{\rm min}$}

%\subsection{A2. Different $s_{\rm min}$}

Among the different options, %affecting our cosmological constraint, 
the one most likely to affect our results is $s_{\rm min}$.
%the smallest scale that are taken into account in the analysis.
%This is expectable. 
The 2pCF has relatively large values on smaller scales
%On small scales, the value of 2pCF is relatively large
(e.g. for the CMASS galaxies $\xi\approx10,5,1,0.25,0.05$ at $s=2,4,10,20,40 h^{-1}{\rm Mpc}$).
Varying $s_{\rm min}$ can dramatically change the value of $\xi_{\Delta s}(\mu)$,
and thus is likely to have large effect on the result.

A series of input-output tests are conducted to check whether the derived constraints depend on $s_{\rm min}$.
The linear regression of the $\delta\hat\xi_{\Delta s}$ (of the observational sample) 
measured in the WMAP5 cosmology ($\Omega_m=0.26$ $\Lambda$CDM) 
is adopted as $\delta\xi_{\Delta s, \rm sys}$. 
We then follow the procedures of Sec. \ref{sec:methodology} to derive cosmological constraint.
%In that case we expect the WMAP5 cosmology being the best-fit.

\begin{figure*}
   \centering{
   %\includegraphics[width=12cm]{Tpcf--contour-diffsmin-dashcontours.eps}}
   \includegraphics[width=5.7cm]{fig13_0.eps}
   \includegraphics[width=10cm]{fig13_1.eps}}
   %\includegraphics[width=5.9cm]{Tpcf--contour-nummock-36.eps}}
   \caption{ \label{fig_contour_diffsmin} 
   Left panel: The input-output test in case of using our default options.
   The derived cosmological constraints are fully consistent with the input WMAP5 cosmology (marked by green plus).
   Right panels: Likelihood contours (68\%, 95.4\%) in the $\Omega_m$-$w$ plane for using $s_{\rm min}=2,4,6,8\ h^{-1} {\rm Mpc}$.
   Gray filled contours are cosmological constraints derived using our AP analysis.
%    From the input-output test we find $s_{\rm min}$
   %For $s_{\rm min}=2,4,8\ h^{-1}{\rm Mpc}$, some correction of the likelihood map was made based on the result of their input-output tests.
   %After the correction they are close to the result using the default option $s_{\rm min}=6h^{-1}\rm Mpc$.
   For $s_{\rm min}=2,4h^{-1}{\rm Mpc}$, the contours are shifted to the upper-left corner, 
   but the deviation from the $s_{\rm min}=6h^{-1}{\rm Mpc}$ is $\lesssim1\sigma$.
   The black solid contour lines show the constraint when combined with CMB+BAO+JLA+$H_0$.
   %The dashed contour lines show the combined constraints in case of no correction made for $s_{\rm min}=2,4,8\ h^{-1}{\rm Mpc}$. 
   The combined result is rather insensitive to choices of $s_{\rm min}$.}
\end{figure*}

When adopting $s_{\rm min}=6\ h^{-1}{\rm Mpc}$, the best-fit cosmology is exactly what we expect: the WMAP5 cosmology, 
i.e. the input cosmology is successfully recovered (left panel of Figure \ref{fig_contour_diffsmin}).
So $s_{\rm min}=6\ h^{-1}{\rm Mpc}$ is adopted as the default option in our analysis.
%When adopting different a $s_{\rm min}$ of $2,4,8\ h^{-1}{\rm Mpc}$, 
Other values of $s_{\rm min}$ do not recover the input cosmology as well as $s_{\rm min}=6h^{-1}{\rm Mpc}$.
%the derived best-fit cosmology can deviate with the input cosmology at $1-2\sigma$.
%This means that there exists a systematics bias in the cosmological constraints derived using these $s_{\rm min}$.
%Therefore, when using $s_{\rm min}=$2,4,8 $h^{-1}{\rm Mpc}$, 
%Similar phenomenon happens when we adopt several different cosmologies ranging from $\Omega_m=0.2-0.4$, 
%\footnote{The reason that why these $s_{\rm min}$ some cosmologies achieve a larger likelihood value than the input cosmology is not very clear. 
%It could be just due to statistical fluctuation, or some inaccuracy in our simple likelihood estimation.
%We believe that the issue can be resolved in case of using the redshift evolution of the 2D likelihood map.
%e.g. the covariance .
%In our likelihood analysis the covariance matrix is estimated in the WMAP5 cosmology and applied to the whole parameter space.
%That is not very precise since the covariance matrix certainly depends on the values of $(\Omega_m,w)$.
%Possibly for some sets of parameters the covariance is relatively smaller, 
%so there the likelihood is {\it overestimated} if still adopting the covariance of WMAP5 cosmology,
%making them appears more preferred in the sense of our likelihood analysis.
 %for $s_{\rm min}=2,4,8\ h^{-1}{\rm Mpc}$.

%So it is not plausible to use these $s_{\rm min}$ values in the analysis,
%if the underlying systematics not properly corrected.

The cosmological constraints obtained using $s_{\rm min}=2,4,6,8\ h^{-1} {\rm Mpc}$ 
are presented in the right panel of Figure \ref{fig_contour_diffsmin}.
In the case of $s_{\rm min}\neq6h^{-1} {\rm Mpc}$, we apply a simple correction to the derived likelihood map, 
based on the discrepancy between the best-fit cosmology and the input cosmology found in the input-output test.

%Here the gray filled contours are constraints from our AP analysis.
These contours are consistent with each other within 1$\sigma$.
The $s_{\rm min}=8\ h^{-1}{\rm Mpc}$ result is very close to the main result.
The $s_{\rm min}=2$ or $4\ h^{-1}{\rm Mpc}$ contours show a systematical shift to the upper-left corner,
but the deviation is $\lesssim1\sigma$.
%we find the systematics mainly shifts the position contour along the 
%upper-left to lower-right diagonal.
The difference choices of $s_{\rm min}$ produce little effect on 
the joint constraint when combined with other cosmological probes (CMB+BAO+JLA+$H_0$). 
%To check that, we plot the joint constraints when our method combined with .
The difference from the main results is $\lesssim0.3\sigma$.
%Actually, even without applying the correction, 
%the combined constraints of $s_{\rm min}=2,4,8\ h^{-1} {\rm Mpc}$ are still very close to the $s_{\rm min}=6h^{-1}{\rm Mpc}$ result,
%with a difference $\lesssim0.6\sigma$ (dashed contour lines).

%In our main analysis we adopt $s_{\rm min}=6 h^{-1}{\rm Mpc}$, which is found to have almost no systematic deviation in the input-output tests.
%The dependence on $s_{\rm min}$ is understandable since the small scale $\xi$ is the dominate contributor in the integration.
%This issue could be resolved if using the 2D $\xi$ to conduce the analysis.

\subsection{$Summary$}

%We conduct a series of tests to check whether the derived cosmological constraints are sensitive to the options adopted in the likelihood analysis.
%For the default options used to derive our main result, 
%we adopt $s_{\rm min}=6h^{-1}{\rm Mpc}$, $s_{\rm max}=40h^{-1}{\rm Mpc}$, $1 - \mu \ge 0.01$,
%the 72 sets of HR3 PSB mocks for covariance estimation,
%and J08 merger timescale model (used in the construction of HR4 mock galaxies).

We conduct a series of tests and find that the derived cosmological constraints are insensitive to the options adopted in the analysis.
Cosmological constraints are derived using different options of $s_{\rm min}$, $s_{\rm max}$, limits on $1-\mu$, number of mocks for covariance estimation,
and satellite galaxy merger time scale.
We do not detect a significant change of our results.

%We modify the above options, 
%derive the corresponding cosmological constraints, 
%and check how much it deviates from the result using default options
%In all tests conducted, we do not detect a change in cosmological constraint which is statistically significant.
%In most cases, the shift of the contour is $\lesssim0.2\sigma$.
%Also, we find the shift only happens along the upper-left to lower-right diagonal of the $\Omega_m$-$w$ plane,
%making the joint constraint (the result when combined with the other cosmological probes) rather stable.

%Among these options, $s_{\rm min}$ is the only one found to have a relative large effect on the result.
%We performed a series of input-output tests, 
%and found using $s_{\rm min}=6h^{-1}{\rm Mpc}$ can lead to unbiased cosmological constraint.
%In case of using $s_{\rm min}=2,4,8\ h^{-1}{\rm Mpc}$, 
%a correction should be made to account for the bias in the derived likelihood map.
%In our main analysis, we adopt $s_{\rm min}=6h^{-1}{\rm Mpc}$, and no such correction is needed.

Yet there are still unchecked options. 
One example is the redshift binning scheme.
In this analysis, the galaxies are split into six redshift bins of
$0.150<z_1<0.274<z_2<0.351<z_3<0.430<z_4<0.511<z_5<0.572<z_6<0.693$.
%and investigate the redshift evolution of the 2pCFs measured in these redshift bins.
We have not checked whether the results depend on choices such as the redshift limits and the number of redshift bins,
because each binning scheme requires to repeat the whole analysis that involves the calculation of the correlation function 
at each point of the parameter space.
This issue is worthy investigation in future studies, 
to design a optimized scheme having the maximal ability to constrain cosmological parameters.
%We did not check whether our result different redshift limits

In summary, the tests show that, the cosmological constraints reported in this paper are quite robust.

%In all, %the options adopted in our main analysis are all based on cautious considerations and careful tests.
%After a series of robustness tests, we find our result relatively insensitive to their values.
%Furthermore, through the input-output test we find the default options adopted in the main analysis is able to derive unbiased cosmological constraint.
%We conclude that, the cosmological constraint reported in this paper is fairly robust.

\

\

\

\begin{thebibliography}{}

\bibitem[Ade et al. (2015)]{Planck2015}
Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. arXiv:1502.01589

\bibitem[Alam et al.(2016)]{Alam2016}
Alam, S., Ata, M., \& Bailey, S., et al. 2016,
submitted to MNRAS (arXiv:1607.03155)

\bibitem[{{Alam} {et~al}\mbox{.}(2015{\natexlab{a}}){Alam}, {Albareti},
  {Allende Prieto}, {Anders}, {Anderson}, {Anderton}, {Andrews}, {Armengaud},
  {Aubourg}, {Bailey}, \& et~al.}]{dr12}
{Alam} S., Albareti, F.D.,\& Allende Prieto, C., {et~al.}, 2015,  ApJS, 219, 12

\bibitem[Alcock \& Paczynski(1979)]{AP1979}
Alcock, C., \& Paczynski, B. 1979, Nature, 281, 358

%\bibitem[Anderson et al.(2012)]{2012MNRAS.427.3435A} 
%Anderson, L., Aubourg, E., Bailey, S., et al.\ 2012, MNRAS, 427, 3435

\bibitem[Anderson et al.(2013)]{Anderson2013}
Anderson, L., Aubourg, \'E., \& Bailey, S. et al. 2014, MNRAS, 441, 24

%\bibitem[Bassett et al.(2002)]{Bassett2002}
%Bassett, B.A., Kunz, M., Silk, J., \& Ungarelli, C. 2002, MNRAS, 336, 1217

\bibitem[Ballinger, Peacock \& Heavens 1996]{Ballinger1996}
Ballinger, W.E., Peacock, J.A., \& Heavens, A.F. 1996, MNRAS, 282, 877

\bibitem[Betoule et al.(2014)]{JLA}
Betoule, M., Kessler, R., \& Guy, J., et al. 2014, A\&A, 568, 32

\bibitem[Beutler et al.(2011)]{6dFGS}
Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017

\bibitem[Beutler et al.(2013)]{Beutler2013}
Beutler, F., Saito, S., \& Seo, H.-J., et al. 2013, MNRAS, 443, 1065

\bibitem[Beutler et al.(2016)]{Beutler2016}
Beutler, F., Seo, H.-J., \& Saito, S., et al. 2016,
arXiv:1607.03150

\bibitem[Blake et al.(2011)]{Blake2011}
Blake, C., Glazebrook, K., \& Davis, T. M., 2011, MNRAS, 418, 1725

\bibitem[Blake et al.(2013)]{WiggleZtopoloy}
Blake, C., James, J.B., \& Poole, G.B. 2013, MNRAS, 437, 2488

\bibitem[Bolton et al.(2012)]{Bolton2012}
Bolton, A.S., Schlegel, \& D.J., Aubourg E., et al. 2012, AJ, 144, 144

\bibitem[Boylan-Kolchin et al.(2008)]{B08}
Boylan-Kolchin, M., Ma, C.-P., \& Quataert, E. 2008, MNRAS, 383, 93

%\bibitem[Bueno Belloso et al. (2012)]{BB2012}
%Bueno Belloso, A., Pettinari, G.W., Meures, N., \& Percival, W.J. 2012, Phys. Rev. D, 86, 023530

%\bibitem[Chevallier \& Polarski(2001)]{CP2001}
%Chevallier, M., Polarski, D. 2001, Int. J. Mod. Phys. D, 10, 213

%\bibitem[Choi et al.(2010)]{choi 2010}
%Choi, Y.-Y., Park, C., Kim, J., Gott, J.R., 
%Weinberg, D.H., Vogeley, M.S., \& Kim, S.S. 2010, ApJS, 190, 181

\bibitem[Christensen et al.(2001)]{Bayesian}
Christensen, N., Meyer, R., Knox, L., \& Luey, B. 2001, Class. Quant. Grav., 18, 2677

%\bibitem[Chuang et al.(2013)]{Chuang2013}
%Chuang, C.-H., Prada, F., Beutler, F., et al. 2013, arXiv:1312.4889

\bibitem[Chuang \& Wang(2012)]{ChuangWang2012}
Chuang, C.-H., \& Wang, Y. 2012, MNRAS, 426, 226

%\bibitem[Corasaniti \& Copeland(2003)]{Corasaniti2003}
%Corasaniti, P.S., Copeland, E.J. 2003, Phys. Rev. D, 67, 063521

%eBOSS: 
%http://arxiv.org/abs/1508.04473
\bibitem[Dawson et al.(2015)]{eBOSS}
Dawson, K.S., Kneib, J.P., \& Percival, W.J., et al. 2015, accepted AJ

\bibitem[Dawson et al.(2012)]{Dawson et al. 2012}
Dawson, K.S., Schlegel, D.J., \& Ahn, C.P., et al. 2012, AJ, 145, 10

\bibitem[Efstathiou (2014)]{E14H0}
Efstathiou, G. 2014, MNRAS, 440, 1138

\bibitem[Eisenstein et al.(2011)]{Eisenstein et al. 2011}
Eisenstein, D.J.,  Weinberg, D.H., \& Agolet, E., et al. 2011, AJ, 142, 72

\bibitem[Feldman, Kaiser \& Peacock (1994)]{1994ApJ...426...23F} 
Feldman, H.A., Kaiser, N., \& Peacock, J.A.\ 1994, ApJ, 426, 23

\bibitem[Fukugita et al. (1996)]{Fukugita1996}
Fukugita, M., Ichikawa, T., \& Gunn, J.E., et al. 1996, AJ, 111, 1748
%Publication:	
%Astronomical Journal v.111, p.1748

%\bibitem[Gingold \& Monaghan(1977)]{GM1977}
%Gingold, R.A., \& Monaghan, J.J. 1977, MNRAS, 181, 375

%\bibitem[Gott et al.(2009)]{gott 2009}
%Gott, J.R., Choi, Y.-Y., Park, C., \& Kim, J. 2009, ApJ, 695, L45

%\bibitem[Gott et al.(2008)]{gott 2008}
%Gott, J.R., Hambrick, D.C., Vogeley, M.S., Kim, J., Park, C., Choi, Y.-Y.,
%Cen, R., Ostriker, J.P., \& Nagamine, K. 2008, ApJ, 675, 16

\bibitem[Gunn et al. (1998)]{Gunn1998}	
Gunn, J.E., Carr, M., \& Rockosi, C. et al. 1998, AJ, 116, 3040

\bibitem[Gunn et al.(2006)]{Gunn et al. 2006}
Gunn, J.E., Siegmund, W.A., \& Mannery, E.J., et al. 2006, AJ, 131, 2332

\bibitem[Guzzo et al.(2008)]{Guzzo2008}
Guzzo, L., Pierleoni, M., \& Meneux, B., et al. 2008, Nature, 451, 541

\bibitem[Hartlap et al.(2006)]{Hartlap}
Hartlap J., Simon P. \& Schneider P. [astro-ph/0608064].

\bibitem[Hong et al.(2016)]{hong2016}
Hong, S.E., Park, C.,\&  Kim, J. 2016, ApJ, 823, 103

\bibitem[Jackson (1972)]{FOG}
Jackson, J., 1972, MNRAS, 156, 1

\bibitem[Jennings et al.(2011)]{Jennings2011}
Jennings, E., Baugh, C.M., \& Pascoli, S. 2011, MNRAS, 420, 1079

%\bibitem[Jeong et al.(2014)]{Jeong2014}
%Jeong, D., Dai, L., Kamionkowski, M., \& Szalay, A.S. 2014, arXiv:1408.4648

\bibitem[Jiang et al.(2008)]{jiang2008}
Jiang, C.Y., Jing, Y. P., \& Faltenbacher, A., et al. 2008, ApJ, 675, 1095

\bibitem[Kaiser (1987)]{Kaiser1987}
Kaiser, N. 1987, MNRAS, 227, 1

\bibitem[Kim \& Park(2006)]{kim and park 2006}
Kim, J., \& Park, C. 2006, ApJ, 639, 600

\bibitem[Kim et al.(2009)]{2009ApJ...701.1547K} 
Kim, J., Park, C., Gott, J.R., III, \& Dubinski, J.\ 2009, ApJ, 701, 1547

\bibitem[Kim et al.(2015)]{hr4}
Kim, J., Park, C., L'Huillier, B., \& Hong, S. E. 2015, JKAS, 48, 213

\bibitem[Kim et al.(2011)]{horizonrun}
Kim, J., Park, C., Rossi, G., Lee, S.M., \& Gott, J.R. 2011, JKAS, 44, 217

\bibitem[Kitaura et al.(2015)]{MDPATCHY}
Kitaura, F.S., Rodrı\'{i}guez-Torres, S., Chuang, C.-H., et al. arXiv:1509.06400

\bibitem[Komatsu et al.(2011)]{komatsu 2011}
Komatsu, E., Smith, K. M., \& Dunkley, J., et al. 2011, ApJS, 192, 18

\bibitem[Lacey \& Cole(1993)]{LC93}
Lacey, C., \& Cole, S. 1993, MNRAS, 262, 627

\bibitem[Landy \& Szalay(1993)]{1993ApJ...412...64L} 
Landy, S.D., \& Szalay, A.S.\ 1993, ApJ, 412, 64

%EUCLID:
%http://arxiv.org/abs/1110.3193
\bibitem[Laureijs et al.(2011)]{EUCLID}
Laureijs, R., Amiaux, J., \& Arduini, S., et al. 2011, arXiv:1110.3193

\bibitem[Lavaux \& Wandelt(2012)]{LavausWandelt1995}
Lavaux, G., \& Wandelt, B.D. 2012, ApJ, 754, 109

%\bibitem[Levi et al.(2013)]{2013arXiv1308.0847L} 
%Levi, M., Bebek, C., Beers, T., et al.\ 2013, arXiv:1308.0847

\bibitem[Lewis \& Bridle (2002)]{LB2002}
Lewis, A., \& Bridle, S. 2002, Phys. Rev. D, 66, 103511

\bibitem[L'Huillier et al.(2014)]{2014NewA...30...79L} 
L'Huillier, B., Park, C., \& Kim, J.\ 2014, New Astronomy, 30, 79

\bibitem[Li et al.(2011)]{Li2011}
Li, M., Li, X.-D., Wang, S., \& Wang, Y. 2011, Commun. Theor. Phys., 56, 525

\bibitem[Li et al.(2014)]{Li2014}
Li, X.-D., Park, C., Forero-Romero, J., \& Kim, J. 2014, ApJ, 796, 137

\bibitem[Li et al.(2015)]{Li2015}
Li, X.-D., Park, C., Sabiu, C.G., \& Kim, J. 2015, MNRAS, 450, 807

%\bibitem[Linder(2003)]{Linder2003}
%Linder, E.V. 2003, Phys. Rev. Lett., 90, 091301

\bibitem[Linder et al.(2014)]{Linder2013}
Linder, E.V., Minji, O., Okumura, T., Sabiu, C.G., \& Song, Y.-S. 2014, Phys. Rev. D, 89, 063525

\bibitem[L{\'o}pez-Corredoira(2014)]{2014ApJ...781...96L} 
L{\'o}pez-Corredoira, M.\ 2014, ApJ, 781, 96

\bibitem[Marinoni \& Buzzi(2010)]{Marinoni2010}
Marinoni, C., \& Buzzi, A. 2010, Nature, 468, 539

\bibitem[Matsubara \& Suto(1996)]{Matsubara1996}
Matsubara T., \& Suto, Y. 1996, ApJ, 470, L1

\bibitem[McCavana et al.(2012)]{M12}
McCavana, T., Micic, M., Lewis, G. F., et al. 2012, MNRAS, 424, 361

\bibitem[Morandi \& Sun (2016)]{MS2016}
Morandi, A., \& Sun, M. arXiv:1601.03741

\bibitem[Outram et al.(2004)]{Outram2004}
Outram, P.J., Shanks, T., Boyle, B.J., Croom, S.M., Hoyle, F., Loaring, N.S., 
Miller, L., \& Smith, R.J. 2004, MNRAS, 348, 745

%\bibitem[Parejko et al.(2013)]{Parejko2013}
%Parejko, J. K., Sunayama, T., Padmanabhan, N., et al. 2013, MNRAS, 429, 98

\bibitem[Parejko et al.(2013)]{Parejko2013}
Parejko J.K., et al., 2013, MNRAS, 429, 98

\bibitem[Parihar et al. (2014)]{CMASSLSS2014}
Parihar, P., Vogeley, M.S., \& Gott, J.R., et al. 2014, ApJ, 796, 86

\bibitem[Park et al.(2005)]{park 2005}
Park, C., Kim, J., \& Gott, J.R. 2005, ApJ, 633, 1

\bibitem[Park \& Kim(2010)]{topology}
Park, C., \& Kim, Y.-R. 2010, ApJL, 715, L185

\bibitem[Park et al. (2012)]{Park2012}
Park, C., Choi, Y.-Y., Kim, J., Gott, J.R., Kim, S.S., \&
Kim, K.-S. 2012, ApJ, 759, 7

\bibitem[Park et al. (2015)]{Park2015}
Park, C., Song, H., Einasto, M., Lietzen, H., \&
Heinamaki, P. 2015, JKAS, 48, 75

\bibitem[Peebles \& Ratra(2003)]{PR2003}
Peebles, P.J.E., \& Ratra, B. 2003, Reviews of Modern Physics, 75, 559

\bibitem[Percival et al.(2014)]{Percival2014}
Percival, W.J., Ross, A.J., \& S\'{a}nchez, A.G., et al. 2014, MNRAS, 439, 2531

\bibitem[Perlmutter et al.(1999)]{Perl1999}
Perlmutter, S., Aldering, G., \& Goldhaber, G., et al. 1999, ApJ, 517, 565

\bibitem[Press \& Shechter(1974)]{PS1974}
Press, W.H., \& Schechter, P.L. 1974, ApJ, 187, 425

\bibitem[Reid et al.(2012)]{Reid2012}
Reid, B., Samushia, L., \& White, M., et al. 2012, MNRAS, 426, 2719

\bibitem[Reid et al.(2016)]{Reidetal:2016}
Reid, B., Ho, S., \& Padmanabhan, N., et al.  2016, MNRAS, 455, 1553

\bibitem[Riess et al.(1998)]{Riess1998}
Riess, A.G., Filippenko, A.V., \& Challis, P., et al. 1998, AJ, 116, 1009

\bibitem[Riess et al.(2011)]{Riess2011}
Riess, A.G., Macri, L., \& Casertano, S., et al. 2011, ApJ, 730, 119
%A 3\% Solution: Determination of the Hubble Constant with the Hubble Space Telescope and Wide Field Camera

\bibitem[Ross et al.(2012)]{2012MNRAS.424..564R} 
Ross, A.J., Percival, W.J., \& S{\'a}nchez, A.G. et al.\ 2012, MNRAS, 424, 564

\bibitem[Ross et al.(2015)]{MGS}
Ross, A.J., Samushia, L., \& Howlett, C., et al. 2015, MNRAS, 449, 835

\bibitem[Ryden(1995)]{Ryden1995}
Ryden, B.S. 1995, ApJ, 452, 25

%\bibitem[Samushia et al.(2014)]{Samushia2014}
%Samushia, L., Reid, B. A., White, M., et al. 2014, MNRAS, 439, 3504

%\bibitem[Sanchez et al.(2013)]{Sanchez2013}
%Sanchez, A. G., Kazin, E. A., Beutler, F., et al. 2013, MNRAS, 433, 1202

%\bibitem[Sutter et al.(2014)]{Sutter2014}
%Sutter, P.M., Pisani, A., Wandelt, B.D., \& Weinberg, D.H. 2014, MNRAS, 443, 2983

\bibitem[Sanchez et al.(2016)]{Sanchez2016}
Sanchez, A. G., Scoccimarro, R., \& Crocce, M., et al.
arXiv:1607.03147

\bibitem[Schlafly et al.(2010)]{Schlafly2010}
Schlafly E.F., Finkbeiner D.P., Schlegel D.J., et al. 2010, ApJ, 725, 1175

\bibitem[Schlafly \& Finkbeiner(2011)]{SF2011}
Schlafly E.F., \& Finkbeiner D.P. 2011, ApJ, 737, 103

%DESI:
%http://arxiv.org/abs/1106.1706
\bibitem[Schlegel et al.(2011)]{DESI}
Schlegel, D., Abdalla, F., \& Abraham, T., et al. 2011, arXiv:1106.1706

\bibitem[Smee et al.(2013)]{Smee2013}
Smee, S.A., Gunn, J.E., \& Uomoto, A., et al. 2013, AJ, 146, 32

\bibitem[Song et al.(2014)]{2014arXiv1407.2257S} 
Song, Y.S., Sabiu, C.G., 
Okumura, T., Oh, M., \& Linder, E.V.\ 2014, JCAP, 12, 005

\bibitem[Speare et al. (2015)]{Speare2015}
Speare, R., Gott, J.R., Kim, J., \& Park, C.
2015, ApJ, 799, 176

%\bibitem[Tojeiro \& Percival(2011)]{Tojeiro2011}
%Tojeiro R., \& Percivial W.J. 2011, MNRAS, 417, 1114

%\bibitem[Tojeiro et al.(2012)]{Tojeiro2012}
%Tojeiro, R., Percival, W. J., Wake, D. A., et al. 2012, MNRAS, 424, 136

\bibitem[Viana \& Liddle(1996)]{VL1996}
Viana, P.T.P., \& Liddle, A.R. 1996, MNRAS, 281, 323

\bibitem[Villalobos et al.(2013)]{V13}
Villalobos, \'{A}., ́De Lucia, G., Weinmann, S.M., Borgani, S., \& Murante, G. 2013, MNRAS, 433, L49

\bibitem[Weinberg (1989)]{SW1989}
Weinberg, S. 1989, Reviews of Modern Physics, 61, 1

\bibitem[White (2011)]{White2011}
White M., et al. 2011, ApJ, 728, 126

\bibitem[York et al.(2000)]{York et al. 2000}
York, D.G., Adelman, J., \& Anderson, J.E., et al. 2000, AJ, 120, 1579

\bibitem[Zehavi et al.(2011)]{zehavi2011}
Zehavi, I., Zheng, Z., \& Weinberg, D.H., et al. 2011, ApJ, 736, 59

\end{thebibliography}

\end{document}

### 2016-08-18 draft/draft0.tex
updates

--- 2016-08-18 draft/BOSSAP.tex
@@
 
-\shorttitle{Reshift Dependent Alcock-Paczynski effect from SDSS-III DR12}
+\shorttitle{Reshift Dependent Volume effect}
 \shortauthors{X.-D. Li, C. Park, C.G. Sabiu, H. Park, D.H. Weinberg, J. Kim, S.E. Hong}
@@
 
-\title{Cosmological constraints from the redshift dependence of the Alcock-Paczynski effect: application to the SDSS-III BOSS DR12 galaxies}
+\title{Cosmological constraints from the redshift dependence of the distance rescaling in wrong cosmologies: 
+the shape of galaxy 2-point correlation function}
 
@@
 
-\author{Xiao-Dong Li, Changbom Park,}
+\author{Xiao-Dong Li, }
+\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
+\author{Cheng Cheng, }
+\affil{blahblahblah}
+\author{Changbom Park,}
 \affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
@@
 \affil{Korea Astronomy and Space Science Institute, Daejeon 305-348, Korea}
-\author{David H. Weinberg,}
-\affil{Department of Astronomy and CCAPP, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA}
-\author{Donald P. Schneider,}
-\affil{Department of Astronomy and Astrophysics, The Pennsylvania State University, 
-University Park, PA 16802 }
-\affil{Institute for Gravitation and the Cosmos, The Pennsylvania State University, 
-University Park, PA 16802 }
+%\author{David H. Weinberg,}
+%\affil{Department of Astronomy and CCAPP, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA}
+%\author{Donald P. Schneider,}
+%\affil{Department of Astronomy and Astrophysics, The Pennsylvania State University, 
+%University Park, PA 16802 }
+%\affil{Institute for Gravitation and the Cosmos, The Pennsylvania State University, 
+%University Park, PA 16802 }
 \author{Juhan Kim\altaffilmark{1},}
@@
 \begin{abstract}
-We apply the methodology developed in \cite{Li2014,Li2015} to BOSS DR12 galaxies and 
-derive cosmological constraints from the redshift dependence of the Alcock-Paczynski (AP) effect.
-The apparent anisotropy in the distribution of observed galaxies arise from two main sources,
-the redshift-space distortion (RSD) effect due to the galaxy peculiar velocities,
-and the geometric distortion when incorrect cosmological models are assumed for 
-%the coordinate transformation from redshift space to comoving space, 
-transforming redshift to comoving distance,
-known as the AP effect.
-%We focus on the redshift dependence of the anisotropic clustering of galaxies to constrain cosmological parameters.
-Anisotropies produced by the RSD effect are, although large,
-maintaining a nearly uniform magnitude over a large range of redshift,
-while the degree of anisotropies from the AP effect varies with redshift by much larger magnitude. 
-%We found that the redshift dependence of the anisotropy introduced by RSD is much less significant compared with the anisotropy caused by AP.
-%We focus on the redshift dependence of the anisotropic clustering of galaxies to constrain cosmological parameters 
-%which is less sensitive to RSD contamination.
-We split the DR12 galaxies into six redshift bins, measure the 2-point correlation function in each bin,
-and assess the redshift evolution of anisotropies.
-%Assuming a flat Universe consisting of a pressure-less dark matter component 
-%with current ratio $\Omega_m$, and a dark energy component with constant equation of state $w$,
-We obtain constraints of $\Omega_m=0.314 \pm 0.038,\ \ w = -1.09 \pm 0.14$,
-which are tighter than the current constraints from other cosmological probes
-such as type Ia supernovae, cosmic microwave background, and baryon acoustic oscillation (BAO).
-Combining these cosmological probes with our method yield tight constraints of 
-$\Omega_m = 0.304 \pm 0.007,\ w=-1.04 \pm 0.03$.
-Our method is complementary to the other large scale structure probes like BAO and topology.
-%We discuss the caveats and possibilities for improving upon our methodology.
-We expect this technique will play an important role in deriving cosmological constraints from
-large scale structure surveys.
+We use the shape of galaxy 2-point correlation function to measure the redshift dependence cosmology volume effect.
+...
 \end{abstract}
@@
 
-The current standard model of cosmology has been highly successful at reproducing the Universe on large scales. %large scale observations of the Universe. 
-From the temperature fluctuations in the cosmic microwave background (CMB), 
-to the late time clustering of galaxies, 
-the vacuum energy dominated cold dark matter model ($\Lambda$CDM) fits the data surprisingly well \citep{Planck2015,Anderson2013}. 
-This result is all the more impressive considering both the underlying assumptions, 
-such as homogeneity, isotropy, scale invariance of the primordial fluctuations, 
-and the minimal set of cosmological parameters that are required.
-
-Nonetheless, these models produce the unsatisfactory prospect that we must include within our ontology both a vacuum energy 
-that is much smaller than that predicted from  quantum mechanics, 
-or alternatively a new scalar field (dark energy) that has negative pressure
-\citep{SW1989,Riess1998,Perl1999,PR2003,Li2011}, 
-and a new matter component, which is not contained within the standard $SU(3)\times SU(2) \times U(1)$ formulation of particle physics.
-
-With an over-abundance of models for both dark energy-like accelerated expansion and dark matter, 
-it is crucial to obtain precise and model-independent measurements of the cosmic evolution, usually referred to as background observables. 
-Two such observables are the angular diameter distance, $D_A$, and the Hubble factor, $H$.  
-If these quantities can be measured at various redshifts and to a high degree of accuracy then our ability to differentiate between various competing models will be greatly increased.
-
-In the last few years there has been increasing interest in using the Alcock-Paczynski (AP) effect \citep{AP1979} 
-in the large-scale clustering of galaxies to obtain constraints on $D_A$ and $H$ \citep{Guzzo2008,topology}. 
-Assuming an incorrect cosmological model for the coordinate transformation from redshift space to comoving space produces residual geometric distortions. 
-These distortions are induced by the fact that measured distances along and perpendicular to the line of sight are fundamentally different. 
-Measuring the ratio of galaxy clustering in the radial and transverse directions provides a probe of this AP effect.
-
-There have been several methods proposed for applying the AP test to the large scale structure (LSS).
-The most widely adopted one uses anisotropic clustering \citep{Ballinger1996,Matsubara1996},
-which has been used for the 2 degree Field Quasar Survey \citep{Outram2004},
-the WiggleZ dark energy survey \citep{Blake2011}, 
-the Sloan Digital Sky Survey-I/II (SDSS-I/II) Luminous Red Galaxy (LRG) survey \citep{Eisenstein et al. 2011,ChuangWang2012},
-and the SDSS-III Baryon Oscillation Spectroscopic Survey (BOSS) 
-%\citep{Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, 2014ApJ...781...96L}.
-\citep{Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, 2014ApJ...781...96L,
-Alam2016, Beutler2016, Sanchez2016}
-The main caveat of this method is that,
-because the radial distances of galaxies are inferred from redshifts,
-AP tests are inevitably limited by redshift-space distortions (RSD) \citep{Ballinger1996},
-which leads to apparent anisotropy even if the adopted cosmology is correct.
-The RSDs must be accurately modeled for the 2-point statistics of galaxy clustering.
-
-\cite{Marinoni2010} proposed using the symmetry properties of galaxy pairs.
-Unfortunately this method is also seriously limited by RSD.
-The peculiar velocity distorts the redshift and changes the apparent tilt angles of galaxy pairs.
-The effect depends on both redshift and underlying cosmology, and is rather difficult to model accurately \citep{Jennings2011}.
-\cite{Ryden1995} and \cite{LavausWandelt1995} proposed another method using the apparent stretching of voids.
-This approach has the advantage that the void regions are easier to model compared with dense regions,
-but has limitations in that it utilizes only low density regions of the LSS
-and requires large samples.
-
-\cite{Li2014} proposed another method utilizing the redshift dependence of AP effect to overcome the RSD problem.
-The anisotropies produced by RSD effect are, although very large,
-close to uniform in magnitude over a large range of redshift.
-Conversely, if cosmological parameters are incorrectly chosen, the LSS
-appear anisotropic and the degree of anisotropy varies with redshift. 
-%We found that the redshift dependence of the anisotropy introduced by RSD is much less significant compared with the anisotropy caused by AP.
-%Thus we can focus on the redshift dependence of the galaxy density gradient field, 
-%which is less affected by RSD, but still sensitive to cosmological parameters.
-We used the {\it galaxy density gradient field} 
-to characterize the anisotropies in LSS and tested the idea on Horizon Run 3 (HR3) N-body simulations \citep{horizonrun},
-demonstrating that the method leads to unbiased estimation of the density parameter $\Omega_m$ and the dark energy equation of state (EoS) $w$.
-
-The same topic was revisited in \cite{Li2015}, but using the {\it galaxy two-point correlation function} (2pCF) as the statistical tool.
-The 2pCF as a function of angle, $\xi(\mu)$, is measured at different redshifts.
-Similar to \cite{Li2014}, we found that the RSD effect, although significantly distorting $\xi(\mu)$, 
-exhibits much less redshift evolution compared to the amount of change in $\xi(\mu)$ due to incorrectly adopted cosmologies.
-When incorrect cosmological parameters are adopted, 
-the shape of $\xi(\mu)$ appears anisotropic due to the AP effect, 
-and the amplitude is shifted by the change in comoving volume;
-both effects have significant redshift dependence.
-%By focusing on the redshift dependence of $\xi(\mu)$, we can correctly recover the cosmological parameters despite the contamination of RSD.
-We test the method using the 2pCF on mock surveys drawn from HR3
-%we measuring the redshift evolution of 2pCF also leads to unbiased estimation of cosmological parameters 
-and find the constraints obtained are tighter than those from the methodology of \cite{Li2014}.
-
-The change of the comoving volume size is another consequence of an incorrectly adopted cosmology, 
-and has motivated investigations constraining cosmological parameters from number counting of 
-galaxy clusters \citep{PS1974,VL1996}. 
-An obstacle in using the comoving volume for cosmological tests is the evolution of the number of target objects.
-The essential need for reducing the evolution effects in applying the test led \cite{topology} to propose a new method
-using the topology of LSS. 
-Since the topology is a measure of intrinsic connectivity of structures,
-it is expected to be insensitive to non-linear gravitational evolution, type of density tracers,
-and RSD on large scales.
-This method has been applied to the WiggleZ Dark Energy Survey data by \cite{WiggleZtopoloy},
-and to simulated BOSS samples \citep{Speare2015}.
-
-In this paper we apply our methodology to SDSS-III BOSS Data Release 12 (DR12) galaxies \citep{Reidetal:2016}.
-%We split the DR12 samples of CMASS and LOWZ into six redshift bins (three in each) and measure the redshift evolution of 
-%anisotropy therein to determine the correct cosmological parameters leading to least redshift evolution of anisotropy.
-We take the 2pCF as statistical tool characterizing the anisotropic clustering and follow the procedure of \cite{Li2015} to conduct the analysis.
-We assume a flat Universe and constrain parameters of $\Omega_m$ and $w$.
-2pCF is a mature statistic in cosmology and its optimal estimation and statistical properties are well understood.
-Compared with the density gradient field statistic, it leads to tighter constraints and is less affected by survey geometry.
+Dark energy ... Large scale structure...
+
+2pCF is a good statistic... blahblah
+In 2d xi(s,mu) ...
+In *** we used the redshift dependence of 2pCF to probe the volume and AP effect...
+The method is applied to BOSS data in *** and obtain tight constraint...
+
+In *** we further propose to use the shape of xi(s) to probe the volume effect...
+Stretch or compression shifts the clustering properties in some particular scale to larger or smaller scales...
+The shape of measured xi(s) is thus stretched or compressed.
 
 The outline of this paper is as follows.
-In Sec. 2 we describe the observational data used in this paper.
-In Sec. 3 we discuss the N-body simulations and mock galaxy catalogues that are used in this analysis.
-In Sec. 4 we briefly review the nature and consequences of the AP effect when performing coordinate transforms in a cosmological context. 
-In Sec. 5 and Sec. 6, we describe our analysis method and present the cosmological constraints obtained from BOSS DR12 galaxies. 
-We conclude in Sec. 7.
 
@@
 
-\section{The Observational Data}\label{sec:data}
-
-The Sloan Digital Sky Survey (SDSS; York et al. 2000) %DANGEROUS
-imaged approximately 7\,606 $\rm deg^2$
-of the Northern Galactic Hemisphere and 
-3\,172 $\rm deg^2$ of the Southern Galactic Hemisphere in the {\it ugriz} bands \citep{Fukugita1996,Gunn1998}.
-The survey was performed using the 
-2.5m Sloan telescope \citep{Gunn et al. 2006}
-at the Apache Point Observatory in New Mexico.
-%BOSS, as part of the SDSS-III survey \citep{Eisenstein et al. 2011},
-%has obtained additional imaging,
-%increasing the region of the south to 3\,172 $\rm deg^2$.
-BOSS \citep{Dawson et al. 2012,Smee2013}, as a part of the SDSS-III survey \citep{Eisenstein et al. 2011},
-has obtained spectra and redshifts 
-of 1.37 million galaxies selected from the SDSS imaging,
-covering a region of 9\,376 $\rm deg^2$.
-The galaxy redshifts were measured by an automated pipeline \citep{Bolton2012}.
+This paper is organized as follows...
+The outline of this paper proceeds as follows. 
+In \S 2 we briefly review the nature and consequences of the AP effect and volume changes when performing coordinate transforms in a cosmological context. 
+In \S 3 we describe the N-body simulations and mock galaxy catalogues that are used to test our methodology.
+In \S 4, we describe our new analysis method for quantifying the redshift dependence of volume effect.
+We conclude in \S 5.
+
+\section{AP and Volume Effect in Wrongly Assumed Cosmologies}
+\label{sec:Voleffect}
 
@@
    \centering{
-   %\includegraphics[width=7cm]{Tpcf--contour.eps}
-   %\includegraphics[width=16cm]{Tpcf--contour-others.eps}
-   %\includegraphics[width=7.5cm,natwidth=8.3,natheight=9]{maskdr12v1lowres.png}
-   %\includegraphics[width=7.5cm,natwidth=8.3,natheight=9]{maskdr12v1lowzlowres.png}
-   %\includegraphics[width=8.5cm,natwidth=8.3,natheight=5]{Tpcf--gal_LN.jpg}
-   %\includegraphics[width=8.5cm,natwidth=8.3,natheight=5]{Tpcf--gal_LS.jpg}
-   %\includegraphics[width=8.5cm,natwidth=8.3,natheight=5]{Tpcf--gal_CN.jpg}
-   %\includegraphics[width=8.5cm,natwidth=8.3,natheight=5]{Tpcf--gal_CS.jpg}
-   \includegraphics[width=8.5cm]{fig1_0.eps}
-   \includegraphics[width=8.5cm]{fig1_1.eps}
-   \includegraphics[width=8.5cm]{fig1_2.eps}
-   \includegraphics[width=8.5cm]{fig1_3.eps}
-   }
-   \caption{\label{fig_radec}
-   The sky coverage of the LOWZ and CMASS samples in the north and south Galactic caps. 
-   The individual points mark position of galaxies in the survey coordinate frame.
-   The solid lines mark the right ascension and declination.
-   The mean completeness is 97.2\% for the LOWZ sample, shown in the upper panels,
-   and 98.8\% for the CMASS sample in the lower panels.
-   The effective sky coverage is 8,337 $\rm deg^2$ for LOWZ and 9,376 $\rm deg^2$ for CMASS.
-   %Each patch corresponds to a plate,
-   %with the color determined by the completeness of that plate.
-   See \cite{Reidetal:2016} for more details.
+%   \includegraphics[height=6cm]{Tpcf--xy.eps}
+%   \includegraphics[height=6cm]{Tpcf--quan.eps}
+   %\includegraphics[height=7cm]{FVol.eps}
+   %\includegraphics[height=8cm]{xy.eps}
+   %\includegraphics[height=8cm]{smu.eps}
+   }
+   \caption{\label{fig_xy}
+   %Apparent distortion of objects in four wrongly assumed cosmologies, assuming a true cosmology of .
+   The redshift dependence of AP and volume effect in two wrongly assumed cosmologies $\Omega_m=0.41$, $w=-1.3$ and $\Omega_m=0.11$, $w=-0.7$,
+   assuming a true cosmology of $\Omega_m=0.26$, $w=-1$.
+   Upper panel shows the apparent distortion of four perfect squares,
+   measured by an observer located at the origin.
+   The apparently distorted shapes are plotted in red solid lines.
+   The underlying true shapes are plotted in blue dashed lines.
+   Lower panel shows the evolution of Equations (\ref{eq:stretch}) and (\ref{eq:volume}).
+   In our mock surveys we split the samples at $z=0.3$, 0.6, 0.9 and 1.2, as marked by the vertical lines.
+   %measured by an observer located at the origin.
+   %For reference, blue dashed squares show their shapes and positions in the true cosmology.
    }
@@
 
-The spectroscopic sample of BOSS has two primary catalogues.
-%the LOWZ at $z\leq0.4$, and CMASS covering $0.4\leq z \leq 0.7$. %of galaxies.
-The LOWZ sample is designed to extend the SDSS-I/II LRG sample to $z\approx 0.4$ and fainter luminosities,
-in order to increase the number density of the sample by a factor of 3.
-The CMASS sample covers a higher redshift ($0.4\lesssim z \lesssim 0.7$).
-It was targeted to be an approximately stellar mass limited sample of massive, luminous galaxies.
-The final data release (DR12) samples are described in \cite{Reidetal:2016},
-where the details of targeting algorithms and the catalogues are provided.
-%The full targeting algorithms used and the method for calculating the galaxy and random catalogues are presented in \citet{Reidetal:2016}, 
-%Full details of targeting algorithms and the catalogues are provided in \citep{}, 
-%and we do not replicate this here.
-
-%The galaxy survey used two primary target algorithms, 
-%selecting samples called LOWZ, with 361\,759 galaxies in the final data release DR12 \citep{dr12} between $0.15<z <0.43$ and CMASS, 
-%with 771\,567 galaxies in DR12 between $0.43< z < 0.70$. 
-%The full targeting algorithms used and the method for calculating the galaxy and random catalogues are presented in \citet{Reidetal:2016}, 
-%which also shows that the samples jointly cover a large cosmic volume $V_{\rm eff}=7.4\,{\rm Gpc}^3$.
-%with a number density of galaxies as a function of observed redshift, 
-%that ensures that the shot noise does not dominate at BAO (baryon acoustic oscillation) scales. 
-%The full targeting algorithms used and the method for calculating the galaxy and random catalogues are presented in \citet{Reidetal:2016}, 
-%Full details of the catalogues are provided in \citet{Reidetal:2016}, 
-%and we do not replicate this here.
-
-%BOSS is designed to obtain 
-%spectra and redshifts of $\sim$1.35 million galaxies 
-%(together with 160\,000 quasars and approximately 100\,000 ancillary targets)
-%selected from the SDSS imaging.
-%The SDSS-I/II data \citep{York et al. 2000}
-
-%CMASS and LOWZ\,
-
-%We use data from the Sloan Digital Sky Survey \citep[SDSS; ][]{2000AJ....120.1579Y}. 
-%SDSS has mapped over one quarter of the sky in five photometric bands down to a limiting magnitude of $r\sim 22.5$. 
-%The photometric data is reduced and from it are selected targets for followup spectroscopy. 
-%The spectroscopic survey, known as the Baryon Oscillation Spectroscopic Survey (BOSS), 
-%is charged with obtaining spectra for 1.35 million galaxies over a 10,000 square degree footprint.
-
-\begin{figure*}
-   \centering{
-   \includegraphics[width=19cm]{fig2.eps}
-   }
-   \caption{\label{fig_nbar}
-      The redshift density distribution of the BOSS DR12 galaxy samples, assuming a $\Lambda$CDM cosmology with $\Omega_m=0.31$.
-      The blue and green solid histograms show the distribution of LOWZ and CMASS galaxies respectively. 
-      The vertical dashed lines define the six redshift bins that are used to cut the samples.
-      Their redshift ranges are listed.
-      The number of LOWZ (CMASS) galaxies in the three low (high) redshift bins are presented in the brackets.
-      }
-\end{figure*}
-
-Figure \ref{fig_radec} presents the sky coverage of the BOSS DR12 samples used in this analysis. 
-%The light grey shaded region shows the expected total footprint of the BOSS survey. 
-%Colors indicate the spectroscopic completeness.
-The mean completeness is 97.2\% for the LOWZ sample, in the upper panels, and 98.8\% for the CMASS sample shown in the lower panels.
-   %Each patch of different color corresponds to a plate,
-   %with the color determined by the completeness of that plate..
-Figure \ref{fig_nbar} shows the galaxy number density of the two samples.
-In this analysis we use 361\,759 LOWZ galaxies at $0.15<z <0.43$ and 
-771\,567 CMASS galaxies at $0.43< z < 0.693$.
-%in total galaxies.
-We split the galaxies into six redshift bins: 
-three bins in LOWZ ($0.150<z_1<0.274<z_2<0.351<z_3<0.430$), 
-and three in CMASS ($0.430<z_4<0.511<z_5<0.572<z_6<0.693$), 
-as illustrated in Figure \ref{fig_nbar}.
-
-\begin{figure*}
-   \centering{
-   \includegraphics[width=19cm]{fig3.eps}
-   }
-   \caption{\label{fig_mock}
-      Creation of mock galaxy samples for BOSS.
-      Using an all-sky mock survey from the HR4 or HR3 simulations,
-       we are able to produce four sets of NGC samples or eight sets of SGC samples with non-overlapping sky coverage.
-      The individual points are the right ascension and declination of 1\% galaxies drawn from the CMASS samples.
-      }
-\end{figure*}
-
-Each spectroscopically observed galaxy is assigned several weights to account for observational effects. 
-The galaxy weights are constructed from three distinct effects.
-%redshift failure, $w_{fail}$, minimum variance, $w_{FKP}$, and angular variation, $w_{sys}$. 
-%These weights are described in more detail in \cite{2012MNRAS.427.3435A} and \cite{2012MNRAS.424..564R}. 
-Firstly, galaxies lacking a redshift due to fiber collisions 
-\footnote{Fiber collisions occur when two objects are close enough together such that two fibers cannot be placed.
-In BOSS, the collision radius is 62 $''$.}
-or inadequate spectral information are accounted for by reweighting
-the nearest galaxy by a weight $w_{\rm fail}=(1+n)$, 
-where $n$ is the number of close neighbors without a measured redshift. 
-Secondly, all galaxies are assigned `FKP' weights \citep{1994ApJ...426...23F}
-%as a function of redshift depending on the number density.
-as a function of number density,
-to optimize the clustering measurements in the face of shot-noise and cosmic variance.
-%according to,
-%\begin{equation}
-%w^i_{FKP}=\frac{1}{1+n_i(z)P_0},
-%\end{equation}
-%where $n_i(z)$ is the comoving space density at redshift $z$ and $P_0 \sim P(k=0.1~{\rm $h^{-1}$Mpc}) \sim 2\times 10^{4}h^{-3}{\rm Mpc^3}$, 
-%as in \cite{2012MNRAS.427.3435A}. 
-The third weight corrects for angular variations of survey completeness and the systematics 
-related to the angular variations in stellar density that make detection of
-galaxies difficult in over-crowded regions of the sky. %\citep{2012MNRAS.424..564R}. 
-The total weight for each galaxy is the product of these three weights, $w_{\rm total}=w_{\rm fail}w_{\rm FKP}w_{\rm sys}$.
-
-For the statistical analyses, 
-random catalogues having the same angular and redshift selection functions as the data 
-are provided along with the data \citep{Reidetal:2016}.
-%Each random point is assigned with a redshift of measured galaxy randomly drawed from galaxies.
-%and a weight given by the $w_{\rm tot}$ of the measured galaxy.
-The random points are also weighted but they only include the minimum variance `FKP' weight. 
-%50 times as many random points as we have galaxies
-
-\section{The Mock Galaxy Data}
-\label{sec:mocks}
-%We use HR3 and HR4...
-%We use HR4 J08 ...
-
-%Shape of $\\xi$ measured in HR4 very similar to data...
-%Shape of
-
-For LSS studies mock survey samples created from simulations are crucial
-for the correction of systematics and covariance estimation.
-The Horizon Run simulations are a suite of large volume N-body simulations that 
-have resolutions and volumes capable of accurately reproducing the observational statistics of the current major redshift surveys like 
-SDSS-III BOSS \citep{park 2005,2009ApJ...701.1547K,horizonrun}.
-The HR3 \citep{horizonrun} and HR4 \citep{hr4} simulations are used in our analysis.
-
-From the HR3 and HR4 simulations we have generated all-sky light cone mock galaxy catalogues.
-The all-sky spherical mocks are then incorporated with the same fiber collision effect, 
-angular masks, and radial selection function with the real observational data,
-creating mock surveys of BOSS DR12.
-
-We impose a minimum mass limit varying along with redshift to match the radial density of BOSS samples.
-The galaxies of the BOSS DR12 samples do not cleanly distribute above some particular mass boundary;
-they always have a fuzzy, blur boundary extending to relatively small values (as an example, see Figure 3 of 
-Parihar et al. 2014). %DANGEROUS
-%rather than shaprly lying above a certain mass cut, 
-Galaxies in the mock samples are systematically more massive than those from observations;
-We will discuss the effect of this discrepancy in Sec. \ref{sec:caveats}.
-
-\subsection{Horizon Run 4}
+%Considering we are Let us consider an object in the universe with certain size and shape.
+%Its observed redshift span $\Delta z$ and angular size $\Delta \theta$ are related with the comoving sizes by
+In this section we briefly introduce the AP and volume effect in wrongly assumed cosmologies.
+A more detailed description of the AP effect has been provided in \cite{Li2014}.
+
+Suppose that we are probing the shape and volume of an object in the Universe.
+We measure its redshift span $\Delta z$ and angular size $\Delta \theta$,
+then compute its sizes in the radial and transverse directions from the relations of 
+\begin{equation}\label{eq:distance}
+\Delta r_{\parallel} = \frac{c}{H(z)}\Delta z,\ \ \Delta r_{\bot}=(1+z)D_A(z)\Delta \theta,
+\end{equation}
+where $H$ is the Hubble parameter, $D_A$ is the angular diameter distance.
+In the particular case of a flat universe with constant dark energy EoS, they take the forms of
+\begin{eqnarray}\label{eq:HDA}
+& &H(z) = H_0\sqrt{\Omega_ma^{-3}+(1-\Omega_m)a^{-3(1+w)}},\nonumber\\
+& &D_A(z) = \frac{1}{1+z}r(z)=\frac{1}{1+z}\int_0^z \frac{dz^\prime}{H(z^\prime)},
+\end{eqnarray}
+where $a=1/(1+z)$ is the cosmic scale factor,
+$H_0$ is the present value of Hubble parameter and $r(z)$ is the comoving distance.
+
+In case we adopted a wrong set of cosmological parameters in Equation (\ref{eq:distance},\ref{eq:HDA}),
+the inferred $\Delta r_{\parallel}$ and $\Delta r_{\bot}$ are wrong,
+resulting in distorted shape (AP effect) and wrongly estimated volume (volume effect).
+The degree of variations in shape and volume can be described by the following quantities
+\begin{equation}\label{eq:stretch}
+ %{\rm Degree\ of\ LOS\ stretch\equiv}
+ %{\rm rat}_{\rm LOS\ stretch}\equiv
+ \frac{[\Delta r_{\parallel}/\Delta r_{\perp}]_{\rm wrong}}{[\Delta r_{\parallel}/\Delta r_{\perp}]_{\rm true}} =
+  \frac{[D_A(z)H(z)]_{\rm true}}{[D_A(z)H(z)]_{\rm wrong}} 
+\end{equation}
+\begin{equation}\label{eq:volume}
+ %{\rm Degree\ of\ volume\ magnification \equiv}
+ %{\rm rat}_{\rm volume\ mag}\equiv
+ \frac{[\Delta r_{\parallel}(\Delta r_{\perp})^{2}]_{\rm wrong}}{[\Delta r_{\parallel}(\Delta r_{\perp})^{2}]_{\rm true}}
+ = \frac{{\rm Volume}_{\rm wrong}}{{\rm Volume}_{\rm true}}
+ = \frac{[D_A(z)^2/H(z)]_{\rm wrong}}{[D_A(z)^2 / H(z)]_{\rm true}},
+\end{equation}
+where ``true'' and ``wrong'' denote the values of quantities in the true cosmology and wrongly assumed cosmology.
+From the AP and volume effects, we can constrain  $D_A(z)H(z)$ and $D_A(z)^2 / H(z)$, respectively.
+
+The AP and volume effect due to wrongly assumed cosmological parameters are shown in the upper panel of Figure \ref{fig_xy}.
+Suppose that the true cosmology is a flat $\Lambda$CDM with present density parameter $\Omega_m=0.26$
+and standard dark energy EoS $w=-1$.
+If we were to distribute four perfect squares at various distances from 500 Mpc/h to 3,000 Mpc/h,
+and an observer located at the origin were to measure their redshifts and compute their positions and shapes 
+using redshift-distance relations of two incorrect cosmologies:
+\begin{enumerate}
+ \item $\Omega_m=0.41$, $w=-1.3$,
+ \item $\Omega_m=0.11$, $w=-0.7$,
+\end{enumerate}
+the shapes of the squares appear distorted (AP effect),
+and their volumes are changed (volume effect).
+In the cosmological model (ii) with $\Omega_m=0.11$, $w=-0.7$, we see a stretch of the shape in the line of sight (LOS) direction (hereafter ``LOS shape stretch'')
+and magnification of the volume (hereafter ``volume magnification''), 
+while in the model with $\Omega_m=0.41$, $w=-1.3$, we see opposite effects of LOS shape compression and volume shrinkage.
+
+In the lower panel of Figure \ref{fig_xy}, we plot the degree of variations in shape and volume as functions of redshift. 
+In cosmology (i), both quantities have values less than 1, 
+indicating LOS shape compression and volume shrink.
+The effect in cosmology (ii) is slightly more subtle. At low redshift, the effect of dark energy is important, 
+and there is LOS shape compression and volume reduction due to the quintessence like dark energy EoS.
+However, at higher redshift the role of dark matter is more important, and we see LOS shape stretch and volume magnification due to the small $\Omega_m$.
+
+More importantly, Figure \ref{fig_xy} highlights the redshift dependence of the AP and volume effects. 
+For example, in the cosmology with $\Omega_m=0.41$, $w=-1.3$, 
+both the LOS shape stretch and volume magnification become more significant with increasing redshift.
+In the cosmology with $\Omega_m=0.11$, $w=-0.7$,
+not only do the magnitudes of the effects evolve with redshift,
+but there is also a turnover from LOS shape compression and volume shrink at lower redshift to LOS shape stretch and volume magnification at higher redshift.
+
+\section{The Simulation Data}\label{sec:data}
 
@@
 The HR4 simulation yield one all-sky light cone mock galaxy catalogue reaching $r=3\,150$ ${h^{-1}}$Mpc.
-As shown in Figure \ref{fig_mock},
+As shown in \cite{bossAP},
 from one all-sky survey, 
@@
 In this paper we use these simulated galaxies for the estimation of the systematics in the 2pCF of the observed galaxies.
-%We create four north
-
-\begin{figure*}
-   \centering{
-   \includegraphics[height=8cm]{fig4_0.eps}
-   \includegraphics[height=8cm]{fig4_1.eps}
-   %\includegraphics[height=7cm]{FVol.eps}
-   %\includegraphics[height=8cm]{xy.eps}
-   %\includegraphics[height=8cm]{smu.eps}
-   }
-   \caption{\label{fig_xy}
-   %Apparent distortion of objects in four wrongly assumed cosmologies, assuming a true cosmology of .
-   The redshift dependence of the AP effect in four incorrect cosmologies,
-   assuming that the true cosmology is $\Omega_m=0.31$, $w=-1$.
-   The left panel shows the apparent distortion of four perfect squares,
-   measured by an observer located at the origin.
-   The apparently distorted shapes are plotted in red solid lines.
-   The underlying true shapes are indicated in blue dashed lines.
-   The right panel displays the degree of the shape distortion, as described by Equations (\ref{eq:stretch}).
-   The BOSS DR12 galaxies used in our analysis have a redshift coverage of $0.15 < z < 0.693$ (marked 
-   by the gray vertical lines). Clearly, the magnitude of the shape distortion due to AP changes with redshift.
-   %measured by an observer located at the origin.
-   %For reference, blue dashed squares show their shapes and positions in the true cosmology.
-   }
-\end{figure*}
-
-\subsection{Horizon Run 3}
-%In our analysis we also mock surveys constructed from one of the Horizon Run simulations, HR3.
-
-As in HR4, HR3 also adopts a flat-space $\Lambda$CDM cosmology with the WMAP 5 year parameters.
-The simulation was made in a cube of volume $(10.815\  h^{-1}{\rm{Gpc}})^3$
-using $7120^3$ particles with particle mass of $1.25\times 10^{11}$\hMsun.
-The simulations were integrated from $z=27$ and reached $z=0$ after making $N_{\rm step}=600$ global timesteps.
-The collapsed high-density regions were identified using the Friend-of-Friend algorithm with the linking length of 0.2 times the mean particle separation.
-The physically self-bound (PSB) subhalos that are gravitationally self-bound and tidally stable \citep{kim and park 2006} 
-are identified and used as galaxy proxies.
-The PSB halo finder is a group-finding algorithm which can efficiently identify halos located even in crowded regions. 
-This method combines two physical criteria such as the tidal radius of a halo and the total energy of each particle to find member particles.
-The group velocity of member particles is adopted as the peculiar velocity of each PSB subhalo.
-
-%This provides a substantial increase in the similarity between simulation and observational data,
-%as these dark matter subhalos are sites for galaxy formation.
-%LRG (Xiao: is it OK to change all the ``LRG'' to ``galaxy''?) formation.
-
-To simulate the SDSS survey,
-HR3 places 27 observers evenly within its cubical volume and allows
-each observer to survey out to a redshift of 0.7
-\footnote{In the analysis we choose the maximal redshift as 0.693 rather than 0.7. 
-%The lightcone data created from HR3 simulations have cosmological redshift limit of $z<0.7$. 
-The outer boundary of the mock survey becomes fuzzy due to the peculiar velocity effect 
-on the galaxy redshifts (Eq. (\ref{eq:zvpeu})).
-A population of galaxies, that are expected to enter the $z<0.7$ region from the outside, is missing.
-%(these $z>0.7$ galaxies have a peculiar velocity toward us and 
-%their observed redshfits become lower than 0.7).
-To avoid this problem we set the maximal redshift at 0.693, 
-23.3 $h^{-1}{\rm Mpc}$ away from $z=0.7$.}, 
-creating 27 samples of independent, non-overlapping spherical regions.
-From the 27 spherical light cone `galaxy' catalogues, 
-we created 72 non-overlapping survey samples 
-\footnote{Using the 27 spherical light cones, we create 72 sets of NGC samples from 18 light cones, 
-and 72 sets of SGC samples from the other 9 light cones.}
-simulating BOSS DR12 within the redshift range of $0.15< z< 0.693$.
-%As will be described in the next section, 
-These mock surveys are used to estimate the covariance of the 2pCF in our analysis.
-
-\section{AP Effect in Incorrect Cosmologies}
-\label{sec:APeffect}
-
-%Considering we are Let us consider an object in the Universe with certain size and shape.
-%Its observed redshift span $\Delta z$ and angular size $\Delta \theta$ are related with the comoving sizes by
-This section illustrates the AP effect when an incorrect cosmological model is used to calculate the distances of galaxies. Similar illustrations have been provided in \cite{Li2014,Li2015}.
-
-Suppose that we probe the shape and volume of an object in the Universe,
-which spans $\Delta z$ in redshift and $\Delta \theta$ in angle.
-Its comoving sizes in the radial and transverse directions are given by
-\begin{eqnarray}\label{eq:distance}
-& &\Delta r_{\parallel} = \frac{c}{H(z)}\Delta z,\nonumber\\
-& &\Delta r_{\bot}=(1+z)D_A(z)\Delta \theta,
-\end{eqnarray}
-where $H$ is the Hubble parameter and $D_A$ the proper angular diameter distance.
-In the particular case of a flat Universe with constant dark energy EoS, they take the forms of
-\begin{eqnarray}\label{eq:HDA}
-& &H(z) = H_0\sqrt{\Omega_ma^{-3}+(1-\Omega_m)a^{-3(1+w)}},\nonumber\\
-& &D_A(z) = \frac{c}{1+z}r(z)=\frac{c}{1+z}\int_0^z \frac{dz^\prime}{H(z^\prime)},
-\end{eqnarray}
-where $a=1/(1+z)$ is the cosmic scale factor,
-$H_0$ is the present value of Hubble parameter and $r(z)$ is the comoving distance.
-
-In case we adopted an incorrect set of cosmological parameters in Equation (\ref{eq:HDA}),
-the inferred $\Delta r_{\parallel}$ and $\Delta r_{\bot}$ are also incorrect,
-resulting in distorted shape (AP effect) and wrongly estimated volume (volume effect).
-The degree of variations in shape and volume are
-\begin{equation}\label{eq:stretch}
- %{\rm Degree\ of\ LOS\ stretch\equiv}
- %{\rm rat}_{\rm LOS\ stretch}\equiv
- \frac{[\Delta r_{\parallel}/\Delta r_{\perp}]_{\rm wrong}}{[\Delta r_{\parallel}/\Delta r_{\perp}]_{\rm true}} =
-  \frac{[D_A(z)H(z)]_{\rm true}}{[D_A(z)H(z)]_{\rm wrong}} 
-\end{equation}
-\begin{equation}\label{eq:volume}
- %{\rm Degree\ of\ volume\ magnification \equiv}
- %{\rm rat}_{\rm volume\ mag}\equiv
- \frac{{\rm Volume}_{\rm wrong}}{{\rm Volume}_{\rm true}}
- = \frac{[\Delta r_{\parallel}(\Delta r_{\perp})^{2}]_{\rm wrong}}{[\Delta r_{\parallel}(\Delta r_{\perp})^{2}]_{\rm true}}
- = \frac{[D_A(z)^2/H(z)]_{\rm wrong}}{[D_A(z)^2 / H(z)]_{\rm true}},
-\end{equation}
-where ``true'' and ``wrong'' denote the values of quantities in the true cosmology and incorrectly assumed cosmology.
-From the AP and volume effects, we can constrain  $D_A(z)H(z)$ and $D_A(z)^2 / H(z)$, respectively.
-
-The apparent distortion of objects due to incorrect cosmological parameters is illustrated in the left panel of Figure \ref{fig_xy}.
-Suppose that the true cosmology is a flat $\Lambda$CDM model with the present density parameter $\Omega_m=0.31$
-and standard dark energy EoS $w=-1$ \citep[the best $\Lambda$CDM model determined by Planck 2015 results][]{Planck2015}.
-%(the best $\Lambda$CDM model determined by Planck 2015 results \citep{Planck2015}).
-If we distributed three square objects at various distances from 500 to 2,000 $h^{-1}$Mpc,
-and had an observer located at the origin measure their redshifts and compute their positions and shapes 
-using redshift-distance relations of four incorrect cosmologies:
-\begin{enumerate}[label=(\roman*)]
-\item $\Omega_m=0.4$, $w=-1$,
-\item $\Omega_m=0.1$, $w=-1$,
-\item $\Omega_m=0.31$, $w=-0.3$,
-\item $\Omega_m=0.31$, $w=-2.5$,
-\end{enumerate}
-the mismatch between the true and assumed cosmology will cause the shapes of the squares appear distorted.
-In the cosmological models (ii) and (iv) the squares are stretched in the line of sight (LOS) direction (hereafter ``LOS shape stretch''),
-%and magnification of the volume (hereafter ``volume magnification''), 
-while in the models (i) and (iii) we see opposite effects of LOS shape compression.
-
-The right panel of Figure \ref{fig_xy} presents the degree of shape distortion as a function of redshift. 
-In cosmology (i) and (iii), $\frac{[D_A(z)H(z)]_{\rm true}}{[D_A(z)H(z)]_{\rm wrong}}$ have values less than 1, 
-indicating LOS shape compression,
-while in cosmology (ii) the curve lies above 1, 
-corresponding to an LOS shape stretch.
-The effect in cosmology (iv) is more subtle. 
-There is a transition from LOS shape stretch to compression at $z \approx 0.65$.
-
-More importantly, Figure \ref{fig_xy} highlights the redshift dependence of the AP effect. 
-If the conversion of redshift to the comoving distance was correctly made,
-there would be no shape distortion at any redshift.
-Conversely, the four cases with incorrectly chosen cosmological parameters illustrated 
-in Figure \ref{fig_xy} 
-show characteristic dependence of the shape distortion on redshift.
-Our method utilizes this redshift dependence to constrain cosmological parameters
-governing the expansion history of the Universe.
-%For example, in cosmology (i), %with $\Omega_m=0.4$, 
-%the LOS shape stretch become more significant with increasing redshift.
-%In cosmology (iv), not only the magnitude of the effect evolves with redshift,
-%but there is also a turnover from LOS shape stretch to compression.
-%The magnitude of anisotropies produced by AP evolves with redshift.
-%We can search for such pattern in the LSS statistic to see whether there exists distortions produced by AP effect,
-%thus determine the correctness of the cosmological model.% adopted for the computation of $r(z)$.
 
@@
 
-We measure the 2pCF in redshift bins of BOSS DR12 galaxies and 
+We measure the 2pCF in redshift bins of galaxies and 
 determine cosmological parameters by examining the redshift evolution of clustering anisotropy.
@@
    \centering{
-   \includegraphics[width=14cm]{fig5.eps}
+%   \includegraphics[width=14cm]{fig5.eps}
    %\includegraphics[width=14cm]{Tpcf--contour.eps}
@@
    \centering{
-   \includegraphics[width=16cm]{fig6.eps}
+%   \includegraphics[width=16cm]{fig6.eps}
    }
@@
    \centering{
-   \includegraphics[width=16cm]{fig7.eps}
+   %\includegraphics[width=16cm]{fig7.eps}
    %\includegraphics[height=9cm]{Tpcf-sys.eps}
@@
    \centering{
-   \includegraphics[width=14cm]{fig8.eps}
+%   \includegraphics[width=14cm]{fig8.eps}
    %\includegraphics[width=14cm]{Tpcf--contour.eps}
@@
 
-\subsection{Averaging a set of replicate measurements to increase the S/N}\label{sec:binningscheme}
-
-The angular cut, $\mu_{\rm max}$, and number of bins, $n_\mu$, is chosen freely.
-%The cut $\mu_{\rm max}$ and the number of bins $n_\mu$ can be chosen freely in our analysis.
-Different choices for these parameters yield slightly different results and different statistical uncertainties.
-To suppress the statistical noise we adopt a large number of binning schemes and average their $\chi^2$s.
-
-A value $\mu_{\rm max} = 0.99$ is sufficient to remove the fiber collision effect.
-We have checked that our results are statistically robust against the choice of $\mu_{\rm max}$.
-
-A larger $n_\mu$ tightens the constraint 
-in the cost of more noise, 
-while $n_\mu$ should be smaller than the number of mock samples used for covariance estimation.
-We find $n_\mu \gtrsim 5$ gives relative tight constraints, 
-and $n_\mu = 40$ is the limit we can reach given the size of the sample and the number of mock samples.
-
-We run through the range $\mu_{\rm max} = 0.85, 0.86, ... 0.99$ at steps of 0.01 and $n_\mu = 5, 6, ... 40$, in total 540 binning schemes.
-%\footnote{In fact we only use 381 schemes.
-%In some cases the estimation of covariance is not very successful, leading to singular matrix or very noisy $\chi^2$;
-%We reject these cases.}.
-We compute $\chi^2$ according to Equation (\ref{eq:chisq1}) for these choices and take an average of these $\chi^2$s.
-This approach suppresses the statistical noise quite effectively. %in the contour map of $\chi^2(\Omega_m,w)$.
-
 %We find noise in the $\chi^2$ probably due to the low statistic caused by the limited size of the sample and the covmat due to small size of mocks ...
@@
    \centering{
-   \includegraphics[width=18cm]{fig9_0.eps}
-   \includegraphics[width=18cm]{fig9_1.eps}
+%   \includegraphics[width=18cm]{fig9_0.eps}
+%   \includegraphics[width=18cm]{fig9_1.eps}
 %   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
@@
 
-\section{Result}
-
-We apply our method to the BOSS DR12 CMASS and LOWZ galaxies.
-We present the results in this section.
-
-\subsection{Redshift evolution in wrong cosmologies}\label{sec:redevolvxi}
-
-%{\bf Figure: $\xi$ curves, in different cosmologies, without and with RSD}
-
-The upper panels of Figure \ref{fig_TpCF} present the $\hat \xi_{\Delta s}$ measured for BOSS galaxies in three different cosmologies.
-In the left panel we adopt the Planck cosmology, i.e., $\Lambda$CDM with $\Omega_m=0.31$;
-%which should be {\it close to the truth}.
-In the other two panels, we choose two sets of parameters ---
-the $\Omega_m=0.1$ $\Lambda$CDM cosmology (middle) and the cosmology with $\Omega_m=0.31$ and $w=-2.5$ (right).
-We split the BOSS DR12 galaxies into six redshift bins,
-construct their 3D distribution in these three cosmologies
-and then measure $\hat \xi_{\Delta s}(\mu)$ according to the procedure of the last section.
-
-For a sample of galaxies with homogeneous, isotropic spatial distribution, 
-the measured $\hat \xi_{\Delta s}(\mu)$ is statistically uniform.
-The distortion in $\hat \xi_{\Delta s}(\mu)$ introduced by RSD is large.
-There are two distinct features in this distortion.
-At $0\lesssim 1-\mu \lesssim 0.1$, $\hat \xi_{\Delta s}(\mu)$ turns up as $\mu\rightarrow1$
-due to the large FOG effect.
-In other directions, the anisotropic clustering produced by the large scale flow creates a monotonic angle dependence of $\hat\xi_{\Delta s}(\mu)$. %a slope in the curve.
-These patterns are evident in all cosmologies.
-
-%\subsubsection{AP effect}
-
-The additional angular dependence of $\hat \xi_{\Delta s}(\mu)$ introduced by AP is not as strong as RSD;
-However, it is still visible. 
-In the middle and right panels, % of Figure \ref{fig_TpCF},
-%where there is clear redshift evolution of $\hat \xi_{\Delta s}$.
-the choice of two incorrect cosmologies results in an enhancement of  $\hat \xi_{\Delta s}(\mu)$ due to the 
-apparent stretch of non-linear structures in the LOS direction
-%As a result, near LOS the value of $\hat \xi_{\Delta s}$ is enhanced 
-\footnote{{\it Stretch of structure enhances the value of $\xi_{\Delta s}$}.
-On relatively small scales, the strong clustering produces large values of $\xi$.
-The apparent stretch of structure means the strong clustering on small scales are, apparently, shifted to larger scales:
-at some fixed scale, we measured larger $\xi$ if there is apparent stretch.
-The value of $\xi_{\Delta s}$, which is the integral of $\xi$ within fixed range of $s$, is also enhanced.}.
-This effect is evident when we compare  $\hat \xi_{\Delta s}(\mu)$ in these two panels to that in the left panel.
-
-More importantly, in incorrect cosmologies the redshift dependence of the AP effect results in a redshift evolution of $\hat \xi_{\Delta s}$.
-This unique feature makes the AP effect detectable even with the existence of the large RSD effect. %distinguishable from the RDS distortion.
-When $\Omega_m=0.1$ and $w=-1$ are adopted, 
-the LOS stretch of structure becomes stronger at higher redshift (see Figure \ref{fig_xy});
-as a result, the enhancement of $\hat \xi_{\Delta s}$ along the LOS 
-becomes more significant at higher redshifts.
-The opposite behavior is seen for the choice of $\Omega_m=0.31$ and $w=-2.5$.
-%We see very evident redshift evolution of $\hat \xi_{\Delta s}$.
-%I.e., the redshift dependence of AP effect results in redshift evolution of $\hat \xi_{\Delta s}$.
-However, we do not see such obvious redshift evolution in the Planck cosmology, % is not so obvious.
- indicating that the cosmological parameters of the Planck cosmology are close to the correct ones.
-%The Planck cosmology is widely accepted as to be close to the true cosmology parameters of our Universe and 
-%There the AP effect is not strong enough to produce an evident redshift evolution.
-
-The lower panels of Figure \ref{fig_TpCF} show the redshift evolution of $\hat\xi_{\Delta s}$ after systematics correction, 
-i.e., the quantity $\delta\hat \xi_{\Delta s}-\delta\hat \xi_{\Delta s,\rm sys}$.
-The result is statistically consistent to 0 in Planck cosmology -- 
-In the four curves, almost all points are consistent with 0 at $\lesssim1\sigma$ confidence level (CL).
-The only exception is the leftmost point of $\delta\hat \xi_{\Delta s}(z_6,z_1)-\delta\hat \xi_{\Delta s,\rm sys}(z_6,z_1)$,
- which is negative at $\sim$2 $\sigma$ CL.
-This result could be due to the overestimation of $\delta\hat\xi_{\Delta s, \rm sys}(z_6,z_1)$ as discussed in Sec. \ref{sec:syscor}.
-This behavior will not affect our derived cosmological constraints:
-Dropping this measurement by imposing a cut $\mu<0.9$
-  does not shift the constrained on $\Omega_m$-$w$ (the pink contour of Figure \ref{fig_contours}).
-
-In the $\Omega_m=0.1$ cosmology and the $w=-2.5$ cosmologies, however,
-the measured $\delta\hat \xi_{\Delta s}-\delta\hat \xi_{\Delta s,\rm sys}$ deviates 
-from zero at significant confidence levels.
-Applying the likelihood analysis described in Sec. \ref{sec:likelihood},
- they are disfavored at 5.3$\sigma$ and 7.5$\sigma$ CL compared to the Planck cosmology.
-Since these two cosmologies deviates from the $\Omega_m=0.31$ $\Lambda$CDM cosmology with $\Delta \Omega_m = 0.21$ and $\Delta w = 1.5$,
-roughly speaking, we expect our method able to constrain $\Omega_m$ and $w$ with 1$\sigma$ uncertainties of 0.04 and 0.2, respectively.
-
-%Overall, the effect of RSD on the 2pCF is large but its redshift dependence is small.
-%The correct cosmology corresponds to the case with the lowest change of $\hat \xi_{\Delta s}$ with $z$.
-%Even with RSD, we can still correctly determine the true cosmology by using the relative change of $\hat \xi_{\Delta s}$ with redshift.
-
-\subsection{Cosmological constraint}\label{sec:constraint}
+\subsection{Cosmological Constraints}
 
@@
    %\includegraphics[width=16cm,natwidth=52,natheight=40]{fig10.eps}
-   \includegraphics[width=16cm]{fig10.eps}
+   %\includegraphics[width=16cm]{fig10.eps}
    }
@@
 
-We find the expected negative degeneracy between $\Omega_m$ and $w$.
-At low redshift, increasing $\Omega_m$ and increasing $w$ have a similar effect on the cosmic expansion.
-When one parameter is increased the other parameter can be decreased to counteract the AP effect
-\footnote{At high redshift the direction of degeneracy completely changes. 
-There the effect of $w$ is less important and the cosmic expansion is mainly governed by $\Omega_m$.
-This behavior is why \cite{Li2015} obtained a positive degeneracy between $\Omega_m$ and $w$ from mock surveys 
-spanning a wide range of $0< z < 1.5$.
-The degeneracy direction between $\Omega_m$ and $w$ depends on the redshift range of the sample used in the analysis.
-}.
-
-For comparison, additional likelihood contours from other cosmological probes are displayed in Figure \ref{fig_contours}:
-the JLA SNIa sample (green area, \cite{JLA}),
-the BAO measurement from BOSS DR11 galaxies (bright yellow, \cite{Anderson2013}),
-%\footnote{The CMASS and LOWZ samples from BOSS DR11 have a sky coverage of 8\,377 $\rm deg^2$ and a completeness of 97\%.
-%They are very close to the DR12 samples.},
-a combination of the BOSS DR11 BAO and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ (dark yellow, \cite{Riess2011,E14H0}),
-and the full-mission Planck observations of temperature and polarization anisotropies, released in 2015 (blue, \cite{Planck2015}).
-
-%
-The SNIa contours occupy a region similar to ours, but provide much weaker constraints. %has similar degeneracy to our method.% to us while the contour size is larger.
-The direction of degeneracy is also similar.
-%This is expectable.
-By measuring the apparent magnitudes of type Ia supernovae distributed at different redshifts, 
- cosmologists can infer the luminosity distance $d_L$ as a function of redshift.
-The JLA sample has similar redshift coverage to the BOSS DR12 galaxies,
-which could be the reason for the similarity between the contours of the SNIa and our AP method.
-%This is to some extent similar to our method, 
-%which probes the redshift evolution of geometric distortion.
-%which maybe the reason of the similarity 
-%So the shapes and the positions of the contours from these two methods are a kind of close to each other.
-%Comparing these two methods, we find our method has better constraining power.
-%For SNIa probe, the degeneracy between $\Omega_m$ and $w$ is more serious and the contour extends to $\Omega_m=0$.
-
-%The BOSS DR11 galaxies BAO measurements yields $D_V(z=0.32) = (1264 \pm 25 {\rm Mpc})(r_d /r_{d,\rm fid})$,
-%$D_A(z=0.57) = (1421 \pm 20 {\rm Mpc})(r_d /r_{d,\rm fid})$, 
-%and $H(z=0.57) = (96.8 \pm 3.4 {\rm km/s/Mpc})(r_{d,\rm fid} /r_d )$.
-%Here $r_d$ is the drag epoch,
-%$D_V(z)$ is the spherically averaged 2-point measurement of the BAO position, defined as $\left[cz(1+z)^2D_A(z)^2H^{-1}(z)\right]^{1/3}$, 
-%and all measurements are presented as the ratio of the distance priors to their values in the fiducial cosmology \citep{Anderson2013}.
-%At $z=0.57$, separating the clustering along and transverse to the LOS enables measurement of the sizes of the BAO ring in these two directions.
-
-BAO itself can not effectively constrain $\Omega_m$ and $w$, 
-since these parameters are highly degenerate with $H_0$ in determining the length scale.
-Combining BAO with the $H_0$ measurements to break the degeneracy yields better constraint on the parameter space.
-%The contour size is a bit larger than ours.
-The direction of degeneracy of the combined constraint is roughly orthogonal to ours.
-%This means we can combine these two LSS probes to break the degeneracy and significantly strengthen the constraining power.
-
-CMB measurements provide a powerful probe of the geometry of the Universe,
-but can not effectively constrain $\Omega_m$ and $w$ due to the strong degeneracy of the parameters.
-%But combining CMB with the other probes can significantly shrink the volume of parameter space and tightens the constraint.
-The CMB contour is almost orthogonal to the AP contour. 
-%Contours from the two probes nicely overlapped with each other.
-%In particular, our contour is well consistent with the Planck 2015 $\Lambad$CDM with $\Omega_m=0.308$.
-
-Among all the individual cosmological probes, our method yields the most stringent 
-constraint on $\Omega_m$ and $w$.
-Our result is consistent with those of all other probes.
-%Also, the degeneracy of our contour is different from most the other probes.
-%We can take the advantage of this fact and tighten the constraint by combing them together.
-
-Assuming that the five different cosmological probes of CMB, BAO, SNIa, $H_0$ and our method are 
-statistically independent,
-we combine the results by simply multiplying their likelihoods,
-resulting in the total likelihood function
-\begin{equation}\label{eq:likelihood}
-\mathcal{L}_{\rm total} = \mathcal{L}_{\rm CMB} \times \mathcal{L}_{\rm BAO} \times \mathcal{L}_{\rm SNIa}\times \mathcal{L}_{\rm H_0}
- \times \mathcal{L}_{\rm Our\ AP}.
-\end{equation}
-The Planck team has released the {\texttt {COSMOMC}} outputs of MCMC samples
-using CMB+BAO+JLA+$H_0$
-\footnote{http://pla.esac.esa.int/pla/\#cosmology; 
-Their BAO datasets include three sets of measurements from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS}}.
-We modify their MCMC samples (by changing the values of sample weight and likelihood)
- to include the likelihood of our method,
-creating samples following the PDF of Eq. (\ref{eq:likelihood}).
-The joint constraint from all five cosmological probes is
-\begin{equation}
- \Omega_m = 0.304 \pm 0.007,\ w=-1.04 \pm 0.03.
-\end{equation}
-%{\bf which are the strongest constraints on these parameters obtained so far}
-%{\bf AMTB: 
-Our AP method plays an important role in strengthening the constraints on $\Omega_m$ and $w$.
-As a comparison, combining CMB and our method yields $\Omega_m = 0.302 \pm 0.011,\ w=-1.05 \pm 0.04$,
-while a combination of CMB and BAO yields $\Omega_m = 0.306 \pm 0.013,\ w=-1.03 \pm 0.06$.
-%by combining the CMB and BAO measurements, %while .
-In the absence of our method, a combination of SNIa, CMB, BAO and $H_0$
-yields $\Omega_m = 0.306 \pm 0.009,\ w=-1.03 \pm 0.04$ \citep{Planck2015}.
-% }
-
 %\bibitem[Blake et al. (2011)]{WiggleZB}
@@
 
-We apply the methodology developed in \cite{Li2014,Li2015} to BOSS DR12 galaxies.
-In LSS surveys, the observed galaxy distribution appears anisotropic due to two reasons:
-the contamination of galaxy redshifts due to the galaxy peculiar velocities, known as the RSD effect, 
-and the error in the distance due to inaccurate cosmological parameters.
-%incorrectly assumed cosmological model for the coordinate transformation from redshift space to comoving space, known as the AP effect.
-\cite{Li2014} reported that anisotropies produced by RSD effect are, although large,
-close to uniform in magnitude over a large range of redshift,
-while the degree of anisotropies introduced by AP varies with redshift. 
-%We found that the redshift dependence of the anisotropy introduced by RSD is much less significant compared with the anisotropy caused by AP.
-Thus we can use the redshift dependence of the anisotropic clustering of galaxies to constrain cosmological parameters without 
-being much affected by RSD.
-
-%The methodology developed in \cite{Li2015} was applied.
-As in \cite{Li2015}, we investigate the redshift-dependence of clustering anisotropy by examining the 2pCF.
-The 2pCF measured along different angular directions was characterized by the function $\hat \xi_{\Delta s}(\mu)$.
-%In incorrectly adopted cosmological models, 
-When the cosmological parameters governing the expansion history of the universe are incorrectly chosen,
-the shape of this function evolves with redshift.
-We split the DR12 galaxies into six redshift bins, measure the 2pCF in each redshift bin,
-and search for the underlying true values of $\Omega_m$ and $w$ of our Universe % (assuming flat Universe)
-by requiring minimal redshift evolution of $\hat \xi_{\Delta s}(\mu)$ across the six redshift bins.
-We obtain tight constraints of $\Omega_m=0.314 \pm 0.038,\ \ w = -1.09 \pm 0.14$ from our method alone.
-
-The constraints on $\Omega_m$ and $w$ from our AP method are tighter % in constraining the parameter space of $\Omega_m$ and $w$ 
-than the other cosmological probes of SNIa, CMB, BAO, and $H_0$.
-For the direction of degeneracy, %between $\Omega_m$ and $w$ in the constrained parameter space,
-our method is similar to SNIa and orthogonal to CMB and BAO+$H_0$.
-Combining the results of our method with those of other cosmological probes, 
-we obtain tight constraints $ \Omega_m = 0.304 \pm 0.007,\ w=-1.04 \pm 0.03$.
-
-\subsection{Comparison with other LSS probes}
-
-Our method uses the anisotropic galaxy on scales from 6 to 40 $h^{-1}$Mpc.
-%a novel analysis method extracting physical information encoded in LSS. % compared with the others.
-%We look at the geometric distortion of LSS due to AP effect 
-%clustering created by AP exhibits redshift evolution.
-%Here the clustering scales we choose to look at in this analysis is 
-Constrains on cosmological parameters are obtained from the redshift dependence of $D_A(z) H(z)$.
-
-As a comparison, the BAO method uses the BAO feature in the 
-clustering of galaxies on scales of 100-150 $h^{-1}$Mpc 
-created by the oscillation of the baryon-photon plasma in the early Universe.
-Measuring the BAO feature in 1D or 2D yields measurements of $D_V$ or $D_A$ and $H$ at some representative redshifts.
-%So the principles and the physical information probed in these two methods are fundamentally different.
-
-The AP methods proposed to date, such as those using 
-galaxy pairs and voids, measure the rate of geometric distortion and are sensitive to $D_A(z) H(z)$,
-while our method uses its the redshift dependence.
-These methods can be combined together to fully utilize the physics of AP test.
-Also, reducing the RSD effect 
-through the redshift dependence could be 
-applicable to these methods.
-
-The topology method proposed by \cite{topology} 
-uses the redshift evolution of the volume effect and is sensitive to the quantity $D_A(z)^2 / H(z)$.
-Combing this method with ours can yield separate constraints on $D_A$ and $H$ 
-for the same observational sample.
-Constraints from the other statistical measures,
-such as the distribution function of size or richness of LSS,
-can be also combined \citep{Park2012,Park2015}.
-%Analyzing the distortion of apparent galaxies clustering due to RSD,
-%people can constrain the growth rate, the clustering strength and the galaxy bias.
-
-Recently, \cite{MS2016} developed a novel method 
-constraining cosmological parameters based on the high-level similarity of the emission measure in the cluster outskirts.
-In incorrect cosmologies, the emission measure from clusters exhibits redshift dependence.
-%This leads to tight constraints on the redshift evolution of the cosmic length scale.
-Utilizing a sample of 320 galaxy clusters ($0.056<z<1.24$) observed with Chandra,
-they achieve tight cosmological constraints comparable to ours.
-The idea of this novel technique is to some extent similar to our method 
-(seeking for the conservation of geometric quantity with redshift),
-and could have promising future.
-%and can be combined with our method to
-
-%The above LSS analysis methods, based on different concepts, 
-%and probing different types of physical information, 
-%are mutually complementary.
-%It is worthy combining them together to comprehensively utilize the physical information encoded in the LSS 
-%and derive tight constraints on parameters of cosmology. % and galaxy science.
-%which is also fundamentally different from our method which is
-
-\subsection{Room for improvements}
-
-This paper is the first application of this redshift dependent AP test to observed LSS data.
-There remains considerable opportunity for improving the analysis methodology,
-e.g., the optimized schemes of redshift binning and 
-optimized choices of the scales of clustering (the values $s_{\rm min}$ and $s_{\rm max}$).
-In this paper, the 2pCF is characterized by $\hat \xi_{\Delta s}(\mu)$.
-It should be more advantageous to use 
-the redshift evolution of 2pCF in two dimensions, i.e., $\hat \xi(s,\mu)$, 
-to capture the full information.
-It is also necessary to combine the 
-information in the higher-order
-statistic beyond the two point functions.
-As pointed out in Sec. \ref{sec:caveats},
-more theoretical and numerical studies on the 
-redshift evolution of the RSD effect 
-will remove the remaining small 
-uncertainties in our results.
-
-To avoid the difficulty of modeling galaxy bias we dropped the information of strength of clustering
-through normalizing the amplitude of $\xi$.
-In the case that we have good knowledge of galaxy bias, one can utilize the amplitude of $\xi$ to probe the redshift dependence of volume effect 
-and obtain much tighter constraints.
-\cite{Li2015} showed that
-the area of constraining regions in $\Omega_m$ and $w$ space from the redshift dependence of the volume effect is 3.5 times smaller 
-than that from the redshift dependence of the AP effect alone.
-
-In this analysis, by reducing the RSD effect, 
-%through looking at the redshift evolution,
-we are able to use the galaxy clustering down to 6 $h^{-1}$Mpc.
-This is a major advance in extracting the cosmological information 
-on small scales where galaxy clustering is strong
-and there are a lot of independent structures.
-
-To make sure that the derived cosmological constraint is robust, 
-in the procedure of systematics correction, 
-one should construct many mock surveys in which the RSD and other systematic effects are reliably modeled.
-%It could be crucial to adopt a good galaxy assignment scheme, 
-%such as the MBP-galaxy correspondence model developed in \citep{hong2016}.
-%adopted in this analysis, could be crucial.
-%So we can obtain an accurate estimation of systematic effect.
-
-It would also be helpful to investigate the effect of galaxy properties.
-For example, in case of a dense survey containing galaxies with various properties, 
-one can split the galaxy sample into subsamples with different galaxy properties, 
-derive cosmological constraints from these subsamples, 
-and check the consistency of the results.
-
-%Our method is to some extent very similar with the methods using the overall shape of 
-%the power spectrum or correlation function Park \& Kim (2010) Shoji et al. 2009 {\bf AMTB: Read them and check }.
-%But we have one addition that uses the shape in a set of redshift slices to reduce the RSD effect.
-
-%This is one of the reasons why our method is powerful.
-%for the strong power of our method -- the small scale galaxy clustering contains abundant information.
-%In future the development of simulation technique may enable us to accurately modeling galaxy clusterings on even smaller scales 
-%and makes our method more powerful.
-
-\subsection{Synergies with future observations}
-
-The constraining power of our method is proportional not only to the size, 
-but also to the redshift coverage of the galaxy sample.
-In this analysis we utilize 1\,133\,326 BOSS DR12 galaxies covering $0.15< z < 0.693$.
-Future redshift surveys such as eBOSS \citep{eBOSS}, EUCLID \citep{EUCLID}, and DESI \citep{DESI}
-will have larger sample sizes and wider redshift coverage.
-Our method is expected to yield much tighter cosmological constraints
-and can be applied to constrain wider classes of 
-cosmological models when these data are available.
-%In the future we will have LSS surveys of 
-% having much wider redshift coverage and much larger number of observed galaxies.
-%{\bf Introducing the redshift range and galaxy numbers of future surveys?: eBOSS, DESI, LSST, ...?}
-%Being able to utilizing small scale clustering information a denser survey will be also helpful to improve the power of our method.
-%Even for the regions already probed by the current SDSS-III survey, 
-%there is still large potential to improve the power of constraint by conducting a deeper survey to increase the S/N.
-
-In this analysis we assume a flat Universe to constrain $\Omega_m$ and $w$.
-Our method should be sensitive to all other cosmological parameters governing the cosmic expansion history,
-e.g., the curvature of the Universe, 
-and the other dark energy parameters.
-
-Overall, the future of our method is extremely promising. 
-With the progressive development of LSS experiments, 
-we expect it to play an important role in deriving cosmological constraints from LSS surveys.
-%and yielding fruitful out-comings.
+ * Can be combined with our redshift dependence of AP to full explore the geometric effects in LSS
+
+ * *** utilizes angular 2pCF as a function of redshift.
+Our method is complementary to it: 1) smaller scales; 2) more bins; 3) could be less affected by RSD; ...
+In case of good modelling of RSD one can rely on their; in case not possible, especially on small scales, one can use ours
+
+ * Complementary to all other LSS probes
+
+ * Promising future
 
@@
 %We thank Seokcheon Lee and Graziano Rossi for many helpful discussions.
-We would like to thank Ho Seong Hwang, Francisco-Shu Kitaura, Benjamin L'Huillier, Donghui Jeong, Teppei Okumura, Will Percival, Hyunmi Song 
-and Yi Zheng for kind helps and helpful discussions.
+We would like to thank Yi Zheng for useful discussions.
 This work was partially supported by the
@@
 
-Based on observations obtained with Planck (http://www.esa.int/Planck), 
-an ESA science mission with instruments and contributions directly funded by 
-ESA Member States, NASA, and Canada.
-
-Funding for SDSS-III has been provided by the Alfred P. Sloan Foundation, the Participating Institutions, the
-National Science Foundation, and the U.S. Department of Energy Office of Science. 
-The SDSS-III web site is http://www.sdss3.org/. 
-SDSS-III is managed by the Astrophysical Research Consortium for the Participating Institutions
-of the SDSS-III Collaboration including the University of Arizona, the Brazilian Participation Group, Brookhaven
-National Laboratory, Carnegie Mellon University, University of Florida, the French Participation Group, 
-the German Participation Group, Harvard University, the Instituto de Astrofisica de Canarias, the Michigan State/Notre
-Dame/JINA Participation Group, Johns Hopkins University, Lawrence Berkeley National Laboratory, Max Planck
-Institute for Astrophysics, Max Planck Institute for Extraterrestrial Physics, New Mexico State University, New
-York University, Ohio State University, Pennsylvania State
-University, University of Portsmouth, Princeton University,
-the Spanish Participation Group, University of Tokyo, University of Utah, Vanderbilt University, University of Virginia, 
-University of Washington, and Yale University.
-
 \appendix
-
-\section{A. Robustness Tests}\label{sec:RBtest}
-
-We conduct a series of tests to check the robustness of our results.
-
-The cosmological constraints presented in Sec. \ref{sec:constraint} (hereafter the ``main results'') are derived using 
-the following options (hereafter the ``default options''):
-\begin{itemize}
- \item We adopt $s_{\rm min}=6 h^{-1} {\rm Mpc},\ s_{\rm max}=40 h^{-1} {\rm Mpc}$ in the integrated 2pCF
- ($\xi_{\Delta s} (\mu) \equiv \int_{s_{\rm min}}^{s_{\rm max}} \xi (s,\mu)\ ds$).
- \item The effects of systematics are estimated from the HR4 mock galaxies. 
- When constructing the mocks, to determine when a satellite galaxy is disrupted,
- we adopt the J08 model to calculate the satellite galaxy merger timescale.
- \item In total 72 sets of HR3 PSB mock surveys are used to construct the covariance matrix.
- \item We drop the angular region $1 - \mu < 0.01$, to mitigate the effects of fiber collisions and redshift failures.
-\end{itemize}
-
-\begin{figure*}
-   \centering{
-   \includegraphics[width=14cm]{fig11.eps}}
-   %\includegraphics[width=5.9cm]{Tpcf--contour-nummock-36.eps}}
-   \caption{ \label{fig_contour_RB}  
-   Likelihood contours (68\%, 95.4\%) in the $\Omega_m$-$w$ plane, derived by applying our AP method to the BOSS DR12 galaxies.
-   The upper-left panel displays the main results derived using the default options.
-   %i.e. using $s_{\rm min}=6h^{-1}{\rm Mpc}$, $s_{\rm max}=40h^{-1}{\rm Mpc}$, $1 - \mu \ge 0.01$,
-   %72 sets of HR3 PSB mocks for covariance estimation,
-   %and J08 model to compute the merger timescale model in the construction of mock surveys.
-   The other panels show the contours when the options are altered one by one.
-   %We find good consistency among these contours. 
-   }
-\end{figure*}
-
-We check whether the results are sensitive to these options.
-We modify the above options one by one, 
-derive the corresponding cosmological constraints, 
-and check how much they deviate from the main results.
-%and are compared with the constraints derived using the default option set.
-We present this information in Figure \ref{fig_contour_RB}. %displays the many sets of cosmological constraints derived with various sets of modified options.
-%The upper-left panel shows the result using the default options, 
-%while the other many panels display the result after changing one of these options.
-
-To be efficient, we adopt a coarser grid with $\delta \Omega_m=0.025,\ \delta w=0.05$ when covering the parameter space.
-%Although the obtained contours look a little coarse, 
-This resolution is high enough for the purpose of testing our methodology.
-
-\subsection{$Different\ s_{\rm max}$}
-
-The upper-panel of Figure \ref{fig_contour_RB} shows the main results, 
-the cosmological constraint when the default options are adopted. %There we use $s_{\rm max}=40 h^{-1}{\rm Mpc}$. 
-The results for $s_{\rm max}=30,\ 50 h^{-1}{\rm Mpc}$ are displayed in the middle and right panels of the first row.
-%While the default choice of $s_{\rm max}=$ 40 $h^{-1}$Mpc gives the tightest constraint, 
-The three choices of $s_{\rm max}$ results more or less similar to the main results.
-
-\subsection{$Number\ of\ mocks\ for\ covariance\ estimation$}
-
-In this analysis we use a set of 72 mock surveys sampled from HR3 to compute the covariance matrix.
-We check whether the relative small number of mock surveys could produce significant bias in the derived cosmological constraint.
-
-We take half of the mock surveys to compute the covariance matrix;
-the result is presented in the second row of Figure \ref{fig_contour_RB}.
-Our main result from 72 mocks gives slightly tighter constraint and less noisy contours than the results from 36 mocks.
-The locations of contour center are similar, and statistically are quite close to each other.
-
-Using 36 mocks we must adopt $n_\mu\lesssim20$ for the binning of $\xi_{\Delta s}(\mu)$,
-so it is expected that the results are slightly weaker than the results of using 72 mocks (where we take $n_{\mu}\leq40$).
-
-We further take the 2,000 sets of MultiDark PATCHY mock catalogues \citep{MDPATCHY} to compute the covaraince matrix.
-%This set of mock surveys have been adopted for the error estimations of the 2pCF and power spectrum measurement of the BOSS galaxies \citep{Alam2016}.
-Following Hartlap et al. (2006) and Percival et al. (2014), we correct the covariance matrix
-for the statistical bias and scattering.
-The obtained results are consistent with the main results.
-The constrained area has a small extension in the upper-left corner, which will not affect the combined cosmological constraint.
-
-%The constraints while using 36 mocks for covariance matrix appears a little weaker.
-%The reason is that, the smaller number of mocks, the smaller number of binning allowed in the analysis. 
-%As discussed in Sec. \ref{sec:binningscheme}, in our main analysis we are able to use as much as 40 bins in the region $0.01\leq\mu\leq1$.
-%When using 36 mocks we limit the largest bin number to 20, which leads to slightly weaker constraint.
-
-\subsection{$Mock\ galaxies\ for\ systematic\ correction$}
-
-In the construction of HR4 mock galaxies \citep{hong2016}, 
-the J08 model \citep{jiang2008}, a model derived from cosmological simulations, 
-was adopted as the default option to calculate the merger timescale and to determine when a satellite galaxy is completely disrupted.
-
-\cite{hong2016} also considered four alternative models for the calculation of merger timescale:
-1) the LC93 model \citep{LC93} based on analytic calculation, 
-2) the B08 \citep{B08} and 3) the V13 \citep{V13} models based on isolated simulations,
-and 4) the M12 model \citep{M12} based on cosmological simulation.
-%Among the five merger timescale models, 
-%J08 was found to result in mock galaxies with properties and 2pCF best matching the observational data.
-Among the five merger timescale models, 
-J08 model produces mock galaxies having properties and 2pCF best agree with the observational data \citep{hong2016};
-%So it was adopted in our main analysis.with
-the LC93 model, having the shortest merger timescale among the five models,
-produces galaxies with properties and 2pCF most deviated from the observations.
-
-\begin{figure*}
-   \centering{
-   \includegraphics[width=16cm]{fig12.eps}
-   %\includegraphics[height=9cm]{Tpcf-sys.eps}
-   }
-   \caption{\label{fig_sys_LC93}
-   %Apparent distortion of objects in four wrongly assumed cosmologies, assuming a true cosmology of .
-   Systematics in $\delta \hat \xi_{\Delta s}$, measured from the HR4 mock galaxies
-   with the LC93 model adopted as the merger timescale model.
-   Compared with the main result using the merger timescale model J08 (Figure \ref{fig_sys}), 
-   there is a $\sim 25\%$ change in the amplitude of $\delta \hat \xi_{\Delta s}$.
-   % so the measured $\hat\xi_{\Delta s}(\mu)$ has larger (smaller) values at $\mu\rightarrow1$ ($\mu\rightarrow0$) 
-   % compared with the others.
-   %See Sec. \ref{sec:syscor} for details.
-   %The values are estimated from the HR4 mock galaxies. % and subtract its contribution.
-   }
-\end{figure*}
-
-%To check whether our result is sensitive to these merger timescale models,
-We adopt mock surveys created using the four alternative models to
-measure the systematic correction $\delta \hat\xi_{\Delta s, {\rm sys}}$
-and derive the cosmological constraints.
-The difference between the $\delta \hat\xi_{\Delta s, {\rm sys}}$ estimated from the J08 model and the other models is $5\%-25\%$.
-As an example, Figure \ref{fig_sys_LC93} presents the systematics correction estimated using LC93,
-which has a $\sim25\%$ difference from the J08 estimation.
-
-Nevertheless, Figure \ref{fig_contour_RB} shows that, 
-when the alternative models adopted, 
-the cosmological constraints are consistent with our main results;
-the discrepancy is $\lesssim0.3\sigma$.
-
-%In case of using the $z=0$ snapshot data rather than the lightcone galaxies to construct mock surveys,
-%we find the contour slightly shifted to the upper-left direction.
-%Statistically,
-
-%Also, the shifts of contours mainly happens along the upper-left to lower-right diagonal.
-%This means the joint constraint result, the constraint when combined with the other cosmological probes such as CMB, will not be very affected,
-%since the CMB contour basically lies in the lower-left to upper-right diagonal.
-
-\subsection{$Cut\ on\ \mu$}
-
-%We checked whether the result is sensitive to the range of angular bins.
-In our default options, we take $1 - \mu\ge0.01$.
-For comparison, Figure \ref{fig_contour_RB} presents the cosmological constraints using the limits 
-%0.02, 0.05, 0.07 and 0.1.
-0.02, 0.05 and 0.07. 
-A larger limit means we abandon more angular regions near the LOS.
-%That will make the result less affected by the factors such as fiber collision.
-We find that changing the cut has little effect on the cosmological constraints.
-%Even for the case of $1 - \mu\ge0.1$,
-%where 10\% of the angular region is dropped,
-%the constraints are still fully consistent with the main results.
-%This suggests that our main result is less affected by the fiber collision.
-
-This test suggests that our result is not affected by the fiber collisions and redshift failures.
-%In the observational data, these effects are taken into consideration by reweighting the nearest neighbor of the galaxy.
-%Also, we add the fiber collision effect when constructing mock surveys.
-If fiber collisions and redshift failures have any sizable effect,
-since they mainly affect the angular region close to LOS,
-one expects a systematic variation of the cosmological constraints when varying the limit on $1-\mu$.
-%Such a variation was not detected in this test.
-%so the fiber collision and redshift failure effects are certainly removed
-
-\subsection{$Different\ s_{\rm min}$}
-
-%\subsection{A2. Different $s_{\rm min}$}
-
-Among the different options, %affecting our cosmological constraint, 
-the one most likely to affect our results is $s_{\rm min}$.
-%the smallest scale that are taken into account in the analysis.
-%This is expectable. 
-The 2pCF has relatively large values on smaller scales
-%On small scales, the value of 2pCF is relatively large
-(e.g. for the CMASS galaxies $\xi\approx10,5,1,0.25,0.05$ at $s=2,4,10,20,40 h^{-1}{\rm Mpc}$).
-Varying $s_{\rm min}$ can dramatically change the value of $\xi_{\Delta s}(\mu)$,
-and thus is likely to have large effect on the result.
-
-A series of input-output tests are conducted to check whether the derived constraints depend on $s_{\rm min}$.
-The linear regression of the $\delta\hat\xi_{\Delta s}$ (of the observational sample) 
-measured in the WMAP5 cosmology ($\Omega_m=0.26$ $\Lambda$CDM) 
-is adopted as $\delta\xi_{\Delta s, \rm sys}$. 
-We then follow the procedures of Sec. \ref{sec:methodology} to derive cosmological constraint.
-%In that case we expect the WMAP5 cosmology being the best-fit.
-
-\begin{figure*}
-   \centering{
-   %\includegraphics[width=12cm]{Tpcf--contour-diffsmin-dashcontours.eps}}
-   \includegraphics[width=5.7cm]{fig13_0.eps}
-   \includegraphics[width=10cm]{fig13_1.eps}}
-   %\includegraphics[width=5.9cm]{Tpcf--contour-nummock-36.eps}}
-   \caption{ \label{fig_contour_diffsmin} 
-   Left panel: The input-output test in case of using our default options.
-   The derived cosmological constraints are fully consistent with the input WMAP5 cosmology (marked by green plus).
-   Right panels: Likelihood contours (68\%, 95.4\%) in the $\Omega_m$-$w$ plane for using $s_{\rm min}=2,4,6,8\ h^{-1} {\rm Mpc}$.
-   Gray filled contours are cosmological constraints derived using our AP analysis.
-%    From the input-output test we find $s_{\rm min}$
-   %For $s_{\rm min}=2,4,8\ h^{-1}{\rm Mpc}$, some correction of the likelihood map was made based on the result of their input-output tests.
-   %After the correction they are close to the result using the default option $s_{\rm min}=6h^{-1}\rm Mpc$.
-   For $s_{\rm min}=2,4h^{-1}{\rm Mpc}$, the contours are shifted to the upper-left corner, 
-   but the deviation from the $s_{\rm min}=6h^{-1}{\rm Mpc}$ is $\lesssim1\sigma$.
-   The black solid contour lines show the constraint when combined with CMB+BAO+JLA+$H_0$.
-   %The dashed contour lines show the combined constraints in case of no correction made for $s_{\rm min}=2,4,8\ h^{-1}{\rm Mpc}$. 
-   The combined result is rather insensitive to choices of $s_{\rm min}$.}
-\end{figure*}
-
-When adopting $s_{\rm min}=6\ h^{-1}{\rm Mpc}$, the best-fit cosmology is exactly what we expect: the WMAP5 cosmology, 
-i.e. the input cosmology is successfully recovered (left panel of Figure \ref{fig_contour_diffsmin}).
-So $s_{\rm min}=6\ h^{-1}{\rm Mpc}$ is adopted as the default option in our analysis.
-%When adopting different a $s_{\rm min}$ of $2,4,8\ h^{-1}{\rm Mpc}$, 
-Other values of $s_{\rm min}$ do not recover the input cosmology as well as $s_{\rm min}=6h^{-1}{\rm Mpc}$.
-%the derived best-fit cosmology can deviate with the input cosmology at $1-2\sigma$.
-%This means that there exists a systematics bias in the cosmological constraints derived using these $s_{\rm min}$.
-%Therefore, when using $s_{\rm min}=$2,4,8 $h^{-1}{\rm Mpc}$, 
-%Similar phenomenon happens when we adopt several different cosmologies ranging from $\Omega_m=0.2-0.4$, 
-%\footnote{The reason that why these $s_{\rm min}$ some cosmologies achieve a larger likelihood value than the input cosmology is not very clear. 
-%It could be just due to statistical fluctuation, or some inaccuracy in our simple likelihood estimation.
-%We believe that the issue can be resolved in case of using the redshift evolution of the 2D likelihood map.
-%e.g. the covariance .
-%In our likelihood analysis the covariance matrix is estimated in the WMAP5 cosmology and applied to the whole parameter space.
-%That is not very precise since the covariance matrix certainly depends on the values of $(\Omega_m,w)$.
-%Possibly for some sets of parameters the covariance is relatively smaller, 
-%so there the likelihood is {\it overestimated} if still adopting the covariance of WMAP5 cosmology,
-%making them appears more preferred in the sense of our likelihood analysis.
- %for $s_{\rm min}=2,4,8\ h^{-1}{\rm Mpc}$.
-
-%So it is not plausible to use these $s_{\rm min}$ values in the analysis,
-%if the underlying systematics not properly corrected.
-
-The cosmological constraints obtained using $s_{\rm min}=2,4,6,8\ h^{-1} {\rm Mpc}$ 
-are presented in the right panel of Figure \ref{fig_contour_diffsmin}.
-In the case of $s_{\rm min}\neq6h^{-1} {\rm Mpc}$, we apply a simple correction to the derived likelihood map, 
-based on the discrepancy between the best-fit cosmology and the input cosmology found in the input-output test.
-
-%Here the gray filled contours are constraints from our AP analysis.
-These contours are consistent with each other within 1$\sigma$.
-The $s_{\rm min}=8\ h^{-1}{\rm Mpc}$ result is very close to the main result.
-The $s_{\rm min}=2$ or $4\ h^{-1}{\rm Mpc}$ contours show a systematical shift to the upper-left corner,
-but the deviation is $\lesssim1\sigma$.
-%we find the systematics mainly shifts the position contour along the 
-%upper-left to lower-right diagonal.
-The difference choices of $s_{\rm min}$ produce little effect on 
-the joint constraint when combined with other cosmological probes (CMB+BAO+JLA+$H_0$). 
-%To check that, we plot the joint constraints when our method combined with .
-The difference from the main results is $\lesssim0.3\sigma$.
-%Actually, even without applying the correction, 
-%the combined constraints of $s_{\rm min}=2,4,8\ h^{-1} {\rm Mpc}$ are still very close to the $s_{\rm min}=6h^{-1}{\rm Mpc}$ result,
-%with a difference $\lesssim0.6\sigma$ (dashed contour lines).
-
-%In our main analysis we adopt $s_{\rm min}=6 h^{-1}{\rm Mpc}$, which is found to have almost no systematic deviation in the input-output tests.
-%The dependence on $s_{\rm min}$ is understandable since the small scale $\xi$ is the dominate contributor in the integration.
-%This issue could be resolved if using the 2D $\xi$ to conduce the analysis.
-
-\subsection{$Summary$}
-
-%We conduct a series of tests to check whether the derived cosmological constraints are sensitive to the options adopted in the likelihood analysis.
-%For the default options used to derive our main result, 
-%we adopt $s_{\rm min}=6h^{-1}{\rm Mpc}$, $s_{\rm max}=40h^{-1}{\rm Mpc}$, $1 - \mu \ge 0.01$,
-%the 72 sets of HR3 PSB mocks for covariance estimation,
-%and J08 merger timescale model (used in the construction of HR4 mock galaxies).
-
-We conduct a series of tests and find that the derived cosmological constraints are insensitive to the options adopted in the analysis.
-Cosmological constraints are derived using different options of $s_{\rm min}$, $s_{\rm max}$, limits on $1-\mu$, number of mocks for covariance estimation,
-and satellite galaxy merger time scale.
-We do not detect a significant change of our results.
-
-%We modify the above options, 
-%derive the corresponding cosmological constraints, 
-%and check how much it deviates from the result using default options
-%In all tests conducted, we do not detect a change in cosmological constraint which is statistically significant.
-%In most cases, the shift of the contour is $\lesssim0.2\sigma$.
-%Also, we find the shift only happens along the upper-left to lower-right diagonal of the $\Omega_m$-$w$ plane,
-%making the joint constraint (the result when combined with the other cosmological probes) rather stable.
-
-%Among these options, $s_{\rm min}$ is the only one found to have a relative large effect on the result.
-%We performed a series of input-output tests, 
-%and found using $s_{\rm min}=6h^{-1}{\rm Mpc}$ can lead to unbiased cosmological constraint.
-%In case of using $s_{\rm min}=2,4,8\ h^{-1}{\rm Mpc}$, 
-%a correction should be made to account for the bias in the derived likelihood map.
-%In our main analysis, we adopt $s_{\rm min}=6h^{-1}{\rm Mpc}$, and no such correction is needed.
-
-Yet there are still unchecked options. 
-One example is the redshift binning scheme.
-In this analysis, the galaxies are split into six redshift bins of
-$0.150<z_1<0.274<z_2<0.351<z_3<0.430<z_4<0.511<z_5<0.572<z_6<0.693$.
-%and investigate the redshift evolution of the 2pCFs measured in these redshift bins.
-We have not checked whether the results depend on choices such as the redshift limits and the number of redshift bins,
-because each binning scheme requires to repeat the whole analysis that involves the calculation of the correlation function 
-at each point of the parameter space.
-This issue is worthy investigation in future studies, 
-to design a optimized scheme having the maximal ability to constrain cosmological parameters.
-%We did not check whether our result different redshift limits
-
-In summary, the tests show that, the cosmological constraints reported in this paper are quite robust.
-
-%In all, %the options adopted in our main analysis are all based on cautious considerations and careful tests.
-%After a series of robustness tests, we find our result relatively insensitive to their values.
-%Furthermore, through the input-output test we find the default options adopted in the main analysis is able to derive unbiased cosmological constraint.
-%We conclude that, the cosmological constraint reported in this paper is fairly robust.
-
-\
-
-\
 

### 2016-08-18 draft/gal2pcf.tex
updates

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{color}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage[T1]{fontenc}
\usepackage{aecompl}

\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$~}\fi}} 
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title[Constraints using the Alcock-Paczynski effect]{Cosmological constraints from the redshift dependence of the Alcock-Paczynski test and volume effect: galaxy two-point correlation function}

\author[Xiao-Dong~Li, Changbom~Park, Cristiano G. Sabiu and Juhan Kim]
{ Xiao-Dong Li$^{\dagger}$, Changbom Park$^{1}$, Cristiano G. Sabiu$^{2,1,\star}$, Juhan Kim$^{3,1}$\\
$^1$School of Physics, Korea Institute for Advanced Study, 85 Heogi-ro, Dongdaemun-gu, Seoul 130-722, Korea\\
$^2$Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 305-348, Korea\\
$^3$Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea\\
$^{\dagger}$xiaodongli@kias.re.kr\\
$\star$Corresponding Author: csabiu@kasi.re.kr}

%\date{Accepted 1988 December 15. Received 1988 December 14; in original form 1988 October 11}

% \begin{keywords}
% methods: data analysis -- methods: statistical -- Galaxies:
% kinematics and dynamics -- Cosmology: observations -- large-scale
% structure of universe
% \end{keywords}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2002}

\maketitle

\label{firstpage}

\begin{abstract}
We propose a method using the redshift dependence of the Alcock-Paczynski (AP) test and volume effect to measure the cosmic expansion history.
The galaxy two-point correlation function as a function of angle, $\xi(\mu)$, is measured at different redshifts.
Assuming an incorrect cosmological model to convert galaxy redshifts to distances,
the shape of $\xi(\mu)$ appears anisotropic due to the AP effect,
and the amplitude shifted by the change in comoving volume.
Due to the redshift dependence of the AP and volume effect,
both the shape and amplitude of $\xi(\mu)$ exhibit redshift dependence.
Similar to \cite{Li2014}, we find the redshift-space distortions (RSD) caused by galaxy peculiar velocities,
although significantly distorts $\xi(\mu)$,
exhibit much less redshift evolution compared to the AP and volume effects.
By focusing on the redshift dependence of $\xi(\mu)$,
we can correctly recover the cosmological parameters despite the contamination of RSD.
The method is tested by using the Horizon Run 3 N-body simulation,
from which we made a series of $1/8$-sky mock surveys
having 8 million physically self-bound halos and sampled to have roughly a uniform number density in $z=0-1.5$.
We find the AP effect results in tight, unbiased constraints on the density parameter and dark energy equation of state,
with 68.3\% CL intervals $\delta \Omega_m\sim0.03$ and $\delta w\sim0.1$,
and the volume effect leads to much tighter constraints of $\delta \Omega_m\sim0.007$ and $\delta w\sim0.035$.
\end{abstract}

% \begin{keywords}
% circumstellar matter -- infrared: stars.
% \end{keywords}

\section{Introduction}

Since the discovery of cosmic acceleration \citep{Riess1998,Perl1999}, 
there have been many models proposed to explain it. These include modifications to general relativity (GR) 
and additional energy components to the constituents of the Universe. 
The simplest and currently favored solution is the additional field called dark energy which has negative pressure and is spatially homogeneous.
%The simplest explanation for dark energy is that it is a cosmological constant or vacuum energy, with constant equation of state (EoS) $w = -1$.

To understand the nature of dark energy, 
we need to make precise measurements of the cosmic expansion history using cosmological observables. 
Two such observables are the angular diameter distance $D_A$ and the Hubble factor, $H$. 
If these can be measured at various redshifts, then tight constraints can be placed on the parameters of the cosmological model,
e.g., the matter density $\Omega_m$ and the equation of state (EoS) of dark energy, $w$.

Assuming an incorrect cosmological model for the coordinate transformation from redshift space to comoving space leaves residual geometric distortions. 
These distortion, known as the redshift-space distortions (RSD), are induced by the fact that distances along and perpendicular to the line of sight are fundamentally different.
Measuring the ratio of galaxy clustering in the radial and transverse directions, provides a probe of the Alcock-Paczynski (AP) effect \citep{AP1979}.

There have been several methods proposed that apply the AP test to the large scale structure
by measuring the clustering of galaxies \citep{Ballinger1996,Matsubara1996},
symmetry properties of galaxy pairs \citep{Marinoni2010,Jennings2011,BB2012}, 
and cosmic voids \citep{Ryden1995,LavausWandelt1995,Sutter2014}.
Among them, the method of galaxy clustering has been widely used to constrain cosmological parameters 
\citep{Outram2004,Blake2011,ChuangWang2012,Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, Jeong2014,2014ApJ...781...96L}.

%However, one advantage of our analysis is that it is significantly model independent and does not assuming LCDM or any other dark energy model.
%Instead we directly fit for the angular distance $D_A$, Hubble parameter $H$.
The main caveat of this method is that, because the radial distances of galaxies are inferred from redshifts, 
AP tests are inevitably limited by RSD,
which leads to apparent anisotropy even if the adopted cosmology is correct \citep{Ballinger1996}.
%This effect must be then accurately modeled for the 2-point statistics of galaxy clustering.
%To avoid the contamination induced by RSD,
In \cite{Li2014} we proposed a new method utilizing the redshift dependence of AP effect to overcome the RSD problem, 
which uses the isotropy of the galaxy density gradient field. 
We found that the redshift dependence of the anisotropy created by RSD is much less significant compared with the anisotropy caused by AP.
Thus we focused on the redshift dependence of the galaxy density gradient field,
which is less affected by RSD, but still sensitive to cosmological parameters.

The two-point correlation analysis is the most widely used method to study the large scale clusterings of galaxies.
So, in this paper we revisit the topic of \cite{Li2014} using the galaxy two-point correlation function (2pCF).
By investigating the redshift dependence of anisotropic galaxy clustering we can measure the AP effect despite of contamination from RSD.
Moreover, when the redshift evolution of galaxy bias can be reliably modelled,
we can measure the redshift evolution of volume effect from the amplitude of 2pCF.
%Except the AP distortion of the shapes of structures, 
The change of the comoving volume size is another consequence of a wrongly adopted cosmology,
which has motivated methods constraining cosmological parameters from number counting of 
galaxy clusters \citep{PS1974,VL1996} and topology \citep{topology}.

The outline of this paper proceeds as follows. 
In \S 2 we briefly review the nature and consequences of the AP effect and volume changes when performing coordinate transforms in a cosmological context. 
In \S 3 we describe the N-body simulations and mock galaxy catalogues that are used to test our methodology.
In \S 4 and \S 5, we describe our new analysis method for quantifying the anisotropic clustering as well as proposing a way to deal with the RSD that are convolved with the AP distortion. 
Here we also present results of our optimised estimator. 
We conclude in \S 6.

% The Alcock-Paczynski (AP) test \citep{AP1979} is a pure geometric probe of the cosmic expansion history
% based on comparison of observed tangential and radial dimensions of objects
% which are known to be isotropic.
% There are a few methods proposed to apply the AP test for cosmological purposes.
% The most widely adopted one is the method using anisotropic clustering \citep{Ballinger1996,Matsubara1996},
% which has been used for the 2-degree Field Quasar Survey \citep{Outram2004},
% the WiggleZ dark energy survey \citep{Blake2011}, the SDSS-II LRG survey \citep{ChuangWang2012},
% and the SDSS-III Baryon Oscillation Spectroscopic Survey (BOSS) \citep{Reid2012,Corredoira2013,Anderson2013,Beutler2013,Chuang2013,Sanchez2013,Linder2013,Samushia2014}.
% The main caveat of this method is that,
% because the radial distances of galaxies are inferred from redshifts,
% AP tests are inevitably limited by redshift-space-distortions (RSD) \citep{Ballinger1996},
% which leads to apparent anisotropy even if the adopted cosmology is correct.
% This effect must be then accurately modeled for the 2-point statistics of galaxy clustering.

% A second interesting approach measures the symmetry properties of galaxy pairs \citep{Marinoni2010}.
% Unfortunately this method is also seriously limited by peculiar velocities.
% The RSD effect in the apparent tilt angles of galaxy pairs is found to be dependent on both redshift and underlying cosmology,
% making it difficult to model accurately \citep{Jennings2011}.
% \cite{Ryden1995} and \cite{LavausWandelt1995} proposed another method using the apparent stretching of voids.
% It has the advantage that the void regions are easier to model compared with high density regions.
% But this method also has limitations in that it utilizes only low density regions of the large scale structure
% and requires much larger samples compared to other methods.

% In this paper we propose a new method that overcomes these limitations.
% It uses the distortion in the apparent density gradient field constructed from galaxy distribution.
% The density gradient vectors are expected to be isotropic if the correct cosmology is adopted,
% while an anisotropic distribution implies a wrongly assumed cosmology.
% Similar to the 2-point statistics, this method is also based on the distribution of galaxies.
% But our method samples the density gradient vectors uniformly within the survey volume,
% and thus the high and low density regions are equally utilized.
% %\footnote{This ``balance'' will is broken when we try to suppress RSD
% %by skipping some high density regions.}.
% In contrast, methods of 2-point statistics and galaxy pairs assign more weights to the high density regions,
% while the void method utilizes low density regions only.
% 
% The observed density gradient field is also affected by RSD,
% which perturbs galaxy positions along the line of sight (LOS) and produce spurious gradients.
% However, we find that these anisotropies can be distinguished from those induced by wrongly assumed cosmological parameters
% by looking at the redshift dependence of the anisotropies.
% We conduct a proof-of-concept test of our method on the Horizon Run 3 (HR3) mock surveys.% to derive constraints on the cosmological parameters.

% anisotropy in the gradient field  induced by peculiar
%velocities has a uniform amplitude at all redshifts,
%so RSD can be distinguished from AP by measuring the
%{\it redshift dependence} of the anisotropy.
%We Test the method on the Horizon Run 3 (HR3) mock surveys, which are simulated for BOSS.
%We find that, by using 2.4 million galaxies in the redshift range 0.18-0.6,

%we find the errors of inferred cosmological parameters,
%induced by the RSD effect, is $\lesssim$1$\sigma$.
%With the help of perturbation theory,
%this acceptable error can be further reduced
%by correcting the galaxy positions before the construction of the gradient field.
% Using a sample of about 2.4 million galaxies,
% the method leads to constraints on $\Omega_m$ and $w$,
% up to errors of $0.07$ and $0.3$ (68.3\% CL), respectively.

\section{AP and Volume Effect in Wrongly Assumed Cosmologies}
\label{sec:APeffect}

\begin{figure*}
   \centering{
   \includegraphics[height=6cm]{Tpcf--xy.eps}
   \includegraphics[height=6cm]{Tpcf--quan.eps}
   %\includegraphics[height=7cm]{FVol.eps}
   %\includegraphics[height=8cm]{xy.eps}
   %\includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_xy}
   %Apparent distortion of objects in four wrongly assumed cosmologies, assuming a true cosmology of .
   The redshift dependence of AP and volume effect in two wrongly assumed cosmologies $\Omega_m=0.41$, $w=-1.3$ and $\Omega_m=0.11$, $w=-0.7$,
   assuming a true cosmology of $\Omega_m=0.26$, $w=-1$.
   Upper panel shows the apparent distortion of four perfect squares,
   measured by an observer located at the origin.
   The apparently distorted shapes are plotted in red solid lines.
   The underlying true shapes are plotted in blue dashed lines.
   Lower panel shows the evolution of Equations (\ref{eq:stretch}) and (\ref{eq:volume}).
   In our mock surveys we split the samples at $z=0.3$, 0.6, 0.9 and 1.2, as marked by the vertical lines.
   %measured by an observer located at the origin.
   %For reference, blue dashed squares show their shapes and positions in the true cosmology.
   }
\end{figure*}

%Considering we are Let us consider an object in the universe with certain size and shape.
%Its observed redshift span $\Delta z$ and angular size $\Delta \theta$ are related with the comoving sizes by
In this section we briefly introduce the AP and volume effect in wrongly assumed cosmologies.
A more detailed description of the AP effect has been provided in \cite{Li2014}.

Suppose that we are probing the shape and volume of an object in the Universe.
We measure its redshift span $\Delta z$ and angular size $\Delta \theta$,
then compute its sizes in the radial and transverse directions from the relations of 
\begin{equation}\label{eq:distance}
\Delta r_{\parallel} = \frac{c}{H(z)}\Delta z,\ \ \Delta r_{\bot}=(1+z)D_A(z)\Delta \theta,
\end{equation}
where $H$ is the Hubble parameter, $D_A$ is the angular diameter distance.
In the particular case of a flat universe with constant dark energy EoS, they take the forms of
\begin{eqnarray}\label{eq:HDA}
& &H(z) = H_0\sqrt{\Omega_ma^{-3}+(1-\Omega_m)a^{-3(1+w)}},\nonumber\\
& &D_A(z) = \frac{1}{1+z}r(z)=\frac{1}{1+z}\int_0^z \frac{dz^\prime}{H(z^\prime)},
\end{eqnarray}
where $a=1/(1+z)$ is the cosmic scale factor,
$H_0$ is the present value of Hubble parameter and $r(z)$ is the comoving distance.

In case we adopted a wrong set of cosmological parameters in Equation (\ref{eq:distance},\ref{eq:HDA}),
the inferred $\Delta r_{\parallel}$ and $\Delta r_{\bot}$ are wrong,
resulting in distorted shape (AP effect) and wrongly estimated volume (volume effect).
The degree of variations in shape and volume can be described by the following quantities
\begin{equation}\label{eq:stretch}
 %{\rm Degree\ of\ LOS\ stretch\equiv}
 %{\rm rat}_{\rm LOS\ stretch}\equiv
 \frac{[\Delta r_{\parallel}/\Delta r_{\perp}]_{\rm wrong}}{[\Delta r_{\parallel}/\Delta r_{\perp}]_{\rm true}} =
  \frac{[D_A(z)H(z)]_{\rm true}}{[D_A(z)H(z)]_{\rm wrong}} 
\end{equation}
\begin{equation}\label{eq:volume}
 %{\rm Degree\ of\ volume\ magnification \equiv}
 %{\rm rat}_{\rm volume\ mag}\equiv
 \frac{[\Delta r_{\parallel}(\Delta r_{\perp})^{2}]_{\rm wrong}}{[\Delta r_{\parallel}(\Delta r_{\perp})^{2}]_{\rm true}}
 = \frac{{\rm Volume}_{\rm wrong}}{{\rm Volume}_{\rm true}}
 = \frac{[D_A(z)^2/H(z)]_{\rm wrong}}{[D_A(z)^2 / H(z)]_{\rm true}},
\end{equation}
where ``true'' and ``wrong'' denote the values of quantities in the true cosmology and wrongly assumed cosmology.
From the AP and volume effects, we can constrain  $D_A(z)H(z)$ and $D_A(z)^2 / H(z)$, respectively.

The AP and volume effect due to wrongly assumed cosmological parameters are shown in the upper panel of Figure \ref{fig_xy}.
Suppose that the true cosmology is a flat $\Lambda$CDM with present density parameter $\Omega_m=0.26$
and standard dark energy EoS $w=-1$.
If we were to distribute four perfect squares at various distances from 500 Mpc/h to 3,000 Mpc/h,
and an observer located at the origin were to measure their redshifts and compute their positions and shapes 
using redshift-distance relations of two incorrect cosmologies:
\begin{enumerate}
 \item $\Omega_m=0.41$, $w=-1.3$,
 \item $\Omega_m=0.11$, $w=-0.7$,
\end{enumerate}
the shapes of the squares appear distorted (AP effect),
and their volumes are changed (volume effect).
In the cosmological model (ii) with $\Omega_m=0.11$, $w=-0.7$, we see a stretch of the shape in the line of sight (LOS) direction (hereafter ``LOS shape stretch'')
and magnification of the volume (hereafter ``volume magnification''), 
while in the model with $\Omega_m=0.41$, $w=-1.3$, we see opposite effects of LOS shape compression and volume shrinkage.

In the lower panel of Figure \ref{fig_xy}, we plot the degree of variations in shape and volume as functions of redshift. 
In cosmology (i), both quantities have values less than 1, 
indicating LOS shape compression and volume shrink.
The effect in cosmology (ii) is slightly more subtle. At low redshift, the effect of dark energy is important, 
and there is LOS shape compression and volume reduction due to the quintessence like dark energy EoS.
However, at higher redshift the role of dark matter is more important, and we see LOS shape stretch and volume magnification due to the small $\Omega_m$.

More importantly, Figure \ref{fig_xy} highlights the redshift dependence of the AP and volume effects. 
For example, in the cosmology with $\Omega_m=0.41$, $w=-1.3$, 
both the LOS shape stretch and volume magnification become more significant with increasing redshift.
In the cosmology with $\Omega_m=0.11$, $w=-0.7$,
not only do the magnitudes of the effects evolve with redshift,
but there is also a turnover from LOS shape compression and volume shrink at lower redshift to LOS shape stretch and volume magnification at higher redshift.

\section{Mock Data}
\label{sec:mocks}
We test the methodology using mock surveys constructed from one of the Horizon Run simulations, HR3.
The Horizon Run simulations are a suite of large volume N-body simulations that have resolutions and volumes capable of reproducing the observational statistics of many current major redshift surveys like the Sloan Digital Sky Survey's (SDSS) Baryon Oscillation Spectroscopic Survey (BOSS) etc \citep{park 2005,2009ApJ...701.1547K,horizonrun}.
HR3 adopts a flat-space $\Lambda$CDM cosmology with the WMAP 5 year parameters
$\Omega_{m}=0.26$, $H_{0}=72{\rm km/s/Mpc}$, $n_{s}=0.96$ and $\sigma_8=0.79$ \citep[]{komatsu 2011}.
The simulation was made in a cube of volume $(10.815 {~ h^{-1}} {\rm{Gpc}})^3$
using $7120^3$ particles with particle mass of $1.25\times 10^{11}$\hMsun.

The simulations were integrated from $z=27$ and reached $z=0$ after making $N_{\rm step}=600$ timesteps.
Dark matter halos were identified using the Friend-of-Friend algorithm with the linking length of 0.2 times the mean particle separation.
Then the physically self-bound (PSB) subhalos that are gravitationally self-bound and tidally stable are identified \citep{kim and park 2006}.
The PSB halo finder is a group finding algorithm which can efficiently identify halos located even in crowded regions. 
This method combines two physical criteria such as the tidal radius of a halo and the total energy of each particle to find member particles.
%This provides a substantial increase in the similarity between simulation and observational data,
%as these dark matter subhalos are sites for galaxy formation.
%LRG (Xiao: is it OK to change all the ``LRG'' to ``galaxy''?) formation.
%To simulate the SDSS survey,
%HR3 places 27 observers evenly within its cubical volume and allows
%each observer to see out to a redshift of 0.7, creating 27
%independent, non-overlapping spherical regions.

An all-sky, very deep light cone survey reaching redshift $z=4.3$ was made by placing an observer located at the center of the box.
The comoving positions and velocities of all CDM particles are saved as they cross the past light cone
and PSB subhalos are identified from this particle data.

To match the observations of recent LRG surveys \citep{gott 2008, gott 2009, choi 2010},
a volume-limited sample of halos with constant number density of $3 \times 10^{-4} (h^{-1}{\rm Mpc})^{-3}$
is selected by imposing a minimum halo mass limit varying along with redshift, 
from $6\times 10^{12}$\hMsun at high redshift to $1.5\times 10^{13}$\hMsun at low redshift.
To do this, the whole sample is split into many thin shells whose radial spans are 30 Mpc/h. 
In each shell, a minimal mass cut is set such that the number density is $\bar n=3\times10^{-4}(h^{-1}{\rm Mpc})^{-3}$. 
These thin shells are then merged together to build up the whole sample. 
Note that all these steps are done before converting the sample to other cosmologies, so the constant number density of halos is only true in the correct cosmology.
%The light cone survey sample consists of subhalos at different redshifts, 
%and thus their redshift dependence on velocities and evolution of clustering are automatically included. 
%The peculiar velocity of the subhalo is set to that of the most-bound particle in that subhalo.
The group velocity of each PSB dark matter halo (or our mock ``galaxy'') 
is used to perturb the redshift of the halo by 
\begin{equation}
\Delta z = (1+z) \frac{v_{{\rm LOS}}}{c},
\end{equation}
where $v_{\rm LOS}$ is the LOS component of the halo proper velocity.

We divide the all-sky survey sample into eight equal sky area subsamples and impose the redshift range $z=0-1.5$. 
This mock data will be relevant for future galaxy spectroscopic surveys \citep[e.g. DESI ][]{2013arXiv1308.0847L}.

% The incorporation of RSD is a crucial point of this method.
% The redshift evolution of RSD effect may depend on the halo finder, the definition of halo velocities, 
% and the properties of the sample (e.g., number density, mass cut). 
% Investigation of these issues are helpful to improve our method.
%We further impose a minimal distance cut of $r>500$ Mpc/h (or equivalently $z>0.17$),
%which is equal to that of the BOSS LOWZ sample. The BOSS LOWZ sample is usually restricted to
%$z>0.15$ where the galaxy number density is more or less uniform \citep{Tojeiro2011,Tojeiro2012,Parejko2013}.
%since low redshift galaxies carry little cosmological information while their positions are severely distorted by RSD.

\section{Methodology}

We probe the effects discussed in \S\ref{sec:APeffect} using the 2pCF. The 2pCF is a mature statistic in cosmology and its optimal estimation considers minimal variance while dealing with complicated masks and selection functions. The most commonly adopted formulation is that of the Landy-Szalay 
estimator~\citep{1993ApJ...412...64L},
\begin{equation}
\xi(s,\mu)=\frac{DD-2DR+RR}{RR}\ ,
\end{equation}
where $DD$ is the number of galaxy--galaxy pairs, $DR$ the number of galaxy-random pairs, and $RR$ is the number of random--random pairs, all separated by a distance defined by 
$s\pm\Delta s$ and $\mu\pm\Delta\mu$, where $s$ is the distance between the pair and $\mu=\cos(\theta)$, with $\theta$ being the angle between the line joining the pair of galaxies and the LOS direction. This statistic therefore captures the radial anisotropy of the clustering signal.

The random point catalogue constitutes an unclustered but observationally representative sample of our mock surveys. 
To reduce the statistical variance of the estimator we use 15 times as many randoms as we have galaxies.

\begin{figure*}
   \centering{
  % \includegraphics[height=4.5cm]{Tpcf--xy.eps}
  \includegraphics[height=11cm]{Tpcf--Scatter.eps}
  }
  \caption{\label{fig_Scatter}
  The influence of the AP and volume effect on the 2pCF statistics, in the wrongly assumed cosmology $\Omega_m=0.41$, $w=-1.3$.
  Scatter points are a 200 Mpc/h $\times$ 200 Mpc/h slice of halos drawn from HR3, with thickness 10 Mpc/h and mean redshift $z=0.43$.
  Their positions are measured by an observer located at the origin, with the LOS direction marked by the green arrow.
  Blue empty circles are their true positions in the correct cosmology, 
  while red filled circles are the apparent positions in the wrong cosmology.
  Blue solid circles are the ``2-point CF rings'' (i.e. the geometrical bins used to evaluate the clustering) 
  with radii 6 and 50 Mpc/h, centered on a galaxy with location $x,y$=1200 Mpc/h.
  Red solid circles are the ``exactly mapped'' rings (bins) in the incorrect cosmology, with its size shrunk and shape distorted.
  Black dashed circles are the actually adopted rings when we measure the 2pCF in the wrong cosmology.
  We expect the result of 2pCF statistics to be affected in three ways.
  First, the shape of structures should appear compressed in the radial direction, introducing anisotropy in $\xi$.
  Secondly, the sizes of structures should appear shrunk due to the volume effect, which shifts the amplitude of $\xi$ .
  Finally, as another consequence of volume effect, structures on larger scales enter the statistics.
  For example, halos within blue solid box are not considered in the correct cosmology,
   but will be considered in the wrong cosmology, as shown by the black dashed box.
   This also shifts the amplitude of $\xi$.
  }
\end{figure*}

To probe the anisotropy, $\xi$ is measured at different directions, 
%In each direction, $\xi(s,\mu_i)$ is measured as a function of scale $s$,
and integrated over the interval $\Delta s = s_{\rm max} - s_{\rm min}$.
We evaluate
\begin{equation}
\xi_{\Delta s} (\mu) \equiv \int_{s_{\rm min}}^{s_{\rm max}} \xi (s,\mu)\ ds.%,\ \ \ {\rm at\ particular\ binned\ direction\ }\mu_i
\end{equation}
%We choose $s_{min}=10$ Mpc/h, $s_{max}=70$ Mpc/h.
We limit the integral at both small and large scales.
At small scales the shape of $\xi_{\Delta s}(\mu)$ is seriously distorted by the finger of god (FoG) effect \citep{FoG}, 
and the distortion is more significant at lower redshift where structure undergoes more non-linear growth.
This introduces redshift evolution in $\xi_{\Delta s}(\mu)$ which is rather difficult to model.
As will be mentioned in \S 5, since FoG is particularly strong near the LOS direction,
in our analysis we also impose a cut $\mu>0.1$ to further suppress its contamination.
At large scales the measurement is dominated by noise due to poor statistics.
We find $s_{\rm min}=6-10$ Mpc/h and $s_{\rm max}=40-70$ Mpc/h are reasonable regions which can provide consistent results of 2pCF 
and tight, unbiased constraints on cosmological parameters.
In our analysis we choose $s_{\rm min}=6$ Mpc/h and $s_{\rm max}=50$ Mpc/h.

As an example Figure \ref{fig_Scatter} shows how the 2pCF is affected by AP and volume effects in the $\Omega_m=0.41$, $w=-1.3$ cosmology.
In choosing incorrect cosmological parameters, we expect the 2pCF to be influenced in three ways.
First, as a result of the AP effect, structures appear compressed in the radial direction.
This induces a nonuniform  variation in $\xi_{\Delta s}(\mu)$ as a function of angle.
Second, as a result of the volume effect, the sizes of structures shrink.
For example, a structure whose original size is $s_0=50$ Mpc/h will show up with a size $s_1<50$ Mpc/h.
As a result, the amplitude of $\xi_{\Delta s}(\mu)$ changes.
Finally, as another consequence of the volume effect, in the wrong cosmology structures on larger scales enter the statistics.
For example, halos within the blue solid box are not considered in the correct cosmology,
but they are taken into consideration in the wrong cosmology, as shown by the black dashed box.
This also results in a change in the amplitude of $\xi_{\Delta s}(\mu)$ since the binning in $s,\mu$-space will be 
inconsistent between different cosmological models. The combined effects of choosing an incorrect cosmology 
on shear and volume have been noted by \citet{topology}, who used the volume effects measured by the genus 
statistic to constrain the expansion history of the Universe.

% Note that the influence of volume effect can be more complicated with existence of AP or RSD effect.
% In that case, the volume effect may introduce extra anisotropy in the 2-point CF
% \footnote{
% At the radial and angular directions we have
% %\begin{equation}
% $Q_{\parallel} = \int_{s_{\rm min}}^{s_{\rm max}} ds\ \xi_{\parallel} (s),\ \ Q_{\perp} = \int_{s_{\rm min}}^{s_{\rm max}} ds\ \xi_{\perp} (s).$
% %\end{equation}
% Suppose the volume effect magnifies the length scale by a factor of $\tau$, i.e., 
% %\begin{equation}
% $s\rightarrow s^\prime= \tau s,\ $
% %\end{equation}
% This changes $\xi$ through a relation
% %\begin{equation}
% $\xi_\parallel(s) \rightarrow \xi^\prime_\parallel(s) = f_\parallel(\tau)\xi(s),
% \ \xi_\perp(s) \rightarrow \xi^\prime_\perp(s) = f_\perp(\tau)\xi(s).$
% %\end{equation}
% In the case that $f_\parallel(\tau) \neq f_\perp(\tau)$, 
% not only the values of $Q_{\parallel}$, $Q_{\perp}$ are changed,
% but also the relative ratio $Q_{\perp}/Q_{\parallel}$ is changed.
% This results in the extra anisotropy in the 2-point CF.
% In the case of no ARSD effect, we have $f_\parallel(\tau)=f_\perp(\tau) $ since $\xi$ is isotropic,
% but that is not guaranteed when there is RSD effect.
% }

%When measure $\int_{s_{\rm min}}^{s_{\rm max}} \xi (s,\mu_i)$ at different $\mu$ bins,
%not only the amplitude changes, but also the shape may change due to the anisotropic

%In the upper panel of Figure \ref{}

%RSD will affect $\xi$, but the redshift dependence is small.
%{\it (put some formular)}
%We need to test that on simulations.

\section{Result}

%\subsection{Some Plottings, Discussions, Definition of $\chi^2$, ...}

%{\bf Figure: $\xi$ curves, in different cosmologies, without and with RSD}

\begin{figure*}
   \centering{
   \includegraphics[height=8cm]{Tpcf--plot--UnNorm.eps}
   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_TpCF}
   The 2pCF measured in four redshift bins, in the correct cosmology (left) and two wrongly assumed cosmologies (middle: $\Omega_m=0.11$, $w=-0.7$; 
   right: $\Omega_m=0.41$, $w=-1.3$). The clustering signal is measured as a function of $1-\mu$, where $\mu=\cos(\theta)$ and $\theta$ is the angle between the LOS and the vector joining the pair of galaxies. 
   Dashed and solid lines show the results with and without the RSD effect, respectively. 
   {\it Upper panel}: In the wrongly assumed cosmologies, we observe a clear change in the amplitudes and shapes of $\xi$ due to the volume and AP effect.
   Additionally, due to the redshift dependence of volume and AP effect,
   the amplitudes and shapes in the four redshift bins are different from each other. 
   {\it Lower panel}: The same as the upper panel, except that the amplitudes of curves are normalized to 1.
   }
\end{figure*}

In this section we present the measurements of 2pCF from our mock data.
Figure \ref{fig_TpCF} shows the $\xi_{\Delta s}$ measured from HR3 mock surveys,
adopting the correct cosmology (left), the $\Omega_m=0.11$, $w=-0.7$ cosmology (middle),
and the $\Omega_m=0.41$, $w=-1.3$ cosmology (right).
To study the redshift evolution, we divide the redshift range $z=0-1.5$ into five equal-width redshift bins
\footnote{We do not show the result of the first redshift bin, which is noisy due to poor statistics.}.
To measure anisotropy, we further divide the full angular range $\mu=0-1$ into 10 equal-width bins.
So we have %$\xi_{\Delta s}(z_i,\mu_j)$, where $i=1,2,...,5$, goes from 1 to 5, and $j$ goes from 1 to 10.
\begin{equation}
\xi_{\Delta s}(z_i,\mu_j)\ \equiv\ \xi_{\Delta s} \rm \ in\ the\ {\it i}-th\ redshift\ bin,\ {\it j}-th\ \mu\ bin
\end{equation}
where $i=1,2,...,5$, $j=1,2,...10$.
Measurements without and with considering RSD effect are plotted in solid and dashed lines, respectively.

The result for the correct cosmology is plotted in the upper left panel of Figure \ref{fig_TpCF}.
In the absence of RSD, we obtain flat curves of $\xi_{\Delta s}(\mu)$ in all redshift bins,
with the amplitude slightly different from one redshift bin to another.
This difference can arise from two sources; (a) The growth of clustering with the decreasing of redshift.
(b) The redshift evolution of the bias of halos having the same comoving density.
The result is significantly changed when we include the RSD effect.
Near the LOS direction ($\mu\rightarrow1$), structures are compressed due to the Kaiser effect,
so the value of $\xi_{\Delta s}(\mu)$ is smaller compared with measurements near the tangential 
direction\footnote{The FoG effect will enhance $\xi_{\Delta s}(\mu)$ in the LOS direction.
It does not significantly show up in our figures since we impose the cut $s_{\rm min}=6$ Mpc/h.}.
But it should be noted that the shape of $\xi_{\Delta s}(\mu)$ is nearly the same at all redshifts,
indicating the small redshift dependence of the RSD effect.
It is this observation that makes our method both feasible and statistically powerful. 
Even though the 2pCF becomes very anisotropic in redshift space, the anisotropy due to RSD does not change much as a function 
of redshift and its redshift-dependence is dominated by the geometric effects introduced by the adopted cosmology.

The results of the $\Omega_m=0.11$, $w=-0.7$ and $\Omega_m=0.41$, $w=-1.3$ cosmologies are plotted in the middle and right panels, respectively.
We can see that $\xi_{\Delta s}$ is significantly altered by the volume and AP effects.
In the $\Omega_m=0.41$, $w=-1.3$ cosmology,
the shrinkage of comoving volume suppresses the amplitude of $\xi_{\Delta s}(\mu)$,
and the LOS shape compression of structures results in a suppression of amplitude in the LOS direction compared with the tangential.
Both effects become increasingly more significant at higher redshift.
In the $\Omega_m=0.11$, $w=-0.7$ cosmology, the comoving volume shrinks at $z<0.6$ and enlarges at $z>0.6$.
Thus, compared to the result of correct cosmology (top left panel),
in this cosmology the 2pCF measured at $z=0.3-0.6$ has slightly suppressed amplitude,
while the other three curves measured at $z>0.6$ have enhanced amplitudes.
Also, due to the LOS shape stretch at $z>0.3$, in all curves the amplitude is relatively enhanced in the LOS direction.
All these effects are more significant at earlier times.

In real observational data the redshift evolution of the bias of observed galaxies is difficult to model.
Thus to mitigate this systematic uncertainty we wish to rely on the shape of $\xi_{\Delta s}(\mu)$, rather than its amplitude.
In the lower panel of Figure \ref{fig_TpCF}, we show the normalized $\xi_{\Delta s}(\mu)$ in each redshift bin, defined as
\begin{equation}\label{eq:norm}
 \hat\xi_{\Delta s}(\mu) \equiv \frac{\xi_{\Delta s}(\mu)}{\int_0^1\xi_{\Delta s}(\mu)\ d\mu}.
\end{equation}
It should be noted that the normalization in Equation (\ref{eq:norm}) is made by the correlation function
in each corresponding redshift bin, not by the global quantity. 
This procedure is critically important since it effectively suppresses the cosmic variance in the correlation function from one redshift bin to another.
When the RSD effect is considered,
in the correct cosmology $\hat {\xi}_{\Delta s}$ at different redshifts are almost identical to each other,
while in the wrong cosmologies we see clear redshift evolution.

Overall, the effect of RSD on the 2pCF is large but its redshift dependence is small.
The correct cosmology corresponds to the case with the lowest change of $\xi_{\Delta s}$ with $z$.
Even with RSD, we can still correctly determine the true cosmology by using the relative change of $\xi_{\Delta s}$ with redshift.
Based on this fact, we define our $\chi^2$ as follows
\begin{equation}\label{eq:chisq1}
\chi^2\equiv \sum_{i=1}^{4} \sum_{j=1}^{10} \frac{[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_5,\mu_j)]^2}
{\sigma_{\hat\xi_{\Delta s}(z_i,\mu_j)}^2+\sigma^2_{\hat\xi_{\Delta s}(z_5,\mu_j)}}.
\end{equation}
The 2pCF measured in the 1-4 redshift bins are compared (or normalized) to the measurement in the last redshift bin.
This $\chi^2$ will prefer minimal shape change over the redshift range, with little of no weight given to the amplitude of the clustering statistic.

Figure \ref{fig_TpCF} shows that the redshift evolution of the RSD effect, although small,
still results in visible redshift evolution in the amplitudes and shapes of the curves.
Also, the amplitude of the 2pCF may evolve due to the growth of clustering and the redshift evolution of selection effect.
So, similar to \cite{Li2014}, we further correct the residual RSD effect, i.e.,
the following quantity is computed in the correct cosmology and subtracted from our results,
\begin{equation}\label{eq:rsdcor}
 \Delta \hat\xi_{\Delta s} \equiv \hat\xi_{\Delta s, {\rm With\ RSD}} - \hat\xi_{\Delta s, \rm No\ RSD}.
\end{equation}
Although this correction factor may have cosmological dependence, we assume that this will not introduce significant systematic to our methodology.
To avoid the contamination from the FoG effect we further impose a cut of $\mu>0.1$ (i.e. $j>1$).
We also take into consideration the correlation between $\xi_{\Delta}(\mu)$ measured in different directions.
So the $\chi^2$ function becomes
\begin{equation}\label{eq:chisq1}
\chi^2\equiv \sum_{i=1}^{4} \sum_{j_1=2}^{10} \sum_{j_2=2}^{10} {\bf p}(z_i,\mu_{j_1}) {\bf Cov}_{i,j_1,j_2}  {\bf p}(z_i,\mu_{j_2}),
\end{equation}
where ${\bf p}(z_i,\mu_{j})$ takes the form
\begin{eqnarray}\label{eq:bfp}
 {\bf p}(z_i,\mu_{j}) \equiv&\ \hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_5,\mu_j) - \nonumber\\
   &\ \ \ \ \ [\Delta\hat\xi_{\Delta s}(z_i,\mu_j)-\Delta\hat\xi_{\Delta s}(z_5,\mu_j)],
\end{eqnarray}
and ${\rm Cov}_i$ is the covariance matrix of ${\bf p}(z_i,\mu_{j})$. 
In testing our methodology, we divide the full sky sample into 48 equal sky coverage subsamples
and construct a measurement covariance matrix. 
%from the 48 equal sky-area mock surveys described in \S\ref{sec:mocks}

\begin{figure*}
   \centering{
   \includegraphics[height=7cm]{Tpcf--contour.eps}
   }
   \caption{\label{fig_contours}
   {\em Left:} Expected likelihood contours (68.3\%, 95.4\%, and 99.7\%) in the $\Omega_m-w$ plane,
   obtained from a $1/8$-sky, $z<1.5$ mock survey with a constant galaxy number density of $\bar n=3\times10^{-4}(h^{-1}{\rm Mpc})^{-3}$.
   We achieve unbiased constraints with $\delta w\sim0.1$ and $\delta \Omega_m\sim0.03$ 
   by comparing the shapes of $\xi_{\Delta s}(\mu)$ measured in different redshift bins.
   {\em Right:} Here we use the unnormalized $\xi_{\Delta s}(\mu)$, 
   which is sensitive to the volume change and thus provides much tighter constraints. 
   Although to use this in practice would mean overcoming some observational systematic uncertainties like galaxy evolution and selection bias.
   }
\end{figure*}

Figure \ref{fig_contours} shows the likelihood contours obtained from our mock survey, 
which is a $1/8$-sky survey with constant number density $\bar n=3\times10^{-4}(h^{-1}{\rm Mpc})^{-3}$ in the redshift range 0-1.5.
The gray contours on the left show the result when we normalize the amplitude of $\xi_{\Delta s}(\mu)$ 
and just utilize the information encoded in the shape
(i.e., we focus only on the AP information and ignore the volume effect).
We obtain tight and unbiased constraint on $\Omega_m$ and $w$, with 68.3\% CL intervals $\delta \Omega_m\sim0.03$ and $\delta w\sim0.1$.
We find that $\Omega_m$ and $w$ are positively degenerated with each other, which is expectable.
For instance, reducing $\Omega_m$ and having a more phantom-like dark energy produce similar influences on the expansion history of the Universe. 
Compared with the result of our gradient field method \cite{Li2014},
the shapes of contours are very similar, and constraint is a little tighter.

The right hand plot of Figure \ref{fig_contours} shows the result when we utilize the volume effect.
To do that, in Equation (\ref{eq:bfp}) we adopt the non-normalized $\xi_{\Delta s}$ instead of the normalized one $\hat\xi_{\Delta s}$
\footnote{Different from the normalized case, in the non-normalized case not only do we correct the RSD effect, 
but we also correct the redshift evolution of the amplitude of 2pCF.
As shown by the top left pannel of Figure \ref{fig_TpCF}, the amplitude of 2pCF can evolve with redshift even in the no RSD case,
mainly due to the growth of structure and the selection bias.
So in the non-normalized case Equation (\ref{eq:rsdcor}) shall be modified as  
$\Delta \xi_{\Delta s}(z_i) \equiv \left[\xi_{\Delta s, {\rm With\ RSD}}(z_i) - \xi_{\Delta s, \rm No\ RSD}(z_i)\right]
+ \left[\xi_{\Delta s, \rm No\ RSD}(z_i) - \xi_{\Delta s, \rm No\ RSD}(z_1)\right]$.}. 
In that case, constraints become much tighter, with $\delta \Omega_m\sim0.007$ and $\delta w\sim0.035$.
Also, the direction of degeneracy changes and is very different from mainstream techniques of CMB, SNIa and BAO,
meaning that combining our method with these techniques can significantly improve the constraint.
To implement it in real observational cases, it is necessary to model the evolution of the clustering amplitude for the observed galaxies.

\section{Conclusion}

\begin{figure*}
   \centering{
   \includegraphics[height=7cm]{Tpcf--deltar.eps}
   }
   \caption{\label{fig_deltar}
   The RMS displacement of halo comoving distance as a function of redshift, for samples with different cuts of halo mass.
   %The RMS peculiar velocity divided by $H(z)$ as a function of radial diastase from the observer (equivalently to redshift) for various mass cuts. 
   Over the redshift range of interest for our study, the peculiar velocity is varying smoothly with a maximal deviation of 13\%.
   Within the wide mass cut range from $5\times 10^{12}$\hMsun to $2\times 10^{13}$\hMsun, 
   the difference in the RMS displacement is $\lesssim1\%$,
   suggesting that the redshift evolution of RSD effect shall be fairly insensitive to the halo mass cut and number density of the sample.
   }
\end{figure*}

We have presented a new anisotropic clustering statistic that can probe the cosmic expansion history.
We measure the integrated 2pCF, $\xi_{\Delta s}(\mu)\equiv\int_{s_{\rm min}}^{s_{\rm max}}\xi(s,\mu)ds$, as a function of direction $\mu$.
The amplitude of $\xi_{\Delta s}(\mu)$ is affected by the volume effect,
and the shape is affected by the AP effect.
Due to the redshift dependence of the volume and AP effects, 
in wrongly adopted cosmologies there are redshift evolutions of the amplitude and shape.
The RSD effect due to galaxy peculiar velocities, although having a strong effect on $\xi_{\Delta s}(\mu)$,
does not exhibit significant redshift evolution.
Thus by focusing on the redshift dependence of $\xi_{\Delta s}(\mu)$,
we are able to derive accurate and unbiased estimates of cosmological parameters in spite of contamination induced by RSD.
We are only assuming that the RSD modelling is accurately captured by the simulations.

The concept of this paper is similar to \cite{Li2014}, 
where the redshift dependence of the AP effect is measured from the anisotropy in the galaxy density gradient field.
However, in this paper we choose a different statistical method, i.e. the 2pCF.
%Both the methods of density gradient field and 2pCF can characterize the anisotropy of the galaxy distribution,
They differ from each other in several aspects.
1) Using the 2pCF method it is more convenient to choose the scales we investigate.
2) The advantage of the density gradient field method is that, it allows us to utilize the information on small scales of $\sim$10 Mpc/h 
(depending on the scale of smoothing).
3) In the 2pCF method we are able to probe the volume effect, which is not possible for the galaxy density field method.
4) The 2pCF is a mature statistic in cosmology and its optimal estimation and statistical properties are well understood.

The volume effect, which causes redshift evolution in the amplitude of 2pCF,
leads to very tight constraint on cosmological parameters.
But it suffers from systematic effects of growth of clustering and the variation of galaxy sample with redshift.
It would be great if one can reliably model these two effects and utilize the volume effect.
In case that the systematic effect can not be correctly modelled,
one can focus on the AP effect by normalizing the amplitude of $\xi_{\Delta s}(\mu)$ and just investigating the redshift evolution of the shape.

In our analysis we consider the case of a flat universe with constant dark energy EoS $w$. 
However, in general one can choose an arbitrary cosmological model and repeat our analysis to constrain the model parameters. 
Furthermore, since our method focuses on the redshift evolution of the 2pCF, 
it may have advantages in constraining models in which the cosmic expansion history displays dynamical features. 
For the popular Chevallier-Polarski-Linder (CPL) parametrization $w=w_0+w_a \frac{z}{1+z}$ \citep{CP2001,Linder2003}, 
the dark energy EoS evolves monotonically from $w_0$ at $z=0$ to $w_0+w_a$ at high redshift. 
Using a LSS sample covering a wide redshift range should be sufficient to constrain the model parameters through the effect on $D_A$ and $H$. 
For dark energy models with a rapidly varying EoS \citep{Bassett2002,Corasaniti2003}, 
a transition of $w$ could happen in a very short period, which is difficult to be detected by common techniques. 
For our method, we can reduce the redshift bin size down the a size similar to the typical width of a transition epoch 
to probe the detailed feature of cosmic expansion history and effectively constrain the model parameters.

The feasibility of our method crucially depends on the fact that the redshift dependence of the RSD effect is small. 
One may suspect that this is a special consequence of the constant number density sample. 
While an exhaustive investigation of this issue is too complicate for this short paper, 
we perform a simple check to show that the weak redshift dependence of the RSD effects is fairly universal. 
From the HR3 lightcone data, we generated a series of samples with a constant mass cut, 
and measured the root mean square (RMS) displacement of halo comoving distance as a function of redshift. 
The degree of the RSD effects shall be statistically directly proportional to the RMS displacement. 
The result is plotted in Figure \ref{fig_deltar}.
We find that the total variation of the RMS displacement between $z=0$ and 1.5 is only about 13\%, which can explain why the redshift dependence of the RSD effects is weak.
We also find that, within the wide mass cut range from $5\times 10^{12}$\hMsun to $2\times 10^{13}$\hMsun, the difference in the RMS displacement is $\lesssim1\%$. 
This suggests that the redshift evolution of RSD effect shall be fairly insensitive to the halo mass cut and number density of the sample.

When dealing with real observational data, 
it will be important to accurately model the galaxy clustering to remove the residual RSD effects on the 2pCF.
It will also require the handling of various observation effects such as survey geometry, fiber collisions, etc. 
We will report the results of such investigations in forthcoming studies.

\section*{Acknowledgments}

We thank the Korea Institute for Advanced Study for providing computing resources (KIAS Center for Advanced Computation Linux Cluster System).
We thank Seokcheon Lee and Graziano Rossi for many helpful discussions.

\begin{thebibliography}{}

\bibitem[Alcock \& Paczynski(1979)]{AP1979}
Alcock, C., \& Paczynski, B. 1979, Nature, 281, 358

\bibitem[Anderson et al.(2013)]{Anderson2013}
Anderson, L., Aubourg, \'E., Bailey, S. et al. 2014, MNRAS, 441, 24

\bibitem[Bassett et al.(2002)]{Bassett2002}
Bassett, B.A., Kunz, M., Silk, J., \& Ungarelli, C. 2002, MNRAS, 336, 1217

\bibitem[Ballinger, Peacock \& Heavens 1996]{Ballinger1996}
Ballinger, W.E., Peacock, J.A., \& Heavens, A.F. 1996, MNRAS, 282, 877

\bibitem[Beutler et al.(2013)]{Beutler2013}
Beutler, F., Saito, S., Seo, H.-J., et al. 2013, MNRAS, 443, 1065

\bibitem[Blake et al.(2011)]{Blake2011}
Blake, C., Glazebrook, K., Davis, T. M., 2011, MNRAS, 418, 1725

\bibitem[Bueno Belloso et al. (2012)]{BB2012}
Bueno Belloso, A., Pettinari, G.W., Meures, N., \& Percival, W.J. 2012, Phys. Rev. D, 86, 023530

\bibitem[Chevallier \& Polarski(2001)]{CP2001}
Chevallier, M., Polarski, D. 2001, Int. J. Mod. Phys. D, 10, 213

\bibitem[Choi et al.(2010)]{choi 2010}
Choi, Y.-Y., Park, C., Kim, J., Gott, J.R., 
Weinberg, D.H., Vogeley, M.S., \& Kim, S.S. 2010, ApJS, 190, 181

%\bibitem[Chuang et al.(2013)]{Chuang2013}
%Chuang, C.-H., Prada, F., Beutler, F., et al. 2013, arXiv:1312.4889

\bibitem[Chuang \& Wang(2012)]{ChuangWang2012}
Chuang, C.-H., \& Wang, Y. 2012, MNRAS, 426, 226

\bibitem[Corasaniti \& Copeland(2003)]{Corasaniti2003}
Corasaniti, P.S., Copeland, E.J. 2003, Phys. Rev. D, 67, 063521

%\bibitem[Gingold \& Monaghan(1977)]{GM1977}
%Gingold, R.A., \& Monaghan, J.J. 1977, MNRAS, 181, 375

\bibitem[Gott et al.(2009)]{gott 2009}
Gott, J.R., Choi, Y.-Y., Park, C., \& Kim, J. 2009, ApJ, 695, L45

\bibitem[Gott et al.(2008)]{gott 2008}
Gott, J.R., Hambrick, D.C., Vogeley, M.S., Kim, J., Park, C., Choi, Y.-Y.,
Cen, R., Ostriker, J.P., \& Nagamine, K. 2008, ApJ, 675, 16

\bibitem[Jackson (1972)]{FoG}
Jackson J., 1972, MNRAS, 156, 1

\bibitem[Jennings et al.(2011)]{Jennings2011}
Jennings, E., Baugh, C.M., \& Pascoli, S. 2011, MNRAS, 420, 1079

\bibitem[Jeong et al.(2014)]{Jeong2014}
Jeong, D., Dai, L., Kamionkowski, M., \& Szalay, A.S. 2014, arXiv:1408.4648

\bibitem[Kim \& Park(2006)]{kim and park 2006}
Kim, J., \& Park, C. 2006, ApJ, 639, 600

\bibitem[Kim et al.(2009)]{2009ApJ...701.1547K} Kim, J., Park, C., Gott, 
J.~R., III, \& Dubinski, J.\ 2009, ApJ, 701, 1547

\bibitem[Kim et al.(2011)]{horizonrun}
Kim, J., Park, C., Rossi, G., Lee, S.M., \& Gott, J.R., 2011, JKAS, 44, 217

\bibitem[Komatsu et al.(2011)]{komatsu 2011}
Komatsu, E., Smith, K. M., Dunkley, J., et al. 2011, ApJS, 192, 18

\bibitem[Landy \& Szalay(1993)]{1993ApJ...412...64L} S.~D. Landy, \& A.~S. Szalay, \ 1993, ApJ, 412, 64

\bibitem[Lavaux \& Wandelt(2012)]{LavausWandelt1995}
Lavaux, G., \& Wandelt, B.D. 2012, ApJ, 754, 109

\bibitem[Levi et al.(2013)]{2013arXiv1308.0847L} 
Levi, M., Bebek, C., Beers, T., et al.\ 2013, arXiv:1308.0847

\bibitem[Li et al.(2014)]{Li2014}
Li, X.-D., Park, C., Forero-Romero, J. E., Kim, J. 2014, ApJ, 796, 137

\bibitem[Linder(2003)]{Linder2003}
Linder, E.V. 2003, Phys. Rev. Lett., 90, 091301

\bibitem[Linder et al.(2014)]{Linder2013}
Linder, E.V., Minji, O., Okumura, T., Sabiu, C.G., \& Song, Y.-S. 2014, Phys. Rev. D, 89, 063525

\bibitem[L{\'o}pez-Corredoira(2014)]{2014ApJ...781...96L} 
L{\'o}pez-Corredoira, M.\ 2014, ApJ, 781, 96

\bibitem[Marinoni \& Buzzi(2010)]{Marinoni2010}
Marinoni, C., \& Buzzi, A. 2010, Nature, 468, 539

\bibitem[Matsubara \& Suto(1996)]{Matsubara1996}
Matsubara T., \& Suto, Y. 1996, ApJ, 470, L1

\bibitem[Outram et al.(2004)]{Outram2004}
Outram, P.J., Shanks, T., Boyle, B.J., Croom, S.M., Hoyle, F., Loaring, N.S., 
Miller, L., \& Smith, R.J. 2004, MNRAS, 348, 745

%\bibitem[Parejko et al.(2013)]{Parejko2013}
%Parejko, J. K., Sunayama, T., Padmanabhan, N., et al. 2013, MNRAS, 429, 98

\bibitem[Park et al.(2005)]{park 2005}
Park, C., Kim, J., \& Gott, J.R. 2005, ApJ, 633, 1

\bibitem[Park \& Kim(2010)]{topology}
Park, C., \& Kim, Y.-R. 2010, ApJL, 715, L185

\bibitem[Press \& Shechter(1974)]{PS1974}
Press, W.H., \& Schechter, P.L. 1974, ApJ, 187, 425

\bibitem[Perlmutter et al.(1999)]{Perl1999}
Perlmutter, S., Aldering, G., Goldhaber, G., et al. 1999, ApJ, 517, 565

\bibitem[Reid et al.(2012)]{Reid2012}
Reid, B. A., Samushia, L., White, M., et al. 2012, MNRAS, 426, 2719

\bibitem[Riess et al.(1998)]{Riess1998}
Riess, A. G., Filippenko, A. V., Challis, P., et al. 1998, AJ, 116, 1009

 %\bibitem[Ross et al.(2012)]{2012MNRAS.424..564R} A.~J. Ross, W.~J. Percival, 
%A.~G. S{\'a}nchez, et al.\ 2012, MNRAS, 424, 564

\bibitem[Ryden(1995)]{Ryden1995}
Ryden, B.S. 1995, ApJ, 452, 25

%\bibitem[Samushia et al.(2014)]{Samushia2014}
%Samushia, L., Reid, B. A., White, M., et al. 2014, MNRAS, 439, 3504

\bibitem[Sanchez et al.(2013)]{Sanchez2013}
Sanchez, A. G., Kazin, E. A., Beutler, F., et al. 2013, MNRAS, 433, 1202

\bibitem[Sutter et al.(2014)]{Sutter2014}
Sutter, P.M., Pisani, A., Wandelt, B.D., \& Weinberg, D.H. 2014, MNRAS, 443, 2983

\bibitem[Song et al.(2014)]{2014arXiv1407.2257S} Song, Y.-S., Sabiu, C.~G., 
Okumura, T., Oh, M., \& Linder, E.~V.\ 2014, JCAP, 12, 005

%\bibitem[Tojeiro \& Percival(2011)]{Tojeiro2011}
%Tojeiro R., \& Percivial W.J. 2011, MNRAS, 417, 1114

%\bibitem[Tojeiro et al.(2012)]{Tojeiro2012}
%Tojeiro, R., Percival, W. J., Wake, D. A., et al. 2012, MNRAS, 424, 136

\bibitem[Viana \& Liddle(1996)]{VL1996}
Viana, P.T.P., \& Liddle, A.R. 1996, MNRAS, 281, 323

\end{thebibliography}

\bsp

\label{lastpage}

\end{document}

### 2016-08-18 draft/BOSSAP/rm.sh

@@ -1,0 +1,3 @@
+
+rm *to.pdf
+rm *.dvi *.aux *.bib *.log

### 2016-08-18 gitpush.sh

@@ -13,5 +13,11 @@ git add plottings/*.*
 git add plottings/*/*.*
 git add src/*.py
 git add src/*.ipynb
+
+git add draft/BOSSAP/*.*
+git add draft/gal2pcf/*.*
+git add draft/*.tex
+git add draft/*.eps
+
 git commit -m 'updates'
 git push

### 2016-08-18 draft/BOSSAP/rm.sh
updates

@@ -1,3 +1,0 @@
-
-rm *to.pdf
-rm *.dvi *.aux *.bib *.log

### 2016-08-19 gitpush.sh
updates

@@ -12,6 +12,7 @@ git add README.md
 git add plottings/*.*
 git add plottings/*/*.*
 git add src/*.py
+git add src/fig*.eps
 git add src/*.ipynb
 
 git add draft/BOSSAP/*.*

### 2016-08-19 src/stdA.py

@@ -31,6 +31,7 @@ Seconds_per_day = S1D = 3600*24# how many
 
 
 PCA = PLOT_COLOR_ARRAY = ['k','b','c','g','m','r', 'y', 'gray']
+PCA2 = PLOT_COLOR_ARRAY_2 = ['k','b','c','g','m','r']
 PSA = PLOT_STYLE_ARRAY = ['-', '--', '-.', '..']
 MA = MARKER_ARRAY = ['o', 'p', 's',  'D',  '^', '*', 'v', '1', '2', '3', '4']
 NUM_PLOT_COLOR = len(PLOT_COLOR_ARRAY)

### 2016-08-26 draft/draft0.tex
updates

@@
 
-\title{Cosmological constraints from the redshift dependence of the distance rescaling in wrong cosmologies: 
-the shape of galaxy 2-point correlation function}
+\title{Cosmological constraints from the redshift dependence of scaling in wrong cosmologies: 
+the shape of galaxy 2-point correlation function {\bf XD: Which word shall I use? mis-scaling? geometric scaling? ...}}
 
@@
 
-%{\bf AMTB: Please chose one kind of tense of verbs. It changes from sentences to sentences!}
-%{\bf AMTB: How many mock BOSS samples are made from HR4?}
-
 This paper is organized as follows...
@@
 
-\section{AP and Volume Effect in Wrongly Assumed Cosmologies}
+\section{Volume Effect}
 \label{sec:Voleffect}
@@
    \centering{
-%   \includegraphics[height=6cm]{Tpcf--xy.eps}
-%   \includegraphics[height=6cm]{Tpcf--quan.eps}
-   %\includegraphics[height=7cm]{FVol.eps}
-   %\includegraphics[height=8cm]{xy.eps}
-   %\includegraphics[height=8cm]{smu.eps}
+   \includegraphics[height=8cm]{fig1_a.eps}
+   \includegraphics[height=8cm]{fig1_b.eps}
    }
-   \caption{\label{fig_xy}
+   \caption{\label{fig_xyquan}
    %Apparent distortion of objects in four wrongly assumed cosmologies, assuming a true cosmology of .
-   The redshift dependence of AP and volume effect in two wrongly assumed cosmologies $\Omega_m=0.41$, $w=-1.3$ and $\Omega_m=0.11$, $w=-0.7$,
+   The scaling in four wrongly assumed cosmologies ..., % $\Omega_m=0.41$, $w=-1.3$ and $\Omega_m=0.11$, $w=-0.7$, 
    assuming a true cosmology of $\Omega_m=0.26$, $w=-1$.
-   Upper panel shows the apparent distortion of four perfect squares,
-   measured by an observer located at the origin.
-   The apparently distorted shapes are plotted in red solid lines.
-   The underlying true shapes are plotted in blue dashed lines.
-   Lower panel shows the evolution of Equations (\ref{eq:stretch}) and (\ref{eq:volume}).
-   In our mock surveys we split the samples at $z=0.3$, 0.6, 0.9 and 1.2, as marked by the vertical lines.
+   Left panel shows a series of circular objects, measured by an observer located at the origin.
+   Their true positions and shapes are plotted in blue dashed lines.
+   The observer measures the redshifts of these objects, adopts the wrong cosmologies to compute the distance,
+   and obtains wrong results (the red solid lines).
+   %The red solid lines show their positions and shapes when the wrong cosmologies 
+   % are assumed to compute distance from measured redshift.
+   %The misestimation of angular diameter distance lead to wrong 
+   Right panel shows the misestimation of angular diameter distance when the wrong cosmologies are adopted.
+   %In our mock surveys we split the samples at $z=0.3$, 0.6, 0.9 and 1.2, as marked by the vertical lines.
    %measured by an observer located at the origin.
@@
    }
+   % Need a better plot to show angular size variation!!!
 \end{figure*}
@@
 %Its observed redshift span $\Delta z$ and angular size $\Delta \theta$ are related with the comoving sizes by
-In this section we briefly introduce the AP and volume effect in wrongly assumed cosmologies.
-A more detailed description of the AP effect has been provided in \cite{Li2014}.
-
-Suppose that we are probing the shape and volume of an object in the Universe.
+In this section we briefly introduce the scaling effect in wrongly assumed cosmologies.
+A more detailed description has been provided in \cite{Li2014,Li2015,Li2016}.
+
+Suppose that we are probing the shape of some objects in the Universe.
 We measure its redshift span $\Delta z$ and angular size $\Delta \theta$,
@@
 resulting in distorted shape (AP effect) and wrongly estimated volume (volume effect).
-The degree of variations in shape and volume can be described by the following quantities
-\begin{equation}\label{eq:stretch}
+These effects have been discussed in \cite{Li2014,Li2015,Li2016}.
+This paper we focus on the scaling of angular size,
+which can be described by the following quantities
+%\begin{equation}\label{eq:stretch}
  %{\rm Degree\ of\ LOS\ stretch\equiv}
  %{\rm rat}_{\rm LOS\ stretch}\equiv
- \frac{[\Delta r_{\parallel}/\Delta r_{\perp}]_{\rm wrong}}{[\Delta r_{\parallel}/\Delta r_{\perp}]_{\rm true}} =
-  \frac{[D_A(z)H(z)]_{\rm true}}{[D_A(z)H(z)]_{\rm wrong}} 
-\end{equation}
-\begin{equation}\label{eq:volume}
+% \frac{[\Delta r_{\parallel}/\Delta r_{\perp}]_{\rm wrong}}{[\Delta r_{\parallel}/\Delta r_{\perp}]_{\rm true}} =
+%  \frac{[D_A(z)H(z)]_{\rm true}}{[D_A(z)H(z)]_{\rm wrong}} 
+%\end{equation}
+%\begin{equation}\label{eq:volume}
+% %{\rm Degree\ of\ volume\ magnification \equiv}
+% %{\rm rat}_{\rm volume\ mag}\equiv
+% \frac{[\Delta r_{\parallel}(\Delta r_{\perp})^{2}]_{\rm wrong}}{[\Delta r_{\parallel}(\Delta r_{\perp})^{2}]_{\rm true}}
+% = \frac{{\rm Volume}_{\rm wrong}}{{\rm Volume}_{\rm true}}
+% = \frac{[D_A(z)^2/H(z)]_{\rm wrong}}{[D_A(z)^2 / H(z)]_{\rm true}},
+%\end{equation}
+\begin{equation}\label{eq:DA}
  %{\rm Degree\ of\ volume\ magnification \equiv}
  %{\rm rat}_{\rm volume\ mag}\equiv
- \frac{[\Delta r_{\parallel}(\Delta r_{\perp})^{2}]_{\rm wrong}}{[\Delta r_{\parallel}(\Delta r_{\perp})^{2}]_{\rm true}}
- = \frac{{\rm Volume}_{\rm wrong}}{{\rm Volume}_{\rm true}}
- = \frac{[D_A(z)^2/H(z)]_{\rm wrong}}{[D_A(z)^2 / H(z)]_{\rm true}},
+ \frac{\Delta r_{\bot, \rm wrong}}{\Delta r_{\bot, \rm true}}
+ = \frac{D_{A, \rm wrong}}{D_{A, \rm true}},
 \end{equation}
-where ``true'' and ``wrong'' denote the values of quantities in the true cosmology and wrongly assumed cosmology.
-From the AP and volume effects, we can constrain  $D_A(z)H(z)$ and $D_A(z)^2 / H(z)$, respectively.
-
-The AP and volume effect due to wrongly assumed cosmological parameters are shown in the upper panel of Figure \ref{fig_xy}.
+where ``true'' and ``wrong'' denote the values of $D_A$ in the true cosmology and wrongly assumed cosmology.
+%From the above effects, we can constrain $D_A(z)H(z)$, $D_A(z)^2 / H(z)$ and $D_A(z)$, respectively.
+
+The effects due to wrongly assumed cosmological parameters are shown in the upper panel of Figure \ref{fig_xy}.
 Suppose that the true cosmology is a flat $\Lambda$CDM with present density parameter $\Omega_m=0.26$
 and standard dark energy EoS $w=-1$.
-If we were to distribute four perfect squares at various distances from 500 Mpc/h to 3,000 Mpc/h,
+If we were to distribute a series of perfect circles at various distances from 500 Mpc/h to ???? Mpc/h,
 and an observer located at the origin were to measure their redshifts and compute their positions and shapes 
-using redshift-distance relations of two incorrect cosmologies:
+using redshift-distance relations of ??? incorrect cosmologies:
 \begin{enumerate}
@@
 
-\begin{figure*}
-   \centering{
-%   \includegraphics[width=16cm]{fig6.eps}
-   }
-   \caption{\label{fig_datamock}
-   %Apparent distortion of objects in four wrongly assumed cosmologies, assuming a true cosmology of .
-   $\hat\xi_{\Delta s}(\mu)$ measured from BOSS DR12 CMASS NGC sample 
-    (consists of $\approx 565\,000$ galaxies at $0.15 < z < 0.693$)
-    and one realization from the HR4 N-body simulation, in the WMAP5 cosmology.
-   The lower panel shows the difference between the results of observational data and mock galaxies.
-   $\hat\xi_{\Delta s}(\mu)$ are obtained by integrating $\xi (s,\mu)$ within the range {\rm 6\ $h^{-1}$Mpc}$\leq s\leq${\rm 40\ $h^{-1}$Mpc} 
-      and normalizing the amplitude, 
-    i.e., Eq. (\ref{eq:xideltas}) and Eq. (\ref{eq:norm}).
-   To produce a clear view of the FOG effect, we split the angular range of $0.01\leq \mu \leq 1$ into as many as 40 bins.
-   Using the HR4 mock galaxies, the enhancement near $\theta=0^\circ$ caused by the FOG effect
-    and the tilt of the shape in $20^\circ\lesssim\theta\lesssim90^\circ$ 
-    as a result of the large-scale flow,
-    are all very well reproduced.
-%    Thw lo
-   This verifies the ability of our galaxies assignment method \citep{hong2016} 
-    to reproduce the properties of galaxy distributions from large scale surveys.
-   %Conversely, the HR3 PSB halo mock can not 
-   %reproduce the shape of $\hat\xi_{\Delta s}(\mu)$.
-   We use the HR4 mock galaxies to correct the systematics effects produced by the RSD.
-   %The 72 sets of PSB mocks from HR3 are used to compute covariance.
-   %measured by an observer located at the origin.
-   %For reference, blue dashed squares show their shapes and positions in the true cosmology.
-   }
-\end{figure*}
-
 The clustering properties may be affected by various properties of the galaxy sample, 
@@
 
-\begin{figure*}
-   \centering{
-   %\includegraphics[width=16cm]{fig7.eps}
-   %\includegraphics[height=9cm]{Tpcf-sys.eps}
-   }
-   \caption{\label{fig_sys}
-   %Apparent distortion of objects in four wrongly assumed cosmologies, assuming a true cosmology of .
-   Systematics in $\delta \hat \xi_{\Delta s}$, measured from the HR4 mock galaxy samples.
-   The redshift evolution of RSD effect and properties of samples can lead to non-zero values of $\delta \hat\xi_{\Delta s}(z_i,z_1)$.
-   For the 1st to 5th redshift bins, $\delta\hat\xi_{\Delta s, \rm sys}(z_i,z_1)\lesssim0.02$,
-    indicating a small redshift evolution of the RSD effect and properties of galaxies.
-   For the 6th redshift bin, the values of $\delta\hat\xi_{\Delta s, \rm sys}(z_6,z_1)$ are relatively large,
-   because galaxies in that highest redshift bin are significantly more massive than those at lower redshifts.
-   % so the measured $\hat\xi_{\Delta s}(\mu)$ has larger (smaller) values at $\mu\rightarrow1$ ($\mu\rightarrow0$) 
-   % compared with the others.
-   See Sec. \ref{sec:syscor} for details.
-   %The values are estimated from the HR4 mock galaxies. % and subtract its contribution.
-   }
-\end{figure*}
-
 %It is impossible to probe $\hat\xi_{\Delta s}(\mu)$ as a continuous function with infinite degrees of freedom. 
@@
 %and modeling the RSD effect in a cosmological dependent manner would be necessary.
-
-\begin{figure*}
-   \centering{
-%   \includegraphics[width=14cm]{fig8.eps}
-   %\includegraphics[width=14cm]{Tpcf--contour.eps}
-   }
-   \caption{
-    \label{fig_2pcf_masscut} 
-    $\hat \xi_{\Delta s}(\mu)$ measured from a small HR4 mock galaxy sample with different minimal mass cuts.
-    The mock galaxies are taken from the $z=0$ snapshot data within the radius $r<600$ $h^{-1}$Mpc.
-    Only small variations of $\hat\xi_{\Delta s}(\mu)$ are produced when changing the minimal mass cuts.
-    Higher mass cuts result in larger (smaller) $\hat\xi_{\Delta s}(\mu)$ at $\mu\rightarrow1$ ($\mu\rightarrow0$).
-    Considering the large variation of mass cuts, the variation of $\hat\xi_{\Delta s}(\mu)$ is not significant.
-   }
-      %The redshift density distribution of the BOSS DR12 galaxy samples, assuming a $\Lambda$CDM cosmology with $\Omega_m=0.31$.
-      %The blue and green solid histograms show the distribution of LOWZ and CMASS galaxies respectively. 
-      %The vertical dashed lines define the 6 redshift bins that are used to cut the samples.   }
-\end{figure*}
 
@@
 %    \includegraphics[height=8cm]{smu.eps}
+    \includegraphics[width=18cm]{fig2.eps}
    }
-   \caption{\label{fig_TpCF}
-   Upper panels: $\hat \xi_{\Delta s}(\mu)$ measured for the BOSS DR12 galaxies,
-   which are divided into six redshift bins.
-   Measurements from the three bins in LOWZ are indicated in solid lines, 
-   while those from CMASS are the dashed lines.
-   We present the measurements in three cosmologies,
-   the $\Omega_m=0.31$ $\Lambda$CDM (left), the $\Omega_m=0.1$ $\Lambda$CDM (middle),
-   and a cosmology with $\Omega_m=0.31$, $w=-2.5$ (right).   
-   %We adopt $s_{\rm min}=6$ $h^{-1}$Mpc and $s_{\rm max}=40$ $h^{-1}$Mpc for the integral over the scale of 2pCF.
-   The angular dependence of 2pCF is measured in 10 bins within the range $0.01\leq1-\mu\leq1$.
-   In the middle and right panels, the redshift dependence of AP distortions leads to clear redshift evolution of $\hat \xi_{\Delta s}(\mu)$.
-   Lower panels: The redshift evolution of the $\hat\xi_{\Delta s}$ after systematics correction,  
-   $\delta\hat \xi_{\Delta s}(z_i,z_1)-\delta\hat \xi_{\Delta s,\rm sys}(z_i,z_1)$
-   (for details of their definitions, see Eq. (\ref{eq:deltahatxi}) and Sec. \ref{sec:syscor}).
-   For clarity we combine the curves of $z_2$ and $z_3$, which fluctuate
-   due to the relatively small sample sizes.
-   The statistical significance is indicated by the 1$\sigma$ error bars of $\delta\hat \xi_{\Delta s}(z_6,z_1)-\delta\hat \xi_{\Delta s,\rm sys}(z_6,z_1)$.
-   The curves are statistically consistent with 0 in the $\Omega_m=0.31$ $\Lambda$CDM cosmology,
-    while they deviate from 0 at significant confidence levels in the $\Omega_m=0.1$ cosmology and the $w=-2.5$ cosmology.
-   %showing the redshift dependence of AP effect.
-   Applying the likelihood analysis described in Sec. \ref{sec:likelihood},
-    the two latter models disfavored at 5.3$\sigma$ and 7.5$\sigma$ CL compared to the $\Omega_m=0.31$ $\Lambda$CDM cosmology.
+   \caption{\label{fig_diffz}
+  2pCF at different redshfits.
    }
@@
 
+\begin{figure*}
+   \centering{
+%   \includegraphics[width=18cm]{fig9_0.eps}
+%   \includegraphics[width=18cm]{fig9_1.eps}
+%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
+%    \includegraphics[height=8cm]{smu.eps}
+    \includegraphics[width=18cm]{fig3.eps}
+   }
+   \caption{\label{fig_cosmo}
+   2pCF in cosmologies.
+   }
+\end{figure*}
+
+\begin{figure*}
+   \centering{
+   \includegraphics[width=16cm]{fig4.eps}
+   \includegraphics[width=16cm]{fig5.eps}
+   }
+   \caption{\label{fig_sys}
+  Systematic effects.
+   }
+\end{figure*}
 \subsection{Cosmological Constraints}
@@
    }
-   \caption{\label{fig_contours}
-   Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method and other cosmological probes.
-   %obtained from the BOSS DR12 CMASS and LOWZ samples.
-   Using the BOSS DR12 galaxies within the redshift range $0.15< z< 0.693$, our method achieves tight cosmological constraints on $\Omega_m$ and $w$.
-   The area of the 1$\sigma$ contour of our method is smaller than all other probes.
-   Constraints from various probes are consistent with each other.
-   See Sec. \ref{sec:constraint} for details.
-   %in very good consistent with the other methods.
+   \caption{\label{fig}
+   Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method.
    }
@@
 
+\bibitem[Li et al.(2016)]{Li2016}
+Li, X.-D., Park, C., Sabiu, C.G., \& Kim, J. 2016, submitted to ApJ
+
 %\bibitem[Linder(2003)]{Linder2003}

### 2016-08-26 gitpush.sh
updates

@@ -17,6 +17,7 @@ git add src/*.ipynb
 
 git add draft/BOSSAP/*.*
 git add draft/gal2pcf/*.*
+git add draft/draft*.pdf
 git add draft/*.tex
 git add draft/*.eps
 

### 2016-08-26 draft/draft0.tex
updates

@@
 
-\title{Cosmological constraints from the redshift dependence of scaling in wrong cosmologies: 
-the shape of galaxy 2-point correlation function {\bf XD: Which word shall I use? mis-scaling? geometric scaling? ...}}
+\title{Cosmological constraints from the redshift dependence of %geometric deformation
+the galaxy angular 2-point correlation function}
 
@@
 These effects have been discussed in \cite{Li2014,Li2015,Li2016}.
-This paper we focus on the scaling of angular size,
+This paper we focus on the misestimation of $\Delta r_{\bot}$,%scaling of angular size,
 which can be described by the following quantities
-%\begin{equation}\label{eq:stretch}
- %{\rm Degree\ of\ LOS\ stretch\equiv}
- %{\rm rat}_{\rm LOS\ stretch}\equiv
-% \frac{[\Delta r_{\parallel}/\Delta r_{\perp}]_{\rm wrong}}{[\Delta r_{\parallel}/\Delta r_{\perp}]_{\rm true}} =
-%  \frac{[D_A(z)H(z)]_{\rm true}}{[D_A(z)H(z)]_{\rm wrong}} 
-%\end{equation}
-%\begin{equation}\label{eq:volume}
-% %{\rm Degree\ of\ volume\ magnification \equiv}
-% %{\rm rat}_{\rm volume\ mag}\equiv
-% \frac{[\Delta r_{\parallel}(\Delta r_{\perp})^{2}]_{\rm wrong}}{[\Delta r_{\parallel}(\Delta r_{\perp})^{2}]_{\rm true}}
-% = \frac{{\rm Volume}_{\rm wrong}}{{\rm Volume}_{\rm true}}
-% = \frac{[D_A(z)^2/H(z)]_{\rm wrong}}{[D_A(z)^2 / H(z)]_{\rm true}},
-%\end{equation}
 \begin{equation}\label{eq:DA}
@@
 where ``true'' and ``wrong'' denote the values of $D_A$ in the true cosmology and wrongly assumed cosmology.
-%From the above effects, we can constrain $D_A(z)H(z)$, $D_A(z)^2 / H(z)$ and $D_A(z)$, respectively.
-
-The effects due to wrongly assumed cosmological parameters are shown in the upper panel of Figure \ref{fig_xy}.
+
+The effects due to wrongly assumed cosmological parameters are shown in the upper panel of Figure \ref{fig_xyquan}.
 Suppose that the true cosmology is a flat $\Lambda$CDM with present density parameter $\Omega_m=0.26$
 and standard dark energy EoS $w=-1$.
-If we were to distribute a series of perfect circles at various distances from 500 Mpc/h to ???? Mpc/h,
+If we were to distribute a series of perfect squares at various distances from 500 Mpc/h to ???? Mpc/h,
 and an observer located at the origin were to measure their redshifts and compute their positions and shapes 
-using redshift-distance relations of ??? incorrect cosmologies:
+using redshift-distance relations of ??? incorrect cosmologies
 \begin{enumerate}
@@
 and their volumes are changed (volume effect).
-In the cosmological model (ii) with $\Omega_m=0.11$, $w=-0.7$, we see a stretch of the shape in the line of sight (LOS) direction (hereafter ``LOS shape stretch'')
+In the cosmological model (ii) with $\Omega_m=0.11$, $w=-0.7$, we see a stretch of the shape in the line of sight (LOS) direction 
+(hereafter ``LOS shape stretch'')
 and magnification of the volume (hereafter ``volume magnification''), 
@@
 
-In the lower panel of Figure \ref{fig_xy}, we plot the degree of variations in shape and volume as functions of redshift. 
+In the lower panel of Figure \ref{fig_xyquan}, we plot the $\frac{\Delta r_{\bot, \rm wrong}}{\Delta r_{\bot, \rm true}}$ redshift. 
 In cosmology (i), both quantities have values less than 1, 
@@
 
-More importantly, Figure \ref{fig_xy} highlights the redshift dependence of the AP and volume effects. 
+More importantly, Figure \ref{fig_xyquan} highlights the redshift dependence of the AP and volume effects. 
 For example, in the cosmology with $\Omega_m=0.41$, $w=-1.3$, 
@@
 not only do the magnitudes of the effects evolve with redshift,
-but there is also a turnover from LOS shape compression and volume shrink at lower redshift to LOS shape stretch and volume magnification at higher redshift.
+but there is also a turnover from LOS shape compression and volume shrink at lower redshift to LOS shape stretch and volume magnification at higher redshift.s
 

### 2016-08-26 draft/draft0.tex
updates

@@
 
-The HR4 simulation  \citep{hr4} used a box size $L={3150}$ $h^{-1}$Mpc, 
-and $N=6300^3$ particles.  
-The simulation used the second order Lagrangian perturbation theory (2LPT) initial conditions at $z_{i}=100$ and a WMAP5 cosmology
-$(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96) \citep[]{komatsu 2011}, 
-yielding a particle mass of $m_{p} \simeq 9.02 \times 10^9 \hMsun$.
-This starting redshift, combined  with 2LPT initial conditions, ensures an accurate mass function and power spectrum \citep{2014NewA...30...79L}.
-
-Mock galaxy samples are produced from the HR4 simulation by using a modified version of the one-to-one correspondence scheme \citep{hong2016}. 
-The most bound member particles (MBPs) of simulated halos are adopted as the tracer of galaxies rather than the subhalos,
-and the merger timescale is taken into account in the lifetime of merged halos.
-We built the merger trees of simulated halos by tracking their MBPs from $z = 12$ to 0.
-When a merger event occurs, we calculate the merger timescale described in \cite{jiang2008} (hereafter J08)
-to determine when a satellite galaxy is completely disrupted.
+We test the method on the Horizon Run 4  (HR4) simulation \citep{hr4}.
+HR4 used $N=6300^3$ particles in a box size of $L={3150}$ $h^{-1}$Mpc.  
+It adopted the second order Lagrangian perturbation theory (2LPT) initial conditions at $z_{i}=100$
+and a WMAP5 cosmology $(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96) \citep[]{komatsu 2011}.
+The particle mass is $\simeq m_{p} \simeq 9.02 \times 10^9 \hMsun$.
+%This starting redshift, combined  with 2LPT initial conditions, ensures an accurate mass function and power spectrum \citep{2014NewA...30...79L}.
+
+Mock galaxy samples are produced from the simulation based on a modified one-to-one correspondence scheme \citep{hong2016}. 
+The most bound member particles (MBPs) of simulated halos are adopted as the tracer of galaxies,
+and the merger timescale is computed to get the lifetime of merged halos.
+Merger trees of simulated halos are constructed by tracking their MBPs from $z = 12$ to 0.
+When a merger event occurs, we adopt the formular of \cite{jiang2008} to calculate the merger timescale 
+and determine when a satellite galaxy is completely disrupted.
 %We modeled the position and the velocity of a galaxy from the position and velocity of its corresponding MBP.
-By using the abundance matching, 
-we modeled the luminosity of a central/isolated galaxies from their current mass
-and of satellite galaxies 
-from their mass at the time of infall.
-
-\cite{hong2016} compared the 2pCF of our mock galaxy sample at $z = 0$ to the SDSS DR7 volume-limited galaxy sample \citep{zehavi2011}.
+%By using the abundance matching, 
+%we modeled the luminosity of a central/isolated galaxies from their current mass
+%and of satellite galaxies from their mass at the time of infall.
+
+\cite{hong2016} compared the 2pCF of the SDSS DR7 volume-limited galaxy sample \citep{zehavi2011} and the HR4 $z=0$ mock galaxies.
 %When a typical subhalo-galaxy correspondence scheme is applied, 
@@
 %We found that %the %2pCF of our galaxy sample agrees well with the observation.
-The simulated 2pCF shows a similar finger of god (FOG) feature \citep{FOG} as the observation in the contour map, 
-and the projected 2pCF agrees with the observation within 1$\sigma$ deviation on scales greater than 1 ${h^{-1}}$Mpc.
+The mock galaxies shows a similar finger of god (FOG) feature \citep{FOG} as the observation.
+On scales greater than 1 ${h^{-1}}$Mpc., 
+the projected 2pCF of the mock and observational samples agree within 1$\sigma$ deviation.
 
 %As will be introduced in the next section, 
-The HR4 simulation yield one all-sky light cone mock galaxy catalogue reaching $r=3\,150$ ${h^{-1}}$Mpc.
-As shown in \cite{bossAP},
-from one all-sky survey, 
-we are able to create four sets of non-overlapping north Galactic cap (NGC) samples for CMASS and LOWZ, 
-or eight sets of non-overlapping south Galactic cap (SGC) samples.
-In this paper we use these simulated galaxies for the estimation of the systematics in the 2pCF of the observed galaxies.
+The output of HR4 simulation includes one all-sky light cone mock galaxy catalogue reaching $r=3\,150$ ${h^{-1}}$Mpc 
+and a series ({\bf how many?}) of snapshot mock galaxy catalogues at different redshifts.
+In this paper we use five snapshot data at $z=0,0.5,1,1.5,2$.
+We require subhalos to have at least 30 member particles, 
+so the minimal mass of galaxies is $\simeq m_{p} \simeq 2.7 \times 10^{11} \hMsun$.
+At the five redshifts, we get a number of
+%$4.57\times 10^8$, $4.06\times 10^8$, $3.52\times 10^8$, $3.06\times 10^8$ and $2.28 \times 10^8$ mock galaxies,
+457, 406, 352, 206 and 228 million mock galaxies,
+corresponding to a number density of 
+%$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
+1.46, 1.30, 1.13, 0.98 and 0.73 in unit of $ 10^{-2} h^{3} \rm Mpc^{-3}$,
+%$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
+respectively.
 
@@
 
-We measure the 2pCF in redshift bins of galaxies and 
-determine cosmological parameters by examining the redshift evolution of clustering anisotropy.
+We measure the angular 2pCF in the five redshifts.
+We determine cosmological parameters by examining the redshift evolution of clustering anisotropy.
 Mock survey samples are used to correct the results for the systematics and to estimate the covariance.

### 2016-08-26 gitpush.sh
updates

@@ -15,6 +15,8 @@ git add src/*.py
 git add src/fig*.eps
 git add src/*.ipynb
 
+git add J08*.slice*
+
 git add draft/BOSSAP/*.*
 git add draft/gal2pcf/*.*
 git add draft/draft*.pdf

### 2016-08-26 awkfile.sh
updates

@@ -1,0 +1,7 @@
+
+for zstr in 0 0.5 1 1.5 2
+do
+nowfile=J08.dat.z_$zstr.mge3.000e11.slice1.1
+awk < $nowfile '{if($1<800 && $2 < 800) print $1,$2}' >> $nowfile.part
+done
+

### 2016-08-26 gitpush.sh
updates

@@ -17,7 +17,7 @@ git add src/*.ipynb
 
 git add J08*.slice*
 
-git add draft/BOSSAP/*.*
+#git add draft/BOSSAP/*.*
 git add draft/gal2pcf/*.*
 git add draft/draft*.pdf
 git add draft/*.tex

### 2016-08-29 draft/draft0.tex
updates

@@
 \author{Cheng Cheng, }
-\affil{blahblahblah}
+\affil{Kavli Institute for Theoretical Physics China, Institute of Theoretical Physics, Chinese Academy of Sciences, Zhong Guan Cun Street 55\#, Beijing, 100190, P.R. China}
+\affil{University of Chinese Academy of Sciences, P.R. China}
 \author{Changbom Park,}
@@
 
-\section{Volume Effect}
+\section{Geometric deformation when }
 \label{sec:Voleffect}
@@
    \includegraphics[height=8cm]{fig1_a.eps}
-   \includegraphics[height=8cm]{fig1_b.eps}
+   \includegraphics[height=8.5cm]{fig1_b.eps}
    }
@@
    assuming a true cosmology of $\Omega_m=0.26$, $w=-1$.
-   Left panel shows a series of circular objects, measured by an observer located at the origin.
+   Left panel shows a series objects distributes as five perfect squares, measured by an observer located at the origin.
    Their true positions and shapes are plotted in blue dashed lines.
@@
 and standard dark energy EoS $w=-1$.
-If we were to distribute a series of perfect squares at various distances from 500 Mpc/h to ???? Mpc/h,
+If we were to distribute a series of perfect squares at various distances from 500 Mpc/h to 3\,000 Mpc/h,
 and an observer located at the origin were to measure their redshifts and compute their positions and shapes 
-using redshift-distance relations of ??? incorrect cosmologies
-\begin{enumerate}
- \item $\Omega_m=0.41$, $w=-1.3$,
- \item $\Omega_m=0.11$, $w=-0.7$,
-\end{enumerate}
+using redshift-distance relations of four incorrect cosmologies
+\begin{eqnarray}
+ & &{\rm (i)}.\ \Omega_m=0.40,\ w=-1.0, \nonumber \\ 
+ & &{\rm (ii)}.\ \Omega_m=0.15,\ w=-1.0, \nonumber\\ \noindent
+ & &{\rm (iii)}.\ \Omega_m=0.26,\ w=-0.5,\nonumber\\ \noindent
+ & &{\rm (iv)}.\ \Omega_m=0.26,\ w=-1.5, \nonumber \noindent
+\end{eqnarray}
 the shapes of the squares appear distorted (AP effect),
 and their volumes are changed (volume effect).
-In the cosmological model (ii) with $\Omega_m=0.11$, $w=-0.7$, we see a stretch of the shape in the line of sight (LOS) direction 
-(hereafter ``LOS shape stretch'')
-and magnification of the volume (hereafter ``volume magnification''), 
-while in the model with $\Omega_m=0.41$, $w=-1.3$, we see opposite effects of LOS shape compression and volume shrinkage.
-
-In the lower panel of Figure \ref{fig_xyquan}, we plot the $\frac{\Delta r_{\bot, \rm wrong}}{\Delta r_{\bot, \rm true}}$ redshift. 
-In cosmology (i), both quantities have values less than 1, 
-indicating LOS shape compression and volume shrink.
-The effect in cosmology (ii) is slightly more subtle. At low redshift, the effect of dark energy is important, 
-and there is LOS shape compression and volume reduction due to the quintessence like dark energy EoS.
-However, at higher redshift the role of dark matter is more important, and we see LOS shape stretch and volume magnification due to the small $\Omega_m$.
-
-More importantly, Figure \ref{fig_xyquan} highlights the redshift dependence of the AP and volume effects. 
-For example, in the cosmology with $\Omega_m=0.41$, $w=-1.3$, 
-both the LOS shape stretch and volume magnification become more significant with increasing redshift.
-In the cosmology with $\Omega_m=0.11$, $w=-0.7$,
-not only do the magnitudes of the effects evolve with redshift,
-but there is also a turnover from LOS shape compression and volume shrink at lower redshift to LOS shape stretch and volume magnification at higher redshift.s
+In the cosmological models in model (i,iii) we see a compression of size (in both angular and LOS direction)
+and the degree of compression increases with increasing distance,
+while in models (ii,iv) we see stretch of size whose degree also evolves with redshift.
+Thus, when wrong cosmological parameters are adopted,
+the apparent size of objects are distorted, and the magnitude of distortion also varies with redshift.
+
+In this paper we will use the galaxy angular 2pCF to probe the redshift dependence of the distortion in angular direction.
+In the right panel of Figure \ref{fig_xyquan} we plot the redshift dependence of the change in angular size, 
+${\Delta r_{\bot, \rm wrong}}/{\Delta r_{\bot, \rm true}}$, in the four wrong cosmologies.
+In all cosmologies, there is clear evolution of ${\Delta r_{\bot, \rm wrong}}/{\Delta r_{\bot, \rm true}}$ 
+in the redshift range $0<z<2$.
+E.g., when use the quintessence cosmology 
+$\Omega_m=0.26,\ w=-0.5$ to infer the postions of objects,
+the angular size is underestimated by 
+%12.5\%, 17.7\%, 20.1\%, 21.3\%
+8.9\%, 12.3\%, 13.6\%, 14.1\% 
+at $z=0.5,1,1.5,2$.
 
@@
 
+\section{Galaxy angular 2pCF}
+
+\subsection{Galaxy distribution at different redshifts}
+
+The left panels of Figure \ref{fig_scatter} show the $x,y$ coordinates of galaxies in a 
+$260 h^{-1} {\rm Mpc} \times 130 h^{-1} {\rm Mpc} \times 105 h^{-1} {\rm Mpc}$ volume, 
+taken from the five snapshots.
+The gravitational growth of structures with decreasing redshift is clearly shown.
+We display all mock galaxies with $M> 3.0 \times 10^{11} \hMsun$.
+At lower redshift, galaxies become more massive, so they are more galaxies satisfying the threshold.
+
+If one adopts a wrong cosmology to compute galaxy positions, there would be a scaling of the galaxy distribution.
+In the left panel we show the case when a wrong set of parameters $\Omega_m=0.05,\ w=-1.5$ is assumed,
+leading to large upscaling of $25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts $z=0.5,1.0,1.5,2.5$.
+
+Compared with the true galaxy distribution, the apparent distribution inferred by wrong set of parameters
+show clear evolution with redshift due to the different scaling at different redshifts.
+In case of Figure \ref{fig_scatter}, the apparent size of large scale structures increases with redshift.
+
+The growth of structure also make the size of structures evolves with redshift.
+In the next subsection we will discuss how to distinguish these two effects in the galaxy angular 2pCF.
+
+\begin{figure*}
+   \centering{
+   %\includegraphics[height=5.9cm]{fig8_0.eps}
+   %\includegraphics[height=5.9cm]{fig8_wrongcos_0.eps}
+   \includegraphics[width=16cm]{fig2.eps}
+   }
+   \caption{\label{fig_scatter}
+  blah
+   }
+   % Need a better plot to show angular size variation!!!
+\end{figure*}
+
+\subsection{Galaxy angular 2pCF at different redshifts}
+
+\begin{figure*}
+   \centering{
+%   \includegraphics[width=18cm]{fig9_0.eps}
+%   \includegraphics[width=18cm]{fig9_1.eps}
+%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
+%    \includegraphics[height=8cm]{smu.eps}
+    \includegraphics[width=18cm]{fig2.eps}
+   }
+   \caption{\label{fig_diffz}
+  2pCF at different redshfits.
+   }
+\end{figure*}
+
+\begin{figure*}
+   \centering{
+%   \includegraphics[width=18cm]{fig9_0.eps}
+%   \includegraphics[width=18cm]{fig9_1.eps}
+%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
+%    \includegraphics[height=8cm]{smu.eps}
+    \includegraphics[width=18cm]{fig3.eps}
+   }
+   \caption{\label{fig_cosmo}
+   2pCF in cosmologies.
+   }
+\end{figure*}
+
+\begin{figure*}
+   \centering{
+   \includegraphics[width=16cm]{fig4.eps}
+   \includegraphics[width=16cm]{fig5.eps}
+   }
+   \caption{\label{fig_sys}
+  Systematic effects.
+   }
+\end{figure*}
+
+\section{cosmological constraint}
+
 \section{Methodology}\label{sec:methodology}
@@
 %Our procedure is as follows.
+
+%\begin{minipage}{0.9\linewidth}
+%\includegraphics[width= 0.3\linewidth]{fig8_0.eps}
+%\caption{\label{fig8} hahaha}
+%\end{minipage}
 
@@
 %   \includegraphics[width=14cm]{fig5.eps}
-   %\includegraphics[width=14cm]{Tpcf--contour.eps}
+   \includegraphics[width=14cm]{fig9.eps}
    }
@@
 
-\begin{figure*}
-   \centering{
-%   \includegraphics[width=18cm]{fig9_0.eps}
-%   \includegraphics[width=18cm]{fig9_1.eps}
-%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
-%    \includegraphics[height=8cm]{smu.eps}
-    \includegraphics[width=18cm]{fig2.eps}
-   }
-   \caption{\label{fig_diffz}
-  2pCF at different redshfits.
-   }
-\end{figure*}
-
-\begin{figure*}
-   \centering{
-%   \includegraphics[width=18cm]{fig9_0.eps}
-%   \includegraphics[width=18cm]{fig9_1.eps}
-%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
-%    \includegraphics[height=8cm]{smu.eps}
-    \includegraphics[width=18cm]{fig3.eps}
-   }
-   \caption{\label{fig_cosmo}
-   2pCF in cosmologies.
-   }
-\end{figure*}
-
-\begin{figure*}
-   \centering{
-   \includegraphics[width=16cm]{fig4.eps}
-   \includegraphics[width=16cm]{fig5.eps}
-   }
-   \caption{\label{fig_sys}
-  Systematic effects.
-   }
-\end{figure*}
 \subsection{Cosmological Constraints}

### 2016-08-30 draft/draft0.tex
updates

@@
 
-\subsection{Galaxy angular 2pCF at different redshifts}
-
-\begin{figure*}
-   \centering{
-%   \includegraphics[width=18cm]{fig9_0.eps}
-%   \includegraphics[width=18cm]{fig9_1.eps}
-%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
-%    \includegraphics[height=8cm]{smu.eps}
-    \includegraphics[width=18cm]{fig2.eps}
-   }
-   \caption{\label{fig_diffz}
-  2pCF at different redshfits.
-   }
-\end{figure*}
+\subsection{Galaxy angular 2pCF: amplitude and shape at different redshifts}
 
@@
    }
+   \caption{\label{fig_diffz}
+  2pCF at different redshfits.
+   }
+\end{figure*}
+
+The left panel of Figure \ref{fig_diffz} displays the measured angular 2pCF of galaxies (multiplied by scale $r$) in the five snapshot.
+
+The amplitude of 2pCF is crucially affected by the cosmic structure growth and the galaxy bias.
+%The amplitude is higher at $z=0$, 
+We find $\xi(z=0)>\xi(z=0.5)>\xi(z=1)$.
+At low redshift, the large scale structures experienced most gravitational growth,
+leading to stronger clustering strength and higher amplitude of 2pCF.
+On the contrary, at higher redshift we find $\xi(z=2)>\xi(z=1.5)>\xi(z=1)$,
+%The trend is different from $z=1,1.5,2$,
+simply because by applying a uniform mass cut we are selecting more biased galaxies at higher redshift.
+
+Different from the large variation of amplitude among the different redshifts, %The shape of $r\xi$ also evolves with redshift.
+the shape of 2pCF maintains similar at all redshifts. 
+At all redshifts, we see the $r\xi$ peaks at $r\sim9 h^{-1}\rm Mpc$,
+and monotonically drops at larger or smaller scales.
+The only exception is the relative enhancement of 2pCF at $r\lesssim 2 h^{-1}\rm Mpc$,
+which is caused by the non-linear growth of structures on small scales 
+and becomes more dramatic at lower redshfit.
+
+The middle panel of Figure \ref{fig_diffz} displays the $r\xi$ normalized by the overall amplitude within $5h^{-1}{\rm Mpc} < r < 50h^{-1}{\rm Mpc}$
+(here after $\hat r\xi$).
+The nice overlapping of the results from five redshifts 
+suggests small evolution of shape with redshift.
+In the right panel, we compare the high redshift $\hat r\xi$ 
+to the $z=0$ result.
+There is 1-4\% relative enhancement 
+at $r<10h^{-1}\rm Mpc$,
+and $<1.5\%$ relative suppression at $r>25 h^{-1}\rm Mpc$.
+The trend is monotonic with redshift.
+
+In all, we conclude that the shape of the 2pCF is more robust than the amplitude against redshift and galaxy bias.
+
+\subsection{Galaxy angular 2pCF: in wrong cosmologies }
+
+\begin{figure*}
+   \centering{
+%   \includegraphics[width=18cm]{fig9_0.eps}
+%   \includegraphics[width=18cm]{fig9_1.eps}
+%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
+%    \includegraphics[height=8cm]{smu.eps}
+    \includegraphics[width=18cm]{fig4.eps}
+   }
    \caption{\label{fig_cosmo}
@@
    \centering{
-   \includegraphics[width=16cm]{fig4.eps}
    \includegraphics[width=16cm]{fig5.eps}
+   \includegraphics[width=16cm]{fig6.eps}
    }

### 2016-08-30 draft/draft0.tex
updates

@@
  %{\rm rat}_{\rm volume\ mag}\equiv
- \frac{\Delta r_{\bot, \rm wrong}}{\Delta r_{\bot, \rm true}}
+ \alpha_{\bot} \equiv \frac{\Delta r_{\bot, \rm wrong}}{\Delta r_{\bot, \rm true}}
  = \frac{D_{A, \rm wrong}}{D_{A, \rm true}},
@@
     \includegraphics[width=18cm]{fig3.eps}
+    \includegraphics[width=18cm]{fig3_b.eps}
    }
@@
 \subsection{Galaxy angular 2pCF: in wrong cosmologies }
+
+When a wrong set of cosmological parameters is adopted,
+the galaxy distribution is artificially scaled.
+This scaling is expected to change the shape of the 2pCF,
+following the relationship,
+\begin{equation}
+ \hat \xi_{\rm wrong}(r) = \hat\xi_{\rm true}(\alpha_{\bot} r),
+\end{equation}
+a simple consequence of the fact that clustering patterns at distance $r$ now appears on a the scale $\alpha_{\bot} r$.
+The redshift evolution of $\alpha_{\bot}$ leads to redshfit evolution of shape.
+
+\begin{figure*}
+   \centering{
+%   \includegraphics[width=18cm]{fig9_0.eps}
+%   \includegraphics[width=18cm]{fig9_1.eps}
+%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
+%    \includegraphics[height=8cm]{smu.eps}
+
+   }
+   \caption{\label{fig_cosmo}
+   2pCF in cosmologies.
+   }
+\end{figure*}
+
+Lower panels of Figure \ref{fig_diffz} shows the $r\xi$ in five 
+snapshots, in case that the cosmology $\Omega_m=0.05,\ w=-1.5$ 
+is adopted to construct the galaxy distribution (the right panels of Figure \ref{fig_scatter}).
+The middle panel displays the clear redshift evolution of shape of $r\xi$.
+E.g, from $z=0$ to $z=2$,
+the peak location is shifted from $r=9h^{-1} \rm Mpc$ to $r\sim15 h^{-1}\rm Mpc$ at $z=2$
+since the angular separation is upscaled by $71.7\%$.
+
+The right panel shows that, 
+at higher redshift, 
+there is a 20-40\% change in the value of $\hat {r\xi}$.
+
+The amplitude of $r\xi$ is amplified due to the stretch of scale.
+As shown in the left panel, the amplitude monotonically increases as a function of redshift.
+But this phenomenon can also appear in case of gravitational growth of structure or increasing of bias,
+so we will not make use of it to do cosmological constraint.
+We utilize the redshift evolution of the 2pCF shape as a signal suggesting that the assumed cosmological parameters are wrong.
+
+In Figure \ref{fig_cosmo} we further plot the redshift evolution of 2pCF in the four wrong cosmologies of Figure \ref{fig_xyquan}.
+In all cases, the scaling leads to evident redshift evolution of the shape of $r\xi$.
+When the cosmologies $\Omega_m=0.4,w=-1$ and $\Omega_m=0.26,w=-0.5$ are adopted,
+the compression of structure makes the clustering patterns appears on smaller scales.
+This leads to ``steeper'' slope of $r\xi$, 
+and the higher the redshift, the steeper the slope.
+To the opposite, when adopting the cosmologies $\Omega_m=0.15,w=-1$ and $\Omega_m=0.26,w=-1.5$,
+the stretch of size makes the slope shallower at higher redshfits.
+
+\subsection{Systematic effects}
+
+\subsection{Likelihood Analysis}
+
+One can build up a likelihood function to 
+describe how significant is the redshift evolution of the 2pCF shape
+so that to determine whether the adopted cosmological parameters are correct.
+\begin{equation}\label{eq:chisq1}
+\chi^2\equiv \sum_{i=2}^{6} \sum_{j_1=1}^{n_{\mu}} \sum_{j_2=1}^{n_{\mu}} {\bf p}(z_i,\mu_{j_1}) ({\bf Cov}_{i}^{-1})_{j_1,j_2}  {\bf p}(z_i,\mu_{j_2}),
+\end{equation}
+where ${\bf p}(z_i,\mu_{j})$ is the redshift evolution of clustering, 
+$\hat \xi_{\Delta s}$, with systematic effects subtracted
+\begin{eqnarray}\label{eq:bfp}
+ {\bf p}(z_i,\mu_{j}) \equiv&\ \delta \hat{r\xi}(z_i,z_1,\mu_j) - \delta \hat{r\xi}_{\rm sys}(z_i,z_1,\mu_j)
+\end{eqnarray}
+${\bf Cov}_i$ is the covariance matrix estimated from the 72 sets of PSB mock galaxies identified from HR3 N-body simulation.
 

### 2016-08-31 draft/draft0.tex
updates

@@
    %\includegraphics[height=5.9cm]{fig8_wrongcos_0.eps}
-   \includegraphics[width=16cm]{fig2.eps}
+   %\includegraphics[width=16cm]{fig2.eps}
+   \includegraphics[width=16cm,natwidth=8,natheight=14]{fig2.pdf}
    }
@@
 
-\begin{figure*}
-   \centering{
-%   \includegraphics[width=18cm]{fig9_0.eps}
-%   \includegraphics[width=18cm]{fig9_1.eps}
-%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
-%    \includegraphics[height=8cm]{smu.eps}
-
-   }
-   \caption{\label{fig_cosmo}
-   2pCF in cosmologies.
-   }
-\end{figure*}
-
 Lower panels of Figure \ref{fig_diffz} shows the $r\xi$ in five 
@@
 \subsection{Systematic effects}
+
+The same as \cite{Li2014,Li2015,Li2016} we need to correct for the redshift evolution of $r\xi$ caused by effects other than the wrongly assumed cosmological parameters.
+
+Figure \ref{fig_diffz} already shows that, the growth of structure, especially in low redshift and on non-linear scales, 
+changes the shape of $r\xi$ and caused relative enhancement on $r\lesssim2 h^{-1}\rm Mpc$.
+So we limit the region of scale to $r>5h^{-1}\rm Mpc$ to minimize its effect.
+
+Galaxies are biased tracers of dark matter field, 
+and more massive galaxies tend to reside in regions with higher density contrast.
+So in large scale structure surveys the bias of the galaxy sample is an important fator which has large effect on the clustering properties of the sample.
+The upper panels of Figure \ref{fig_sys} displays five set of galaxy samples in a $3175\times3175\times105$ $(h^{-1}\rm Mpc)^3$ volume, taken from the $z=0$ snapshots data.
+Different lower mass limits of $3\times 10^{11} M_{\odot}$, $3\times 10^{11} M_{\odot}$, $3\times 10^{11} M_{\odot}$ and $3\times 10^{11} M_{\odot}$
+are imposed to create subsamples with different galaxy bias, 
+and the measured angular 2pCF are displayed.
+The different mass cuts result in large variation in the amplitude of the 2pCF (left panel),
+while the shape of the 2pCF remains less affected (middle panel).
+Compared with the sample with mass cut $M>3\times 10^{11} M_{\odot}$,
+samples with mass limit $3\times 10^{11} M_{\odot}$, $3\times 10^{11} M_{\odot}$ and $3\times 10^{11} M_{\odot}$
+have the amplitude of 2pCFs enhanced by $10\%,\ 50\%$ and $100\%$,
+while the change in $\hat{r\xi}$ is only $0.5\%,\ 2\%$ and $4\%$.
+Considering the very large change in the mass cut,
+the change in the shape of 2pCF is not significant.
+
+The galaxy peculiar velocity contribute to the observed galaxy redshift and distorted the galaxy radial position in redshift space,
+known as the redshift space distortion (RSD).
+It is the major source of systematics for our analysis of \cite{Li2014,Li2015,Li2016}, where the 3D galaxy distribution is utilized to derive cosmological constraint.
+In this analysis its effect becomes much milder since the angular positions of the galaxies is not affected by RSD at all.
+But it still affects our analysis in the procedure of preparing the subsamples of galaxies for 2pCF analysis.
+The galaxies observed in a survey are split into shells of subsamples, with different redshift ranges, to get the 2pCF at different redshifts.
+RSD disortes the galaxy redshift and as a result some galaxies close the boundaries of shells will be distributed to wrong redshift shells.
+
+The lower panel of Figure \ref{fig_sys} displays the RSD effect on 2pCF.
+To mimick the effect of RSD we shift the $Z$ coordinates of galaxies according to the relation 
+\begin{equation}\label{eq:zvpeu}
+\Delta z = (1+z) \frac{v_{{\rm Z}}}{c},
+\end{equation}
+where $v_{{\rm Z}}$ is the galaxy peculiar velocity in $Z$ direction.
+Then we split the whole box into 30 slices with thickness $105h^{-1}\rm Mpc$, 
+and measure the angular 2pCF.
+The left panel shows that the amplitude of measured 2pCF is enhanced by $\sim 10\%$ in case of considering the RSD effect on spliting samples.
+The middle panel shows that the shape of 2pCF is also altered -- the slop is suppressed.
+If looking at the redshift evolution,
+the curves $\hat{r\xi} - \hat{r\xi}(z=0)$ displayed in the right panel,
+they changed a lot compared with the case of no RSD effect (the right panel of Figure \ref{fig_diffz}),
+but do not become much larger. %But RSD effect does not introduce large redshfit evolution, although the shape of  is
+
+Another effect is redshfit errors ...
+Especially large in photometric surveys...
+
+One shall construct reliable mock surveys to correct the systematic effects ...
+
+%The outer boundary of the mock survey becomes fuzzy due to the peculiar velocity effect 
+%on the galaxy redshifts (Eq. (\ref{eq:zvpeu})).
+%A population of galaxies, that are expected to enter the $z<0.7$ region from the outside, is missing.
+%(these $z>0.7$ galaxies have a peculiar velocity toward us and 
+%their observed redshfits become lower than 0.7).
+%To avoid this problem we set the maximal redshift at 0.693, 
+%23.3 $h^{-1}{\rm Mpc}$ away from $z=0.7$.
+
+%3.000e11', '1.000e12', '4.000e12',  '1.000e13
+
+\begin{figure*}
+   \centering{
+   \includegraphics[width=16cm]{fig5.eps}
+   \includegraphics[width=16cm]{fig6.eps}
+   }
+   \caption{\label{fig_sys}
+  Systematic effects.
+   }
+\end{figure*}
 
@@
    2pCF in cosmologies.
-   }
-\end{figure*}
-
-\begin{figure*}
-   \centering{
-   \includegraphics[width=16cm]{fig5.eps}
-   \includegraphics[width=16cm]{fig6.eps}
-   }
-   \caption{\label{fig_sys}
-  Systematic effects.
    }

### 2016-09-01 draft/draft0.tex
updates

@@
 
-Another effect is redshfit errors ...
-Especially large in photometric surveys...
-
-One shall construct reliable mock surveys to correct the systematic effects ...
+Similar to RSD, the redshift errors in survey can affect the subsamples of galaxies by buring the boundaries of shells.
+This effect should be properly quantified, especially in case of a photometric survey where the redshift uncertainty can be $\Delta z \\approx 0.02$.
+
+In \cite{Li2014,Li2015,Li2016}, the systematic effects contributing to the redshfit evolution of galaxy clusterings 
+are modeled in mock surveys and subtracted.
+Similar treatment could be conducted here.
+One shall construct mock surveys with the above effects included for the correction of systematics.
 
@@
 
-One can build up a likelihood function to 
-describe how significant is the redshift evolution of the 2pCF shape
+We build up a likelihood function to 
+describe how significant is the redshift evolution of the 2pCF shape,
 so that to determine whether the adopted cosmological parameters are correct.
+The redshift evolution is characterized by the difference between the $\hat{r\xi}$ measured in the lowest redshift and higher ones;
+the cosmology having least redshift evolution of $\hat{r\xi}$ is considered to be the most plausible one and has smallest $\chi^2$.
+So we have
 \begin{equation}\label{eq:chisq1}
-\chi^2\equiv \sum_{i=2}^{6} \sum_{j_1=1}^{n_{\mu}} \sum_{j_2=1}^{n_{\mu}} {\bf p}(z_i,\mu_{j_1}) ({\bf Cov}_{i}^{-1})_{j_1,j_2}  {\bf p}(z_i,\mu_{j_2}),
+\chi^2\equiv \sum_{i=2}^{n_{z}} \sum_{j_1=1}^{n_{r}} \sum_{j_2=1}^{n_{r}} {\bf p}(z_i,r_{j_1}) ({\bf Cov}_{i}^{-1})_{j_1,j_2}  {\bf p}(z_i,r_{j_2}),
 \end{equation}
-where ${\bf p}(z_i,\mu_{j})$ is the redshift evolution of clustering, 
-$\hat \xi_{\Delta s}$, with systematic effects subtracted
+where $n_z$ is the number of redshifts, 
+is number of bins in $\hat{r\xi(r)}$;
+in this analysis we have five redshift bins, 
+and 35 $r$ bins with bin width $1h^{-1}\rm Mpc$ in the range $5h^{-1}{\rm Mpc}<r<40h^{-1}{\rm Mpc}$.
+${\bf p}(z_i,r_{j})$ is the redshift evolution of clustering, 
+$\hat {r\xi}$, with systematic effects subtracted
 \begin{eqnarray}\label{eq:bfp}
- {\bf p}(z_i,\mu_{j}) \equiv&\ \delta \hat{r\xi}(z_i,z_1,\mu_j) - \delta \hat{r\xi}_{\rm sys}(z_i,z_1,\mu_j)
+ {\bf p}(z_i,r_{j}) \equiv&\ \delta \hat{r\xi}(z_i,z_1,r_j) - \delta \hat{r\xi}_{\rm sys}(z_i,z_1,r_j)
 \end{eqnarray}
-${\bf Cov}_i$ is the covariance matrix estimated from the 72 sets of PSB mock galaxies identified from HR3 N-body simulation.
+${\bf Cov}_i$ is the covariance matrix.
+
+It is difficult to conduct the 2pCF of the whole snapshot box with hundreds of millions of galaxies.
+We split the box into 120 subsamples with $X,Y,Z$ sizes of $1575h^{-1}{\rm Mpc},1575h^{-1}{\rm Mpc}, 105h^{-1}{\rm Mpc}$
+and measure the angular 2pCF in the $X-Y$ plan in these subsamples. 
+The average of the 2pCFs are taken as the 2pCF of the whole box.
+The covariance matrix is also estimated from these 2pCFs.
+
+In real observations we observe {\it different} objects at different redshfit shells.
+To mimick this when calculating the redshift evolution of 2pCF we use subsamples at different positions at different redshfits.
+E.g., if for the $z=0$ snapshot we use the $\hat{r\xi}$ measured in the subsample $0h^{-1}{\rm Mpc}<Z<105 h^{-1}{\rm Mpc}$,
+at higher redshifts we adopt the $\hat{r\xi}$ measured in a subsample $105h^{-1}{\rm Mpc}<Z<210 h^{-1}{\rm Mpc}$,
+and take the difference between them to get $\delta \hat{r\xi}$.
+So we are always comparing 2pCF measured from different samples of galaxies.
+If simply comparing the 2pCF of a same sample of galaxies at different redshifts, 
+one would significantly underestimate the statistical undertainty of $\delta \hat{r\xi}$ by ignoring the cosmic variance
+\footnote{The error bars displayed in all figures are estimated from the 120 subsamples and for the error bar of redshift evolution of 2pCF 
+we always take the cosmic variance into consideration.}.
+%estimated from the 72 sets of PSB mock galaxies identified from HR3 N-body simulation.
+
+Figure \ref{fig_cosmo} displayed the 2pCF measured in the four cosmologies displayed in Figure \ref{fig_xyquan}.
+For the cosmologies $\Omega_m=0.4,w=-1$ and $\Omega_m=0.26,w=-0.5$,
+the compression of structure rescale large scale clustering patterns into small scales;
+the compression becomes more significant at higher redshift.
+In these cosmologies we get 2pCFs with steeper slope and, the higher redshift, the steeper.
+For $\Omega_m=0.15,w=-1$ and $\Omega_m=0.26,w=-1.5$,
+the stretch of structure leads to shallower slope of $\hat{r\xi}$ and, the higher the redshift, the shallower.
+In all cosmologies we find significant detection of redshift evolution of $\hat{r\xi}$ (in the lowest panels, $\delta \hat{r\xi}\neq0$).
+We computed the $\chi^2$ values according to Equation \ref{eq:chisq1} and found these sets of cosmological parameters are strongly disfacored 
+at $\gtrsim30\sigma$ CL.
 
@@
 
-\section{cosmological constraint}
-
-\section{Methodology}\label{sec:methodology}
-
-We measure the angular 2pCF in the five redshifts.
-We determine cosmological parameters by examining the redshift evolution of clustering anisotropy.
-Mock survey samples are used to correct the results for the systematics and to estimate the covariance.
-%Our procedure is as follows.
-
-%\begin{minipage}{0.9\linewidth}
-%\includegraphics[width= 0.3\linewidth]{fig8_0.eps}
-%\caption{\label{fig8} hahaha}
-%\end{minipage}
-
-\subsection{Grid of cosmology parameters}
-
-The observed coordinates ({\it RA, Dec, z}) of galaxies
-need to be converted to comoving coordinates ({\it x, y, z}) for the 2pCF analysis.
-The dependence of clustering anisotropy on cosmology enters through the conversion from redshift to comoving distance,
-i.e. the distance-redshift relation $r(z)$.
-We consider the case of a flat Universe dominated by matter and dark energy,
-so our $r(z)$ is governed by two parameters, $\Omega_m$ and $w$, as presented in Equation (\ref{eq:HDA})	.
-
-To constrain these two parameters we examine the parameter space of 
-$0.06\leq \Omega_m\leq 0.41$ and $-1.5 \leq w \leq -0.4$ with intervals of 
-$\delta \Omega_m = 0.005$ and $\delta w = 0.025$,
-forming a 71$\times$45 grid.
-%This coverage and step size shall be enough for us to determine the 95\% confidence level (CL) region with satisfactory precision.
-For each set of ($\Omega_m$, $w$), 
-the comoving coordinates of all galaxies are computed, 
-%the 2pCF of these galaxies in six redshift bins are measured,
-%and a $\chi^2$ value is then obtained by requiring least redshift evolution of anisotropy.
-%This enables us to infer the values and underlying distributions of $\Omega_m$ and $w$ through Bayesian analysis.
-and the 2pCF is ready to be calculated.
-
-\begin{figure*}
-   \centering{
-%   \includegraphics[width=14cm]{fig5.eps}
-   \includegraphics[width=14cm]{fig9.eps}
-   }
-   \caption{
-    \label{fig_2pcfcon} 
-    2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples 
-      in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
-    The black dashed lines mark the scales 6\ $h^{-1}$Mpc $\leq s\leq$ 40\ $h^{-1}$Mpc.
-    %The correlation functions have rather large values on small sales such as $s=5$ $h^{-1}$Mpc,
-    %  and monotonically decreases to smaller values on larger scales due to weaker clustering.
-    The contour lines are not horizontal due to the effects of peculiar velocity.
-    The FOG and Kaiser effects clearly manifest themselves through the tilting of contour 
-     lines where $1-\mu \rightarrow 0$ and $1-\mu \gtrsim0.1$, respectively.
-    The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$.
-   }
-      %The redshift density distribution of the BOSS DR12 galaxy samples, assuming a $\Lambda$CDM cosmology with $\Omega_m=0.31$.
-      %The blue and green solid histograms show the distribution of LOWZ and CMASS galaxies respectively. 
-      %The vertical dashed lines define the 6 redshift bins that are used to cut the samples.   }
-\end{figure*}
-
-\subsection{Measuring the correlation function}
-
-%We probe the Alcock-Paczynski effects using the 2pCF. 
-%The 2pCF is a mature statistic in cosmology and its optimal estimation considers minimal variance 
-%while dealing with complicated masks and selection functions. 
-%The most commonly adopted formulation is that of the 
-We adopt the Landy-Szalay estimator~\citep{1993ApJ...412...64L} to calculate the 2pCF,
+\section{Cosmological constraint}
+
+We constrain $\Omega_m$ and $w$ through Bayesian analysis (\citep{Bayesian}; also see \citep{LB2002,Li2016} for details).
+We assue the likelihood takes the form
 \begin{equation}
-\xi(s,\mu)=\frac{DD-2DR+RR}{RR}\ ,
+ \mathcal{L} \propto \exp\left[-\frac{\chi^2}{2}\right]
 \end{equation}
-where $DD$ is the number of galaxy--galaxy pairs, 
-$DR$ the number of galaxy-random pairs, 
-and $RR$ is the number of random--random pairs, 
-all separated by a distance defined by $s\pm\Delta s$ and $\mu\pm\Delta\mu$, 
-where $s$ is the distance between the pair and $\mu=\cos(\theta)$, 
-with $\theta$ being the angle between the line joining the pair of galaxies and the LOS direction to the target galaxy. 
-This statistic captures the anisotropy of the clustering signal.
-
-The random catalogue consists of unclustered points whose number density in redshift space mimics the radial selection function of the observational data. 
-To reduce the statistical variance of the estimator we use 50 times as many random points as we have galaxies.
-The galaxies and random points are weighted as described in Sec. \ref{sec:data}.
-
-Figure \ref{fig_2pcfcon} shows the 2D contour of measured $\xi$ as a function of $\mu$ and $s$,
-from the six redshift bins of LOWZ and CMASS samples 
-in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
-%The correlation functions have rather large values on small sales such as $s=5$ $h^{-1}$Mpc,
-%and monotonically decrease to smaller values on larger scales due to weaker clustering.
-Due to the peculiar velocity effect, the contour lines are not horizontal.
-The FOG \citep{FOG} and Kaiser \citep{Kaiser1987} effects 
-clearly manifest themselves through the tilting of contour lines in regions of $\mu \rightarrow 1$ and $1-\mu \gtrsim0.1$, respectively.
-A visual inspection of the contour maps from the six redshift bins 
-reveals that they all have a similar appearance,
-implying small redshift evolution of $\xi$.
-
-\subsection{Probing the anisotropy through 2pCF}
-
-The 2pCF is measured as a function of the separation $s$ and the angular direction $\mu$.
-To probe the anisotropy we are more interested in the dependence of the 2pCF on $\mu$.
-We follow the procedure of \cite{Li2015} and integrate the $\xi$ over the interval $s_{\rm max} \leq s \leq s_{\rm min}$.
-We evaluate
-\begin{equation}\label{eq:xideltas}
-\xi_{\Delta s} (\mu) \equiv \int_{s_{\rm min}}^{s_{\rm max}} \xi (s,\mu)\ ds.%,\ \ \ {\rm at\ particular\ binned\ direction\ }\mu_i
-\end{equation}
-The integration is limited at both small and large scales.
-At small scales the value of $\xi$ is seriously affected by the FOG effect \citep{FOG}
-which depends on the galaxies bias.
-This may introduce a redshift evolution in $\xi_{\Delta s}(\mu)$ that is relatively difficult to model.
-At large scales the measurement is dominated by noise due to poor statistics.
-\cite{Li2015} found that $s_{\rm min}=6-10$ $h^{-1}$Mpc and $s_{\rm max}=40-70$ $h^{-1}$Mpc are reasonable choices 
-which provide consistent, tight and unbiased constraints on cosmological parameters.
-In this analysis we choose $s_{\rm min}=6$ $h^{-1}$Mpc and $s_{\rm max}=40$ $h^{-1}$Mpc.
-
-The redshift evolution of the bias of observed galaxies leads to redshift evolution of the strength of clustering,
-which is difficult to accurately model.
-To mitigate this systematic uncertainty we rely on the shape of $\xi_{\Delta s}(\mu)$, rather than its amplitude,
-\begin{equation}\label{eq:norm}
- \hat\xi_{\Delta s}(\mu) \equiv \frac{\xi_{\Delta s}(\mu)}{\int_{0}^{\mu_{\rm max}}\xi_{\Delta s}(\mu)\ d\mu}.
-\end{equation}
-We impose a cut $\mu<\mu_{\rm max}$ to reduce the fiber collision and FOG effects which are stronger toward the LOS ($\mu\rightarrow1$) direction.
-
-The clustering properties may be affected by various properties of the galaxy sample, 
-such as, for example the mass, morphology, color, concentration. 
-In our simulation, using the merger tree, 
-we identify ``galaxies'', therefore we only use the galaxy mass building history to simulate BOSS galaxies. 
-Therefore, it is necessary for us to test if our mock galaxies can accurately 
-reproduce the $\hat\xi_{\Delta s}(\mu)$ of observed galaxies.
-
-%The clustering properties may be affected by the redshift evolution of properties of the galaxy sample, 
-%such as the mass, morphology, color, concentration, and so on. 
-%In our simulation, using the merger tree, we identify 'galaxies' so that we only use the galaxy mass to simulate BOSS galaxies.
-Therefore, it was necessary for us to test if our mock galaxies can accurately reproduce the shape of $\xi_{\Delta s}(\mu)$ of observed galaxies.
-
-%As shown by Figure 6, the mock galaxies from our HR4 simulation can well reproduce the 
-%$\hat\xi_{\Delta s}(\mu)$ of the observed galaxies.
-Figure \ref{fig_datamock}  compares the shape of $\hat\xi_{\Delta s}(\mu)$ measured from observational data and mock survey samples.
-It is clear that $\hat \xi_{\Delta s}(\mu)$ from mock galaxies identified in the HR4 simulation (green dotted line) agrees well with the observation.
-%The HR4 galaxy mock can well reproduce the result from observational measurement.
-The enhancement near $\theta=0^\circ$ is caused by the FOG effect,
-and the characteristic shape in $20^\circ\lesssim\theta\lesssim90^\circ$ 
-produced from the large-scale flow
-are all very well reproduced.
-This result verifies the ability of our mock galaxies to reproduce the clustering properties of the observed galaxies.
-The small overestimate (underestimate) of $\hat\xi_{\Delta s}$ at large (small) $\mu$ could be due to 
-that our mocks galaxies are more massive than those in the observations.
-%methodology. (AMTB: need some good expression; need consult SW)
-%Conversely, the HR3 PSB halo galaxies do not accurately reproduce the observations.
-We use the HR4 galaxy mocks to correct the systematics.
-%The HR3 PSB mock galaxies are used to estimate the covariance of 2pCF since 72 mock survey samples are available.
-
-%It is impossible to probe $\hat\xi_{\Delta s}(\mu)$ as a continuous function with infinite degrees of freedom. 
-We divide the full angular range $0\leq\mu\leq\mu_{\rm max}$ into $n_{\mu}$ bins and measure its value in each bin.
-Since we are free to choose $\mu_{\rm max}$ and $n_{\mu}$,
-they are varied to optimize the S/N of our results.
-This topic will be discussed in Sec. \ref{sec:binningscheme}.
-
-\subsection{Characterizing the redshift evolution}
-
-As shown in Figure \ref{fig_nbar}, we split the BOSS DR12 galaxies into six redshift bins, three in LOWZ and three in CMASS.
-To study the redshift evolution of the clustering anisotropy 
-we use the {\it first redshift bin} as the reference and compare the measurements in other bins with that in the first.
-We define
-\begin{equation} \label{eq:deltahatxi}
-\delta \hat\xi_{\Delta s}(z_i,z_1,\mu_j)\ \equiv\ \hat\xi_{\Delta s}(z_i,\mu_j) - \hat\xi_{\Delta s}(z_1,\mu_j)
-\end{equation}
-where $\hat\xi_{\Delta s}(z_i,\mu_j)$ is $\hat\xi_{\Delta s}$ measured in the $i$th redshift bin and $j$th $\mu$ bin,
-where $1\leq i \leq 6$ and $1\leq j \leq n_{\mu}$.
-To characterize the shape of the curve well $n_\mu \gtrsim5$ is required.
-
-\subsection{Correction for systematics}\label{sec:syscor}
-
-Other than the AP effect, there are additional effects 
-which may produce redshift-dependent anisotropy and affect the results.
-
-The observational artifacts, such as fiber collisions, redshift failures, 
-and the non-cosmological density fluctuations with stellar density and seeing,
-are accounted for in the galaxy weights \citep{Reidetal:2016}.
-Fiber collisions and redshift failures may affect the value of $\hat\xi(\mu)$ in the region close to LOS;
-%We correct them by reweighting galaxies, include fiber collisions in the construction of mock surveys,
-we abandon the angular region of $1-\mu<0.01$, 
-to avoid possible systematics (see Appendix \ref{sec:RBtest} for more discussion).
-
-%The SGC catalogues have higher target density than NGC and 
-%thus a higher galaxy number density, known as the north/south asymmetry.
-The non-contiguous NGC and SGC are less well cross-calibrated with respect to each other 
-than they are internally calibrated \citep{Schlafly2010,SF2011,Parejko2013}.
-We construct the NGC and SGC mock surveys separately to avoid possible systematics.
-The 2pCF analysis is also carried out for the NGC and SGC independently.
-%Also, in this analysis we only look at the radial evolution of clustering properties. 
-The result should be robust as long as each catalogue is well calibrated internally.
-
-%The variation in the density of catalogues is not expected to have large effect on our analysis.
-
-%The redshift evolution of AP effect, RSD effect and properties of samples all may lead to non-zero values of $\delta \hat\xi_{\Delta s}$.
-%To measure the signal from the redshift evolution of the AP effect,
-%we estimate the value of $\delta \hat\xi_{\Delta s}$ from the other effects and subtract their contribution
-%(hereafter $\delta\hat\xi_{\Delta s, \rm sys}$) from the total variation.
-
-The apparent anisotropy introduced by RSD is, 
-although greatly reduced by focusing on the redshift evolution, 
-still the most significant systematic effect.
-
-We estimate the value of $\delta \hat\xi_{\Delta s}$ from the systematic effects and subtract their contribution
-(hereafter $\delta\hat\xi_{\Delta s, \rm sys}$) from the total variation.
-The quantity $\delta\hat\xi_{\Delta s, \rm sys}$ is estimated from the HR4 mock galaxies.
-The mock survey sample imitates the SDSS BOSS sample by mimicking
-the survey as close as possible and includes past light cone effects.
-The observational systematics such as the RSD, survey geometry, and shot noise
-are included in the exactly same way as the observation.
-The peculiar velocity perturbs the observed redshift through the relation
-\begin{equation}\label{eq:zvpeu}
-\Delta z = (1+z) \frac{v_{{\rm LOS}}}{c},
-\end{equation}
-where $v_{\rm LOS}$ is the LOS component of the peculiar velocity of galaxies.
-The redshift evolution of galaxy peculiar velocities, 
-resulting from growth of structure,
-causes the anisotropy produced by RSD to have a small redshift evolution; 
-this is the main source of systematic uncertainty in our results.
-
-We take the HR4 mock galaxy samples and compute $r(z)$ of galaxies in the cosmology under which the simulation is based.
-In this case there is no AP effect. 
-Thus, the measured $\delta \hat\xi_{\Delta s}$ are the redshift evolution purely created by systematics effects.
-They are adopted as the estimation of $\delta\hat\xi_{\Delta s, \rm sys}$,
-and the results are illustrated in Figure \ref{fig_sys}. %shows $\delta\hat\xi_{\Delta s, \rm sys}(z_i,z_1)$ measured from the HR4 mock galaxy samples.
-%Measurements of $\hat\xi_{\Delta s}$ in the 2th to 6th redshift bins are compared with that in the first bin.
-
-For the 1st to 5th redshift bins, $\delta\hat\xi_{\Delta s, \rm sys}(z_i,z_1)\lesssim0.02$,
-indicating a small redshift evolution of the RSD effect and properties of galaxies.
-The only exception is the 6th redshift bin where the values of $\delta\hat\xi_{\Delta s, \rm sys}(z_6,z_1)$ are relatively large.
-The reason for the large values is that the galaxies in that highest redshift bin are significantly more massive than those at lower redshifts,
-so the measured high redshift $\hat\xi_{\Delta s}(\mu)$ has larger (smaller) values at $\mu\rightarrow1$ ($\mu\rightarrow0$) 
-compared with the others
-(an investigation of the dependence of $\hat\xi_{\Delta s}(\mu)$ on galaxy mass is provided in Sec. \ref{sec:caveats}).
-
-%This should be the reason why .
-
-\subsection{The caveats}\label{sec:caveats}
-
-%The biggest systematic of our method, like all other applications of AP, is still the RSD problem.
-\cite{Li2014,Li2015} found the RSD effect exhibits a small redshift dependence of $\hat \xi_{\Delta s}(\mu)$, 
-mainly due to the structure growth and the selection effect
-(different galaxy bias at different redshifts).
-In this analysis we use the mock galaxy sample from HR4 to correct this systematics.
-The galaxy assignment scheme of \cite{hong2016} applied to HR4 is very successful in modeling both the 
-large scale Kaiser effect and the small scale FOG effect in nonlinear regions.
-%After correcting the systematic effect of RSD, we obtain reasonable cosmological constraint consistent with all other cosmological probes.
-
-There are two possible caveats in our procedure of the modeling of the RSD effect.
-
-1) The RSD effect is estimated from mock survey samples created in a particular cosmology, 
-i.e., the $\Omega_m=0.26$ $\Lambda$CDM model. %model from WMAP5 observations with .
-If this adopted cosmology is different from the truth, then there could be a systematic bias in the estimation. %of RSD
-We believe that this will not seriously affect our cosmological constraints.
-\cite{Li2014} shows that the redshift dependence of RSD is not sensitive to cosmological parameters.
-Also, the cosmologies adopted in the HR3 and HR4 simulations are consistent with our best-fit cosmological parameters within 1$\sigma$,
-therefore our inferred cosmological constraints should be fairly accurate.
-In a future analysis,
-we will estimate the redshift evolution of the RSD effect from a set of cosmological simulations 
-covering the relevant part of the parameter space.
-This approach will remove the remaining uncertainty associated with the RSD effect, 
-which is already a minor effect in our analysis.
-%the statistical uncertainty of this method could be much smaller,
-%and modeling the RSD effect in a cosmological dependent manner would be necessary.
-
-2) The selection effect, i.e., the evolution of galaxy bias with redshifts, 
-can introduce redshift evolution in the clustering properties of the observed galaxies.
-%If that is not accurately modeled, people may worry about systematics. %may suffer from systematic errors.
-%Again, we believe this is not a serious problem for our analysis.
-In our analysis the amplitude of the 2pCF is normalized and only its angular information, 
-the function $\hat \xi_{\Delta s}(\mu)$, is used.
-This function is rather insensitive to the galaxy bias,
-which mainly affects the strength of clustering.
-
-As a test, Figure \ref{fig_2pcf_masscut} shows $\hat \xi_{\Delta s}(\mu)$ measured from a small HR4 galaxy sample with different minimal mass cuts.
-The mock galaxies are taken from the $z=0$ snapshot data within the radius $r<600$ $h^{-1}$Mpc.
-Applying the minimal mass cuts of $1,2,4\times 10^{13} h^{-1} M_{\odot}$, 
-we created three sets of subsamples with number density of 
-$\bar n=4.56,\ 2.10,\ 0.91 \times 10^{-4} ( h^{-1} \rm Mpc)^{-3}$, 
-which roughly covers the scatter of the number density of BOSS DR12 galaxies at $0.15<z<0.7$
-\footnote{The BOSS LOWZ and CMASS galaxies reside in massive haloes 
-with a mean halo mass of $5.2 \times 10^{13} h^{-1} M_{\odot}$ and $2.6 \times 10^{13} h^{-1} M_{\odot}$ \citep{Parejko2013,White2011,Reidetal:2016},
-respectively.
-For CMASS galaxies, when the redshift changes from $z=0.43$ to $0.7$,
-the mean stellar mass varies from $10^{11.6} {M_{\odot}}$ to $10^{11.9} {M_{\odot}}$ \citep{CMASSLSS2014}.}.
-
-For subsamples with higher mass cuts the $\hat\xi_{\Delta s}(\mu)$
-has larger (smaller) values at $\mu\rightarrow1$ ($\mu\rightarrow0$).
-More massive samples result in less tilted $\hat\xi_{\Delta s}(\mu)$ in the region of $1-\mu\gtrsim0.1$
-\footnote{This phenomenon is understandable.
-The tilt of $\hat\xi_{\Delta s}(\mu)$ is related to the RSD effect, 
-and also the overall amplitude of the 2pCF (the denominator of Eq. (\ref{eq:norm})).
-The slope should be roughly proportional to $(v/b_g)^2$, 
-where the peculiar velocity term $v^2$ denotes the effect of RSD, 
-and the galaxy bias term $b_g^2$ represents the amplitude of the 2pCF. 
-For the more massive sample, $b_g$ is much larger while $v$ is still close to the peculiar velocity of dark matter field,
-%So their curves are less tilted.
-therefore the slope is smaller.
-}.
-This explains the relative large value of $\hat \xi_{\Delta s,\rm sys}(z_6, z_1)$.
-In particular, comparing the subsamples with mass cuts $4\times 10^{13}h^{-1} M_{\odot}$ and $1\times 10^{13}h^{-1} M_{\odot}$, 
-we find the red dotted curve is higher (lower) than the blue solid line at $\mu\rightarrow1$ ($\mu\rightarrow0$),
-with a difference of $\approx$0.1 (0.05),
-consistent with the value of $\hat \xi_{\Delta s,\rm sys}(z_6, z_1)$ shown in Figure \ref{fig_sys}.
-
-In addition, this result also explains the small discrepancy between the $\hat\xi_{\Delta s}(\mu)$ measured from the 
-observational data and the HR4 simulations (Figure \ref{fig_datamock}).
-The mock galaxies could be systematically more massive than the observed ones.
-These systematics could be most significant in the 6th redshift bin
-where mock galaxies are most massive, 
-leading to possible overestimation of $\delta\hat\xi_{\Delta s,{\rm sys}}$.
-We discuss the impact of this effect in Sec. 6.1.
-
-Considering the large variation of mass cuts, the change of $\hat\xi_{\Delta s}(\mu)$ is not significant,
-so we conclude that $\hat\xi_{\Delta s}(\mu)$ is relatively insensitive to the galaxy bias.
-
-%In addition, Figure 5 of \cite{Li2015} also shows that the peculiar velocities of the halos (PSB halos from HR3) are very insensitive to their masses. 
-%This means the RSD effect coming from galaxies with different biases are similar.
-%So the modeling of RSD effect does not require accurate modeling of the biases of the observed galaxies.
-
-\subsection{$\chi^2$ function}\label{sec:likelihood}
-
-We define a $\chi^2$ function to quantify the redshift evolution of clustering anisotropy
-\begin{equation}\label{eq:chisq1}
-\chi^2\equiv \sum_{i=2}^{6} \sum_{j_1=1}^{n_{\mu}} \sum_{j_2=1}^{n_{\mu}} {\bf p}(z_i,\mu_{j_1}) ({\bf Cov}_{i}^{-1})_{j_1,j_2}  {\bf p}(z_i,\mu_{j_2}),
-\end{equation}
-where ${\bf p}(z_i,\mu_{j})$ is the redshift evolution of clustering, 
-$\hat \xi_{\Delta s}$, with systematic effects subtracted
-\begin{eqnarray}\label{eq:bfp}
- {\bf p}(z_i,\mu_{j}) \equiv&\ \delta \hat\xi_{\Delta s}(z_i,z_1,\mu_j) - \delta \hat\xi_{\Delta s, \rm sys}(z_i,z_1,\mu_j)
-\end{eqnarray}
-${\bf Cov}_i$ is the covariance matrix estimated from the 72 sets of PSB mock galaxies identified from HR3 N-body simulation.
-
-%We find noise in the $\chi^2$ probably due to the low statistic caused by the limited size of the sample and the covmat due to small size of mocks ...
-%So we compute many values of $\chi^2$ using different $n_\mu$ and $\mu_{\rm max}$...
-%The noise in $\chi^2$ shall be statistically random and by taking an average it is suppressed while the physical signal is preserved...
-%We tested the dependence of the result on $\mu_{\rm max}$ and find the result is rather stable within the range $\mu_{\rm max}=0.85 - 0.99$...
-%So we use $\mu_{\rm max} = 0.85, 0.86, ... 0.99$...
-%Increasing $n_\mu$ tighens the constraintm, but in cost of larger noise in the result...
-%Also $n_\mu$ shall be smaller than the number of mocks to compute covmat...
-%So we use $n_\mu = 5, 6, ... 40$...
-%So we define...
-%\begin{equation}\label{eq:chisq2}
-%\bar\chi^2\equiv \frac{ \sum \chi^2(n_\mu,\ \mu_{\rm max}) } {\rm Number\ of\ \chi^2} ... (find a proper way to illustrate this equation)
-%\end{equation}
-
-%{\bf AMTB: We need to give some results on the systematic effects. }
-
-\subsection{Cosmological Constraints}
-
-We constrain $\Omega_m$ and $w$ through Bayesian analysis \citep{Bayesian},
-which derives the probability distribution function (PDF) of some parameters $\bf \theta$ (=($\Omega_m,w$) in this paper)
-given observational data $\bf D$, 
-according to Bayes' theorem:
-\begin{equation}
- P({\bf \theta}|{\bf D}) = \frac{P({\bf \theta})P({\bf D}|{\bf \theta})}{m({\bf D})}.
-\end{equation}
-Here $P(\bf \theta)$, the prior distribution of the parameters,
-contains all the information about the parameters known from substantive knowledge 
-and expert opinion {\it before} observing the data.
-The marginal PDF of $\bf D$, 
-$m({\bf D})=\int P({\bf D|\theta})P({\bf \theta})d{\bf \theta}$, 
-is a normalization constant independent of $\theta$.
-All the information about the parameter $\bf \theta$ that stems from the experiment
-is contained in the function $P({\bf D}|{\bf \theta})$, 
-the conditional PDF of the observation $\bf D$ given the value of parameter.
+and scan the parameter space in $\Omega_m-w$ plane to obtain the 68.3\% and 97.4\% CL regions.
+The result is displayed in Figure \ref{fig_contours}.
 
@@
    }
-   \caption{\label{fig}
+   \caption{\label{fig9.eps}
    Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method.
@@
 
-In this analysis we simply assume flat priors for $\Omega_m$ and $w$,
-and approximate $P({\bf D}|{\bf \theta})$ by a likelihood function $\mathcal{L}$
-satisfying  $-2 \ln \mathcal{L}=\chi^2$;
-the PDF of $\theta$ derived from our AP method takes the form
-%The PDF cu is approximated by the {\it likelihood} function of $\mathcal{L}\propto \exp\left(-\frac{\chi^2}{2}\right)$.
-%It is approximated by the {\it likelihood} function.
-%So we have
-\begin{equation}
- P({\bf \theta}|{\bf D}) \propto \mathcal{L} \propto \exp\left[-\frac{\chi^2}{2}\right].
-\end{equation}
-We use the {\texttt {COSMOMC}} software \citep{LB2002}
-to obtain the Markov Chain Monte Carlo (MCMC) samples of $\theta$ following the PDF of $P({\bf \theta}|{\bf D})$.
-Constraints on $\Omega_m$ and $w$ are derived from these samples.
-
-The 68\% and 95\% likelihood contours of $\Omega_m$ and $w$ 
-obtained from this analysis are shown in Figure \ref{fig_contours} (pink areas).
-%For comparison, results from some other cosmological probes are also plotted.
-Our AP method yields tight constraints on $\Omega_m$ and $w$ .
-The mean values and 68\% CL are
-\begin{equation}
- \Omega_m=0.314 \pm 0.038,\ \ w = -1.09 \pm 0.14.
-\end{equation}
-This result is consistent with the Planck $\Lambda$CDM cosmology within 1$\sigma$ \citep{Planck2015}.
-
-%\bibitem[Blake et al. (2011)]{WiggleZB}
-%Blake, C., Kazin, E.A., Beutler, F., et al.
-%2011, MNRAS, 418, 1707
-%\bibitem[Kazin et al. (2014)]{WiggleZK}
-%Kazin, E.A., Koda, J., Blake, C., et al.
-%2014, MNRAS, 441, 352
+We get tight constraint on the two paramters.
+The 2$\sigma$ contour lies within the region $0.23<\Omega_m<0.285$, $-1.1<w<-0.9$.
+The thin shape of contour means, when combining with the another observational data with different direction of degeneracy (e.g. CMB),
+very tight combined constraint can be obtained.
+In case of fixing one parameter at its best-fit value and infer the statistical uncertainty of the other one,
+one will obtain 1$\sigma$ uncertainty of $\delta\Omega_m\approx0.002,\delta w\approx0.01$.
 

### 2016-09-08 draft/draft0.tex
updates

@@
    % are assumed to compute distance from measured redshift.
-   %The misestimation of angular diameter distance lead to wrong 
-   Right panel shows the misestimation of angular diameter distance when the wrong cosmologies are adopted.
+   %The mis-estimation of angular diameter distance lead to wrong 
+   Right panel shows the mis-estimation of angular diameter distance when the wrong cosmologies are adopted.
    %In our mock surveys we split the samples at $z=0.3$, 0.6, 0.9 and 1.2, as marked by the vertical lines.
@@
 %Its observed redshift span $\Delta z$ and angular size $\Delta \theta$ are related with the comoving sizes by
-In this section we briefly introduce the scaling effect in wrongly assumed cosmologies.
+In this section we briefly introduce the scaling effect caused by wrongly assumed cosmological parameters.
 A more detailed description has been provided in \cite{Li2014,Li2015,Li2016}.
 
-Suppose that we are probing the shape of some objects in the Universe.
+Suppose that we are probing the size of some objects in the Universe.
 We measure its redshift span $\Delta z$ and angular size $\Delta \theta$,
-then compute its sizes in the radial and transverse directions from the relations of 
+then compute its sizes in the radial and transverse directions using the following formulas
 \begin{equation}\label{eq:distance}
@@
 \end{equation}
-where $H$ is the Hubble parameter, $D_A$ is the angular diameter distance.
-In the particular case of a flat universe with constant dark energy EoS, they take the forms of
+where $H$ is the Hubble parameter and $D_A$ is the angular diameter distance.
+In the particular case of a flat universe composed by a cold dark matter component and a constant EoS dark energy component, they take the forms of
 \begin{eqnarray}\label{eq:HDA}
@@
 
-In case we adopted a wrong set of cosmological parameters in Equation (\ref{eq:distance},\ref{eq:HDA}),
+In case wrong values of $\Omega_m$ and $w$ are adopted, 
 the inferred $\Delta r_{\parallel}$ and $\Delta r_{\bot}$ are wrong,
-resulting in distorted shape (AP effect) and wrongly estimated volume (volume effect).
-These effects have been discussed in \cite{Li2014,Li2015,Li2016}.
-This paper we focus on the misestimation of $\Delta r_{\bot}$,%scaling of angular size,
-which can be described by the following quantities
+resulting in wrong estimation in the object's shape (AP effect) and size (volume effect).
+These effects and their cosmological consequences have been investigated in \cite{Li2014,Li2015,Li2016}.
+
+In this paper we focus on the mis-estimation of the angular size $\Delta r_{\bot}$. %scaling of angular size,
+The ratio of mis-estimation is
 \begin{equation}\label{eq:DA}
@@
 \end{equation}
-where ``true'' and ``wrong'' denote the values of $D_A$ in the true cosmology and wrongly assumed cosmology.
-
-The effects due to wrongly assumed cosmological parameters are shown in the upper panel of Figure \ref{fig_xyquan}.
-Suppose that the true cosmology is a flat $\Lambda$CDM with present density parameter $\Omega_m=0.26$
+where ``true'' and ``wrong'' denote the values of $D_A$ in the true cosmology and wrongly assumed cosmologies, respectively.
+
+An illustration is provided in the left panels of Figure \ref{fig_xyquan}.
+Suppose that the true cosmology is a flat $\Lambda$CDM with present matter ratio $\Omega_m=0.26$
 and standard dark energy EoS $w=-1$.
-If we were to distribute a series of perfect squares at various distances from 500 Mpc/h to 3\,000 Mpc/h,
-and an observer located at the origin were to measure their redshifts and compute their positions and shapes 
-using redshift-distance relations of four incorrect cosmologies
+If we were to distribute a series of perfect squares at various distances ranging from 500 Mpc/h to 3\,000 Mpc/h,
+and an observer located at the origin were to measure their redshifts and infer the sizes of the squares
+using the distance-redshift relations of four incorrect cosmologies
 \begin{eqnarray}
@@
 \end{eqnarray}
+as a result, 
 the shapes of the squares appear distorted (AP effect),
-and their volumes are changed (volume effect).
-In the cosmological models in model (i,iii) we see a compression of size (in both angular and LOS direction)
-and the degree of compression increases with increasing distance,
-while in models (ii,iv) we see stretch of size whose degree also evolves with redshift.
-Thus, when wrong cosmological parameters are adopted,
-the apparent size of objects are distorted, and the magnitude of distortion also varies with redshift.
-
-In this paper we will use the galaxy angular 2pCF to probe the redshift dependence of the distortion in angular direction.
-In the right panel of Figure \ref{fig_xyquan} we plot the redshift dependence of the change in angular size, 
-${\Delta r_{\bot, \rm wrong}}/{\Delta r_{\bot, \rm true}}$, in the four wrong cosmologies.
-In all cosmologies, there is clear evolution of ${\Delta r_{\bot, \rm wrong}}/{\Delta r_{\bot, \rm true}}$ 
-in the redshift range $0<z<2$.
-E.g., when use the quintessence cosmology 
-$\Omega_m=0.26,\ w=-0.5$ to infer the postions of objects,
+and their sizes are wrongly estimated (volume effect).
+Cosmological models (i,iii) yield to compressed size (in both angular and LOS direction),
+and the degree of compression increases with increasing distance;
+
+The mis-estimation of angular size, ${\Delta r_{\bot, \rm wrong}}/{\Delta r_{\bot, \rm true}}$, 
+are displayed in the right panel of Figure \ref{fig_xyquan}.
+All cosmologies, ${\Delta r_{\bot, \rm wrong}}/{\Delta r_{\bot, \rm true}}$ evolves a lot in the redshift range $0<z<2$.
+As an example, when adopting the quintessence cosmology $\Omega_m=0.26,\ w=-0.5$,
 the angular size is underestimated by 
@@
 
+%Thus, when wrong cosmological parameters are adopted,
+%the apparent size of objects are distorted, and the magnitude of distortion also varies with redshift.
+
+In sum, as a consequence of incorrectly adopted cosmologies, 
+the size of the objects is mis-estimated and the magnitude of mis-estimation depends on the redshift.
+In this paper we use the galaxy angular 2pCF to probe the mis-estimation of angular size ${\Delta r_{\bot, \rm wrong}}/{\Delta r_{\bot, \rm true}}$.
+
 \section{The Simulation Data}\label{sec:data}
 
-We test the method on the Horizon Run 4  (HR4) simulation \citep{hr4}.
+We test the idea on the mock galaxy samples provided by the Horizon Run 4  (HR4) N-body simulation \citep{hr4}.
+(Check Cris's revision on BOSS AP paper!!!!)
 HR4 used $N=6300^3$ particles in a box size of $L={3150}$ $h^{-1}$Mpc.  
@@
 
-The same as \cite{Li2014,Li2015,Li2016} we need to correct for the redshift evolution of $r\xi$ caused by effects other than the wrongly assumed cosmological parameters.
+The same as \cite{Li2014,Li2015,Li2016} we need to correct for the redshift evolution of $r\xi$ caused by effects other than the cosmological effect.
 

### 2016-09-09 draft/draft0.tex
updates

@@
 \affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
-\author{Cristiano G. Sabiu, Hyunbae Park,}
+\author{Hyunbae Park, Cristiano G. Sabiu, }
 \affil{Korea Astronomy and Space Science Institute, Daejeon 305-348, Korea}
@@
 
-\section{Geometric deformation when }
+\section{Volume Effect in a Nutshell}
 \label{sec:Voleffect}
@@
 \begin{equation}\label{eq:distance}
-\Delta r_{\parallel} = \frac{c}{H(z)}\Delta z,\ \ \Delta r_{\bot}=(1+z)D_A(z)\Delta \theta,
+\Delta r_{\parallel} = \frac{c}{H(z)}\Delta z,\ \ \Delta r_{\perp}=(1+z)D_A(z)\Delta \theta,
 \end{equation}
@@
 In case wrong values of $\Omega_m$ and $w$ are adopted, 
-the inferred $\Delta r_{\parallel}$ and $\Delta r_{\bot}$ are wrong,
+the inferred $\Delta r_{\parallel}$ and $\Delta r_{\perp}$ are wrong,
 resulting in wrong estimation in the object's shape (AP effect) and size (volume effect).
@@
 
-In this paper we focus on the mis-estimation of the angular size $\Delta r_{\bot}$. %scaling of angular size,
+In this paper we focus on the mis-estimation of the angular size $\Delta r_{\perp}$. %scaling of angular size,
 The ratio of mis-estimation is
@@
  %{\rm rat}_{\rm volume\ mag}\equiv
- \alpha_{\bot} \equiv \frac{\Delta r_{\bot, \rm wrong}}{\Delta r_{\bot, \rm true}}
+ \alpha_{\perp} \equiv \frac{\Delta r_{\perp, \rm wrong}}{\Delta r_{\perp, \rm true}}
  = \frac{D_{A, \rm wrong}}{D_{A, \rm true}},
@@
 
-The mis-estimation of angular size, ${\Delta r_{\bot, \rm wrong}}/{\Delta r_{\bot, \rm true}}$, 
+The mis-estimation of angular size, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$, 
 are displayed in the right panel of Figure \ref{fig_xyquan}.
-All cosmologies, ${\Delta r_{\bot, \rm wrong}}/{\Delta r_{\bot, \rm true}}$ evolves a lot in the redshift range $0<z<2$.
+All cosmologies, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$ evolves a lot in the redshift range $0<z<2$.
 As an example, when adopting the quintessence cosmology $\Omega_m=0.26,\ w=-0.5$,
@@
 the size of the objects is mis-estimated and the magnitude of mis-estimation depends on the redshift.
-In this paper we use the galaxy angular 2pCF to probe the mis-estimation of angular size ${\Delta r_{\bot, \rm wrong}}/{\Delta r_{\bot, \rm true}}$.
+In this paper we use the galaxy angular 2pCF to probe the mis-estimation of angular size ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$.
 
@@
 
-We test the idea on the mock galaxy samples provided by the Horizon Run 4  (HR4) N-body simulation \citep{hr4}.
-(Check Cris's revision on BOSS AP paper!!!!)
-HR4 used $N=6300^3$ particles in a box size of $L={3150}$ $h^{-1}$Mpc.  
-It adopted the second order Lagrangian perturbation theory (2LPT) initial conditions at $z_{i}=100$
-and a WMAP5 cosmology $(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96) \citep[]{komatsu 2011}.
-The particle mass is $\simeq m_{p} \simeq 9.02 \times 10^9 \hMsun$.
+We test the method using the mock galaxy samples produced by the Horizon Run 4  (HR4) N-body simulation \citep{hr4,hong2016}.
+
+HR4 was made within a cube of volume $({3.15}\ h^{-1}\rm Gpc)^3$ using  $6300^3$ particles with mass $m_p\simeq 9 \times 10^9 \hMsun$.
+The simulation adopted the second order Lagrangian perturbation theory (2LPT) initial conditions at $z_{i}=100$
+and a WMAP5 cosmology $(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96) \citep{komatsu 2011}.
+%The particle mass is $\simeq m_{p} \simeq 9.02 \times 10^9 \hMsun$.
 %This starting redshift, combined  with 2LPT initial conditions, ensures an accurate mass function and power spectrum \citep{2014NewA...30...79L}.
 
-Mock galaxy samples are produced from the simulation based on a modified one-to-one correspondence scheme \citep{hong2016}. 
-The most bound member particles (MBPs) of simulated halos are adopted as the tracer of galaxies,
-and the merger timescale is computed to get the lifetime of merged halos.
-Merger trees of simulated halos are constructed by tracking their MBPs from $z = 12$ to 0.
-When a merger event occurs, we adopt the formular of \cite{jiang2008} to calculate the merger timescale 
-and determine when a satellite galaxy is completely disrupted.
+Mock galaxies are produced from the simulation based on a modified one-to-one correspondence scheme \citep{hong2016}. 
+The most bound member particles (MBPs) of simulated halos are adopted as tracers of galaxies.
+The merger timescale is computed to get the lifetime of merged halos.
+Merger trees of halos are constructed by tracking their MBPs from $z = 12$ to 0;
+when a merger event occurs, the merger timescale is computed using the formular of \cite{jiang2008} to 
+determine when the satellite galaxy is completely disrupted.
 %We modeled the position and the velocity of a galaxy from the position and velocity of its corresponding MBP.
@@
 
-\cite{hong2016} compared the 2pCF of the SDSS DR7 volume-limited galaxy sample \citep{zehavi2011} and the HR4 $z=0$ mock galaxies.
-%When a typical subhalo-galaxy correspondence scheme is applied, 
-%the 2pCF from our simulation is smaller than the observation and does not show a proper Finger-of-God (FOG) feature in our simulation resolution. 
-%We found that %the %2pCF of our galaxy sample agrees well with the observation.
+The resulting mock galaxies was found to reproduce the 2pCF of SDSS DR7 volume-limited galaxy sample \citep{zehavi2011} very well \citep{hong2016}.
 The mock galaxies shows a similar finger of god (FOG) feature \citep{FOG} as the observation.
-On scales greater than 1 ${h^{-1}}$Mpc., 
-the projected 2pCF of the mock and observational samples agree within 1$\sigma$ deviation.
+The projected 2pCF of the mock and observational samples agree within 1$\sigma$ CL
+on scales greater than 1 ${h^{-1}}$Mpc.
 
 %As will be introduced in the next section, 
-The output of HR4 simulation includes one all-sky light cone mock galaxy catalogue reaching $r=3\,150$ ${h^{-1}}$Mpc 
-and a series ({\bf how many?}) of snapshot mock galaxy catalogues at different redshifts.
-In this paper we use five snapshot data at $z=0,0.5,1,1.5,2$.
-We require subhalos to have at least 30 member particles, 
-so the minimal mass of galaxies is $\simeq m_{p} \simeq 2.7 \times 10^{11} \hMsun$.
-At the five redshifts, we get a number of
+%The output of HR4 simulation includes one all-sky light cone mock galaxy catalogue reaching $r=3\,150$ ${h^{-1}}$Mpc 
+%and a series ({\bf how many?}) of snapshot mock galaxy catalogues at different redshifts.
+In this analysis we use snapshot data of HR4 galaxies at $z=0,0.5,1,1.5,2$.
+%We require subhalos to have at least 30 member particles, 
+%so the minimal mass of galaxies is $\simeq m_{p} \simeq 2.7 \times 10^{11} \hMsun$.
+Setting a minimal halo mass of $3\times 10^{11} \hMsun$, 
 %$4.57\times 10^8$, $4.06\times 10^8$, $3.52\times 10^8$, $3.06\times 10^8$ and $2.28 \times 10^8$ mock galaxies,
-457, 406, 352, 206 and 228 million mock galaxies,
+we select 457, 406, 352, 206 and 228 million mock galaxies at the five redshifts,
 corresponding to a number density of 
@@
 respectively.
-
-\section{Galaxy angular 2pCF}
-
-\subsection{Galaxy distribution at different redshifts}
-
-The left panels of Figure \ref{fig_scatter} show the $x,y$ coordinates of galaxies in a 
-$260 h^{-1} {\rm Mpc} \times 130 h^{-1} {\rm Mpc} \times 105 h^{-1} {\rm Mpc}$ volume, 
-taken from the five snapshots.
-The gravitational growth of structures with decreasing redshift is clearly shown.
-We display all mock galaxies with $M> 3.0 \times 10^{11} \hMsun$.
-At lower redshift, galaxies become more massive, so they are more galaxies satisfying the threshold.
-
-If one adopts a wrong cosmology to compute galaxy positions, there would be a scaling of the galaxy distribution.
-In the left panel we show the case when a wrong set of parameters $\Omega_m=0.05,\ w=-1.5$ is assumed,
-leading to large upscaling of $25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts $z=0.5,1.0,1.5,2.5$.
-
-Compared with the true galaxy distribution, the apparent distribution inferred by wrong set of parameters
-show clear evolution with redshift due to the different scaling at different redshifts.
-In case of Figure \ref{fig_scatter}, the apparent size of large scale structures increases with redshift.
+By applying a uniform mass cut, at higher redshift we are selecting less galaxies with larger galaxy bias.
+
+As an illustration, Figure \ref{fig_scatter} displays the 2D distribution of a subsample of mock galaxies in five redshifts,
+with $x$, $y$ coordinates computed using the ``correct'' values of cosmological parameters $\Omega_m=0.26,\ w=-1$ (left panels) 
+and a wrong set of cosmological parameters $\Omega_m=0.05,\ w=-1.5$ (right panels), respectively.
+
+When the correct cosmology is adopted the cosmic scale is correctly estimated in five redshifts.
+The only factor leads to evolution of galaxy distribution with redshift is the gravitational growth of structure.
+With the decreasing the redshift, we clearly see how the clusters and filaments form and grow.
+On the other hand, when the wrong cosmology is adopted, there is an artifical scaling of scales in the constructed map.
+The separations among galaxies are over-estimated by 
+$25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$,
+leading to a clear evolution of the sizes of structures with redshift.
+
+The growth of structure leads to growth of clustering strength of structures on all scales,
+while the volume effect maintain the clustering pattern and uniformly re-scale all the structures.
+Their imprints on the large scale structure is different and should be distinguishable in the statistical analysis.
+In the following, we show that they affect the angular correlation function measurements in different ways, 
+and can be easily separated.
+
+%The growth of structure also make the size of structures evolves with redshift.
+%In the next subsection we will discuss how to distinguish these two effects in the galaxy angular 2pCF.
+
+%The left panels of Figure \ref{fig_scatter} show the $x,y$ coordinates of galaxies in a 
+%$260 h^{-1} {\rm Mpc} \times 130 h^{-1} {\rm Mpc} \times 105 h^{-1} {\rm Mpc}$ volume, 
+%taken from the five snapshots.
+%The gravitational growth of structures with decreasing redshift is clearly shown.
+%We display all mock galaxies with $M> 3.0 \times 10^{11} \hMsun$.
+%At lower redshift, galaxies become more massive, so they are more galaxies satisfying the threshold.
+
+%If one adopts a wrong cosmology to compute galaxy positions, there would be a scaling of the galaxy distribution.
+%In the left panel we show the case when a wrong set of parameters $\Omega_m=0.05,\ w=-1.5$ is assumed,
+%leading to large upscaling of $25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts $z=0.5,1.0,1.5,2.5$.
+
+%Compared with the true galaxy distribution, the apparent distribution inferred by wrong set of parameters
+%show clear evolution with redshift due to the different scaling at different redshifts.
+%In case of Figure \ref{fig_scatter}, the apparent size of large scale structures increases with redshift.
 
@@
    %\includegraphics[width=16cm]{fig2.eps}
-   \includegraphics[width=16cm,natwidth=8,natheight=14]{fig2.pdf}
+   %\includegraphics[width=16cm,natwidth=8,natheight=14]{fig2.pdf}
+   \includegraphics[width=16cm]{fig2.eps}
    }
@@
 \end{figure*}
+
+\section{Methodology}
+
+%\subsection{Galaxy distribution at different redshifts}
+
+We use the angular 2pCF as a statistical tool to probe the volume effect.
+The galaxy 2pCF as a function of galaxy separation in the angular direction, $\omega(r_\perp)$, is computed for snapshot data of mock galaxies at five redshifts.
+We adopt the Landy-Szalay estimator~\citep{1993ApJ...412...64L},
+\begin{equation}
+\omega(r_\perp)=\frac{DD-2DR+RR}{RR}\ ,
+\end{equation}
+where $DD$ is the number of galaxy--galaxy pairs, 
+$DR$ the number of galaxy-random pairs, 
+and $RR$ is the number of random--random pairs, 
+all separated by a distance defined by $r_\perp\pm\Delta_{r_\perp}$ where we choose $\Delta_{r_\perp}=1h^{-1}\rm Mpc$.
+The random catalogue consists of unclustered points uniformly distributed in a same size box. 
+In an effort to reduce the statistical variance of the estimator, we use 50 times as many random points as we have galaxies.
+
+Considering the large number of galaxies and random points the 2pCF is computed part by part in subsamples with 
+size of 1575 $h^{-1}{\rm Mpc}\times 1575\ h^{-1}{\rm Mpc}\times 105\ h^{-1}{\rm Mpc}$.
+The Z direction with thickness $105\ h^{-1}\rm Mpc$ is treated as the radial direction and the X, Y direction with width $1575 h^{-1}\ \rm Mpc$ are treated as the angular plane.
+In our simulation box we can have 120 such subsamples.
+The average of the measurements in all subsamples is adopted as the 2pCF of the whole sample,
+while the covariances of them are adopted as the covariance matrix after multiplying a factor of $1/\sqrt{119}$.
 
@@
 
-The left panel of Figure \ref{fig_diffz} displays the measured angular 2pCF of galaxies (multiplied by scale $r$) in the five snapshot.
-
-The amplitude of 2pCF is crucially affected by the cosmic structure growth and the galaxy bias.
-%The amplitude is higher at $z=0$, 
-We find $\xi(z=0)>\xi(z=0.5)>\xi(z=1)$.
-At low redshift, the large scale structures experienced most gravitational growth,
-leading to stronger clustering strength and higher amplitude of 2pCF.
-On the contrary, at higher redshift we find $\xi(z=2)>\xi(z=1.5)>\xi(z=1)$,
+The upper-left panel of Figure \ref{fig_diffz} displays the angular 2pCF measured from HR4 mock galaxies. % (multiplied by scale $r$) in the five snapshot.
+We multiply $\omega$ by the separation $r_\perp$ to have similar amount of statistical uncertainty on all scales.
+
+At different redshifts, we see large evolution in the amplitude of $\omega(r_\perp)$.
+The amplitude of 2pCF is proportional to the clustering strengh which is affected by the gravitational growth of structures and the bias of the galaxies.
+The amplitude is highest at $z=0$ where the large scale structures experienced most gravitational growth,
+and also gets higher at $z>1$ with increasing redshift as a reason of more biased galaxies at higher redshift.
+%leading to stronger clustering strength and higher amplitude of 2pCF.
+%On the contrary, at higher redshift we find $\omega(z=2)>\omega(z=1.5)>\omega(z=1)$,
 %The trend is different from $z=1,1.5,2$,
-simply because by applying a uniform mass cut we are selecting more biased galaxies at higher redshift.
-
-Different from the large variation of amplitude among the different redshifts, %The shape of $r\xi$ also evolves with redshift.
-the shape of 2pCF maintains similar at all redshifts. 
-At all redshifts, we see the $r\xi$ peaks at $r\sim9 h^{-1}\rm Mpc$,
-and monotonically drops at larger or smaller scales.
-The only exception is the relative enhancement of 2pCF at $r\lesssim 2 h^{-1}\rm Mpc$,
+%simply because by applying a uniform mass cut we are selecting more biased galaxies at higher redshift.
+
+Different from the large variation of amplitude among the different redshifts, %The shape of $r_\perp\omega$ also evolves with redshift.
+the shape of $r_\perp\omega$ maintains similar at all redshifts;
+it always peaks at $r\sim9 h^{-1}\rm Mpc$ and monotonically drops at larger or smaller scales.
+The only exception is the small enhancement at $r\lesssim 2 h^{-1}\rm Mpc$,
 which is caused by the non-linear growth of structures on small scales 
-and becomes more dramatic at lower redshfit.
-
-The middle panel of Figure \ref{fig_diffz} displays the $r\xi$ normalized by the overall amplitude within $5h^{-1}{\rm Mpc} < r < 50h^{-1}{\rm Mpc}$
-(here after $\hat r\xi$).
-The nice overlapping of the results from five redshifts 
-suggests small evolution of shape with redshift.
-In the right panel, we compare the high redshift $\hat r\xi$ 
-to the $z=0$ result.
-There is 1-4\% relative enhancement 
+and is much more significant at lower redshfit.
+
+In order to directly compare the shape of 2pCF at different redshifts,
+in the middle panel of Figure \ref{fig_diffz} we show the $r_\perp\omega$ normalized by the overall amplitude within $5h^{-1}{\rm Mpc} < r < 50h^{-1}{\rm Mpc}$
+(here after $\hat r_\perp\omega$).
+The nice overlapping of the five redshift results
+justify the small evolution of shape with redshift.
+In the right panel, we further show the residual evolution of $\hat r_\perp\omega$ at high redshifts 
+with respect to $z=0$.
+There is only 1-4\% relative enhancement 
 at $r<10h^{-1}\rm Mpc$,
@@
 
-In all, we conclude that the shape of the 2pCF is more robust than the amplitude against redshift and galaxy bias.
+As shown by Figure \ref{fig_scatter}, the gravitational growth of strucutre enhance the clustering strengh of structures on all scales;
+here it manifests itself as an enhanced amplitude of 2pCF at low redshift.
+The shape of 2pCF, which represents the {\it relative strength of clustering among different scales},
+maintain similar with redshift except the non-linear scales of $r_\perp < 5 h^{-1}\rm Mpc$.
+%mainly increases the amplitude of
+
+%In all, we conclude that the shape of the 2pCF is more robust than the amplitude against redshift and galaxy bias.
 
@@
 \begin{equation}
- \hat \xi_{\rm wrong}(r) = \hat\xi_{\rm true}(\alpha_{\bot} r),
+ \hat \omega_{\rm wrong}(r) = \hat\omega_{\rm true}(\alpha_{\perp} r),
 \end{equation}
-a simple consequence of the fact that clustering patterns at distance $r$ now appears on a the scale $\alpha_{\bot} r$.
-The redshift evolution of $\alpha_{\bot}$ leads to redshfit evolution of shape.
-
-Lower panels of Figure \ref{fig_diffz} shows the $r\xi$ in five 
+a simple consequence of the fact that clustering patterns at distance $r$ now appears on a the scale $\alpha_{\perp} r$.
+The redshift evolution of $\alpha_{\perp}$ leads to redshfit evolution of shape.
+
+Lower panels of Figure \ref{fig_diffz} shows the $r_\perp\omega$ in five 
 snapshots, in case that the cosmology $\Omega_m=0.05,\ w=-1.5$ 
 is adopted to construct the galaxy distribution (the right panels of Figure \ref{fig_scatter}).
-The middle panel displays the clear redshift evolution of shape of $r\xi$.
+The middle panel displays the clear redshift evolution of shape of $r_\perp\omega$.
 E.g, from $z=0$ to $z=2$,
@@
 at higher redshift, 
-there is a 20-40\% change in the value of $\hat {r\xi}$.
-
-The amplitude of $r\xi$ is amplified due to the stretch of scale.
+there is a 20-40\% change in the value of $\hat {r_\perp\omega}$.
+
+The amplitude of $r_\perp\omega$ is amplified due to the stretch of scale.
 As shown in the left panel, the amplitude monotonically increases as a function of redshift.
@@
 In Figure \ref{fig_cosmo} we further plot the redshift evolution of 2pCF in the four wrong cosmologies of Figure \ref{fig_xyquan}.
-In all cases, the scaling leads to evident redshift evolution of the shape of $r\xi$.
+In all cases, the scaling leads to evident redshift evolution of the shape of $r_\perp\omega$.
 When the cosmologies $\Omega_m=0.4,w=-1$ and $\Omega_m=0.26,w=-0.5$ are adopted,
 the compression of structure makes the clustering patterns appears on smaller scales.
-This leads to ``steeper'' slope of $r\xi$, 
+This leads to ``steeper'' slope of $r_\perp\omega$, 
 and the higher the redshift, the steeper the slope.
@@
 
-The same as \cite{Li2014,Li2015,Li2016} we need to correct for the redshift evolution of $r\xi$ caused by effects other than the cosmological effect.
+The same as \cite{Li2014,Li2015,Li2016} we need to correct for the redshift evolution of $r_\perp\omega$ caused by effects other than the cosmological effect.
 
 Figure \ref{fig_diffz} already shows that, the growth of structure, especially in low redshift and on non-linear scales, 
-changes the shape of $r\xi$ and caused relative enhancement on $r\lesssim2 h^{-1}\rm Mpc$.
+changes the shape of $r_\perp\omega$ and caused relative enhancement on $r\lesssim2 h^{-1}\rm Mpc$.
 So we limit the region of scale to $r>5h^{-1}\rm Mpc$ to minimize its effect.
@@
 have the amplitude of 2pCFs enhanced by $10\%,\ 50\%$ and $100\%$,
-while the change in $\hat{r\xi}$ is only $0.5\%,\ 2\%$ and $4\%$.
+while the change in $\hat{r_\perp\omega}$ is only $0.5\%,\ 2\%$ and $4\%$.
 Considering the very large change in the mass cut,
@@
 If looking at the redshift evolution,
-the curves $\hat{r\xi} - \hat{r\xi}(z=0)$ displayed in the right panel,
+the curves $\hat{r_\perp\omega} - \hat{r_\perp\omega}(z=0)$ displayed in the right panel,
 they changed a lot compared with the case of no RSD effect (the right panel of Figure \ref{fig_diffz}),
@@
 so that to determine whether the adopted cosmological parameters are correct.
-The redshift evolution is characterized by the difference between the $\hat{r\xi}$ measured in the lowest redshift and higher ones;
-the cosmology having least redshift evolution of $\hat{r\xi}$ is considered to be the most plausible one and has smallest $\chi^2$.
+The redshift evolution is characterized by the difference between the $\hat{r_\perp\omega}$ measured in the lowest redshift and higher ones;
+the cosmology having least redshift evolution of $\hat{r_\perp\omega}$ is considered to be the most plausible one and has smallest $\chi^2$.
 So we have
@@
 where $n_z$ is the number of redshifts, 
-is number of bins in $\hat{r\xi(r)}$;
+is number of bins in $\hat{r_\perp\omega(r)}$;
 in this analysis we have five redshift bins, 
@@
 ${\bf p}(z_i,r_{j})$ is the redshift evolution of clustering, 
-$\hat {r\xi}$, with systematic effects subtracted
+$\hat {r_\perp\omega}$, with systematic effects subtracted
 \begin{eqnarray}\label{eq:bfp}
- {\bf p}(z_i,r_{j}) \equiv&\ \delta \hat{r\xi}(z_i,z_1,r_j) - \delta \hat{r\xi}_{\rm sys}(z_i,z_1,r_j)
+ {\bf p}(z_i,r_{j}) \equiv&\ \delta \hat{r_\perp\omega}(z_i,z_1,r_j) - \delta \hat{r_\perp\omega}_{\rm sys}(z_i,z_1,r_j)
 \end{eqnarray}
@@
 To mimick this when calculating the redshift evolution of 2pCF we use subsamples at different positions at different redshfits.
-E.g., if for the $z=0$ snapshot we use the $\hat{r\xi}$ measured in the subsample $0h^{-1}{\rm Mpc}<Z<105 h^{-1}{\rm Mpc}$,
-at higher redshifts we adopt the $\hat{r\xi}$ measured in a subsample $105h^{-1}{\rm Mpc}<Z<210 h^{-1}{\rm Mpc}$,
-and take the difference between them to get $\delta \hat{r\xi}$.
+E.g., if for the $z=0$ snapshot we use the $\hat{r_\perp\omega}$ measured in the subsample $0h^{-1}{\rm Mpc}<Z<105 h^{-1}{\rm Mpc}$,
+at higher redshifts we adopt the $\hat{r_\perp\omega}$ measured in a subsample $105h^{-1}{\rm Mpc}<Z<210 h^{-1}{\rm Mpc}$,
+and take the difference between them to get $\delta \hat{r_\perp\omega}$.
 So we are always comparing 2pCF measured from different samples of galaxies.
 If simply comparing the 2pCF of a same sample of galaxies at different redshifts, 
-one would significantly underestimate the statistical undertainty of $\delta \hat{r\xi}$ by ignoring the cosmic variance
+one would significantly underestimate the statistical undertainty of $\delta \hat{r_\perp\omega}$ by ignoring the cosmic variance
 \footnote{The error bars displayed in all figures are estimated from the 120 subsamples and for the error bar of redshift evolution of 2pCF 
@@
 For $\Omega_m=0.15,w=-1$ and $\Omega_m=0.26,w=-1.5$,
-the stretch of structure leads to shallower slope of $\hat{r\xi}$ and, the higher the redshift, the shallower.
-In all cosmologies we find significant detection of redshift evolution of $\hat{r\xi}$ (in the lowest panels, $\delta \hat{r\xi}\neq0$).
+the stretch of structure leads to shallower slope of $\hat{r_\perp\omega}$ and, the higher the redshift, the shallower.
+In all cosmologies we find significant detection of redshift evolution of $\hat{r_\perp\omega}$ (in the lowest panels, $\delta \hat{r_\perp\omega}\neq0$).
 We computed the $\chi^2$ values according to Equation \ref{eq:chisq1} and found these sets of cosmological parameters are strongly disfacored 
@@
    %\includegraphics[width=16cm,natwidth=52,natheight=40]{fig10.eps}
-   %\includegraphics[width=16cm]{fig10.eps}
+   \includegraphics[width=16cm]{fig9.eps}
    }

### 2016-09-16 draft/BOSSAP.tex
updates

@@
 but has limitations in that it utilizes only low density regions of the LSS
-and requires large samples.
+and requires large samples \citep{Qingqing2016}.
 
@@
 
+\bibitem[Mao et al. (2016)]{Qingqing2016}
+Mao, Q., Berlind, A.A., Scherrer, R.J., et al. 2016, submitted to ApJ
+
 \bibitem[Marinoni \& Buzzi(2010)]{Marinoni2010}

### 2016-09-16 draft/draft0.tex
updates

@@
 \and
-\author{Sungwook E. Hong}
+\author{Stephen Appleby, Sungwook E. Hong}
 \affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
@@
 \begin{abstract}
-We use the shape of galaxy 2-point correlation function to measure the redshift dependence cosmology volume effect.
-...
+We propose to use the redshift of the shape of galaxy angular 2-point correlation function (2pCF) to constrain cosmology.
+The method is a continue of our series of works \citep{Li2014,Li2015,Li2016} probing the redshift dependence of Alcock-Paczynski effect and volume effect. 
+A wrongly adopted cosmology result in redshift-dependent mis-scaling in the constructed galaxy distribution,
+which leads to redshift-dependent rescaling in the measured angular 2pCF.
+We test our method on the HR4 mock galaxies having 457, 406, 352, 206 and 228 million galaxies at redshfits 0, 0.5, 1, 1.5, 2,
+and find the redshift evolution of the scaling of angular 2pCF is sensitive to the adopted cosmological parameters and 
+relatively insensitive to the gravitational growth of structure,
+the galaxy bias, and the redshift space distortion.
+Analyzing redshift evolution of the shape of 2pCF on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$ we derive tight constraints on $\Omega_m$ and $w$.
+Our method is complementary to current works using 2pCF to constrain cosmological parameters.
+The method could be applicable to future photometric surveys of DES, LSST to derive tight cosmological constraints.
+
 \end{abstract}
@@
 
-Dark energy ... Large scale structure...
-
-2pCF is a good statistic... blahblah
-In 2d xi(s,mu) ...
-In *** we used the redshift dependence of 2pCF to probe the volume and AP effect...
-The method is applied to BOSS data in *** and obtain tight constraint...
-
-In *** we further propose to use the shape of xi(s) to probe the volume effect...
-Stretch or compression shifts the clustering properties in some particular scale to larger or smaller scales...
-The shape of measured xi(s) is thus stretched or compressed.
-
-The outline of this paper is as follows.
-
-This paper is organized as follows...
+Dark energy has become the most important scientific issue since the discovery of cosmic acceleration \citep{Riess1998,Perl1999}.
+Many theoretical and observational effect has been made \citep{Weinberg,Li2011,DHW2013}, but its properties still remain far from accurately known and its nature still remains mystery. 
+%The simplest and currently favored solution is the additional field called dark energy which has negative pressure and is spatially homogeneous.
+%The simplest explanation for dark energy is that it is a cosmological constant or vacuum energy, with constant equation of state (EoS) $w = -1$.
+
+To measure the properties dark energy we need accurate probe of the cosmic expansion history. 
+In large scale structure surveys the two representative geometrical observables are the angular diameter distance $D_A$ and the Hubble factor, $H$. 
+If these can be precisely measured as functions of redshift, then tight constraints can be placed on the parameters of the cosmological model,
+e.g., the matter density $\Omega_m$ and the equation of state (EoS) of dark energy, $w$.
+
+Assuming an incorrect cosmological model for the coordinate transformation from redshift space to comoving space leaves residual geometric distortions. 
+These distortion include volume effect which is the alteration of the comoving volume size of structures,
+and the Alcock-Paczynski (AP) effect, induced by the fact that distances along and perpendicular to the line of sight are fundamentally different.
+%Measuring the ratio of galaxy clustering in the radial and transverse directions, provides a probe of the Alcock-Paczynski (AP) effect \citep{AP1979}.
+%There have been a series of works studying the application of the AP test to the LSS
+A series of statistically method has been proposed to measure the AP test in the LSS
+\citep{Ballinger1996,Matsubara1996,Marinoni2010,Ryden1995,LavausWandelt1995}
+and have been applied to a series of LSS surveys \citep{Outram2004,Blake2011,ChuangWang2012,
+Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, Jeong2014,Sutter2014,2014ApJ...781...96L,
+Alam2016, Beutler2016, Sanchez2016,Qingqing2016}. 
+The probe of volume effect is usually probed through number counting of 
+galaxy clusters \citep{PS1974,VL1996}, topology \citep{topology};
+it is also part of the physical effects measured in the measurements of the BAO scale \citep{some reference},
+or the probe of the shape of 2pCF and power spectrum \citep{some reference}.
+
+In \cite{Li2014,Li2015,Li2016} we proposed a series of methods to probe the geometric information encoded in the LSS data.
+We make use of the fact that the AP or volume effect commonly introduce redshift-dependent geometric distorion in the LSS,
+which can be distinguished from the other effects such as the redshfit space distortion (RSD).
+RSD arises because the radial distances of galaxies are inferred from redshifts which is contaminated by the pecular motion of galaxies, 
+leading to apparent anisotropy even if the adopted cosmology is correct \citep{Ballinger1996}.
+RSD is the usually main caveats for probe geometry using LSS,
+and we found it can be largerly avoid by focusing on the the redshift dependence of the anisotropy.
+
+\cite{Li2014} proposed used the {\it galaxy density gradient field} 
+to characterize the anisotropies in LSS and tested the idea on Horizon Run 3 (HR3) N-body simulations \citep{horizonrun},
+showing the redsift evolution of the gardient field can be used to infer unbiased constraints cosmological parameters and is insensitive to RSD.
+The same topic was revisited in \cite{Li2015}, but using the statistical tool of {\it galaxy two-point correlation function} (2pCF) as a function of angle, $\xi(\mu)$.
+When incorrect cosmological parameters are adopted, the shape of $\xi(\mu)$ appears anisotropic due to the AP effect, 
+and the amplitude is shifted by the change in comoving volume;
+both effects have significant redshift dependence.
+The RSD effect, although significantly distorting $\xi(\mu)$, 
+exhibits much less redshift evolution compared to the effect coming from incorrectly adopted cosmologies.
+The method was applied to BOSS DR12 galaxies \citep{Li2016} to probe the redshift dependent of AP effect and lead to tight cosmological constraints.
+
+We developed a method measuring the redshift of the shape of galaxy angular correlation function to constrain cosmology.
+A wrongly adopted cosmology result in redshift-dependent mis-scaling in the constructed galaxy distribution,
+which leads to redshift-dependent change in the angular 2pCF shape.
+The signal is sensitive to the adopted cosmological parameters and relatively insensitive to the gravitational growth of structure,
+the galaxy bias, and the RSD effect.
+We test our method on the HR4 mock galaxies having hundreds of million galaxies at redshfits 0-2.
+Analyzing redshift evolution of the shape of 2pCF on scales $5 - 40 h^{-1} {\rm Mpc}$, we derive tight constraints on $\Omega_m$ and $w$.
+
+In this paper we continue our series of work and probe to use the angular correlation function as a statistical tool to probing the volume effect in the angular direction.
+%The method of redshift dependent AP effect has been shown great power to constrain cosmological parameters \cite{Li2014,Li2015,Li2015}.
+%We hope this method also.
+%The two methods probe different information encoded in the 2pCF and can be combined to fully probe the geometrical effect in LSS.
+%Or one can also use the redshift evolution of 2D 2pCF xi(s,mu) to have all information included.
+%We developed a method measuring the redshift of the shape of galaxy angular correlation function, $\hat \omega_{r_\perp}$, to constrain cosmology.
+A wrongly adopted cosmology result in redshift-dependent mis-scaling in the constructed galaxy distribution,
+which shifts apparent scale of the clustering patterns;
+this manifests itself as a redshift-dependent rescaling of the measured angular correlation function.
+We find this signal is sensitive to the adopted cosmological parameters and relatively insensitive to the gravitational growth of structure,
+the galaxy bias, and the RSD effect.
+We test our method on the HR4 mock galaxies.
+The method can be applied to current and future LSS surveys,
+especially, the photometric surveys such as DES and LSST which probe a large amount of galaxies and the large redshift error will not quite affect the angular 2pCF measurement.
+
 The outline of this paper proceeds as follows. 
-In \S 2 we briefly review the nature and consequences of the AP effect and volume changes when performing coordinate transforms in a cosmological context. 
-In \S 3 we describe the N-body simulations and mock galaxy catalogues that are used to test our methodology.
-In \S 4, we describe our new analysis method for quantifying the redshift dependence of volume effect.
-We conclude in \S 5.
+In \S 2 we briefly review the nature and consequences of the geometric distortion in LSS when performing coordinate transforms in a cosmological context. 
+In \S 3 we describe the mock galaxies produced from N-body simulations which are used to test our methodology.
+The methodology is presented in \S 4.
+We conclude in \S 6.
 
@@
 size of 1575 $h^{-1}{\rm Mpc}\times 1575\ h^{-1}{\rm Mpc}\times 105\ h^{-1}{\rm Mpc}$.
-The Z direction with thickness $105\ h^{-1}\rm Mpc$ is treated as the radial direction and the X, Y direction with width $1575 h^{-1}\ \rm Mpc$ are treated as the angular plane.
-In our simulation box we can have 120 such subsamples.
+The Z direction with thickness $105\ h^{-1}\rm Mpc$ is treated as the radial direction (the $r$ direction) 
+and the X-Y directions with each of width $1575 h^{-1}\ \rm Mpc$ are the angular plane.
+For our simulation box size we can have 120 such subsamples.
 The average of the measurements in all subsamples is adopted as the 2pCF of the whole sample,
@@
 
-\subsection{Galaxy angular 2pCF: amplitude and shape at different redshifts}
+\subsection{Galaxy angular 2pCF: amplitude and shape at different redshifts}\label{sec_2pCF_diffz}
 
@@
 in the middle panel of Figure \ref{fig_diffz} we show the $r_\perp\omega$ normalized by the overall amplitude within $5h^{-1}{\rm Mpc} < r < 50h^{-1}{\rm Mpc}$
-(here after $\hat r_\perp\omega$).
+(here after $\hat \omega_{r_\perp}$):
+\begin{equation}
+ \hat \omega_{ r_\perp} \equiv  \frac{ {r_\perp\omega}(r_{\perp})}{ \int_{r_{\perp, \rm min}}^{r_{\perp, \rm max}}r_{\perp} \omega(r_{\perp}) d r_{\perp} / (r_{\perp,\rm max}-r_{\perp,\rm min}) },
+\end{equation}
+where we choose $r_{\perp, \rm min}=5 h^{-1}$ Mpc, $r_{\perp, \rm max}=40 h^{-1}$ Mpc in this analysis.
+Scales of $r_{\perp, \rm min}<5 h^{-1}$ Mpc are affected by non-linear growth of strucutre, 
+the mis-estimation of whose contribution may lead to systematic errors in the derived cosmological constraints.
+On scales larger than $40 h^{-1}$ Mpc it is may be possible to have precise analytically modelling the shape of the 2pCF
+ \citep{Salvador2014,Salvador2016} which should be able to extract more cosmological information than our method 
+(although out method should is also applicable).
+
 The nice overlapping of the five redshift results
@@
 
+There is one point should be emphasized here.
+In real observations we are observing {\it different} objects in different redshfit shells.
+To mimick this we comparing slices of different redshifts at {\it different} locations.
+As an exammple, if at $z=0$ we take $\hat\omega_{r_\perp}$ measured within $0h^{-1}{\rm Mpc}<Z<105 h^{-1}{\rm Mpc}$,
+at higher redshifts we then adopt measurement within $105h^{-1}{\rm Mpc}<Z<210 h^{-1}{\rm Mpc}$ for a comparision.
+%and take the difference between them to get $\delta \hat{r_\perp\omega}$.
+%So we are always comparing 2pCF measured from different samples of galaxies.
+If simply comparing the 2pCF of a {\it same} subsample of galaxies at different redshifts, 
+one would significantly underestimate the statistical undertainty of $\delta \hat{\omega_{r_\perp}}$ by ignoring the cosmic variance.
+The error bars and covariance are always estimated in this way to take the cosmic variance into consideration.
+%\footnote{In all figures of this paper The error bars displayed in all figures are estimated in this way; 
+%from the 120 subsamples and for the error bar of redshift evolution of 2pCF 
+%we always take the cosmic variance into consideration.}.
+
 As shown by Figure \ref{fig_scatter}, the gravitational growth of strucutre enhance the clustering strengh of structures on all scales;
@@
 
-\subsection{Galaxy angular 2pCF: in wrong cosmologies }
-
-When a wrong set of cosmological parameters is adopted,
-the galaxy distribution is artificially scaled.
-This scaling is expected to change the shape of the 2pCF,
-following the relationship,
+\subsection{Galaxy angular 2pCF: Cosmological Effect }
+
+The measured angular correlation function of galaxies with positions constructed using the wrong cosmology $\Omega_m=0.05,\ w=-1.5$
+is displayed in the lower panels of Figure \ref{fig_diffz}.
+The mis-scaling uniformly shifts clustering patterns on all scales, lead to a wrong estimation of $\hat \omega_{r_\perp}$ 
+related with the correct one as
 \begin{equation}
- \hat \omega_{\rm wrong}(r) = \hat\omega_{\rm true}(\alpha_{\perp} r),
+ \hat \omega_{r_\perp,\rm wrong}(r) = \hat \omega_{r_\perp, \rm correct}(\alpha_{\perp} r),
 \end{equation}
-a simple consequence of the fact that clustering patterns at distance $r$ now appears on a the scale $\alpha_{\perp} r$.
+a simple consequence of the phenomenon that clustering patterns at distance $r$ now appears on $\alpha_{\perp} r$.
 The redshift evolution of $\alpha_{\perp}$ leads to redshfit evolution of shape.
 
-Lower panels of Figure \ref{fig_diffz} shows the $r_\perp\omega$ in five 
-snapshots, in case that the cosmology $\Omega_m=0.05,\ w=-1.5$ 
-is adopted to construct the galaxy distribution (the right panels of Figure \ref{fig_scatter}).
-The middle panel displays the clear redshift evolution of shape of $r_\perp\omega$.
-E.g, from $z=0$ to $z=2$,
-the peak location is shifted from $r=9h^{-1} \rm Mpc$ to $r\sim15 h^{-1}\rm Mpc$ at $z=2$
-since the angular separation is upscaled by $71.7\%$.
-
-The right panel shows that, 
-at higher redshift, 
-there is a 20-40\% change in the value of $\hat {r_\perp\omega}$.
-
-The amplitude of $r_\perp\omega$ is amplified due to the stretch of scale.
-As shown in the left panel, the amplitude monotonically increases as a function of redshift.
-But this phenomenon can also appear in case of gravitational growth of structure or increasing of bias,
-so we will not make use of it to do cosmological constraint.
-We utilize the redshift evolution of the 2pCF shape as a signal suggesting that the assumed cosmological parameters are wrong.
-
-In Figure \ref{fig_cosmo} we further plot the redshift evolution of 2pCF in the four wrong cosmologies of Figure \ref{fig_xyquan}.
-In all cases, the scaling leads to evident redshift evolution of the shape of $r_\perp\omega$.
-When the cosmologies $\Omega_m=0.4,w=-1$ and $\Omega_m=0.26,w=-0.5$ are adopted,
-the compression of structure makes the clustering patterns appears on smaller scales.
-This leads to ``steeper'' slope of $r_\perp\omega$, 
-and the higher the redshift, the steeper the slope.
-To the opposite, when adopting the cosmologies $\Omega_m=0.15,w=-1$ and $\Omega_m=0.26,w=-1.5$,
-the stretch of size makes the slope shallower at higher redshfits.
+%Lower panels of Figure \ref{fig_diffz} shows the $r_\perp\omega$ in five 
+%snapshots, in case that the cosmology $\Omega_m=0.05,\ w=-1.5$ 
+%is adopted to construct the galaxy distribution (the right panels of Figure \ref{fig_scatter}).
+The change in shape as well as the redshift evolution is displayed in the middle panel.
+The upscaling of comoving distance lead to a stretched shape.
+With the increasing of redshift,
+the peak location is shifted from $9h^{-1} \rm Mpc$ to $15 h^{-1}\rm Mpc$ at $z=2$,
+as a result of the fact that the angular separation is upscaled by $71.7\%$.
+Correspondingly, the right panel shows that, 
+compared with $\hat \omega_{r_\perp}$ at $z=0$ there is a 20-40\% change at higher redshifts.
+
+The mis-scaling not only changes the of the 2pCF but also modifies its amplitude. %The amplitude of $r_\perp\omega$ is amplified due to the stretch of scale.
+as shown in the left panel, due to the stretch of scale the amplitude is enhanced at higher redshifts;
+the higher the redshift, the more the enhancement.%the amplitude monotonically increases as a function of redshift.
+
+Although the change of amplitude could be a more significant consequence of wrong cosmology than the alteration of shape,
+it is mixed with other factors; 
+the growth of structure and a larger galaxy bias can also lead to a stronger clustering and thus an enhanced amplitude of 2pCF.
+%it is more difficult to 
+%But this phenomenon can also appear in case of gravitational growth of structure or increasing of bias,
+%so we will not make use of it to do cosmological constraint.
+In the analysis to extract cosmological information, we just make use of the redshift evolution of the 2pCF shape, 
+which is less affected by factors of structure growth and galaxy bias.
+%which is as a signal suggesting that the assumed cosmological parameters are wrong.
 
@@
 
-The same as \cite{Li2014,Li2015,Li2016} we need to correct for the redshift evolution of $r_\perp\omega$ caused by effects other than the cosmological effect.
-
-Figure \ref{fig_diffz} already shows that, the growth of structure, especially in low redshift and on non-linear scales, 
-changes the shape of $r_\perp\omega$ and caused relative enhancement on $r\lesssim2 h^{-1}\rm Mpc$.
-So we limit the region of scale to $r>5h^{-1}\rm Mpc$ to minimize its effect.
-
-Galaxies are biased tracers of dark matter field, 
-and more massive galaxies tend to reside in regions with higher density contrast.
-So in large scale structure surveys the bias of the galaxy sample is an important fator which has large effect on the clustering properties of the sample.
-The upper panels of Figure \ref{fig_sys} displays five set of galaxy samples in a $3175\times3175\times105$ $(h^{-1}\rm Mpc)^3$ volume, taken from the $z=0$ snapshots data.
-Different lower mass limits of $3\times 10^{11} M_{\odot}$, $3\times 10^{11} M_{\odot}$, $3\times 10^{11} M_{\odot}$ and $3\times 10^{11} M_{\odot}$
-are imposed to create subsamples with different galaxy bias, 
-and the measured angular 2pCF are displayed.
+Sec. \ref{sec_2pCF_diffz} shows that $\hat \omega_{r_\perp}$ measured from a set of constant mass cut samples at different redshifts is close to each other.
+The gravitational growth of structure will not have a large impact on $\hat \omega_{r_\perp}$ on scales $\gtrsim5 h^{-1}$ Mpc.
+The other factors may introduce redshift evolution of the clustering of measured galaxies include the 
+redshift space distortion (RSD), galaxy bias, redshift error, and other properties of galaxies, such as the mass, morphology, color, concentration. 
+Here we test two ``major'' systematical effects, the galaxy bias and the RSD effect.
+
+%The same as \cite{Li2014,Li2015,Li2016} we need to correct for the redshift evolution of $r_\perp\omega$ caused by effects other than the cosmological effect.
+
+%Figure \ref{fig_diffz} already shows that, the growth of structure, especially in low redshift and on non-linear scales, 
+%changes the shape of $r_\perp\omega$ and caused relative enhancement on $r\lesssim2 h^{-1}\rm Mpc$.
+%So we limit the region of scale to $r>5h^{-1}\rm Mpc$ to minimize its effect.
+
+\subsubsection{Galaxy Bias}
+
+Galaxies are biased tracers of dark matter field;
+more massive galaxies reside in regions with higher density contrast.
+In large scale structure surveys, the bias of the galaxy sample is an important fator affecting on the clustering properties of the sample.
+
+We check the effect of galaxy bias on $\hat \omega_{r_\perp}$.
+The upper panels of Figure \ref{fig_sys} displays the 2pCF measured from galaxies within a $3175\times3175\times105$ $(h^{-1}\rm Mpc)^3$ volume, taken from the $z=0$ snapshot.
+Four values of minimal mass limits, $3\times 10^{11} M_{\odot}$, $1\times 10^{12} M_{\odot}$, $4\times 10^{12} M_{\odot}$ and $1\times 10^{13} M_{\odot}$,
+are imposed to create three samples with different galaxy bias.
+The measured angular 2pCF are displayed.
+
 The different mass cuts result in large variation in the amplitude of the 2pCF (left panel),
 while the shape of the 2pCF remains less affected (middle panel).
-Compared with the sample with mass cut $M>3\times 10^{11} M_{\odot}$,
-samples with mass limit $3\times 10^{11} M_{\odot}$, $3\times 10^{11} M_{\odot}$ and $3\times 10^{11} M_{\odot}$
-have the amplitude of 2pCFs enhanced by $10\%,\ 50\%$ and $100\%$,
-while the change in $\hat{r_\perp\omega}$ is only $0.5\%,\ 2\%$ and $4\%$.
-Considering the very large change in the mass cut,
-the change in the shape of 2pCF is not significant.
-
-The galaxy peculiar velocity contribute to the observed galaxy redshift and distorted the galaxy radial position in redshift space,
-known as the redshift space distortion (RSD).
-It is the major source of systematics for our analysis of \cite{Li2014,Li2015,Li2016}, where the 3D galaxy distribution is utilized to derive cosmological constraint.
-In this analysis its effect becomes much milder since the angular positions of the galaxies is not affected by RSD at all.
-But it still affects our analysis in the procedure of preparing the subsamples of galaxies for 2pCF analysis.
-The galaxies observed in a survey are split into shells of subsamples, with different redshift ranges, to get the 2pCF at different redshifts.
-RSD disortes the galaxy redshift and as a result some galaxies close the boundaries of shells will be distributed to wrong redshift shells.
+Compared with the sample of $M>3\times 10^{11} M_{\odot}$,
+samples with mass limits of $1\times 10^{12} M_{\odot}$, $4\times 10^{12} M_{\odot}$ and $1\times 10^{13} M_{\odot}$
+have amplitude of 2pCFs enhanced by $10\%,\ 50\%$ and $100\%$,
+while the change in $\hat\omega_{r_\perp}$ is only $0.5\%,\ 2\%$ and $4\%$.
+So the effect of galaxy bias is much avoided by utilizing the shape of the 2pCF rather than the amplitude.
+
+\subsubsection{Redshift Space Distortion}
+
+The galaxy peculiar velocity contributes to the observed redshift and distorted the inferred galaxy radial position,
+known as the redshift space distortion.
+It is the major systematics in our previous works \citep{Li2014,Li2015,Li2016}
+where we derive cosmological constraints from the redshift evolution of the 3D galaxy distribution.
+
+The effect of RSD is expected to be much milder in this work. 
+The angular positions of the galaxies is not shifted by RSD at all;
+the only effect of RSD come in the procedure of sample preparation. %preparing the subsamples of galaxies for 2pCF analysis.
+The galaxies observed in a survey are split into shells of subsamples with different redshift ranges for the purpose 2pCF measurement.
+RSD disortes the galaxy redshift and as a result some galaxies (especially those close to the boundaries of shells) could be classified to wrong redshift shells.
 
 The lower panel of Figure \ref{fig_sys} displays the RSD effect on 2pCF.
-To mimick the effect of RSD we shift the $Z$ coordinates of galaxies according to the relation 
+To have the effect of RSD we shift the radial coordinates of galaxies according to the relation 
 \begin{equation}\label{eq:zvpeu}
@@
 \end{equation}
-where $v_{{\rm Z}}$ is the galaxy peculiar velocity in $Z$ direction.
-Then we split the whole box into 30 slices with thickness $105h^{-1}\rm Mpc$, 
-and measure the angular 2pCF.
-The left panel shows that the amplitude of measured 2pCF is enhanced by $\sim 10\%$ in case of considering the RSD effect on spliting samples.
-The middle panel shows that the shape of 2pCF is also altered -- the slop is suppressed.
-If looking at the redshift evolution,
-the curves $\hat{r_\perp\omega} - \hat{r_\perp\omega}(z=0)$ displayed in the right panel,
-they changed a lot compared with the case of no RSD effect (the right panel of Figure \ref{fig_diffz}),
-but do not become much larger. %But RSD effect does not introduce large redshfit evolution, although the shape of  is
-
-Similar to RSD, the redshift errors in survey can affect the subsamples of galaxies by buring the boundaries of shells.
-This effect should be properly quantified, especially in case of a photometric survey where the redshift uncertainty can be $\Delta z \\approx 0.02$.
-
-In \cite{Li2014,Li2015,Li2016}, the systematic effects contributing to the redshfit evolution of galaxy clusterings 
-are modeled in mock surveys and subtracted.
-Similar treatment could be conducted here.
-One shall construct mock surveys with the above effects included for the correction of systematics.
+where $v_{{\rm LOS}}$ is the galaxy peculiar velocity in the radial direction.
+This lead to mis-classfication of some galaxies when we split the box into slices.
+%Then we split the whole box into 30 slices with thickness $105h^{-1}\rm Mpc$, 
+%and measure the angular 2pCF.
+
+Comparing the plot with Figure \ref{fig_diffz} one clearly see the effect of RSD.
+The amplitude of measured 2pCF is enhanced by $\sim 10\%$ in case of considering the RSD effect.
+The slop of $\hat\omega_{r_\perp}$ slightly suppressed.
+While the redshift evolution of $\hat\omega_{r_\perp}$ is still small...
+Although the pattern is a little modified...
+So RSD is not a big issue here... {\bf after anna jobs finished we have better plots and re-revise this section }
+%If looking at the redshift evolution,
+%the curves $\hat{r_\perp\omega} - \hat{r_\perp\omega}(z=0)$ displayed in the right panel,
+%they changed a lot compared with the case of no RSD effect (the right panel of Figure \ref{fig_diffz}),
+%but do not become much larger. %But RSD effect does not introduce large redshfit evolution, although the shape of  is
+
+Similar to RSD, redshift errors of galaxies (typically 0.02 for photometric survey) also results in fuzzy boundaries of shells and mis-classfication of galaxies.
+This effect should also be properly quantified in real observations.
+
+%In \cite{Li2014,Li2015,Li2016}, the systematic effects contributing to the redshfit evolution of galaxy clusterings 
+%are modeled in mock surveys and subtracted.
+%Similar treatment could be conducted here.
+%One shall construct mock surveys with the above effects included for the correction of systematics.
 
@@
    \centering{
-   \includegraphics[width=16cm]{fig5.eps}
-   \includegraphics[width=16cm]{fig6.eps}
+   \includegraphics[width=16cm]{fig4_a.eps}
+   \includegraphics[width=16cm]{fig4_b.eps}
    }
@@
 
-We build up a likelihood function to 
-describe how significant is the redshift evolution of the 2pCF shape,
-so that to determine whether the adopted cosmological parameters are correct.
-The redshift evolution is characterized by the difference between the $\hat{r_\perp\omega}$ measured in the lowest redshift and higher ones;
-the cosmology having least redshift evolution of $\hat{r_\perp\omega}$ is considered to be the most plausible one and has smallest $\chi^2$.
-So we have
+We design the likelihood function to quantify
+the redshift evolution of $\hat\omega_{r_\perp}$.
+A cosmology resulting in smaller evolution is considered to be more likely the correct one.
+The procedure here is very similar to what we did in \cite{Li2014,Li2015,Li2016}.
+We comapre the high redshift $\hat\omega_{r_perp}$ and the lowest redshift measurement:
 \begin{equation}\label{eq:chisq1}
@@
 \end{equation}
-where $n_z$ is the number of redshifts, 
-is number of bins in $\hat{r_\perp\omega(r)}$;
-in this analysis we have five redshift bins, 
-and 35 $r$ bins with bin width $1h^{-1}\rm Mpc$ in the range $5h^{-1}{\rm Mpc}<r<40h^{-1}{\rm Mpc}$.
-${\bf p}(z_i,r_{j})$ is the redshift evolution of clustering, 
-$\hat {r_\perp\omega}$, with systematic effects subtracted
+where $n_z$ is the number of redshifts which is 5 in this analysis, 
+$n_r$ is number of binning in $\hat{\omega_{r_\perp}}(r_\perp)$,
+which is 35 since we have $r_\perp$ bins 
+with width $1h^{-1}\rm Mpc$ in a range of $5h^{-1}{\rm Mpc}\leq r\leq 40h^{-1}{\rm Mpc}$.
+${\bf p}(z_i,r_{j})$ is the redshift evolution of the angular correlation function shape with systematic effects subtracted
 \begin{eqnarray}\label{eq:bfp}
@@
 \end{eqnarray}
-${\bf Cov}_i$ is the covariance matrix.
-
-It is difficult to conduct the 2pCF of the whole snapshot box with hundreds of millions of galaxies.
-We split the box into 120 subsamples with $X,Y,Z$ sizes of $1575h^{-1}{\rm Mpc},1575h^{-1}{\rm Mpc}, 105h^{-1}{\rm Mpc}$
-and measure the angular 2pCF in the $X-Y$ plan in these subsamples. 
-The average of the 2pCFs are taken as the 2pCF of the whole box.
-The covariance matrix is also estimated from these 2pCFs.
-
-In real observations we observe {\it different} objects at different redshfit shells.
-To mimick this when calculating the redshift evolution of 2pCF we use subsamples at different positions at different redshfits.
-E.g., if for the $z=0$ snapshot we use the $\hat{r_\perp\omega}$ measured in the subsample $0h^{-1}{\rm Mpc}<Z<105 h^{-1}{\rm Mpc}$,
-at higher redshifts we adopt the $\hat{r_\perp\omega}$ measured in a subsample $105h^{-1}{\rm Mpc}<Z<210 h^{-1}{\rm Mpc}$,
-and take the difference between them to get $\delta \hat{r_\perp\omega}$.
-So we are always comparing 2pCF measured from different samples of galaxies.
-If simply comparing the 2pCF of a same sample of galaxies at different redshifts, 
-one would significantly underestimate the statistical undertainty of $\delta \hat{r_\perp\omega}$ by ignoring the cosmic variance
-\footnote{The error bars displayed in all figures are estimated from the 120 subsamples and for the error bar of redshift evolution of 2pCF 
-we always take the cosmic variance into consideration.}.
+${\bf Cov}_i$ is the covariance matrix estimated from the ${\bf p}(z_i,r_{j})$ measured from 120 subsamples.
+%It is difficult to conduct the 2pCF of the whole snapshot box with hundreds of millions of galaxies.
+%We split the box into 120 subsamples with $X,Y,Z$ sizes of $1575h^{-1}{\rm Mpc},1575h^{-1}{\rm Mpc}, 105h^{-1}{\rm Mpc}$
+%and measure the angular 2pCF in the $X-Y$ plan in these subsamples. 
+%The average of the 2pCFs are taken as the 2pCF of the whole box.
+%The covariance matrix is also estimated from the redshift evolution of these subsamples.
+As mentioned before, for a robust estimation of covariance matrix, 
+we always compare slices at different locations to 
+include the cosmic variance.
+
+The covariance matrix inferred from a finite number of samples
+is always a biased estimate of the true matrix \citep{Hartlap}.
+This can be corrected by rescaling the inverse covariance matrix as 
+\begin{equation}
+ {\bf Cov}^{-1}_{ij,\rm Hartlap} = \frac{N_s - n_{r}-2}{N_s-1} {\bf Cov}^{-1}_{ij},
+\end{equation}
+where $N_s=120$ is the number of mocks used in covariance estimation.
+For the options of this analysis the rescaling is as large as 1.43.
+In the case that one have 2\,000 mocks the rescaling is less than 1.02.
+
 %estimated from the 72 sets of PSB mock galaxies identified from HR3 N-body simulation.
 
-Figure \ref{fig_cosmo} displayed the 2pCF measured in the four cosmologies displayed in Figure \ref{fig_xyquan}.
+Figure \ref{fig_cosmo} displays the 2pCF and the likelihood values in case of adopting 
+the four wrong cosmologies of Figure \ref{fig_xyquan}.
 For the cosmologies $\Omega_m=0.4,w=-1$ and $\Omega_m=0.26,w=-0.5$,
-the compression of structure rescale large scale clustering patterns into small scales;
-the compression becomes more significant at higher redshift.
-In these cosmologies we get 2pCFs with steeper slope and, the higher redshift, the steeper.
-For $\Omega_m=0.15,w=-1$ and $\Omega_m=0.26,w=-1.5$,
-the stretch of structure leads to shallower slope of $\hat{r_\perp\omega}$ and, the higher the redshift, the shallower.
-In all cosmologies we find significant detection of redshift evolution of $\hat{r_\perp\omega}$ (in the lowest panels, $\delta \hat{r_\perp\omega}\neq0$).
-We computed the $\chi^2$ values according to Equation \ref{eq:chisq1} and found these sets of cosmological parameters are strongly disfacored 
+the compression of structure shift the large scale clustering patterns into small scales,
+and also becomes more significant at higher redshift.
+We get 2pCFs with steeper slope and the higher redshift the steeper.
+For cosmologies $\Omega_m=0.15,w=-1$ and $\Omega_m=0.26,w=-1.5$,
+the stretch of structure leads to shallower slope of $\hat{\omega_{r_\perp}}$ and the higher the redshift the shallower.
+In all cosmologies we have significant detection of redshift evolution.
+We computed the $\chi^2$ values according to Equation \ref{eq:chisq1}, 
+and found these cosmological parameters are strongly disfacored 
 at $\gtrsim30\sigma$ CL.
@@
 %    \includegraphics[height=8cm]{smu.eps}
-    \includegraphics[width=18cm]{fig4.eps}
+    \includegraphics[width=18cm]{fig5.eps}
    }
@@
 
-We constrain $\Omega_m$ and $w$ through Bayesian analysis (\citep{Bayesian}; also see \citep{LB2002,Li2016} for details).
+We constrain $\Omega_m$ and $w$ through Bayesian analysis (\cite{Bayesian}; also see \cite{LB2002,Li2016}).
 We assue the likelihood takes the form
@@
    }
-   \caption{\label{fig9.eps}
+   \caption{\label{fig_contours}
    Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method.
@@
 
- * Can be combined with our redshift dependence of AP to full explore the geometric effects in LSS
-
- *  *** utilizes angular 2pCF as a function of redshift.
-Our method is complementary to it: 1) smaller scales; 2) more bins; 3) could be less affected by RSD; ...
-In case of good modelling of RSD one can rely on their; in case not possible, especially on small scales, one can use ours
-
- * Complementary to all other LSS probes
-
- * Promising future
+We developed a method measuring the redshift of the shape of galaxy angular correlation function, $\hat \omega_{r_\perp}$, to constrain cosmology.
+A wrongly adopted cosmology result in redshift-dependent mis-scaling in the constructed galaxy distribution,
+which leads to redshift-dependent rescaling of $\hat \omega_{r_\perp}(r_\perp)$.
+The signal is sensitive to the adopted cosmological parameters and relatively insensitive to the gravitational growth of structure,
+the galaxy bias, and the RSD effect.
+We test our method on the HR4 mock galaxies having 457, 406, 352, 206 and 228 million galaxies at redshfits 0, 0.5, 1, 1.5, 2;
+analyzing redshift evolution of the shape of 2pCF on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$ we derive tight constraints on $\Omega_m$ and $w$.
+
+The angular correlation function is adopted as a statistical tool to probing the scaling effect in the angular direction.
+One can also use the 2D 2pCF as a function of both angular and radial scale to fully probe the scaling effect in 3D galaxy distribution.
+
+There are already works using the shape of angular 2pCF to constrain cosmology
+by directly comparing the theoretical 2pCF to the observed one \citep{Salvador2014,Salvador2016}.
+While our method just utilize the fact the the shape of angular 2pCF is insensitive to redshift in correct cosmology.
+Our method is complementary to these works in the sense that,
+we do not require accurate analytic modeling and should be applicable on smaller scales.
+The two different approaches can be combined together to fully extract the cosmological information.
+
+The method of redshift dependent AP effect has been shown great power to constrain cosmological parameters \cite{Li2014,Li2015,Li2015}.
+We hope this method also.
+The two methods probe different information encoded in the 2pCF and can be combined to fully probe the geometrical effect in LSS.
+Or one can also use the redshift evolution of 2D 2pCF xi(s,mu) to have all information included.
+
+The method is designed to be applied to current and future LSS surveys,
+with a particular emphasis to the photometric surveys which probe a large amount of galaxies and the large redshift error will not quite affect the angular 2pCF measurement.
+An accurate modeling of redshfit error, galaxy bias and RSD effects could be crucial for the successful application of the method.
+DES will probe 300 million galaxies at $z<1.4$, and LSST will probe 20 billion galaxies at $z<2$.
+We hope our method play an active role in  deriving cosmological constraints from LSS surveys.
 
@@
 %Sutter, P.M., Pisani, A., Wandelt, B.D., \& Weinberg, D.H. 2014, MNRAS, 443, 2983
+
+\bibitem[Salvador et al. (2014)]{Salvador2014}
+Salvador, S.A., S\^{a}nchez, A.G., Padilla, N.D., \& Baugh, C.M. 2014, MNRAS, 443, 2612
+
+\bibitem[Salvador et al. (2016)]{Salvador2016}
+Salvador, S.A., S\^{a}nchez, A.G., \& Grieb, J.N., et al. 2016, submitted to MNRAS
 
@@
 
+\bibitem[Weinberg et al. (2013)]{DHW2013}
+Weinberg, D.H, Mortonson, M.J., Eisenstein, D.J., et al. 2013, Physics Reports, 530, 87
+
 \bibitem[White (2011)]{White2011}

### 2016-09-18 draft/draft0.tex
update draft

@@
 
-Dark energy has become the most important scientific issue since the discovery of cosmic acceleration \citep{Riess1998,Perl1999}.
-Many theoretical and observational effect has been made \citep{Weinberg,Li2011,DHW2013}, but its properties still remain far from accurately known and its nature still remains mystery. 
+The discovery of cosmic acceleration \citep{Riess1998,Perl1999} implies the existence of a ``dark energy'' component in the Universe 
+or the breakdown of Einstein's gravity theory on cosmological scales.
+The theoretical explanation and observational probe of cosmic acceleration has attracted 
+tremendous effort in the last two decades and are still far from well understood or accurately measured \citep{SW1989,Li2011,DHW2013}.
+%, but its properties still remain far from accurately known and its nature still remains mystery. 
 %The simplest and currently favored solution is the additional field called dark energy which has negative pressure and is spatially homogeneous.
@@
 
-To measure the properties dark energy we need accurate probe of the cosmic expansion history. 
-In large scale structure surveys the two representative geometrical observables are the angular diameter distance $D_A$ and the Hubble factor, $H$. 
-If these can be precisely measured as functions of redshift, then tight constraints can be placed on the parameters of the cosmological model,
-e.g., the matter density $\Omega_m$ and the equation of state (EoS) of dark energy, $w$.
-
-Assuming an incorrect cosmological model for the coordinate transformation from redshift space to comoving space leaves residual geometric distortions. 
-These distortion include volume effect which is the alteration of the comoving volume size of structures,
-and the Alcock-Paczynski (AP) effect, induced by the fact that distances along and perpendicular to the line of sight are fundamentally different.
+In an effort to probe the cosmic expansion history the large scale structure (LSS) surveys enable measurements of two geometrical quantities, 
+the angular diameter distance $D_A$ and the Hubble factor, $H$. 
+If they were precisely measured as a function of redshift, 
+tight constraints can be placed on cosmological parameters, 
+e.g. the matter density $\Omega_m$ and the equation of state (EoS) of dark energy $w$.
+
+As one geometrical effect of cosmological parameters on LSS,  
+when an incorrect cosmological model is assumed for the coordinate transformation from redshift space to comoving space,
+geometric distortions are produced in the constructed galaxy distribution. 
+These distortion include the ``volume effect'' which is the mis-scaling of the size of structures,
+and the Alcock-Paczynski (AP) effect, the shape distortion induced by the fact that distances along and perpendicular to the line of sight are fundamentally different.
 %Measuring the ratio of galaxy clustering in the radial and transverse directions, provides a probe of the Alcock-Paczynski (AP) effect \citep{AP1979}.
 %There have been a series of works studying the application of the AP test to the LSS
-A series of statistically method has been proposed to measure the AP test in the LSS
-\citep{Ballinger1996,Matsubara1996,Marinoni2010,Ryden1995,LavausWandelt1995}
-and have been applied to a series of LSS surveys \citep{Outram2004,Blake2011,ChuangWang2012,
-Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, Jeong2014,Sutter2014,2014ApJ...781...96L,
-Alam2016, Beutler2016, Sanchez2016,Qingqing2016}. 
-The probe of volume effect is usually probed through number counting of 
-galaxy clusters \citep{PS1974,VL1996}, topology \citep{topology};
-it is also part of the physical effects measured in the measurements of the BAO scale \citep{some reference},
-or the probe of the shape of 2pCF and power spectrum \citep{some reference}.
+
+Various statistically methods has been proposed to measure these effects.
+The AP effect has been proposed to measure through the clustering of galaxies \citep{Ballinger1996,Matsubara1996} which has been applied to a series of LSS surveys
+\citep{Outram2004,Blake2011,ChuangWang2012,Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, Jeong2014,Sutter2014,2014ApJ...781...96L,Alam2016, Beutler2016, Sanchez2016},
+the alternative approaches using the symmetry properties of galaxy pairs \citep{Marinoni2010,Jennings2011,BB2012}
+and cosmic voids \citep{Ryden1995,LavausWandelt1995,Sutter2014,Qingqing2016}.
+Methods proposed able to probe the volume effect include the number counting of 
+galaxy clusters \citep{PS1974,VL1996} and topology \citep{topology},
+the BAO scale \citep{EHT1998,BG03,SE03},
+and the shape of 2pCF and power spectrum \citep{Sanchez2006,Sanchez2009}.
+
+%\bibiem[Kazin et al (2012)]{KSB2012}
+%Kazin, E.A., S\'{a}nchez, A.G., Blanton, M.R. 2012, MNRAS, 419, 3223
 
@@
 
+\bibitem[Blake \& Glazebrook (2003)]{BG03};
+ Blake, C., \& Glazebrook, K. 2003, ApJ, 594, 665
+
 \bibitem[Blake et al.(2011)]{Blake2011}
@@
 Efstathiou, G. 2014, MNRAS, 440, 1138
+\bibitem[Eisenstein et al. (1998)]{EHT1998}
+Eisenstein, D.J., Hu, W., \& Tegmark, M. 1998, ApJ, 504, L57
 
@@
 
-%\bibitem[Jeong et al.(2014)]{Jeong2014}
-%Jeong, D., Dai, L., Kamionkowski, M., \& Szalay, A.S. 2014, arXiv:1408.4648
+\bibitem[Jeong et al.(2014)]{Jeong2014}
+Jeong, D., Dai, L., Kamionkowski, M., \& Szalay, A.S. 2014, arXiv:1408.4648
 
@@
 
-%\bibitem[Sutter et al.(2014)]{Sutter2014}
-%Sutter, P.M., Pisani, A., Wandelt, B.D., \& Weinberg, D.H. 2014, MNRAS, 443, 2983
+\bibitem[Sutter et al.(2014)]{Sutter2014}
+Sutter, P.M., Pisani, A., Wandelt, B.D., \& Weinberg, D.H. 2014, MNRAS, 443, 2983
 
 \bibitem[Salvador et al. (2014)]{Salvador2014}
-Salvador, S.A., S\^{a}nchez, A.G., Padilla, N.D., \& Baugh, C.M. 2014, MNRAS, 443, 2612
+Salvador, S.A., S\'{a}nchez, A.G., Padilla, N.D., \& Baugh, C.M. 2014, MNRAS, 443, 2612
 
 \bibitem[Salvador et al. (2016)]{Salvador2016}
-Salvador, S.A., S\^{a}nchez, A.G., \& Grieb, J.N., et al. 2016, submitted to MNRAS
+Salvador, S.A., S\'{a}nchez, A.G., \& Grieb, J.N., et al. 2016, submitted to MNRAS
+
+\bibitem[S\'{a}chez et al. (2006)]{Sanchez2006}
+S\'{a}chez, A.G., Baugh, C.M., \& Percival, W.J. et al. 2006, MNRAS, 366, 187
+
+\bibitem[S\'{a}nchez et al. (2009)]{Sanchez2009}
+S\'{a}nchez, A. G., Crocce, M., Cabr\'{e}, A., Baugh, C.M., \& Gaztaaga, E. 2009, MNRAS, 400, 1643
 
 \bibitem[Sanchez et al.(2016)]{Sanchez2016}
-Sanchez, A. G., Scoccimarro, R., \& Crocce, M., et al.
+S\'{a}nchez, A. G., Scoccimarro, R., \& Crocce, M., et al.
 arXiv:1607.03147
@@
 
+\bibitem[Seo \& Eisenstein (2003)]{SE03}
+Seo, H.-J., \& Eisenstein, D.J. 2003, ApJ, 598, 720
+
 \bibitem[Smee et al.(2013)]{Smee2013}

### 2016-09-19 draft/draft0.tex
updates

@@
 
-In \cite{Li2014,Li2015,Li2016} we proposed a series of methods to probe the geometric information encoded in the LSS data.
-We make use of the fact that the AP or volume effect commonly introduce redshift-dependent geometric distorion in the LSS,
-which can be distinguished from the other effects such as the redshfit space distortion (RSD).
-RSD arises because the radial distances of galaxies are inferred from redshifts which is contaminated by the pecular motion of galaxies, 
-leading to apparent anisotropy even if the adopted cosmology is correct \citep{Ballinger1996}.
-RSD is the usually main caveats for probe geometry using LSS,
-and we found it can be largerly avoid by focusing on the the redshift dependence of the anisotropy.
-
-\cite{Li2014} proposed used the {\it galaxy density gradient field} 
-to characterize the anisotropies in LSS and tested the idea on Horizon Run 3 (HR3) N-body simulations \citep{horizonrun},
-showing the redsift evolution of the gardient field can be used to infer unbiased constraints cosmological parameters and is insensitive to RSD.
-The same topic was revisited in \cite{Li2015}, but using the statistical tool of {\it galaxy two-point correlation function} (2pCF) as a function of angle, $\xi(\mu)$.
-When incorrect cosmological parameters are adopted, the shape of $\xi(\mu)$ appears anisotropic due to the AP effect, 
-and the amplitude is shifted by the change in comoving volume;
+In \cite{Li2014,Li2015,Li2016} we developed a novel strategy to probe $D_A$ and $H$ from LSS data.
+%proposed a series of methods to probe the geometric information encoded in the LSS data.
+We found fact that the AP or volume effect in general introduces a geometric distortion significantly evolves with redshift;
+this phenomenon can be utilized to distinguish the the from the other effects such as the redshift space distortion (RSD).
+The radial distances of galaxies are inferred from the measured redshifts which are distorted by the peculiar motion of galaxies, 
+leading to apparent distortion in the redshift space galaxy distribution \citep{FOG,Kaiser1987,Ballinger1996}.
+It is the major systematic effects limiting our ability to probe the geometry of LSS from galaxy distribution.
+We found its influence is significantly reduced in case of studying the redshift dependence of the distortion.
+
+\cite{Li2014} attempted to use the {\it galaxy density gradient field} 
+to characterize the redshift evolution of the LSS distortion. 
+We tested the idea on Horizon Run 3 (HR3) N-body simulations \citep{horizonrun},
+showing the redshift evolution of the statistical property of the gradient field 
+can be used to infer unbiased constraints cosmological parameters and is insensitive to RSD.
+The same topic was revisited in \cite{Li2015}, 
+using the statistical tool of {\it galaxy two-point correlation function} (2pCF) as a function of angle, $\xi(\mu)$, 
+where $\mu\equiv \cos \theta$ and $\theta$ is the direction between the connection of the galaxy pairs and the direction.
+When incorrect cosmological parameters are adopted, 
+the shape of $\xi(\mu)$ is altered due to the anisotropic shape of the LSS (the AP effect), 
+and the amplitude is shifted due to the change in the size of comoving volume;
 both effects have significant redshift dependence.
-The RSD effect, although significantly distorting $\xi(\mu)$, 
-exhibits much less redshift evolution compared to the effect coming from incorrectly adopted cosmologies.
-The method was applied to BOSS DR12 galaxies \citep{Li2016} to probe the redshift dependent of AP effect and lead to tight cosmological constraints.
-
-We developed a method measuring the redshift of the shape of galaxy angular correlation function to constrain cosmology.
-A wrongly adopted cosmology result in redshift-dependent mis-scaling in the constructed galaxy distribution,
-which leads to redshift-dependent change in the angular 2pCF shape.
-The signal is sensitive to the adopted cosmological parameters and relatively insensitive to the gravitational growth of structure,
+The RSD effect, although {\it very significantly} distorts $\xi(\mu)$, 
+exhibits less redshift evolution.
+The method was applied to BOSS DR12 galaxies \citep{Li2016} to probe the redshift dependent of the AP effect, 
+and we come up with tight cosmological constraints comparable to the mainstream probes of SNIa, BAO, CMB and so on.
+
+In this paper we continue our exploration of our strategy and presented 
+a new method using the redshift of the shape of {\it galaxy angular 2pCF} as a function of radial scale, $\omega(r_{\bot})$,
+to constrain cosmology.
+A wrongly adopted cosmology result in {\it redshift-dependent mis-scaling} of the galaxy distribution,
+which leads to redshift-evolution of the shape of $\omega(r_{\bot})$.
+The signal is sensitive to the cosmological parameters and relatively insensitive to the other effects such as the gravitational growth of structure,
 the galaxy bias, and the RSD effect.
-We test our method on the HR4 mock galaxies having hundreds of million galaxies at redshfits 0-2.
-Analyzing redshift evolution of the shape of 2pCF on scales $5 - 40 h^{-1} {\rm Mpc}$, we derive tight constraints on $\Omega_m$ and $w$.
-
-In this paper we continue our series of work and probe to use the angular correlation function as a statistical tool to probing the volume effect in the angular direction.
+We apply our method to the HR4 mock galaxies having hundreds of million galaxies at redshfits 0-2
+and develop the statistical procedure to constrain cosmological parameters.
+
+%In this paper we continue our series of work and probe to use the angular correlation function as a statistical tool to probing the volume effect in the angular direction.
 %The method of redshift dependent AP effect has been shown great power to constrain cosmological parameters \cite{Li2014,Li2015,Li2015}.
@@
 %We developed a method measuring the redshift of the shape of galaxy angular correlation function, $\hat \omega_{r_\perp}$, to constrain cosmology.
-A wrongly adopted cosmology result in redshift-dependent mis-scaling in the constructed galaxy distribution,
-which shifts apparent scale of the clustering patterns;
-this manifests itself as a redshift-dependent rescaling of the measured angular correlation function.
-We find this signal is sensitive to the adopted cosmological parameters and relatively insensitive to the gravitational growth of structure,
-the galaxy bias, and the RSD effect.
-We test our method on the HR4 mock galaxies.
-The method can be applied to current and future LSS surveys,
-especially, the photometric surveys such as DES and LSST which probe a large amount of galaxies and the large redshift error will not quite affect the angular 2pCF measurement.
+%A wrongly adopted cosmology result in redshift-dependent mis-scaling in the constructed galaxy distribution,
+%which shifts apparent scale of the clustering patterns;
+%this manifests itself as a redshift-dependent rescaling of the measured angular correlation function.
+%We find this signal is sensitive to the adopted cosmological parameters and relatively insensitive to the gravitational growth of structure,
+%the galaxy bias, and the RSD effect.
+%We test our method on the HR4 mock galaxies.
+%The method can be applied to current and future LSS surveys,
+%especially, the photometric surveys such as DES and LSST which probe a large amount of galaxies and the large redshift error will not quite affect the angular 2pCF measurement.
 
 The outline of this paper proceeds as follows. 
-In \S 2 we briefly review the nature and consequences of the geometric distortion in LSS when performing coordinate transforms in a cosmological context. 
-In \S 3 we describe the mock galaxies produced from N-body simulations which are used to test our methodology.
+In \S 2 we briefly review the nature and consequences of the LSS geometric distortion when performing coordinate transforms in a cosmological context. 
+In \S 3 we describe the N-body mock galaxies used to test our method.
 The methodology is presented in \S 4.
-We conclude in \S 6.
+We conclude in \S 5.
 

### 2016-10-06 draft/draft0.tex
updates

@@
 \shorttitle{Reshift Dependent Volume effect}
-\shortauthors{X.-D. Li, C. Park, C.G. Sabiu, H. Park, D.H. Weinberg, J. Kim, S.E. Hong}
+\shortauthors{X.-D. Li, C. Cheng, C. Park, C.G. Sabiu, H. Park, J. Kim, S.E. Hong}
 
@@
 \and
-\author{Stephen Appleby, Sungwook E. Hong}
+\author{Sungwook E. Hong}
 \affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
@@
 \begin{abstract}
-We propose to use the redshift of the shape of galaxy angular 2-point correlation function (2pCF) to constrain cosmology.
-The method is a continue of our series of works \citep{Li2014,Li2015,Li2016} probing the redshift dependence of Alcock-Paczynski effect and volume effect. 
-A wrongly adopted cosmology result in redshift-dependent mis-scaling in the constructed galaxy distribution,
-which leads to redshift-dependent rescaling in the measured angular 2pCF.
-We test our method on the HR4 mock galaxies having 457, 406, 352, 206 and 228 million galaxies at redshfits 0, 0.5, 1, 1.5, 2,
-and find the redshift evolution of the scaling of angular 2pCF is sensitive to the adopted cosmological parameters and 
-relatively insensitive to the gravitational growth of structure,
+We use the redshift dependence of the galaxy angular 2-point correlation function (2pCF) shape 
+to constrain cosmological parameters.
+A wrongly adopted cosmology introduces redshift-dependent mis-scaling 
+of the constructed galaxy distribution,
+leading to redshift-dependent rescaling in the measured angular 2pCF.
+We test our method on the HR4 mock galaxies having hundreds of millions of galaxies at redshifts 
+0, 0.5, 1, 1.5, 2.
+We find the redshift evolution of shape of angular 2pCF, as a function of scale,
+is sensitive to the adopted cosmological parameters. 
+It is relatively insensitive to the gravitational growth of structure,
 the galaxy bias, and the redshift space distortion.
-Analyzing redshift evolution of the shape of 2pCF on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$ we derive tight constraints on $\Omega_m$ and $w$.
-Our method is complementary to current works using 2pCF to constrain cosmological parameters.
-The method could be applicable to future photometric surveys of DES, LSST to derive tight cosmological constraints.
-
+Analyzing the 2pCF shape on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
+we derive tight constraints on $\Omega_m$ and $w$.
+%Our method is complementary to current works using 2pCF to constrain cosmological parameters.
+The method could be applicable to future photometric surveys like DES, LSST 
+to derive tight cosmological constraints.
+The work is a continue of our previous works \citep{Li2014,Li2015,Li2016}
+as a strategy to constrain cosmological parameters based on some nearly redshift-invariant physical quantity;
+they are all powerful in constrain cosmology and have a lot of merits,
+e.g., are less affected by the systematic effects introduced by non-linear clustering or RSD,
+does not require accurate modeling of galaxy clustering,
+and are applicable on relative small clustering scales.
 \end{abstract}
@@
 %Kazin, E.A., S\'{a}nchez, A.G., Blanton, M.R. 2012, MNRAS, 419, 3223
+
+%The  Alcock-Paczynski (AP) effect referes to
+%the geometric distortion when incorrect cosmological models are assumed for 
+%transforming redshift to comoving distance,
+%induced by the fact that measured distances along and perpendicular to the line of sight are fundamentally different.
+
+%The AP effect can be measured through the staistial study of galaxies clustering  \citep{Ballinger1996,Matsubara1996,
+%Outram2004,Blake2011,ChuangWang2012,Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, Jeong2014,Sutter2014,2014ApJ...781...96L,Alam2016, Beutler2016, Sanchez2016},
+%symmetry properties of galaxy pairs \citep{Marinoni2010,Jennings2011,BB2012},
+%and cosmic voids \citep{Ryden1995,LavausWandelt1995,Sutter2014,Qingqing2016}.
+%The main caveat of these methods is that,
+%because the radial distances of galaxies are inferred from redshifts,
+%AP tests are inevitably limited by redshift-space distortions (RSD) \citep{Ballinger1996},
+%which leads to apparent anisotropy even if the adopted cosmology is correct.
+
+%\cite{Li2014,Li2015,Li2016} proposed a novel strategy to measure the redshift dependence of AP.
+%Anisotropies produced by the RSD effect are, although large,
+%maintaining a nearly uniform magnitude over a large range of redshift,
+%while the degree of anisotropies from the AP effect varies with redshift by much larger magnitude. 
+%\citep{Li2016} applies this method to the SDSS-III BOSS DR12 galaxies, and obtained tight cosmological constraints 
+%comparable to the mainstream probes of SNIa, BAO or CMB.
+%This method could play an important role in deriving cosmological constraints from future LSS surveys.
 
@@
    \caption{\label{fig_xyquan}
-   %Apparent distortion of objects in four wrongly assumed cosmologies, assuming a true cosmology of .
-   The scaling in four wrongly assumed cosmologies ..., % $\Omega_m=0.41$, $w=-1.3$ and $\Omega_m=0.11$, $w=-0.7$, 
-   assuming a true cosmology of $\Omega_m=0.26$, $w=-1$.
-   Left panel shows a series objects distributes as five perfect squares, measured by an observer located at the origin.
+   A description of how wrongly assumed cosmologies can distort the interpretation of observation,
+   assuming $\Omega_m=0.26,w=-1$ is the true cosmology. 
+   Left panel shows a series of five regular squares, measured by an observer at the origin.
    Their true positions and shapes are plotted in blue dashed lines.
-   The observer measures the redshifts of these objects, adopts the wrong cosmologies to compute the distance,
-   and obtains wrong results (the red solid lines).
-   %The red solid lines show their positions and shapes when the wrong cosmologies 
-   % are assumed to compute distance from measured redshift.
-   %The mis-estimation of angular diameter distance lead to wrong 
-   Right panel shows the mis-estimation of angular diameter distance when the wrong cosmologies are adopted.
-   %In our mock surveys we split the samples at $z=0.3$, 0.6, 0.9 and 1.2, as marked by the vertical lines.
-   %measured by an observer located at the origin.
-   %For reference, blue dashed squares show their shapes and positions in the true cosmology.
+   When the observer adopts the wrong cosmologies to compute the distance from measured redshifts and infer the positions and shapes of the squares,
+   he/she obtains distorted squares shown as the red solid lines.
+   Right panel shows the redshift evolution of the wrongly estimated angular diameter distance (divided by the correct value).
    }
@@
 the inferred $\Delta r_{\parallel}$ and $\Delta r_{\perp}$ are wrong,
-resulting in wrong estimation in the object's shape (AP effect) and size (volume effect).
-These effects and their cosmological consequences have been investigated in \cite{Li2014,Li2015,Li2016}.
+resulting in wrong estimations of the object's shape (AP effect) and size (volume effect).
+These effects and their cosmological consequences have been studied in \cite{Li2014,Li2015,Li2016}.
 
@@
 \end{equation}
-where ``true'' and ``wrong'' denote the values of $D_A$ in the true cosmology and wrongly assumed cosmologies, respectively.
+where ``true'' and ``wrong'' denote the values in the true cosmology and wrongly assumed cosmologies, respectively.
 
@@
 and standard dark energy EoS $w=-1$.
-If we were to distribute a series of perfect squares at various distances ranging from 500 Mpc/h to 3\,000 Mpc/h,
+If we were to distribute a series of perfect squares at distances ranging from 500 Mpc/h to 3\,000 Mpc/h,
 and an observer located at the origin were to measure their redshifts and infer the sizes of the squares
@@
 and the degree of compression increases with increasing distance;
+the situation is opposite for the other two cosmologies.
 
 The mis-estimation of angular size, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$, 
-are displayed in the right panel of Figure \ref{fig_xyquan}.
-All cosmologies, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$ evolves a lot in the redshift range $0<z<2$.
+is displayed in the right panel of Figure \ref{fig_xyquan}.
+In all cosmologies, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$ evolves a lot in the redshift range $0<z<2$.
 As an example, when adopting the quintessence cosmology $\Omega_m=0.26,\ w=-0.5$,
@@
 
-In sum, as a consequence of incorrectly adopted cosmologies, 
-the size of the objects is mis-estimated and the magnitude of mis-estimation depends on the redshift.
-In this paper we use the galaxy angular 2pCF to probe the mis-estimation of angular size ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$.
+In sum, as a consequence of incorrect cosmologies, 
+the size of objects is mis-estimated, and the magnitude of mis-estimation depends on the redshift.
+We use the galaxy angular 2pCF to probe the mis-estimation of angular size, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$.
 
@@
 
-The resulting mock galaxies was found to reproduce the 2pCF of SDSS DR7 volume-limited galaxy sample \citep{zehavi2011} very well \citep{hong2016}.
+The resulting mock galaxies was found to reproduce the 2pCF of SDSS DR7 volume-limited galaxy sample \citep{zehavi2011} very well.
 The mock galaxies shows a similar finger of god (FOG) feature \citep{FOG} as the observation.
@@
 %and a series ({\bf how many?}) of snapshot mock galaxy catalogues at different redshifts.
-In this analysis we use snapshot data of HR4 galaxies at $z=0,0.5,1,1.5,2$.
+We take the snapshot data of the mock galaxies at $z=0,0.5,1,1.5,2$.
 %We require subhalos to have at least 30 member particles, 
@@
 respectively.
-By applying a uniform mass cut, at higher redshift we are selecting less galaxies with larger galaxy bias.
+By applying a uniform mass cut, at higher redshift we have smaller number of galaxies with {\it larger bias}.
 
 As an illustration, Figure \ref{fig_scatter} displays the 2D distribution of a subsample of mock galaxies in five redshifts,
-with $x$, $y$ coordinates computed using the ``correct'' values of cosmological parameters $\Omega_m=0.26,\ w=-1$ (left panels) 
-and a wrong set of cosmological parameters $\Omega_m=0.05,\ w=-1.5$ (right panels), respectively.
-
-When the correct cosmology is adopted the cosmic scale is correctly estimated in five redshifts.
-The only factor leads to evolution of galaxy distribution with redshift is the gravitational growth of structure.
-With the decreasing the redshift, we clearly see how the clusters and filaments form and grow.
+with $x$, $y$ coordinates computed using the ``correct'' cosmological parameters $\Omega_m=0.26,\ w=-1$ (left panels) 
+and a set of wrong cosmological parameters $\Omega_m=0.05,\ w=-1.5$ (right panels), respectively.
+
+When the correct cosmology is adopted the cosmic scale is correctly estimated,
+the main factor leads to redshift evolution of galaxy distribution is the gravitational growth of structure.
+With the decreasing the redshift, we clearly see the clusters and filaments form and grow.
 On the other hand, when the wrong cosmology is adopted, there is an artifical scaling of scales in the constructed map.
@@
 $25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$,
-leading to a clear evolution of the sizes of structures with redshift.
-
-The growth of structure leads to growth of clustering strength of structures on all scales,
-while the volume effect maintain the clustering pattern and uniformly re-scale all the structures.
-Their imprints on the large scale structure is different and should be distinguishable in the statistical analysis.
+leading to a clear redshift evolution of sizes of structures.
+
+The growth of structure strengths the clustering and make structures more compact,
+while the volume effect maintain the clustering pattern and uniformly re-scale the structures on all scales.
+Their imprints on the large scale structure is different and should be distinguishable.
 In the following, we show that they affect the angular correlation function measurements in different ways, 
@@
 
-The growth of structure also make the size of structures evolves with redshift.
-In the next subsection we will discuss how to distinguish these two effects in the galaxy angular 2pCF.
+%The growth of structure also make the size of structures evolves with redshift.
+%In the next subsection we will discuss how to distinguish these two effects in the galaxy angular 2pCF.
 
@@
    \caption{\label{fig_scatter}
-  blah
+  The 2D distribution of a $260\times130\times105 (h^{-1}{\rm Mpc})^3$ subsample of HR4 mock galaxies, 
+  at redshifts 0.5, 1, 1.5 and 2.
+  Left and right panels whos the $x$, $y$ coordinates computed using the ``correct'' parameters $\Omega_m=0.26,\ w=-1$ 
+  and a set of wrong cosmological parameters $\Omega_m=0.05,\ w=-1.5$, respectively.
+  The growth of structure strengths the clustering and make structures more compact at lower redshift.
+  When the wrong cosmology is adopted, the covmoving distances is mis-scaled and over-estimated by $25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$,
+  leading to a clear redshift evolution of sizes of structures.
    }
@@
 We use the angular 2pCF as a statistical tool to probe the volume effect.
-The galaxy 2pCF as a function of galaxy separation in the angular direction, $\omega(r_\perp)$, is computed for snapshot data of mock galaxies at five redshifts.
+The galaxy 2pCF as a function of galaxy separation in the angular direction, $\omega(r_\perp)$, is computed for snapshot data of mock galaxies at redshifts 0.5, 1, 1.5 and 2.
 We adopt the Landy-Szalay estimator~\citep{1993ApJ...412...64L},
@@
 size of 1575 $h^{-1}{\rm Mpc}\times 1575\ h^{-1}{\rm Mpc}\times 105\ h^{-1}{\rm Mpc}$.
+The sheet shape of the subsample is close to the shape of redshift shells in the real observational case.
 The Z direction with thickness $105\ h^{-1}\rm Mpc$ is treated as the radial direction (the $r$ direction) 
-and the X-Y directions with each of width $1575 h^{-1}\ \rm Mpc$ are the angular plane.
-For our simulation box size we can have 120 such subsamples.
+and the X-Y directions %with each of width $1575 h^{-1}\ \rm Mpc$ 
+are the angular plane.
+For our simulation box size we have 120 such subsamples.
 The average of the measurements in all subsamples is adopted as the 2pCF of the whole sample,
-while the covariances of them are adopted as the covariance matrix after multiplying a factor of $1/\sqrt{119}$.
-
-\subsection{Galaxy angular 2pCF: amplitude and shape at different redshifts}\label{sec_2pCF_diffz}
+while the covariances of them are adopted as the covariance matrix (after multiplying a factor of $1/\sqrt{119}$).
+
+\subsection{Galaxy angular 2pCF: at different redshifts}\label{sec_2pCF_diffz}
 
@@
    \caption{\label{fig_diffz}
-  2pCF at different redshfits.
+  The angular 2pCF ($\omega_{r_\perp}$, left panels), the shape of the angular 2pCF ($\hat{\omega}_{r_\perp}$, middle panels),
+  and the evolution with respect to the $z=0$ value ($\hat{\omega}_{r_{\perp}}(z=z_i) - \hat{\omega}_{r_{\perp}}(z=0)$, right panels). 
+  Upper panels show that in the correct cosmology the redshift evolution of the shape of 2pCF is rather small, 
+  whereas the lower panels show that, in a wrong cosmology $\Omega_m = 0.05,w=-1.5$, the redshift evolution of $\hat{\omega}_{r_\perp}$ is very significant.
    }
@@
 The upper-left panel of Figure \ref{fig_diffz} displays the angular 2pCF measured from HR4 mock galaxies. % (multiplied by scale $r$) in the five snapshot.
-We multiply $\omega$ by the separation $r_\perp$ to have similar amount of statistical uncertainty on all scales.
-
-At different redshifts, we see large evolution in the amplitude of $\omega(r_\perp)$.
-The amplitude of 2pCF is proportional to the clustering strengh which is affected by the gravitational growth of structures and the bias of the galaxies.
-The amplitude is highest at $z=0$ where the large scale structures experienced most gravitational growth,
-and also gets higher at $z>1$ with increasing redshift as a reason of more biased galaxies at higher redshift.
+We multiply $\omega$ by the separation $r_\perp$ to have similar size of statistical uncertainty on all scales.
+
+Among different redshifts there is large variation in the amplitude of $\omega(r_\perp)$.
+The amplitude is proportional to the clustering strengh which is affected by the gravitational growth of structures and the galaxy bias.
+The amplitude is highest at $z=0$ where the structures experienced most growth.
+$\omega(r_\perp)$ also increases with redshift at $z>1$ with increasing redshift 
+as a reason of increasing galaxy bias.
 %leading to stronger clustering strength and higher amplitude of 2pCF.
@@
 
-Different from the large variation of amplitude among the different redshifts, %The shape of $r_\perp\omega$ also evolves with redshift.
+Different from the large variation of amplitude among different redshifts, 
+%The shape of $r_\perp\omega$ also evolves with redshift.
 the shape of $r_\perp\omega$ maintains similar at all redshifts;
-it always peaks at $r\sim9 h^{-1}\rm Mpc$ and monotonically drops at larger or smaller scales.
+in general it peaks at $r\sim9 h^{-1}\rm Mpc$ and monotonically drops or increases at larger or smaller scales.
 The only exception is the small enhancement at $r\lesssim 2 h^{-1}\rm Mpc$,
-which is caused by the non-linear growth of structures on small scales 
+which is caused by the non-linear growth of structures 
 and is much more significant at lower redshfit.
@@
 In order to directly compare the shape of 2pCF at different redshifts,
-in the middle panel of Figure \ref{fig_diffz} we show the $r_\perp\omega$ normalized by the overall amplitude within $5h^{-1}{\rm Mpc} < r < 50h^{-1}{\rm Mpc}$
+in the middle panel of Figure \ref{fig_diffz} 
+we show the $r_\perp\omega$ normalized by the overall amplitude within 
+$5h^{-1}{\rm Mpc} < r < 40h^{-1}{\rm Mpc}$
 (here after $\hat \omega_{r_\perp}$):
@@
 where we choose $r_{\perp, \rm min}=5 h^{-1}$ Mpc, $r_{\perp, \rm max}=40 h^{-1}$ Mpc in this analysis.
-Scales of $r_{\perp, \rm min}<5 h^{-1}$ Mpc are affected by non-linear growth of strucutre, 
-the mis-estimation of whose contribution may lead to systematic errors in the derived cosmological constraints.
-On scales larger than $40 h^{-1}$ Mpc it is may be possible to have precise analytically modelling the shape of the 2pCF
- \citep{Salvador2014,Salvador2016} which should be able to extract more cosmological information than our method 
+Below $5 h^{-1}$ Mpc the non-linear growth of structure 
+leads to systematic redshift evolution which could be difficult to be reliably accounted;
+On scales larger than $40 h^{-1}$ Mpc,
+the analytical modelling of the shape of the angular 2pCF is relatively well understood;
+one can just fit the 2pCF with the theoretical predictions \citep{Salvador2014,Salvador2016} 
+instead of using our method 
 (although out method should is also applicable).
 
-The nice overlapping of the five redshift results
-justify the small evolution of shape with redshift.
-In the right panel, we further show the residual evolution of $\hat r_\perp\omega$ at high redshifts 
+In the upper-middle panel, the nice overlapping of the $\hat\omega_{r_\perp}$
+more clearly shows the the small redshift evolution of the shape.
+In the upper-right panel, 
+we further show the residual evolution at high redshifts 
 with respect to $z=0$.
-There is only 1-4\% relative enhancement 
+There is only 1-4\% enhancement 
 at $r<10h^{-1}\rm Mpc$,
-and $<1.5\%$ relative suppression at $r>25 h^{-1}\rm Mpc$.
+and $<1.5\%$ suppression at $r>25 h^{-1}\rm Mpc$.
 The trend is monotonic with redshift.
 
-There is one point should be emphasized here.
-In real observations we are observing {\it different} objects in different redshfit shells.
-To mimick this we comparing slices of different redshifts at {\it different} locations.
+There is one detail in the analysis which should be emphasized here.
+In real observations we are observing {\it different} objects in different redshift shells.
+Considering this fact in the comparison of $\hat\omega_{r_\perp}$ 
+we compare subsamples of galaxies at {\it different} locations.
 As an exammple, if at $z=0$ we take $\hat\omega_{r_\perp}$ measured within $0h^{-1}{\rm Mpc}<Z<105 h^{-1}{\rm Mpc}$,
@@
 If simply comparing the 2pCF of a {\it same} subsample of galaxies at different redshifts, 
-one would significantly underestimate the statistical undertainty of $\delta \hat{\omega_{r_\perp}}$ by ignoring the cosmic variance.
-The error bars and covariance are always estimated in this way to take the cosmic variance into consideration.
+one would significantly underestimate the statistical undertainty of $\delta \hat{\omega}_{r_\perp}$ by ignoring the cosmic variance.
+%The error bars and covariance are always estimated in this way to take the cosmic variance into consideration.
 %\footnote{In all figures of this paper The error bars displayed in all figures are estimated in this way; 
@@
 
-As shown by Figure \ref{fig_scatter}, the gravitational growth of strucutre enhance the clustering strengh of structures on all scales;
-here it manifests itself as an enhanced amplitude of 2pCF at low redshift.
-The shape of 2pCF, which represents the {\it relative strength of clustering among different scales},
-maintain similar with redshift except the non-linear scales of $r_\perp < 5 h^{-1}\rm Mpc$.
+%As shown by Figure \ref{fig_scatter}, the gravitational growth of strucutre enhance the clustering strengh of structures on all scales;
+%here it manifests itself as an enhanced amplitude of 2pCF at low redshift.
+%The shape of 2pCF, which represents the {\it relative strength of clustering among different scales},
+%maintain similar with redshift except the non-linear scales of $r_\perp < 5 h^{-1}\rm Mpc$.
 %mainly increases the amplitude of
@@
 
-The measured angular correlation function of galaxies with positions constructed using the wrong cosmology $\Omega_m=0.05,\ w=-1.5$
+The angular 2pCF of galaxy positions constructed in a wrong cosmology $\Omega_m=0.05,\ w=-1.5$
 is displayed in the lower panels of Figure \ref{fig_diffz}.
-The mis-scaling uniformly shifts clustering patterns on all scales, lead to a wrong estimation of $\hat \omega_{r_\perp}$ 
+The mis-scaling uniformly shifts clustering patterns on all scales, 
+leading to a wrong $\hat \omega_{r_\perp}$ 
 related with the correct one as
@@
 \end{equation}
-a simple consequence of the phenomenon that clustering patterns at distance $r$ now appears on $\alpha_{\perp} r$.
-The redshift evolution of $\alpha_{\perp}$ leads to redshfit evolution of shape.
-
+a simple consequence of the fact that clustering patterns at scale $r$ is rescaled to $\alpha_{\perp} r$.
+The redshift evolution of $\alpha_{\perp}$ leads to redshift evolution of 
+$\hat \omega_{r_\perp, \rm correct}$,
 %Lower panels of Figure \ref{fig_diffz} shows the $r_\perp\omega$ in five 
@@
 %is adopted to construct the galaxy distribution (the right panels of Figure \ref{fig_scatter}).
-The change in shape as well as the redshift evolution is displayed in the middle panel.
-The upscaling of comoving distance lead to a stretched shape.
+which is displayed in the lower-middle panel.
+The upscaling of comoving distance leads to a stretched shape.
 With the increasing of redshift,
@@
 
-The mis-scaling not only changes the of the 2pCF but also modifies its amplitude. %The amplitude of $r_\perp\omega$ is amplified due to the stretch of scale.
-as shown in the left panel, due to the stretch of scale the amplitude is enhanced at higher redshifts;
+The mis-scaling not only changes the shape of the 2pCF but also modifies its amplitude. %The amplitude of $r_\perp\omega$ is amplified due to the stretch of scale.
+As is shown in the left panel, due to the stretch of scale the amplitude is enhanced at higher redshifts;
 the higher the redshift, the more the enhancement.%the amplitude monotonically increases as a function of redshift.
 
-Although the change of amplitude could be a more significant consequence of wrong cosmology than the alteration of shape,
-it is mixed with other factors; 
-the growth of structure and a larger galaxy bias can also lead to a stronger clustering and thus an enhanced amplitude of 2pCF.
+Although the change of amplitude could be a more significant cosmological consequence 
+than the alteration of shape,
+it is mixed with the other effects; 
+the growth of structure and a larger galaxy bias can also lead to a stronger clustering and thus an enhanced amplitude.
 %it is more difficult to 
@@
 %so we will not make use of it to do cosmological constraint.
-In the analysis to extract cosmological information, we just make use of the redshift evolution of the 2pCF shape, 
-which is less affected by factors of structure growth and galaxy bias.
+In order to reliably extract the cosmological information, 
+we just utilize the the redshift evolution of the 2pCF shape, 
+which is less affected by other factors.
 %which is as a signal suggesting that the assumed cosmological parameters are wrong.
@@
 
-Sec. \ref{sec_2pCF_diffz} shows that $\hat \omega_{r_\perp}$ measured from a set of constant mass cut samples at different redshifts is close to each other.
-The gravitational growth of structure will not have a large impact on $\hat \omega_{r_\perp}$ on scales $\gtrsim5 h^{-1}$ Mpc.
-The other factors may introduce redshift evolution of the clustering of measured galaxies include the 
-redshift space distortion (RSD), galaxy bias, redshift error, and other properties of galaxies, such as the mass, morphology, color, concentration. 
+Sec. \ref{sec_2pCF_diffz} shows that $\hat \omega_{r_\perp}$ measured from 
+constant mass cut samples at different redshifts is close to each other.
+The gravitational growth of structure will not have large impact on $\hat \omega_{r_\perp}$ on scales $\gtrsim5 h^{-1}$ Mpc.
+Yet there are many other factors may introduce redshift evolution,
+including galaxy bias, RSD, redshift error, and 
+the redshift evolution of properties of galaxies 
+such as the mass, morphology, color, concentration, and so on. 
 Here we test two ``major'' systematical effects, the galaxy bias and the RSD effect.
@@
 Galaxies are biased tracers of dark matter field;
-more massive galaxies reside in regions with higher density contrast.
-In large scale structure surveys, the bias of the galaxy sample is an important fator affecting on the clustering properties of the sample.
-
-We check the effect of galaxy bias on $\hat \omega_{r_\perp}$.
+more massive galaxies reside in regions with higher density contrast
+and exhibit stronger clustering (i.e. larger bias).
+%In large scale structure surveys, the bias of the galaxy sample is an important fator affecting on the clustering properties of the sample.
+
+We vary the mass cut and check the effect of galaxy bias on $\hat \omega_{r_\perp}$.
 The upper panels of Figure \ref{fig_sys} displays the 2pCF measured from galaxies within a $3175\times3175\times105$ $(h^{-1}\rm Mpc)^3$ volume, taken from the $z=0$ snapshot.
@@
 have amplitude of 2pCFs enhanced by $10\%,\ 50\%$ and $100\%$,
-while the change in $\hat\omega_{r_\perp}$ is only $0.5\%,\ 2\%$ and $4\%$.
-So the effect of galaxy bias is much avoided by utilizing the shape of the 2pCF rather than the amplitude.
+while the change in the shape is only $0.5\%,\ 2\%$ and $4\%$.
+The effect of galaxy bias becomes much smaller by utilizing the shape of the 2pCF rather than the amplitude.
 
@@
 
-The galaxy peculiar velocity contributes to the observed redshift and distorted the inferred galaxy radial position,
+The galaxy peculiar velocity contributes to the observed redshift and distorts 
+the inferred galaxy radial position,
 known as the redshift space distortion.
 It is the major systematics in our previous works \citep{Li2014,Li2015,Li2016}
-where we derive cosmological constraints from the redshift evolution of the 3D galaxy distribution.
-
-The effect of RSD is expected to be much milder in this work. 
-The angular positions of the galaxies is not shifted by RSD at all;
-the only effect of RSD come in the procedure of sample preparation. %preparing the subsamples of galaxies for 2pCF analysis.
-The galaxies observed in a survey are split into shells of subsamples with different redshift ranges for the purpose 2pCF measurement.
-RSD disortes the galaxy redshift and as a result some galaxies (especially those close to the boundaries of shells) could be classified to wrong redshift shells.
+of statistical analysis on the 3D galaxy distribution.
+
+The effect of RSD is much milder in this work. 
+The angular positions of galaxies are not shifted by RSD at all;
+the only effect of RSD enter in the procedure of 
+splitting galaxies into redshift shells.
+The galaxies observed in a survey are split into shells of subsamples, 
+with different redshift ranges, for the 2pCF measurement.
+RSD distorts the galaxy redshift and as a result some galaxies 
+(especially those close to the boundaries of shells) are classified to wrong redshift shells.
 
 The lower panel of Figure \ref{fig_sys} displays the RSD effect on 2pCF.
-To have the effect of RSD we shift the radial coordinates of galaxies according to the relation 
+We shift the radial coordinates of galaxies according to the relation 
 \begin{equation}\label{eq:zvpeu}
@@
 \end{equation}
-where $v_{{\rm LOS}}$ is the galaxy peculiar velocity in the radial direction.
-This lead to mis-classfication of some galaxies when we split the box into slices.
+where $v_{{\rm Z}}$ (Z is treated as the radial direction in this analysis) 
+is the galaxy peculiar velocity in the LOS direction.
+This lead to mis-classification of some galaxies when we split the box into slices.
 %Then we split the whole box into 30 slices with thickness $105h^{-1}\rm Mpc$, 
@@
 
-Similar to RSD, redshift errors of galaxies (typically 0.02 for photometric survey) also results in fuzzy boundaries of shells and mis-classfication of galaxies.
+Similar to RSD, redshift errors of galaxies
+also results in fuzzy boundaries of shells and mis-classification of galaxies.
 This effect should also be properly quantified in real observations.
@@
    \caption{\label{fig_sys}
-  Systematic effects.
+  Upper panels: $\omega_{r_\perp}$ (left) and $\hat{\omega}_{r_\perp}$ (middle) are shown for four different halo-mass-cuts, $3\times 10^{11},~1\times 10^{12},~4\times 10^{12},~\&~1\times 10^{13}~M_\odot$,
+  below which we remove from 2pCF calculation. 
+  The right panel shows the difference in $\hat{\omega}_{r_\perp}$ between the $3\times 10^{11}~M_\odot$ mass-cut case and the other mass-cut cases. 
+  Lower panels: $\omega_{r_\perp}$ (left), $\hat{\omega}_{r_\perp}$ (middle), and $\hat\omega_{r_\perp}(z=z_i)-\hat\omega_{r_\perp}(z=0)$ (right) calculated with the RSD effect included.
    }
@@
 
-We design the likelihood function to quantify
-the redshift evolution of $\hat\omega_{r_\perp}$.
-A cosmology resulting in smaller evolution is considered to be more likely the correct one.
+A cosmology resulting in smaller evolution is considered to be more likely to be the correct one.
 The procedure here is very similar to what we did in \cite{Li2014,Li2015,Li2016}.
-We comapre the high redshift $\hat\omega_{r_perp}$ and the lowest redshift measurement:
+We compare the high redshift $\hat\omega_{r_\perp}$ and the lowest redshift measurement,
+\begin{equation}
+ \delta \hat{r_\perp\omega}(z_i,z_1) \equiv \hat{r_\perp\omega}(z_i) - \hat{r_\perp\omega}(z_1),
+\end{equation}
+and design the likelihood function to quantify
+the redshift evolution of $\hat\omega_{r_\perp}$:
 \begin{equation}\label{eq:chisq1}
@@
 where $n_z$ is the number of redshifts which is 5 in this analysis, 
-$n_r$ is number of binning in $\hat{\omega_{r_\perp}}(r_\perp)$,
+$n_r$ is number of binning in $\hat{\omega}_{r_\perp}(r_\perp)$,
 which is 35 since we have $r_\perp$ bins 
@@
 \begin{eqnarray}\label{eq:bfp}
- {\bf p}(z_i,r_{j}) \equiv&\ \delta \hat{r_\perp\omega}(z_i,z_1,r_j) - \delta \hat{r_\perp\omega}_{\rm sys}(z_i,z_1,r_j)
+ {\bf p}(z_i,r_{j}) \equiv&\ \delta \hat{\omega}(z_i,z_1,r_j) - \delta \hat{\omega}_{r_\perp,\rm sys}(z_i,z_1,r_j)
 \end{eqnarray}
@@
 where $N_s=120$ is the number of mocks used in covariance estimation.
-For the options of this analysis the rescaling is as large as 1.43.
+For this analysis the rescaling is as large as 1.43.
 In the case that one have 2\,000 mocks the rescaling is less than 1.02.
@@
 For the cosmologies $\Omega_m=0.4,w=-1$ and $\Omega_m=0.26,w=-0.5$,
-the compression of structure shift the large scale clustering patterns into small scales,
-and also becomes more significant at higher redshift.
-We get 2pCFs with steeper slope and the higher redshift the steeper.
+the compression shifts the large scale clustering patterns into small scales
+at higher redshift and make the 2pCFs steeper.
+%and also becomes more significant at higher redshift.
+%We get 2pCFs with steeper slope and the higher redshift the steeper.
 For cosmologies $\Omega_m=0.15,w=-1$ and $\Omega_m=0.26,w=-1.5$,
-the stretch of structure leads to shallower slope of $\hat{\omega_{r_\perp}}$ and the higher the redshift the shallower.
-In all cosmologies we have significant detection of redshift evolution.
-We computed the $\chi^2$ values according to Equation \ref{eq:chisq1}, 
-and found these cosmological parameters are strongly disfacored 
+the stretch of structure leads to shallower slope of $\hat{\omega}_{r_\perp}$ at higher redshift.
+%the shallower.
+In all cosmologies there is significant detection of redshift evolution.
+We compute the $\chi^2$ values according to Equation \ref{eq:chisq1}, 
+and find these cosmologies are disfavored 
 at $\gtrsim30\sigma$ CL.
@@
    \caption{\label{fig_cosmo}
-   2pCF in cosmologies.
+    $\hat{\omega}_{r_\perp}$ (upper panels) and $\hat{\omega}_{r_\perp}(z=z_i) - \hat{\omega}_{r_\perp}(z=0)$ (lower panels) at several redshifts,
+    for the four wrong cosmologies.
+    The redshift evolution of angular 2pCF shape in these wrong cosmologlies are detected at high CL.
    }
@@
 We assue the likelihood takes the form
-\begin{equation}
- \mathcal{L} \propto \exp\left[-\frac{\chi^2}{2}\right]
+\begin{equation}\label{eq:like}
+ \mathcal{L} \propto \exp\left[-\frac{\chi^2}{2}\right],
 \end{equation}
@@
    \caption{\label{fig_contours}
-   Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method.
+   Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method,
+   a likelihood value computed using Equations (\ref{eq:like,eq:chisq1}), 
+   based on the redshfit evolution of the angular 2pCF shape $\hat\omega_{r_\perp}$.
+   Utilizing the HR4 snapshots data of mock galaxies at five redshifts,
+   the method can lead to very tight cosmological constraint.
    }
@@
 The 2$\sigma$ contour lies within the region $0.23<\Omega_m<0.285$, $-1.1<w<-0.9$.
-The thin shape of contour means, when combining with the another observational data with different direction of degeneracy (e.g. CMB),
+The two parameters are very strongly degenerated with each other.
+The thin shape of contour implies that, 
+when combining with the another observational data with different direction of degeneracy (e.g. CMB, BAO),
 very tight combined constraint can be obtained.
-In case of fixing one parameter at its best-fit value and infer the statistical uncertainty of the other one,
-one will obtain 1$\sigma$ uncertainty of $\delta\Omega_m\approx0.002,\delta w\approx0.01$.
+In case of fixing one parameter at its best-fit value and constrain the other one,
+one obtain 1$\sigma$ uncertainty of $\delta\Omega_m\approx0.002,\delta w\approx0.01$.
 
@@
 which leads to redshift-dependent rescaling of $\hat \omega_{r_\perp}(r_\perp)$.
-The signal is sensitive to the adopted cosmological parameters and relatively insensitive to the gravitational growth of structure,
+The signal is sensitive to cosmology and relatively insensitive to the gravitational growth of structure,
 the galaxy bias, and the RSD effect.
-We test our method on the HR4 mock galaxies having 457, 406, 352, 206 and 228 million galaxies at redshfits 0, 0.5, 1, 1.5, 2;
-analyzing redshift evolution of the shape of 2pCF on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$ we derive tight constraints on $\Omega_m$ and $w$.
-
-The angular correlation function is adopted as a statistical tool to probing the scaling effect in the angular direction.
-One can also use the 2D 2pCF as a function of both angular and radial scale to fully probe the scaling effect in 3D galaxy distribution.
-
-There are already works using the shape of angular 2pCF to constrain cosmology
-by directly comparing the theoretical 2pCF to the observed one \citep{Salvador2014,Salvador2016}.
-While our method just utilize the fact the the shape of angular 2pCF is insensitive to redshift in correct cosmology.
-Our method is complementary to these works in the sense that,
-we do not require accurate analytic modeling and should be applicable on smaller scales.
-The two different approaches can be combined together to fully extract the cosmological information.
-
-The method of redshift dependent AP effect has been shown great power to constrain cosmological parameters \cite{Li2014,Li2015,Li2015}.
-We hope this method also.
-The two methods probe different information encoded in the 2pCF and can be combined to fully probe the geometrical effect in LSS.
-Or one can also use the redshift evolution of 2D 2pCF xi(s,mu) to have all information included.
-
-The method is designed to be applied to current and future LSS surveys,
-with a particular emphasis to the photometric surveys which probe a large amount of galaxies and the large redshift error will not quite affect the angular 2pCF measurement.
-An accurate modeling of redshfit error, galaxy bias and RSD effects could be crucial for the successful application of the method.
-DES will probe 300 million galaxies at $z<1.4$, and LSST will probe 20 billion galaxies at $z<2$.
-We hope our method play an active role in  deriving cosmological constraints from LSS surveys.
+We test our method on the HR4 mock galaxies having 457, 406, 352, 206 and 228 million galaxies at redshfits 0, 0.5, 1, 1.5, 2.
+Analyzing the redshift evolution of $\hat \omega_{r_\perp}(r_\perp)$ 
+on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
+we derive tight constraints on $\Omega_m$ and $w$.
+
+In this analysis we restrict our focus to the rescaling in angular direction.
+%The angular correlation function is adopted as a statistical tool to probing the scaling effect in the angular direction.
+One can also use the 2D 2pCF $\xi(s,\mu)$ 
+as a function of both angular and radial scale to fully probe the scaling effect in 3D galaxy distribution.
+
+There are already works using the angular 2pCF to constrain cosmology
+by directly comparing the theoretical 2pCF and the observed one \citep{Salvador2014,Salvador2016}.
+Our method is simpler and just utilizes the fact in the correct cosmology the angular 2pCF shape
+does not exhibit much redshift evolution.
+%is insensitive to redshift in correct cosmology.
+Our method is complementary to these works in that
+it does not require accurate analytic modeling, 
+and could be applicable on smaller scales.
+%The two different approaches can be combined together to fully extract the cosmological information.
+
+\cite{Li2015,Li2016} shows that using the redshift dependent of AP effect 
+one can derive very tight cosmological constraint.
+%We hope this method also.
+These two methods probe different information encoded in the 2pCF 
+and can be combined to have a complete geometric probe of LSS galaxy distribution.
+%Or one can also use the redshift evolution of 2D 2pCF xi(s,mu) to have all information included.
+
+This method is designed to be applied to current and future LSS surveys,
+with a particular emphasis to the {\it photometric surveys},
+such as DES (300 million galaxies at $z\lesssim1.5$) and LSST (20 billion galaxies at $z\lesssim2$) [CHECK THEM!!!].
+These surveys probe a large amount of galaxies 
+and the redshift error will not quite affect the angular 2pCF measurement 
+as long as the redshift dependence of the photometric redshift can be reliably understood.
+
+Our series of works \cite{Li2014,Li2015,Li2016}, together with this analysis, 
+and also \citep{topology,MS2016},
+are introducing a new strategy to constrain cosmology from LSS data.
+We seek for the statistical pattern which maintains nearly constant at all redshifts;
+this invariance is broken if wrong cosmologies are adopted to construct the galaxy distribution
+and introduces redshift evolution of geometric distortion.
+The systematic effects can be corrected by performing a N-body simulation 
+in a cosmology with values of parameters close enough to the underlying correct one.
+This avoids the difficult modeling of galaxy bias, galaxy clustering and RSD,
+enables reliable cosmological constraint on scales much smaller than BAO.
+We hope these methods play an important role in deriving cosmological constraints from future LSS surveys.
 
@@
 %We thank Seokcheon Lee and Graziano Rossi for many helpful discussions.
-We would like to thank Yi Zheng for useful discussions.
+We would like to thank Stephen Appleby and Yi Zheng for kind helps and valuable comments.
 This work was partially supported by the
@@
 
-\bibitem[Ade et al. (2015)]{Planck2015}
-Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. arXiv:1502.01589
+%\bibitem[Ade et al. (2015)]{Planck2015}
+%Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. arXiv:1502.01589
 
@@
 
-\bibitem[{{Alam} {et~al}\mbox{.}(2015{\natexlab{a}}){Alam}, {Albareti},
-  {Allende Prieto}, {Anders}, {Anderson}, {Anderton}, {Andrews}, {Armengaud},
-  {Aubourg}, {Bailey}, \& et~al.}]{dr12}
-{Alam} S., Albareti, F.D.,\& Allende Prieto, C., {et~al.}, 2015,  ApJS, 219, 12
+%\bibitem[{{Alam} {et~al}\mbox{.}(2015{\natexlab{a}}){Alam}, {Albareti},
+%  {Allende Prieto}, {Anders}, {Anderson}, {Anderton}, {Andrews}, {Armengaud},
+%  {Aubourg}, {Bailey}, \& et~al.}]{dr12}
+%{Alam} S., Albareti, F.D.,\& Allende Prieto, C., {et~al.}, 2015,  ApJS, 219, 12
 
@@
 
-\bibitem[Anderson et al.(2013)]{Anderson2013}
-Anderson, L., Aubourg, \'E., \& Bailey, S. et al. 2014, MNRAS, 441, 24
+%\bibitem[Anderson et al.(2013)]{Anderson2013}
+%Anderson, L., Aubourg, \'E., \& Bailey, S. et al. 2014, MNRAS, 441, 24
 
@@
 
-\bibitem[Betoule et al.(2014)]{JLA}
-Betoule, M., Kessler, R., \& Guy, J., et al. 2014, A\&A, 568, 32
-
-\bibitem[Beutler et al.(2011)]{6dFGS}
+%\bibitem[Betoule et al.(2014)]{JLA}
+%Betoule, M., Kessler, R., \& Guy, J., et al. 2014, A\&A, 568, 32
+
+%\bibitem[Beutler et al.(2011)]{6dFGS}
 Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017
@@
 
-\bibitem[Blake et al.(2013)]{WiggleZtopoloy}
-Blake, C., James, J.B., \& Poole, G.B. 2013, MNRAS, 437, 2488
-
-\bibitem[Bolton et al.(2012)]{Bolton2012}
-Bolton, A.S., Schlegel, \& D.J., Aubourg E., et al. 2012, AJ, 144, 144
-
-\bibitem[Boylan-Kolchin et al.(2008)]{B08}
-Boylan-Kolchin, M., Ma, C.-P., \& Quataert, E. 2008, MNRAS, 383, 93
+%\bibitem[Blake et al.(2013)]{WiggleZtopoloy}
+%Blake, C., James, J.B., \& Poole, G.B. 2013, MNRAS, 437, 2488
+
+%\bibitem[Bolton et al.(2012)]{Bolton2012}
+%Bolton, A.S., Schlegel, \& D.J., Aubourg E., et al. 2012, AJ, 144, 144
+
+%\bibitem[Boylan-Kolchin et al.(2008)]{B08}
+%Boylan-Kolchin, M., Ma, C.-P., \& Quataert, E. 2008, MNRAS, 383, 93
 
@@
 %http://arxiv.org/abs/1508.04473
-\bibitem[Dawson et al.(2015)]{eBOSS}
-Dawson, K.S., Kneib, J.P., \& Percival, W.J., et al. 2015, accepted AJ
-
-\bibitem[Dawson et al.(2012)]{Dawson et al. 2012}
-Dawson, K.S., Schlegel, D.J., \& Ahn, C.P., et al. 2012, AJ, 145, 10
-
-\bibitem[Efstathiou (2014)]{E14H0}
-Efstathiou, G. 2014, MNRAS, 440, 1138
+%\bibitem[Dawson et al.(2015)]{eBOSS}
+%Dawson, K.S., Kneib, J.P., \& Percival, W.J., et al. 2015, accepted AJ
+
+%\bibitem[Dawson et al.(2012)]{Dawson et al. 2012}
+%Dawson, K.S., Schlegel, D.J., \& Ahn, C.P., et al. 2012, AJ, 145, 10
+
+%\bibitem[Efstathiou (2014)]{E14H}
+%Efstathiou, G. 2014, MNRAS, 440, 1138
+
 \bibitem[Eisenstein et al. (1998)]{EHT1998}
@@
 
-\bibitem[Eisenstein et al.(2011)]{Eisenstein et al. 2011}
-Eisenstein, D.J.,  Weinberg, D.H., \& Agolet, E., et al. 2011, AJ, 142, 72
-
-\bibitem[Feldman, Kaiser \& Peacock (1994)]{1994ApJ...426...23F} 
-Feldman, H.A., Kaiser, N., \& Peacock, J.A.\ 1994, ApJ, 426, 23
-
-\bibitem[Fukugita et al. (1996)]{Fukugita1996}
-Fukugita, M., Ichikawa, T., \& Gunn, J.E., et al. 1996, AJ, 111, 1748
+%\bibitem[Eisenstein et al.(2011)]{Eisenstein et al. 2011}
+%Eisenstein, D.J.,  Weinberg, D.H., \& Agolet, E., et al. 2011, AJ, 142, 72
+
+%\bibitem[Feldman, Kaiser \& Peacock (1994)]{1994ApJ...426...23F} 
+%Feldman, H.A., Kaiser, N., \& Peacock, J.A.\ 1994, ApJ, 426, 23
+
+%\bibitem[Fukugita et al. (1996)]{Fukugita1996}
+%Fukugita, M., Ichikawa, T., \& Gunn, J.E., et al. 1996, AJ, 111, 1748
 %Publication:	
@@
 
-\bibitem[Gunn et al. (1998)]{Gunn1998}	
-Gunn, J.E., Carr, M., \& Rockosi, C. et al. 1998, AJ, 116, 3040
-
-\bibitem[Gunn et al.(2006)]{Gunn et al. 2006}
-Gunn, J.E., Siegmund, W.A., \& Mannery, E.J., et al. 2006, AJ, 131, 2332
-
-\bibitem[Guzzo et al.(2008)]{Guzzo2008}
-Guzzo, L., Pierleoni, M., \& Meneux, B., et al. 2008, Nature, 451, 541
+%\bibitem[Gunn et al. (1998)]{Gunn1998}	
+%Gunn, J.E., Carr, M., \& Rockosi, C. et al. 1998, AJ, 116, 3040
+
+%\bibitem[Gunn et al.(2006)]{Gunn et al. 2006}
+%Gunn, J.E., Siegmund, W.A., \& Mannery, E.J., et al. 2006, AJ, 131, 2332
+
+%\bibitem[Guzzo et al.(2008)]{Guzzo2008}
+%Guzzo, L., Pierleoni, M., \& Meneux, B., et al. 2008, Nature, 451, 541
 
@@
 
-\bibitem[Kim \& Park(2006)]{kim and park 2006}
-Kim, J., \& Park, C. 2006, ApJ, 639, 600
-
-\bibitem[Kim et al.(2009)]{2009ApJ...701.1547K} 
-Kim, J., Park, C., Gott, J.R., III, \& Dubinski, J.\ 2009, ApJ, 701, 1547
+%\bibitem[Kim \& Park(2006)]{kim and park 2006}
+%Kim, J., \& Park, C. 2006, ApJ, 639, 600
+
+%\bibitem[Kim et al.(2009)]{2009ApJ...701.1547K} 
+%Kim, J., Park, C., Gott, J.R., III, \& Dubinski, J.\ 2009, ApJ, 701, 1547
 
@@
 
-\bibitem[Kitaura et al.(2015)]{MDPATCHY}
-Kitaura, F.S., Rodrı\'{i}guez-Torres, S., Chuang, C.-H., et al. arXiv:1509.06400
+%\bibitem[Kitaura et al.(2015)]{MDPATCHY}
+%Kitaura, F.S., Rodrı\'{i}guez-Torres, S., Chuang, C.-H., et al. arXiv:1509.06400
 
@@
 
-\bibitem[Lacey \& Cole(1993)]{LC93}
-Lacey, C., \& Cole, S. 1993, MNRAS, 262, 627
+%\bibitem[Lacey \& Cole(1993)]{LC93}
+%Lacey, C., \& Cole, S. 1993, MNRAS, 262, 627
 
@@
 %http://arxiv.org/abs/1110.3193
-\bibitem[Laureijs et al.(2011)]{EUCLID}
-Laureijs, R., Amiaux, J., \& Arduini, S., et al. 2011, arXiv:1110.3193
+%\bibitem[Laureijs et al.(2011)]{EUCLID}
+%Laureijs, R., Amiaux, J., \& Arduini, S., et al. 2011, arXiv:1110.3193
 
@@
 
-\bibitem[L'Huillier et al.(2014)]{2014NewA...30...79L} 
-L'Huillier, B., Park, C., \& Kim, J.\ 2014, New Astronomy, 30, 79
+%\bibitem[L'Huillier et al.(2014)]{2014NewA...30...79L} 
+%L'Huillier, B., Park, C., \& Kim, J.\ 2014, New Astronomy, 30, 79
 
@@
 
-\bibitem[McCavana et al.(2012)]{M12}
-McCavana, T., Micic, M., Lewis, G. F., et al. 2012, MNRAS, 424, 361
+%\bibitem[McCavana et al.(2012)]{M12}
+%McCavana, T., Micic, M., Lewis, G. F., et al. 2012, MNRAS, 424, 361
 
@@
 
-%\bibitem[Parejko et al.(2013)]{Parejko2013}
-%Parejko, J. K., Sunayama, T., Padmanabhan, N., et al. 2013, MNRAS, 429, 98
-
 \bibitem[Parejko et al.(2013)]{Parejko2013}
@@
 
-\bibitem[Parihar et al. (2014)]{CMASSLSS2014}
-Parihar, P., Vogeley, M.S., \& Gott, J.R., et al. 2014, ApJ, 796, 86
-
-\bibitem[Park et al.(2005)]{park 2005}
-Park, C., Kim, J., \& Gott, J.R. 2005, ApJ, 633, 1
+%\bibitem[Parihar et al. (2014)]{CMASSLSS2014}
+%Parihar, P., Vogeley, M.S., \& Gott, J.R., et al. 2014, ApJ, 796, 86
+
+%\bibitem[Park et al.(2005)]{park 2005}
+%Park, C., Kim, J., \& Gott, J.R. 2005, ApJ, 633, 1
 
@@
 
-\bibitem[Park et al. (2012)]{Park2012}
-Park, C., Choi, Y.-Y., Kim, J., Gott, J.R., Kim, S.S., \&
-Kim, K.-S. 2012, ApJ, 759, 7
-
-\bibitem[Park et al. (2015)]{Park2015}
-Park, C., Song, H., Einasto, M., Lietzen, H., \&
-Heinamaki, P. 2015, JKAS, 48, 75
-
-\bibitem[Peebles \& Ratra(2003)]{PR2003}
-Peebles, P.J.E., \& Ratra, B. 2003, Reviews of Modern Physics, 75, 559
-
-\bibitem[Percival et al.(2014)]{Percival2014}
-Percival, W.J., Ross, A.J., \& S\'{a}nchez, A.G., et al. 2014, MNRAS, 439, 2531
+%\bibitem[Park et al. (2012)]{Park2012}
+%Park, C., Choi, Y.-Y., Kim, J., Gott, J.R., Kim, S.S., \&
+%Kim, K.-S. 2012, ApJ, 759, 7
+
+%\bibitem[Park et al. (2015)]{Park2015}
+%Park, C., Song, H., Einasto, M., Lietzen, H., \&
+%Heinamaki, P. 2015, JKAS, 48, 75
+
+%\bibitem[Peebles \& Ratra(2003)]{PR2003}
+%Peebles, P.J.E., \& Ratra, B. 2003, Reviews of Modern Physics, 75, 559
+
+%\bibitem[Percival et al.(2014)]{Percival2014}
+%Percival, W.J., Ross, A.J., \& S\'{a}nchez, A.G., et al. 2014, MNRAS, 439, 2531
 
@@
 
-\bibitem[Reid et al.(2016)]{Reidetal:2016}
-Reid, B., Ho, S., \& Padmanabhan, N., et al.  2016, MNRAS, 455, 1553
+%\bibitem[Reid et al.(2016)]{Reidetal:2016}
+%Reid, B., Ho, S., \& Padmanabhan, N., et al.  2016, MNRAS, 455, 1553
 
@@
 
-\bibitem[Riess et al.(2011)]{Riess2011}
-Riess, A.G., Macri, L., \& Casertano, S., et al. 2011, ApJ, 730, 119
+%\bibitem[Riess et al.(2011)]{Riess2011}
+%Riess, A.G., Macri, L., \& Casertano, S., et al. 2011, ApJ, 730, 119
 %A 3\% Solution: Determination of the Hubble Constant with the Hubble Space Telescope and Wide Field Camera
 
-\bibitem[Ross et al.(2012)]{2012MNRAS.424..564R} 
-Ross, A.J., Percival, W.J., \& S{\'a}nchez, A.G. et al.\ 2012, MNRAS, 424, 564
-
-\bibitem[Ross et al.(2015)]{MGS}
-Ross, A.J., Samushia, L., \& Howlett, C., et al. 2015, MNRAS, 449, 835
+%\bibitem[Ross et al.(2012)]{2012MNRAS.424..564R} 
+%Ross, A.J., Percival, W.J., \& S{\'a}nchez, A.G. et al.\ 2012, MNRAS, 424, 564
+
+%\bibitem[Ross et al.(2015)]{MGS}
+%Ross, A.J., Samushia, L., \& Howlett, C., et al. 2015, MNRAS, 449, 835
 
@@
 
-\bibitem[Schlafly et al.(2010)]{Schlafly2010}
-Schlafly E.F., Finkbeiner D.P., Schlegel D.J., et al. 2010, ApJ, 725, 1175
-
-\bibitem[Schlafly \& Finkbeiner(2011)]{SF2011}
-Schlafly E.F., \& Finkbeiner D.P. 2011, ApJ, 737, 103
+%\bibitem[Schlafly et al.(2010)]{Schlafly2010}
+%Schlafly E.F., Finkbeiner D.P., Schlegel D.J., et al. 2010, ApJ, 725, 1175
+
+%\bibitem[Schlafly \& Finkbeiner(2011)]{SF2011}
+%Schlafly E.F., \& Finkbeiner D.P. 2011, ApJ, 737, 103
 
@@
 %http://arxiv.org/abs/1106.1706
-\bibitem[Schlegel et al.(2011)]{DESI}
-Schlegel, D., Abdalla, F., \& Abraham, T., et al. 2011, arXiv:1106.1706
+%\bibitem[Schlegel et al.(2011)]{DESI}
+%Schlegel, D., Abdalla, F., \& Abraham, T., et al. 2011, arXiv:1106.1706
 
@@
 
-\bibitem[Smee et al.(2013)]{Smee2013}
-Smee, S.A., Gunn, J.E., \& Uomoto, A., et al. 2013, AJ, 146, 32
+%\bibitem[Smee et al.(2013)]{Smee2013}
+%Smee, S.A., Gunn, J.E., \& Uomoto, A., et al. 2013, AJ, 146, 32
 
@@
 
-\bibitem[Speare et al. (2015)]{Speare2015}
-Speare, R., Gott, J.R., Kim, J., \& Park, C.
-2015, ApJ, 799, 176
+%\bibitem[Speare et al. (2015)]{Speare2015}
+%Speare, R., Gott, J.R., Kim, J., \& Park, C.
+%2015, ApJ, 799, 176
 
@@
 
-\bibitem[Villalobos et al.(2013)]{V13}
-Villalobos, \'{A}., ́De Lucia, G., Weinmann, S.M., Borgani, S., \& Murante, G. 2013, MNRAS, 433, L49
+%\bibitem[Villalobos et al.(2013)]{V13}
+%Villalobos, \'{A}., ́De Lucia, G., Weinmann, S.M., Borgani, S., \& Murante, G. 2013, MNRAS, 433, L49
 
@@
 
-\bibitem[White (2011)]{White2011}
-White M., et al. 2011, ApJ, 728, 126
-
-\bibitem[York et al.(2000)]{York et al. 2000}
-York, D.G., Adelman, J., \& Anderson, J.E., et al. 2000, AJ, 120, 1579
+%\bibitem[White (2011)]{White2011}
+%White M., et al. 2011, ApJ, 728, 126
+
+%\bibitem[York et al.(2000)]{York et al. 2000}
+%York, D.G., Adelman, J., \& Anderson, J.E., et al. 2000, AJ, 120, 1579
 

### 2016-10-06 draft/draft0_cris.tex
updates

--- 2016-10-06 draft/draft0.tex
@@
 \documentclass[iop]{emulateapj}
+\usepackage{color}
 \renewcommand{\baselinestretch}{0.95}
@@
 \def\ea{\end{eqnarray}}
+
+\newcommand{\scr}{\textcolor{red}}
 
@@
 
-%The  Alcock-Paczynski (AP) effect referes to
-%the geometric distortion when incorrect cosmological models are assumed for 
-%transforming redshift to comoving distance,
-%induced by the fact that measured distances along and perpendicular to the line of sight are fundamentally different.
-
-%The AP effect can be measured through the staistial study of galaxies clustering  \citep{Ballinger1996,Matsubara1996,
-%Outram2004,Blake2011,ChuangWang2012,Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, Jeong2014,Sutter2014,2014ApJ...781...96L,Alam2016, Beutler2016, Sanchez2016},
-%symmetry properties of galaxy pairs \citep{Marinoni2010,Jennings2011,BB2012},
-%and cosmic voids \citep{Ryden1995,LavausWandelt1995,Sutter2014,Qingqing2016}.
-%The main caveat of these methods is that,
-%because the radial distances of galaxies are inferred from redshifts,
-%AP tests are inevitably limited by redshift-space distortions (RSD) \citep{Ballinger1996},
-%which leads to apparent anisotropy even if the adopted cosmology is correct.
-
-%\cite{Li2014,Li2015,Li2016} proposed a novel strategy to measure the redshift dependence of AP.
-%Anisotropies produced by the RSD effect are, although large,
-%maintaining a nearly uniform magnitude over a large range of redshift,
-%while the degree of anisotropies from the AP effect varies with redshift by much larger magnitude. 
-%\citep{Li2016} applies this method to the SDSS-III BOSS DR12 galaxies, and obtained tight cosmological constraints 
-%comparable to the mainstream probes of SNIa, BAO or CMB.
-%This method could play an important role in deriving cosmological constraints from future LSS surveys.
-
 In \cite{Li2014,Li2015,Li2016} we developed a novel strategy to probe $D_A$ and $H$ from LSS data.
 %proposed a series of methods to probe the geometric information encoded in the LSS data.
-We found fact that the AP or volume effect in general introduces a geometric distortion significantly evolves with redshift;
-this phenomenon can be utilized to distinguish the the from the other effects such as the redshift space distortion (RSD).
-The radial distances of galaxies are inferred from the measured redshifts which are distorted by the peculiar motion of galaxies, 
+We found fact that the AP or volume effect in general introduces a geometric distortion that evolves significantly with redshift;
+this phenomenon can be utilized to distinguish the \scr{AP effect(?)} the from the other effects such as the redshift space distortion (RSD).
+The radial distances of galaxies are inferred from the measured redshifts, which are distorted by the peculiar motion of galaxies, 
 leading to apparent distortion in the redshift space galaxy distribution \citep{FOG,Kaiser1987,Ballinger1996}.
@@
 to characterize the redshift evolution of the LSS distortion. 
-We tested the idea on Horizon Run 3 (HR3) N-body simulations \citep{horizonrun},
+We tested the idea on the Horizon Run 3 (HR3) N-body simulations \citep{horizonrun},
 showing the redshift evolution of the statistical property of the gradient field 
-can be used to infer unbiased constraints cosmological parameters and is insensitive to RSD.
+can be used to infer unbiased constraints on certain cosmological parameters and that it is, largely, insensitive to RSD.
 The same topic was revisited in \cite{Li2015}, 
-using the statistical tool of {\it galaxy two-point correlation function} (2pCF) as a function of angle, $\xi(\mu)$, 
+using a slightly modified version of the usual anisotropic galaxy two-point correlation function (2pCF), $\xi(\mu)$, 
 where $\mu\equiv \cos \theta$ and $\theta$ is the direction between the connection of the galaxy pairs and the direction.
-When incorrect cosmological parameters are adopted, 
-the shape of $\xi(\mu)$ is altered due to the anisotropic shape of the LSS (the AP effect), 
-and the amplitude is shifted due to the change in the size of comoving volume;
+When an incorrect cosmological model is adopted, 
+the shape of $\xi(\mu)$ is altered due to the anisotropic distortion of the LSS (the AP effect), 
+and the amplitude is shifted due to the change in the comoving volume elements;
 both effects have significant redshift dependence.
-The RSD effect, although {\it very significantly} distorts $\xi(\mu)$, 
-exhibits less redshift evolution.
+The RSD effect, significantly distorts $\xi(\mu)$, however it
+exhibits much less redshift evolution.
 The method was applied to BOSS DR12 galaxies \citep{Li2016} to probe the redshift dependent of the AP effect, 
@@
 In this paper we continue our exploration of our strategy and presented 
-a new method using the redshift of the shape of {\it galaxy angular 2pCF} as a function of radial scale, $\omega(r_{\bot})$,
+a new method using the redshift of the shape of the {\it galaxy angular 2pCF} as a function of radial scale, $\omega(r_{\bot})$,
 to constrain cosmology.
@@
    \caption{\label{fig_xyquan}
-   A description of how wrongly assumed cosmologies can distort the interpretation of observation,
+   A description of how incorrectly assumed cosmologies can distort the interpretation of observation,
    assuming $\Omega_m=0.26,w=-1$ is the true cosmology. 
@@
 The most bound member particles (MBPs) of simulated halos are adopted as tracers of galaxies.
-The merger timescale is computed to get the lifetime of merged halos.
+The merger timescale is computed to obtain the lifetime of merged halos.
 Merger trees of halos are constructed by tracking their MBPs from $z = 12$ to 0;
-when a merger event occurs, the merger timescale is computed using the formular of \cite{jiang2008} to 
+when a merger event occurs, the merger timescale is computed using the formula of \cite{jiang2008} to 
 determine when the satellite galaxy is completely disrupted.
@@
 
-The resulting mock galaxies was found to reproduce the 2pCF of SDSS DR7 volume-limited galaxy sample \citep{zehavi2011} very well.
+The resulting mock galaxies were found to reproduce the 2pCF of the SDSS DR7 volume-limited galaxy sample \citep{zehavi2011} very well.
 The mock galaxies shows a similar finger of god (FOG) feature \citep{FOG} as the observation.
@@
 respectively.
-By applying a uniform mass cut, at higher redshift we have smaller number of galaxies with {\it larger bias}.
+Applying a uniform mass cut, at higher redshift we obtained a smaller number of galaxies with {\it larger bias}.
 
@@
 
-When the correct cosmology is adopted the cosmic scale is correctly estimated,
+\scr{When the correct cosmology is adopted the cosmic scale is correctly estimated,
 the main factor leads to redshift evolution of galaxy distribution is the gravitational growth of structure.
 With the decreasing the redshift, we clearly see the clusters and filaments form and grow.
-On the other hand, when the wrong cosmology is adopted, there is an artifical scaling of scales in the constructed map.
+On the other hand, when the wrong cosmology is adopted, there is an artificial scaling of scales in the constructed map.
 The separations among galaxies are over-estimated by 
 $25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$,
-leading to a clear redshift evolution of sizes of structures.
-
-The growth of structure strengths the clustering and make structures more compact,
-while the volume effect maintain the clustering pattern and uniformly re-scale the structures on all scales.
-Their imprints on the large scale structure is different and should be distinguishable.
-In the following, we show that they affect the angular correlation function measurements in different ways, 
-and can be easily separated.
+leading to a clear redshift evolution of sizes of structures.}
+
+The growth of structure enhances the clustering and results in more compact structures,
+while the volume effect maintains the clustering pattern and uniformly re-scales the structures on all scales.
+The imprint of each of these effects on the large scale structure is different and should be distinguishable.
+In the following section we show that they affect the angular correlation function measurements in different ways, 
+and thus can be easily separated.
 
@@
   at redshifts 0.5, 1, 1.5 and 2.
-  Left and right panels whos the $x$, $y$ coordinates computed using the ``correct'' parameters $\Omega_m=0.26,\ w=-1$ 
+  Left and right panels show the $x$, $y$ coordinates computed using the ``correct'' parameters $\Omega_m=0.26,\ w=-1$ 
   and a set of wrong cosmological parameters $\Omega_m=0.05,\ w=-1.5$, respectively.
   The growth of structure strengths the clustering and make structures more compact at lower redshift.
-  When the wrong cosmology is adopted, the covmoving distances is mis-scaled and over-estimated by $25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$,
-  leading to a clear redshift evolution of sizes of structures.
+  When the wrong cosmology is adopted, the covmoving distances are mis-scaled and over-estimated by $25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$, respectively,  leading to a clear redshift evolution of the sizes of structures.
    }
@@
 all separated by a distance defined by $r_\perp\pm\Delta_{r_\perp}$ where we choose $\Delta_{r_\perp}=1h^{-1}\rm Mpc$.
-The random catalogue consists of unclustered points uniformly distributed in a same size box. 
+The random catalogue consists of unclustered points uniformly distributed in the same space as the simulated data.. 
 In an effort to reduce the statistical variance of the estimator, we use 50 times as many random points as we have galaxies.
@@
 size of 1575 $h^{-1}{\rm Mpc}\times 1575\ h^{-1}{\rm Mpc}\times 105\ h^{-1}{\rm Mpc}$.
-The sheet shape of the subsample is close to the shape of redshift shells in the real observational case.
+The `sheet'-like shape of the subsample is similar to the shape of redshift shells in the real observational case.
 The Z direction with thickness $105\ h^{-1}\rm Mpc$ is treated as the radial direction (the $r$ direction) 
@@
 For our simulation box size we have 120 such subsamples.
-The average of the measurements in all subsamples is adopted as the 2pCF of the whole sample,
-while the covariances of them are adopted as the covariance matrix (after multiplying a factor of $1/\sqrt{119}$).
+The average of the measurements in all subsamples is taken as the 2pCF of the whole sample,
+while the covariances of them are taken to be the covariance matrix (after multiplying a factor of $1/\sqrt{119}$).
 
@@
 Among different redshifts there is large variation in the amplitude of $\omega(r_\perp)$.
-The amplitude is proportional to the clustering strengh which is affected by the gravitational growth of structures and the galaxy bias.
+The amplitude is proportional to the clustering strength, which is affected by the gravitational growth of structures and the galaxy bias.
 The amplitude is highest at $z=0$ where the structures experienced most growth.
@@
 
-Different from the large variation of amplitude among different redshifts, 
+Apart from the large variation in amplitude between the different redshifts bins, 
 %The shape of $r_\perp\omega$ also evolves with redshift.
-the shape of $r_\perp\omega$ maintains similar at all redshifts;
+the shape of $r_\perp\omega$  is similar at all redshifts;
 in general it peaks at $r\sim9 h^{-1}\rm Mpc$ and monotonically drops or increases at larger or smaller scales.
@@
 which is caused by the non-linear growth of structures 
-and is much more significant at lower redshfit.
+and is much more significant at lower redshift.
 
@@
 instead of using our method 
-(although out method should is also applicable).
-
-In the upper-middle panel, the nice overlapping of the $\hat\omega_{r_\perp}$
-more clearly shows the the small redshift evolution of the shape.
+(although our method should also be applicable).
+
+In the upper-middle panel, the overlapping $\hat\omega$'s
+clearly show the minimal redshift evolution of the shape.
 In the upper-right panel, 
@@
 
-There is one detail in the analysis which should be emphasized here.
-In real observations we are observing {\it different} objects in different redshift shells.
+There is one detail in the analysis that should be emphasized here.
+In real observations we may be selecting {\it different} types of galaxies at different redshifts.
 Considering this fact in the comparison of $\hat\omega_{r_\perp}$ 
 we compare subsamples of galaxies at {\it different} locations.
-As an exammple, if at $z=0$ we take $\hat\omega_{r_\perp}$ measured within $0h^{-1}{\rm Mpc}<Z<105 h^{-1}{\rm Mpc}$,
-at higher redshifts we then adopt measurement within $105h^{-1}{\rm Mpc}<Z<210 h^{-1}{\rm Mpc}$ for a comparision.
+As an example, if at $z=0$ we take $\hat\omega_{r_\perp}$ measured within $0h^{-1}{\rm Mpc}<Z<105 h^{-1}{\rm Mpc}$,
+at higher redshifts we then adopt measurement within $105h^{-1}{\rm Mpc}<Z<210 h^{-1}{\rm Mpc}$ for a comparison.
 %and take the difference between them to get $\delta \hat{r_\perp\omega}$.
 %So we are always comparing 2pCF measured from different samples of galaxies.
-If simply comparing the 2pCF of a {\it same} subsample of galaxies at different redshifts, 
-one would significantly underestimate the statistical undertainty of $\delta \hat{\omega}_{r_\perp}$ by ignoring the cosmic variance.
+If we simply compare the 2pCF of the {\it same} subsample of galaxies at different redshifts, 
+one would significantly underestimate the statistical uncertainty of $\delta \hat{\omega}_{r_\perp}$ by ignoring the cosmic variance.
 %The error bars and covariance are always estimated in this way to take the cosmic variance into consideration.
@@
 
-The angular 2pCF of galaxy positions constructed in a wrong cosmology $\Omega_m=0.05,\ w=-1.5$
+The angular 2pCF of galaxy positions constructed in a wrongly assumed cosmology $\Omega_m=0.05,\ w=-1.5$
 is displayed in the lower panels of Figure \ref{fig_diffz}.
-The mis-scaling uniformly shifts clustering patterns on all scales, 
-leading to a wrong $\hat \omega_{r_\perp}$ 
-related with the correct one as
+The mis-scaling uniformly shifts the clustering pattern on all scales, 
+leading to a biased $\hat \omega_{r_\perp}$, which is 
+related with the true $\hat \omega$ as
 \begin{equation}
@@
 \end{equation}
-a simple consequence of the fact that clustering patterns at scale $r$ is rescaled to $\alpha_{\perp} r$.
+a simple consequence of the fact that the clustering pattern at scale $r$ is rescaled to $\alpha_{\perp} r$.
 The redshift evolution of $\alpha_{\perp}$ leads to redshift evolution of 
@@
 The upscaling of comoving distance leads to a stretched shape.
-With the increasing of redshift,
-the peak location is shifted from $9h^{-1} \rm Mpc$ to $15 h^{-1}\rm Mpc$ at $z=2$,
+When increasing redshift,
+the peak location is shifted from $\sim9h^{-1} \rm Mpc$ to $\sim15 h^{-1}\rm Mpc$ at $z=2$,
 as a result of the fact that the angular separation is upscaled by $71.7\%$.
@@
 
-Sec. \ref{sec_2pCF_diffz} shows that $\hat \omega_{r_\perp}$ measured from 
-constant mass cut samples at different redshifts is close to each other.
-The gravitational growth of structure will not have large impact on $\hat \omega_{r_\perp}$ on scales $\gtrsim5 h^{-1}$ Mpc.
-Yet there are many other factors may introduce redshift evolution,
+In Sec. \ref{sec_2pCF_diffz} we showed that $\hat \omega_{r_\perp}$ measured from the
+constant mass cut samples at different redshifts are relatively close to each other.
+The gravitational growth of structure will not have a large impact on $\hat \omega_{r_\perp}$ on scales $\gtrsim5 h^{-1}$ Mpc.
+Yet there are many other factors that may induce redshift evolution,
 including galaxy bias, RSD, redshift error, and 
-the redshift evolution of properties of galaxies 
-such as the mass, morphology, color, concentration, and so on. 
-Here we test two ``major'' systematical effects, the galaxy bias and the RSD effect.
+the redshift evolution of galaxies properties 
+such as mass, morphology, color, concentration, and so on. 
+Here we test two ``major'' systematical effects; the galaxy bias and the RSD effect.
 
@@
 
-Galaxies are biased tracers of dark matter field;
+Galaxies are biased tracers of the dark matter field;
 more massive galaxies reside in regions with higher density contrast
@@
 Four values of minimal mass limits, $3\times 10^{11} M_{\odot}$, $1\times 10^{12} M_{\odot}$, $4\times 10^{12} M_{\odot}$ and $1\times 10^{13} M_{\odot}$,
-are imposed to create three samples with different galaxy bias.
+are imposed to create three \scr{four?} samples with different galaxy bias.
 The measured angular 2pCF are displayed.
@@
 The different mass cuts result in large variation in the amplitude of the 2pCF (left panel),
-while the shape of the 2pCF remains less affected (middle panel).
+while the shape of the \scr{normalised} 2pCF remains less affected (middle panel).
 Compared with the sample of $M>3\times 10^{11} M_{\odot}$,
 samples with mass limits of $1\times 10^{12} M_{\odot}$, $4\times 10^{12} M_{\odot}$ and $1\times 10^{13} M_{\odot}$
-have amplitude of 2pCFs enhanced by $10\%,\ 50\%$ and $100\%$,
+have amplitude of 2pCFs enhanced by $10\%,\ 50\%$ and $100\%$, respectively, 
 while the change in the shape is only $0.5\%,\ 2\%$ and $4\%$.
@@
 
-The galaxy peculiar velocity contributes to the observed redshift and distorts 
-the inferred galaxy radial position,
-known as the redshift space distortion.
+The galaxy peculiar velocity contaminates the observed redshift and distorts 
+the inferred galaxy radial position.
 It is the major systematics in our previous works \citep{Li2014,Li2015,Li2016}
@@
 RSD distorts the galaxy redshift and as a result some galaxies 
-(especially those close to the boundaries of shells) are classified to wrong redshift shells.
-
-The lower panel of Figure \ref{fig_sys} displays the RSD effect on 2pCF.
+(especially those close to the boundaries of shells) are assigned to the wrong redshift shells.
+
 We shift the radial coordinates of galaxies according to the relation 
@@
 is the galaxy peculiar velocity in the LOS direction.
-This lead to mis-classification of some galaxies when we split the box into slices.
+This lead to misclassification of some galaxies when we split the box into slices.
 %Then we split the whole box into 30 slices with thickness $105h^{-1}\rm Mpc$, 
@@
 
-Comparing the plot with Figure \ref{fig_diffz} one clearly see the effect of RSD.
-The amplitude of measured 2pCF is enhanced by $\sim 10\%$ in case of considering the RSD effect.
-The slop of $\hat\omega_{r_\perp}$ slightly suppressed.
+The lower panel of Figure \ref{fig_sys} shows the RSD effect on the 2pCF.
+Comparing this plot with Figure \ref{fig_diffz} one can clearly see the effect of RSD.
+The amplitude of the measured 2pCF is enhanced by $\sim 10\%$ when considering the RSD effect 
+and the slop of $\hat\omega_{r_\perp}$ is slightly suppressed.
 While the redshift evolution of $\hat\omega_{r_\perp}$ is still small...
@@
 Similar to RSD, redshift errors of galaxies
-also results in fuzzy boundaries of shells and mis-classification of galaxies.
+also results in fuzzy boundaries of shells and misclassification of galaxies.
 This effect should also be properly quantified in real observations.
@@
 
-A cosmology resulting in smaller evolution is considered to be more likely to be the correct one.
+Adopting the correct cosmological model will resulting in minimal evolution of the normalised 2pCF.
+Thus we proceed to construct a quantitative likelihood estimator.
 The procedure here is very similar to what we did in \cite{Li2014,Li2015,Li2016}.
@@
 
-%\bibitem[Bueno Belloso et al. (2012)]{BB2012}
-%Bueno Belloso, A., Pettinari, G.W., Meures, N., \& Percival, W.J. 2012, Phys. Rev. D, 86, 023530
+\bibitem[Bueno Belloso et al. (2012)]{BB2012}
+Bueno Belloso, A., Pettinari, G.W., Meures, N., \& Percival, W.J. 2012, Phys. Rev. D, 86, 023530
 

### 2016-10-06 draft/draft1.tex
updates

--- 2016-10-06 draft/draft0_cris.tex
@@
 \begin{abstract}
-We use the redshift dependence of the galaxy angular 2-point correlation function (2pCF) shape 
-to constrain cosmological parameters.
-A wrongly adopted cosmology introduces redshift-dependent mis-scaling 
-of the constructed galaxy distribution,
-leading to redshift-dependent rescaling in the measured angular 2pCF.
+We propose to use the redshift dependence of the galaxy angular 2-point correlation function (2pCF)
+for a purpose of cosmological constraints.
+When an incorrect cosmological model is assumed for the coordinate transformation from redshift space to comoving space, 
+it produces {\it redshift-dependent mis-scaling} in the constructed galaxy distribution.
+As a result, we find a redshift-dependent rescaling in the measured galaxy angular 2pCF .
 We test our method on the HR4 mock galaxies having hundreds of millions of galaxies at redshifts 
-0, 0.5, 1, 1.5, 2.
+$0\leq z\leq2$.
 We find the redshift evolution of shape of angular 2pCF, as a function of scale,
-is sensitive to the adopted cosmological parameters. 
-It is relatively insensitive to the gravitational growth of structure,
+is sensitive to the adopted cosmological parameters,
+and is relatively insensitive to the gravitational growth of structure,
 the galaxy bias, and the redshift space distortion.
 Analyzing the 2pCF shape on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
-we derive tight constraints on $\Omega_m$ and $w$.
+we derive tight constraints on $\Omega_m$ and $w$ with 68.3\% CL uncertainties of 0.015 and 0.05.
 %Our method is complementary to current works using 2pCF to constrain cosmological parameters.
-The method could be applicable to future photometric surveys like DES, LSST 
+The method could be applicable to future large scale structure surveys, especially the photometric surveys such as DES, LSST, 
 to derive tight cosmological constraints.
-The work is a continue of our previous works \citep{Li2014,Li2015,Li2016}
-as a strategy to constrain cosmological parameters based on some nearly redshift-invariant physical quantity;
-they are all powerful in constrain cosmology and have a lot of merits,
+This work is a continuation of our previous works \citep{Li2014,Li2015,Li2016}
+as a strategy to constraining cosmological parameters based on some nearly redshift-invariant physical quantity;
+they are all powerful in constraining cosmology and have a lot of merit,
 e.g., are less affected by the systematic effects introduced by non-linear clustering or RSD,
-does not require accurate modeling of galaxy clustering,
-and are applicable on relative small clustering scales.
+do not require accurate analytical modeling of the galaxy correlation function,
+and are applicable on relatively small clustering scales.
 \end{abstract}
@@
 
-As one geometrical effect of cosmological parameters on LSS,  
-when an incorrect cosmological model is assumed for the coordinate transformation from redshift space to comoving space,
+%As one geometrical effect of cosmological parameters on LSS,  
+When an incorrect cosmological model is assumed for the coordinate transformation from redshift space to comoving space,
 geometric distortions are produced in the constructed galaxy distribution. 
-These distortion include the ``volume effect'' which is the mis-scaling of the size of structures,
+These distortions include the ``volume effect'' which is the mis-scaling of the size of structures,
 and the Alcock-Paczynski (AP) effect, the shape distortion induced by the fact that distances along and perpendicular to the line of sight are fundamentally different.
@@
 
-Various statistically methods has been proposed to measure these effects.
-The AP effect has been proposed to measure through the clustering of galaxies \citep{Ballinger1996,Matsubara1996} which has been applied to a series of LSS surveys
+Various statistical methods have been proposed to measure these effects.
+The AP effect can be measured through statistical study of the clustering of galaxies \citep{Ballinger1996,Matsubara1996}.
+This method has been applied to a series of LSS surveys
 \citep{Outram2004,Blake2011,ChuangWang2012,Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, Jeong2014,Sutter2014,2014ApJ...781...96L,Alam2016, Beutler2016, Sanchez2016},
-the alternative approaches using the symmetry properties of galaxy pairs \citep{Marinoni2010,Jennings2011,BB2012}
+Alternative approaches uses the symmetry properties of galaxy pairs \citep{Marinoni2010,Jennings2011,BB2012}
 and cosmic voids \citep{Ryden1995,LavausWandelt1995,Sutter2014,Qingqing2016}.
-Methods proposed able to probe the volume effect include the number counting of 
+Methods proposed that are able to probe the volume effect include the number counting of 
 galaxy clusters \citep{PS1974,VL1996} and topology \citep{topology},
@@
 %proposed a series of methods to probe the geometric information encoded in the LSS data.
-We found fact that the AP or volume effect in general introduces a geometric distortion that evolves significantly with redshift;
-this phenomenon can be utilized to distinguish the \scr{AP effect(?)} the from the other effects such as the redshift space distortion (RSD).
+We found that the AP or volume effect in general introduces a geometric distortion that evolves significantly with redshift;
+this phenomenon can be utilized to distinguish the AP effect from the other effects, such as the redshift space distortion (RSD).
 The radial distances of galaxies are inferred from the measured redshifts, which are distorted by the peculiar motion of galaxies, 
 leading to apparent distortion in the redshift space galaxy distribution \citep{FOG,Kaiser1987,Ballinger1996}.
-It is the major systematic effects limiting our ability to probe the geometry of LSS from galaxy distribution.
-We found its influence is significantly reduced in case of studying the redshift dependence of the distortion.
+This is the major systematic effect limiting our ability to probe the geometry of LSS from galaxy distribution.
+We found its influence is significantly reduced when studying the redshift dependence of the distortion.
 
@@
 to characterize the redshift evolution of the LSS distortion. 
-We tested the idea on the Horizon Run 3 (HR3) N-body simulations \citep{horizonrun},
-showing the redshift evolution of the statistical property of the gradient field 
-can be used to infer unbiased constraints on certain cosmological parameters and that it is, largely, insensitive to RSD.
+We tested the idea on the Horizon Run 3 (HR3) N-body simulation \citep{horizonrun},
+showing that the redshift evolution of the gradient field 
+can be used to infer unbiased constraints on cosmological parameters and that it is, largely, insensitive to RSD.
 The same topic was revisited in \cite{Li2015}, 
 using a slightly modified version of the usual anisotropic galaxy two-point correlation function (2pCF), $\xi(\mu)$, 
-where $\mu\equiv \cos \theta$ and $\theta$ is the direction between the connection of the galaxy pairs and the direction.
+where $\mu\equiv \cos \theta$ and $\theta$ is the direction between the connection of the galaxy pairs and the line of sight.
 When an incorrect cosmological model is adopted, 
@@
 both effects have significant redshift dependence.
-The RSD effect, significantly distorts $\xi(\mu)$, however it
-exhibits much less redshift evolution.
-The method was applied to BOSS DR12 galaxies \citep{Li2016} to probe the redshift dependent of the AP effect, 
-and we come up with tight cosmological constraints comparable to the mainstream probes of SNIa, BAO, CMB and so on.
-
-In this paper we continue our exploration of our strategy and presented 
+Although the RSD effect significantly distorts $\xi(\mu)$, 
+it exhibits much less redshift evolution.
+The method was applied to BOSS DR12 galaxies \citep{Li2016} to probe the redshift dependence of the AP effect, 
+and we arrive at tight cosmological constraints comparable to mainstream probes of SNIa, BAO, CMB.
+
+In this paper we continue our exploration of this strategy and presented 
 a new method using the redshift of the shape of the {\it galaxy angular 2pCF} as a function of radial scale, $\omega(r_{\bot})$,
@@
 the galaxy bias, and the RSD effect.
-We apply our method to the HR4 mock galaxies having hundreds of million galaxies at redshfits 0-2
+We apply our method to HR4 mock galaxies, using hundreds of millions of galaxies at redshfits $0\leq z\leq2$
 and develop the statistical procedure to constrain cosmological parameters.
@@
 %Its observed redshift span $\Delta z$ and angular size $\Delta \theta$ are related with the comoving sizes by
-In this section we briefly introduce the scaling effect caused by wrongly assumed cosmological parameters.
+In this section we briefly introduce the scaling effect caused by incorrectly assumed cosmological parameters.
 A more detailed description has been provided in \cite{Li2014,Li2015,Li2016}.
@@
 Suppose that we are probing the size of some objects in the Universe.
-We measure its redshift span $\Delta z$ and angular size $\Delta \theta$,
-then compute its sizes in the radial and transverse directions using the following formulas
+We measure their redshift span $\Delta z$ and angular size $\Delta \theta$,
+then compute their sizes in the radial and transverse directions using the following formulas
 \begin{equation}\label{eq:distance}
@@
 where $H$ is the Hubble parameter and $D_A$ is the angular diameter distance.
-In the particular case of a flat universe composed by a cold dark matter component and a constant EoS dark energy component, they take the forms of
+In the particular case of a flat universe composed of a cold dark matter component and a constant EoS dark energy, they take the forms
 \begin{eqnarray}\label{eq:HDA}
@@
 
-In case wrong values of $\Omega_m$ and $w$ are adopted, 
-the inferred $\Delta r_{\parallel}$ and $\Delta r_{\perp}$ are wrong,
+When incorrect values of $\Omega_m$ and $w$ are adopted, 
+the inferred $\Delta r_{\parallel}$ and $\Delta r_{\perp}$ are also wrong,
 resulting in wrong estimations of the object's shape (AP effect) and size (volume effect).
@@
 \end{equation}
-where ``true'' and ``wrong'' denote the values in the true cosmology and wrongly assumed cosmologies, respectively.
+where ``true'' and ``wrong'' denote the values in the true cosmology and wrongly assumed cosmologies respectively.
 
@@
 \end{eqnarray}
-as a result, 
-the shapes of the squares appear distorted (AP effect),
+then the shapes of the squares appear distorted (AP effect),
 and their sizes are wrongly estimated (volume effect).
@@
 is displayed in the right panel of Figure \ref{fig_xyquan}.
-In all cosmologies, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$ evolves a lot in the redshift range $0<z<2$.
+In all cosmologies, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$ evolves significantly in the redshift range $0\leq z\leq 2$.
 As an example, when adopting the quintessence cosmology $\Omega_m=0.26,\ w=-0.5$,
@@
 
-In sum, as a consequence of incorrect cosmologies, 
-the size of objects is mis-estimated, and the magnitude of mis-estimation depends on the redshift.
+In sum, as a consequence of incorrect cosmologies 
+the size of objects is mis-estimated and the magnitude of mis-estimation depends on the redshift.
 We use the galaxy angular 2pCF to probe the mis-estimation of angular size, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$.
@@
 %$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
-1.46, 1.30, 1.13, 0.98 and 0.73 in unit of $ 10^{-2} h^{3} \rm Mpc^{-3}$,
+1.46, 1.30, 1.13, 0.98 and 0.73 in units of $ 10^{-2} h^{3} \rm Mpc^{-3}$
 %$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
@@
 the main factor leads to redshift evolution of galaxy distribution is the gravitational growth of structure.
-With the decreasing the redshift, we clearly see the clusters and filaments form and grow.
-On the other hand, when the wrong cosmology is adopted, there is an artificial scaling of scales in the constructed map.
+With decreasing redshift, we clearly see the clusters and filaments form and grow.
+On the other hand, when the wrong cosmology is adopted, there is an artificial scaling of distances in the constructed map.
 The separations among galaxies are over-estimated by 
@@
 
-The growth of structure enhances the clustering and results in more compact structures,
-while the volume effect maintains the clustering pattern and uniformly re-scales the structures on all scales.
+The growth of structure increases the clustering and results in more compact structures,
+while the volume effect maintains the clustering pattern and uniformly re-scales structures on all scales.
 The imprint of each of these effects on the large scale structure is different and should be distinguishable.
@@
 The average of the measurements in all subsamples is taken as the 2pCF of the whole sample,
-while the covariances of them are taken to be the covariance matrix (after multiplying a factor of $1/\sqrt{119}$).
+while the covariances of them are taken to be the covariance matrix (after multiplying by a factor of $1/\sqrt{119}$).
 
@@
 The amplitude is proportional to the clustering strength, which is affected by the gravitational growth of structures and the galaxy bias.
-The amplitude is highest at $z=0$ where the structures experienced most growth.
+The amplitude is highest at $z=0$ where the structures experienced the most growth.
 $\omega(r_\perp)$ also increases with redshift at $z>1$ with increasing redshift 
@@
 
-Apart from the large variation in amplitude between the different redshifts bins, 
+Although there is large variation in amplitude between the different redshifts bins, 
 %The shape of $r_\perp\omega$ also evolves with redshift.
-the shape of $r_\perp\omega$  is similar at all redshifts;
+the shape of $r_\perp\omega$  remains similar at all redshifts;
 in general it peaks at $r\sim9 h^{-1}\rm Mpc$ and monotonically drops or increases at larger or smaller scales.
@@
 
-In order to directly compare the shape of 2pCF at different redshifts,
+In order to directly compare the shape of the 2pCF at different redshifts,
 in the middle panel of Figure \ref{fig_diffz} 
@@
 
-In the upper-middle panel, the overlapping $\hat\omega$'s
+In the upper-middle panel, the overlapping of $\hat\omega$
 clearly show the minimal redshift evolution of the shape.
@@
 If we simply compare the 2pCF of the {\it same} subsample of galaxies at different redshifts, 
-one would significantly underestimate the statistical uncertainty of $\delta \hat{\omega}_{r_\perp}$ by ignoring the cosmic variance.
+one would significantly underestimate the statistical uncertainty of $\delta \hat{\omega}_{r_\perp}$ by ignoring cosmic variance.
 %The error bars and covariance are always estimated in this way to take the cosmic variance into consideration.
@@
 As is shown in the left panel, due to the stretch of scale the amplitude is enhanced at higher redshifts;
-the higher the redshift, the more the enhancement.%the amplitude monotonically increases as a function of redshift.
+the higher the redshift, the greater the enhancement.%the amplitude monotonically increases as a function of redshift.
 
@@
 In Sec. \ref{sec_2pCF_diffz} we showed that $\hat \omega_{r_\perp}$ measured from the
-constant mass cut samples at different redshifts are relatively close to each other.
-The gravitational growth of structure will not have a large impact on $\hat \omega_{r_\perp}$ on scales $\gtrsim5 h^{-1}$ Mpc.
-Yet there are many other factors that may induce redshift evolution,
+constant mass cut samples at different redshifts show good agreement.
+The gravitational growth of structure will not have a large impact on $\hat \omega_{r_\perp}$ on scales $\gtrsim5 h^{-1}$ Mpc,
+yet there are many other factors that may induce redshift evolution
 including galaxy bias, RSD, redshift error, and 
 the redshift evolution of galaxies properties 
-such as mass, morphology, color, concentration, and so on. 
-Here we test two ``major'' systematical effects; the galaxy bias and the RSD effect.
+such as mass, morphology, color, concentration. 
+Here we test two ``major'' systematical effects; galaxy bias and the RSD effect.
 
@@
 
-The different mass cuts result in large variation in the amplitude of the 2pCF (left panel),
+Different mass cuts result in large variation in the amplitude of the 2pCF (left panel),
 while the shape of the \scr{normalised} 2pCF remains less affected (middle panel).
@@
 the inferred galaxy radial position.
-It is the major systematics in our previous works \citep{Li2014,Li2015,Li2016}
+It is the major systematic in our previous works \citep{Li2014,Li2015,Li2016}
 of statistical analysis on the 3D galaxy distribution.
@@
 The amplitude of the measured 2pCF is enhanced by $\sim 10\%$ when considering the RSD effect 
-and the slop of $\hat\omega_{r_\perp}$ is slightly suppressed.
-While the redshift evolution of $\hat\omega_{r_\perp}$ is still small...
-Although the pattern is a little modified...
-So RSD is not a big issue here... {\bf after anna jobs finished we have better plots and re-revise this section }
+and the slop of $\hat\omega_{r_\perp}$ is suppressed.
+The redshift evolution of $\hat\omega_{r_\perp}$ is still small, remain $\lesssim4\%$ at $0.5\leq z \leq 2$.
+So RSD should not very affect the application of our method as long as it is precisely modeled and corrected.
 %If looking at the redshift evolution,
@@
 Thus we proceed to construct a quantitative likelihood estimator.
-The procedure here is very similar to what we did in \cite{Li2014,Li2015,Li2016}.
+The procedure here is very similar to \cite{Li2014,Li2015,Li2016}.
 We compare the high redshift $\hat\omega_{r_\perp}$ and the lowest redshift measurement,
@@
 %The covariance matrix is also estimated from the redshift evolution of these subsamples.
-As mentioned before, for a robust estimation of covariance matrix, 
+As mentioned previously, for a robust estimation of the covariance matrix, 
 we always compare slices at different locations to 
@@
 For this analysis the rescaling is as large as 1.43.
-In the case that one have 2\,000 mocks the rescaling is less than 1.02.
+In the case that one has 2\,000 mocks the rescaling is less than 1.02.
 
@@
 
-Figure \ref{fig_cosmo} displays the 2pCF and the likelihood values in case of adopting 
-the four wrong cosmologies of Figure \ref{fig_xyquan}.
+Figure \ref{fig_cosmo} displays the 2pCF and the likelihood values when adopting 
+the four incorrect cosmologies used in Figure \ref{fig_xyquan}.
 For the cosmologies $\Omega_m=0.4,w=-1$ and $\Omega_m=0.26,w=-0.5$,
@@
 We compute the $\chi^2$ values according to Equation \ref{eq:chisq1}, 
-and find these cosmologies are disfavored 
+and find that these cosmologies are disfavored 
 at $\gtrsim30\sigma$ CL.
@@
 
-We constrain $\Omega_m$ and $w$ through Bayesian analysis (\cite{Bayesian}; also see \cite{LB2002,Li2016}).
+We constrain $\Omega_m$ and $w$ through a Bayesian analysis (\cite{Bayesian}; also see \cite{LB2002,Li2016}).
 We assue the likelihood takes the form
@@
 
-We get tight constraint on the two paramters.
+We obtain tight constraints on the two paramters.
 The 2$\sigma$ contour lies within the region $0.23<\Omega_m<0.285$, $-1.1<w<-0.9$.
 The two parameters are very strongly degenerated with each other.
-The thin shape of contour implies that, 
-when combining with the another observational data with different direction of degeneracy (e.g. CMB, BAO),
-very tight combined constraint can be obtained.
-In case of fixing one parameter at its best-fit value and constrain the other one,
-one obtain 1$\sigma$ uncertainty of $\delta\Omega_m\approx0.002,\delta w\approx0.01$.
+The thin shape of the contour implies that, 
+when combining with the another observational data with a different direction of degeneracy (e.g. CMB, BAO),
+a very tight combined constraint can be obtained.
+In the case of fixing one parameter at its best-fit value and constraining the other,
+one obtains 1$\sigma$ uncertainties of $\delta\Omega_m\approx0.002,\delta w\approx0.01$.
 
@@
 
-We developed a method measuring the redshift of the shape of galaxy angular correlation function, $\hat \omega_{r_\perp}$, to constrain cosmology.
-A wrongly adopted cosmology result in redshift-dependent mis-scaling in the constructed galaxy distribution,
-which leads to redshift-dependent rescaling of $\hat \omega_{r_\perp}(r_\perp)$.
+We developed a method of measuring the redshift of the shape of the galaxy angular correlation function, $\hat \omega_{r_\perp}$, to constrain cosmology.
+A wrongly adopted cosmology results in redshift-dependent mis-scaling in the constructed galaxy distribution,
+which leads to a redshift-dependent rescaling of $\hat \omega_{r_\perp}(r_\perp)$.
 The signal is sensitive to cosmology and relatively insensitive to the gravitational growth of structure,
@@
 
-In this analysis we restrict our focus to the rescaling in angular direction.
+In this analysis we restrict our focus to the rescaling in the angular direction.
 %The angular correlation function is adopted as a statistical tool to probing the scaling effect in the angular direction.
@@
 by directly comparing the theoretical 2pCF and the observed one \citep{Salvador2014,Salvador2016}.
-Our method is simpler and just utilizes the fact in the correct cosmology the angular 2pCF shape
-does not exhibit much redshift evolution.
+Our method is simpler and simply utilizes the fact in the correct cosmology the angular 2pCF shape
+does not exhibit significant redshift evolution.
 %is insensitive to redshift in correct cosmology.
@@
 
-\cite{Li2015,Li2016} shows that using the redshift dependent of AP effect 
+\cite{Li2015,Li2016} shows that using the redshift dependence of the AP effect, 
 one can derive very tight cosmological constraint.
@@
 This method is designed to be applied to current and future LSS surveys,
-with a particular emphasis to the {\it photometric surveys},
-such as DES (300 million galaxies at $z\lesssim1.5$) and LSST (20 billion galaxies at $z\lesssim2$) [CHECK THEM!!!].
-These surveys probe a large amount of galaxies 
-and the redshift error will not quite affect the angular 2pCF measurement 
-as long as the redshift dependence of the photometric redshift can be reliably understood.
+with a particular emphasis to the {\it photometric surveys}.
+DES will probe hundreds of millions of galaxies at $z\lesssim1.5$, 
+and LSST will probe tens of billions of galaxies at $z\lesssim2$.
+We expect very tight cosmological constraints from these surveys.
+%and the redshift error will not quite affect the angular 2pCF measurement 
+%as long as the redshift dependence of the photometric redshift can be reliably understood.
 
@@
 and also \citep{topology,MS2016},
-are introducing a new strategy to constrain cosmology from LSS data.
-We seek for the statistical pattern which maintains nearly constant at all redshifts;
+are introducing a new strategy to constrain cosmology from galaxy clustering.
+We seek the statistical pattern which remains constant at all redshifts;
 this invariance is broken if wrong cosmologies are adopted to construct the galaxy distribution
@@
 in a cosmology with values of parameters close enough to the underlying correct one.
-This avoids the difficult modeling of galaxy bias, galaxy clustering and RSD,
-enables reliable cosmological constraint on scales much smaller than BAO.
+This avoids the difficulty in the analytical modeling the galaxy clustering, galaxy bias and RSD,
+and enables reliable cosmological constraint on scales much smaller than BAO.
 We hope these methods play an important role in deriving cosmological constraints from future LSS surveys.

### 2016-10-06 105thick/scp.sh

@@ -1,4 +1,5 @@
 
 #scp xiaodongli@annapurna.kias.re.kr:~/105thick/*.2pcf ./
 #scp xiaodongli@annapurna.kias.re.kr:~/105thick/*.py ./
-scp xiaodongli@annapurna.kias.re.kr:/home/xiaodongli/105thick/*shiftz*.2pcf ./
+#scp xiaodongli@annapurna.kias.re.kr:/home/xiaodongli/105thick/*shiftz*.2pcf ./
+scp xiaodongli@newton.kias.re.kr:/home3/xiaodongli/cpfromanna/*shiftz*.2pcf ./

### 2016-10-06 draft/draft1.tex
updates

@@
 it produces {\it redshift-dependent mis-scaling} in the constructed galaxy distribution.
-As a result, we find a redshift-dependent rescaling in the measured galaxy angular 2pCF .
+As a result, we observe a redshift-dependent rescaling of the measured galaxy angular 2pCF.
 We test our method on the HR4 mock galaxies having hundreds of millions of galaxies at redshifts 
@@
 and is relatively insensitive to the gravitational growth of structure,
-the galaxy bias, and the redshift space distortion.
+the galaxy bias, and the redshift-space distortion.
 Analyzing the 2pCF shape on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
@@
 We found that the AP or volume effect in general introduces a geometric distortion that evolves significantly with redshift;
-this phenomenon can be utilized to distinguish the AP effect from the other effects, such as the redshift space distortion (RSD).
+this phenomenon can be utilized to distinguish the AP effect from the other effects, such as the redshift-space distortion (RSD).
 The radial distances of galaxies are inferred from the measured redshifts, which are distorted by the peculiar motion of galaxies, 
@@
 the galaxy bias, and the RSD effect.
-We apply our method to HR4 mock galaxies, using hundreds of millions of galaxies at redshfits $0\leq z\leq2$
+We apply our method to HR4 mock galaxies, using hundreds of millions of galaxies at redshifts $0\leq z\leq2$
 and develop the statistical procedure to constrain cosmological parameters.
@@
 On scales larger than $40 h^{-1}$ Mpc,
-the analytical modelling of the shape of the angular 2pCF is relatively well understood;
+the analytical modeling of the shape of the angular 2pCF is relatively well understood;
 one can just fit the 2pCF with the theoretical predictions \citep{Salvador2014,Salvador2016} 
@@
     for the four wrong cosmologies.
-    The redshift evolution of angular 2pCF shape in these wrong cosmologlies are detected at high CL.
+    The redshift evolution of angular 2pCF shape in these wrong cosmologies are detected at high CL.
    }
@@
    Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method, 
-   a likelihood value computed using Equations (\ref{eq:like,eq:chisq1}), 
    based on the redshfit evolution of the angular 2pCF shape $\hat\omega_{r_\perp}$.
@@
 
-We obtain tight constraints on the two paramters.
+We obtain tight constraints on the two parameters.
 The 2$\sigma$ contour lies within the region $0.23<\Omega_m<0.285$, $-1.1<w<-0.9$.

### 2017-04-01 draft/draft1.tex
updates

@@
 
-\author{Xiao-Dong Li, }
+\author{Xiao-Dong Li, Changbom Park, }
 \affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
-\author{Cheng Cheng, }
-\affil{Kavli Institute for Theoretical Physics China, Institute of Theoretical Physics, Chinese Academy of Sciences, Zhong Guan Cun Street 55\#, Beijing, 100190, P.R. China}
-\affil{University of Chinese Academy of Sciences, P.R. China}
-\author{Changbom Park,}
-\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
-\author{Hyunbae Park, Cristiano G. Sabiu, }
+\author{Cristiano G. Sabiu, Hyunbae Park, }
 \affil{Korea Astronomy and Space Science Institute, Daejeon 305-348, Korea}
@@
 %University Park, PA 16802 }
+\author{Cheng Cheng, }
+\affil{Kavli Institute for Theoretical Physics China, Institute of Theoretical Physics, Chinese Academy of Sciences, Zhong Guan Cun Street 55\#, Beijing, 100190, P.R. China}
+\affil{University of Chinese Academy of Sciences, P.R. China}
 \author{Juhan Kim\altaffilmark{1},}
@@
 %\altaffiltext{4}{\bf Hyunbae: your email}
-\altaffiltext{1}{Corresponding Author: kjhan@kias.re.kr}
+\altaffiltext{1}{Corresponding Author: Cris, Add your email!!!}
 
@@
 We propose to use the redshift dependence of the galaxy angular 2-point correlation function (2pCF)
-for a purpose of cosmological constraints.
-When an incorrect cosmological model is assumed for the coordinate transformation from redshift space to comoving space, 
+to constrain cosmological parameters.
+When an incorrect set of parameters is assumed for the coordinate transformation from redshift space to comoving space, 
 it produces {\it redshift-dependent mis-scaling} in the constructed galaxy distribution.
 As a result, we observe a redshift-dependent rescaling of the measured galaxy angular 2pCF.
-We test our method on the HR4 mock galaxies having hundreds of millions of galaxies at redshifts 
-$0\leq z\leq2$.
-We find the redshift evolution of shape of angular 2pCF, as a function of scale,
-is sensitive to the adopted cosmological parameters,
-and is relatively insensitive to the gravitational growth of structure,
+We test our method on the Horizon Run 4 N-body simulation snapshot data, 
+which contains hundreds of millions of galaxies at redshifts 
+0, 0.5, 1, 1.5 and 2
+We find the shape of angular 2pCF, as a function of scale,
+exhibits evident redshift evolution when an incorrect set of cosmological parameters adopted,
+and is relatively insensitive to the other effects such as gravitational growth of structure,
 the galaxy bias, and the redshift-space distortion.
@@
 to derive tight cosmological constraints.
-This work is a continuation of our previous works \citep{Li2014,Li2015,Li2016}
-as a strategy to constraining cosmological parameters based on some nearly redshift-invariant physical quantity;
-they are all powerful in constraining cosmology and have a lot of merit,
-e.g., are less affected by the systematic effects introduced by non-linear clustering or RSD,
+This work is a continuation of our previous works \cite{Li2014,Li2015,Li2016},
+which use a strategy to constraining cosmological parameters based on some redshift-invariant physical quantity;
+they have a lot of merit,
+e.g., lead to powerful constraints, are less affected by the systematic effects introduced by non-linear clustering or RSD,
 do not require accurate analytical modeling of the galaxy correlation function,
-and are applicable on relatively small clustering scales.
+are applicable on relatively small clustering scales,
+and are applicable to many future LSS surveys.
 \end{abstract}
@@
 
-In \cite{Li2014,Li2015,Li2016} we developed a novel strategy to probe $D_A$ and $H$ from LSS data.
+In \cite{Li2014,Li2015,Li2016} we developed a novel strategy to probe $D_A$ and $H$ from the LSS data.
 %proposed a series of methods to probe the geometric information encoded in the LSS data.
@@
 The method was applied to BOSS DR12 galaxies \citep{Li2016} to probe the redshift dependence of the AP effect, 
-and we arrive at tight cosmological constraints comparable to mainstream probes of SNIa, BAO, CMB.
+and we arrive at tight cosmological constraints competitive with mainstream probes of SNIa, BAO, CMB.
 
@@
 
-\scr{When the correct cosmology is adopted the cosmic scale is correctly estimated,
+When the correct cosmology is adopted the cosmic scale is correctly estimated,
 the main factor leads to redshift evolution of galaxy distribution is the gravitational growth of structure.
@@
 $25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$,
-leading to a clear redshift evolution of sizes of structures.}
+leading to a clear redshift evolution of sizes of structures.
 
@@
   and the evolution with respect to the $z=0$ value ($\hat{\omega}_{r_{\perp}}(z=z_i) - \hat{\omega}_{r_{\perp}}(z=0)$, right panels). 
-  Upper panels show that in the correct cosmology the redshift evolution of the shape of 2pCF is rather small, 
+  Upper panels show that in the correct cosmology the redshift evolution of the shape of 2pCF is rather small regardless of the large redshfit evolution of the amplitude, 
   whereas the lower panels show that, in a wrong cosmology $\Omega_m = 0.05,w=-1.5$, the redshift evolution of $\hat{\omega}_{r_\perp}$ is very significant.
@@
 We multiply $\omega$ by the separation $r_\perp$ to have similar size of statistical uncertainty on all scales.
+For convenience we will use the denotation
+\begin{equation}
+ \hat \omega_{r_{\perp}} \equiv r_{\perp} \omega.
+\end{equation}
 
@@
 The amplitude is highest at $z=0$ where the structures experienced the most growth.
-$\omega(r_\perp)$ also increases with redshift at $z>1$ with increasing redshift 
+$\omega(r_\perp)$ increases at $z>1$ with increasing redshift 
 as a reason of increasing galaxy bias.
@@
 %The shape of $r_\perp\omega$ also evolves with redshift.
-the shape of $r_\perp\omega$  remains similar at all redshifts;
+the shape of $\omega_{r_{\perp}}$  remains similar at all redshifts;
 in general it peaks at $r\sim9 h^{-1}\rm Mpc$ and monotonically drops or increases at larger or smaller scales.
@@
 
-In the upper-middle panel, the overlapping of $\hat\omega$
+In the upper-middle panel, the overlapping of $\hat\omega_{r_{\perp}}$
 clearly show the minimal redshift evolution of the shape.
@@
 
-\subsection{Galaxy angular 2pCF: Cosmological Effect }
+\subsection{Galaxy angular 2pCF: cosmological effect }
 
@@
 a simple consequence of the fact that the clustering pattern at scale $r$ is rescaled to $\alpha_{\perp} r$.
+
 The redshift evolution of $\alpha_{\perp}$ leads to redshift evolution of 
@@
 Four values of minimal mass limits, $3\times 10^{11} M_{\odot}$, $1\times 10^{12} M_{\odot}$, $4\times 10^{12} M_{\odot}$ and $1\times 10^{13} M_{\odot}$,
-are imposed to create three \scr{four?} samples with different galaxy bias.
+are imposed to create samples with different galaxy bias.
 The measured angular 2pCF are displayed.
 
-Different mass cuts result in large variation in the amplitude of the 2pCF (left panel),
-while the shape of the \scr{normalised} 2pCF remains less affected (middle panel).
+Different mass cuts result in large variation in the amplitude of the 2pCF (left panel);
+but the shape of the \scr{normalised} 2pCF remains less affected (middle panel).
 Compared with the sample of $M>3\times 10^{11} M_{\odot}$,
 samples with mass limits of $1\times 10^{12} M_{\odot}$, $4\times 10^{12} M_{\odot}$ and $1\times 10^{13} M_{\odot}$
-have amplitude of 2pCFs enhanced by $10\%,\ 50\%$ and $100\%$, respectively, 
-while the change in the shape is only $0.5\%,\ 2\%$ and $4\%$.
-The effect of galaxy bias becomes much smaller by utilizing the shape of the 2pCF rather than the amplitude.
+have amplitude of 2pCFs enhanced by $10\%,\ 50\%$ and $100\%$, 
+while the change in the shape is only $0.5\%,\ 2\%$ and $4\%$, respectively.
+The effect of galaxy bias becomes much less significant by utilizing the shape of the 2pCF rather than the amplitude.
 
@@
 The galaxies observed in a survey are split into shells of subsamples, 
-with different redshift ranges, for the 2pCF measurement.
+with different redshift ranges. So that we can get the 2pCF measurement at different redshfits.
 RSD distorts the galaxy redshift and as a result some galaxies 
@@
 \end{equation}
-where $v_{{\rm Z}}$ (Z is treated as the radial direction in this analysis) 
+where $v_{{\rm Z}}$ (Z is the third coordinate of the galaxy in the box, treated as the radial direction in this analysis) 
 is the galaxy peculiar velocity in the LOS direction.
-This lead to misclassification of some galaxies when we split the box into slices.
+This lead to {\it misclassification} of some galaxies when we split the box into slices.
 %Then we split the whole box into 30 slices with thickness $105h^{-1}\rm Mpc$, 
@@
 
-The lower panel of Figure \ref{fig_sys} shows the RSD effect on the 2pCF.
+The lower panel of Figure \ref{fig_sys} shows how it affects on the 2pCF.
 Comparing this plot with Figure \ref{fig_diffz} one can clearly see the effect of RSD.
@@
 and the slop of $\hat\omega_{r_\perp}$ is suppressed.
-The redshift evolution of $\hat\omega_{r_\perp}$ is still small, remain $\lesssim4\%$ at $0.5\leq z \leq 2$.
-So RSD should not very affect the application of our method as long as it is precisely modeled and corrected.
+But the redshift evolution of $\hat\omega_{r_\perp}$ is still small, remain $\lesssim4\%$ at $0.5\leq z \leq 2$.
+So RSD should not very affect the application of our method as long as its redshift evolution is small;
+the small effect of RSD can be precisely modeled by simulations and corrected.
 %If looking at the redshift evolution,
@@
 also results in fuzzy boundaries of shells and misclassification of galaxies.
-This effect should also be properly quantified in real observations.
+This effect should be properly quantified when dealing with real observational data.
 
@@
 \begin{equation}
- \delta \hat{r_\perp\omega}(z_i,z_1) \equiv \hat{r_\perp\omega}(z_i) - \hat{r_\perp\omega}(z_1),
+ \delta \hat{\omega_{r_\perp}}(z_i,z_1) \equiv \hat{\omega_{r_\perp}}(z_i) - \hat{\omega_{r_\perp}}(z_1),
 \end{equation}
@@
 which is 35 since we have $r_\perp$ bins 
-with width $1h^{-1}\rm Mpc$ in a range of $5h^{-1}{\rm Mpc}\leq r\leq 40h^{-1}{\rm Mpc}$.
+with width $1h^{-1}\rm Mpc$ in a range of $5h^{-1}{\rm Mpc}\leq r_\perp\leq 40h^{-1}{\rm Mpc}$.
 ${\bf p}(z_i,r_{j})$ is the redshift evolution of the angular correlation function shape with systematic effects subtracted
 \begin{eqnarray}\label{eq:bfp}
- {\bf p}(z_i,r_{j}) \equiv&\ \delta \hat{\omega}(z_i,z_1,r_j) - \delta \hat{\omega}_{r_\perp,\rm sys}(z_i,z_1,r_j)
+ {\bf p}(z_i,r_{j}) \equiv&\ \delta \hat{\omega_\perp}(z_i,z_1,r_j) - \delta \hat{\omega}_{r_\perp,\rm sys}(z_i,z_1,r_j)
 \end{eqnarray}
@@
 For the cosmologies $\Omega_m=0.4,w=-1$ and $\Omega_m=0.26,w=-0.5$,
-the compression shifts the large scale clustering patterns into small scales
+the compression shifts the clustering patterns into smaller scales
 at higher redshift and make the 2pCFs steeper.
@@
     $\hat{\omega}_{r_\perp}$ (upper panels) and $\hat{\omega}_{r_\perp}(z=z_i) - \hat{\omega}_{r_\perp}(z=0)$ (lower panels) at several redshifts,
-    for the four wrong cosmologies.
-    The redshift evolution of angular 2pCF shape in these wrong cosmologies are detected at high CL.
+    for four wrong cosmologies.
+    The redshift evolution of the angular 2pCF shape in these wrong cosmologies are detected at high CL.
    }
@@
 The 2$\sigma$ contour lies within the region $0.23<\Omega_m<0.285$, $-1.1<w<-0.9$.
-The two parameters are very strongly degenerated with each other.
+The two parameters are very strongly degenerated with each other,
+and the area of constrained region is quite small.
 The thin shape of the contour implies that, 
@@
 a very tight combined constraint can be obtained.
+
 In the case of fixing one parameter at its best-fit value and constraining the other,
-one obtains 1$\sigma$ uncertainties of $\delta\Omega_m\approx0.002,\delta w\approx0.01$.
+one obtains very small 1$\sigma$ uncertainties of $\delta\Omega_m\approx0.002,\delta w\approx0.01$.
 
@@
 
-We developed a method of measuring the redshift of the shape of the galaxy angular correlation function, $\hat \omega_{r_\perp}$, to constrain cosmology.
+We developed a simple method of measuring the redshift of the shape of the galaxy angular correlation function, $\hat \omega_{r_\perp}$, to constrain cosmology.
 A wrongly adopted cosmology results in redshift-dependent mis-scaling in the constructed galaxy distribution,
@@
 one can derive very tight cosmological constraint.
+The method presented in this paper studies the redshift evolution of the volume effect.
 %We hope this method also.
@@
 with a particular emphasis to the {\it photometric surveys}.
+The galaxy angular 2pCF in redshift shells is much less affected by the large redshift errors compared wit the 3D 2pCF.
 DES will probe hundreds of millions of galaxies at $z\lesssim1.5$, 
@@
 Our series of works \cite{Li2014,Li2015,Li2016}, together with this analysis, 
-and also \citep{topology,MS2016},
+and also \cite{topology,MS2016},
 are introducing a new strategy to constrain cosmology from galaxy clustering.
-We seek the statistical pattern which remains constant at all redshifts;
+We utilize a statistical pattern which remains constant at all redshifts;
 this invariance is broken if wrong cosmologies are adopted to construct the galaxy distribution
@@
 This avoids the difficulty in the analytical modeling the galaxy clustering, galaxy bias and RSD,
-and enables reliable cosmological constraint on scales much smaller than BAO.
+and enables reliable cosmological constraint on relatively small clustering scales.
 We hope these methods play an important role in deriving cosmological constraints from future LSS surveys.

### 2017-04-01 draft/draft1_cris.tex
updates

--- 2017-04-01 draft/draft1.tex
@@
 \shorttitle{Reshift Dependent Volume effect}
-\shortauthors{X.-D. Li, C. Cheng, C. Park, C.G. Sabiu, H. Park, J. Kim, S.E. Hong}
+\shortauthors{X.-D. Li, C. Park, C.G. Sabiu, H. Park, C. Cheng, J. Kim, S.E. Hong}
 
@@
 
-\title{Cosmological constraints from the redshift dependence of %geometric deformation
-the galaxy angular 2-point correlation function}
+\title{Cosmological constraints from the redshift dependence of the volume effect: galaxy angular 2-point correlation function}
 
@@
 \affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
-\author{Cristiano G. Sabiu, Hyunbae Park, }
+\author{Cristiano G. Sabiu\altaffilmark{1}, Hyunbae Park, }
 \affil{Korea Astronomy and Space Science Institute, Daejeon 305-348, Korea}
@@
 \affil{University of Chinese Academy of Sciences, P.R. China}
-\author{Juhan Kim\altaffilmark{1},}
+\author{Juhan Kim,}
 \affil{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
@@
 %\altaffiltext{4}{\bf Hyunbae: your email}
-\altaffiltext{1}{Corresponding Author: Cris, Add your email!!!}
+\altaffiltext{1}{Corresponding Author: csabiu@kasi.re.kr}
 
@@
 As a result, we observe a redshift-dependent rescaling of the measured galaxy angular 2pCF.
-We test our method on the Horizon Run 4 N-body simulation snapshot data, 
-which contains hundreds of millions of galaxies at redshifts 
-0, 0.5, 1, 1.5 and 2
-We find the shape of angular 2pCF, as a function of scale,
-exhibits evident redshift evolution when an incorrect set of cosmological parameters adopted,
-and is relatively insensitive to the other effects such as gravitational growth of structure,
-the galaxy bias, and the redshift-space distortion.
+Using mock galaxy catalogues (containing millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2) from the Horizon Run 4 N-body simulation, we find that the redshift evolution of the angular 2pCF shape, as a function of scale,
+is sensitive to the adopted cosmological parameters. 
+% mock galaxy catalogues having hundreds of millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2.
+However, it is relatively insensitive to the gravitational growth of structure,
+the galaxy bias, and the effect of redshift space distortions.
 Analyzing the 2pCF shape on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
@@
 %Our method is complementary to current works using 2pCF to constrain cosmological parameters.
-The method could be applicable to future large scale structure surveys, especially the photometric surveys such as DES, LSST, 
+The method could be applicable to future large scale structure surveys, especially photometric surveys such as DES, LSST, 
 to derive tight cosmological constraints.
-This work is a continuation of our previous works \cite{Li2014,Li2015,Li2016},
-which use a strategy to constraining cosmological parameters based on some redshift-invariant physical quantity;
-they have a lot of merit,
-e.g., lead to powerful constraints, are less affected by the systematic effects introduced by non-linear clustering or RSD,
-do not require accurate analytical modeling of the galaxy correlation function,
-are applicable on relatively small clustering scales,
-and are applicable to many future LSS surveys.
+This work is a continuation of our previous works \citep{Li2014,Li2015,Li2016}
+as a strategy to constrain cosmological parameters using redshift-invariant physical quantities;
+they are all powerful in constrain cosmology and have a lot of merits,
+e.g., are less affected by the systematic effects introduced by non-linear clustering or RSD,
+does not require accurate modeling of galaxy clustering,
+and are applicable on relative small clustering scales.
 \end{abstract}
@@
 Various statistical methods have been proposed to measure these effects.
-The AP effect can be measured through statistical study of the clustering of galaxies \citep{Ballinger1996,Matsubara1996}.
-This method has been applied to a series of LSS surveys
-\citep{Outram2004,Blake2011,ChuangWang2012,Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, Jeong2014,Sutter2014,2014ApJ...781...96L,Alam2016, Beutler2016, Sanchez2016},
-Alternative approaches uses the symmetry properties of galaxy pairs \citep{Marinoni2010,Jennings2011,BB2012}
+The AP effect was first suggested to be measured through the anisotropic clustering of galaxies \citep{Ballinger1996,Matsubara1996}.
+Later, with the advent of large observational spectroscopic programs, this was applied to a series of LSS surveys
+\citep{Outram2004,Blake2011,ChuangWang2012,Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, Jeong2014,Sutter2014,2014ApJ...781...96L,Alam2016, Beutler2016, Sanchez2016}.
+Although there have also been alternative approaches using the symmetry properties of galaxy pairs \citep{Marinoni2010,Jennings2011,BB2012}
 and cosmic voids \citep{Ryden1995,LavausWandelt1995,Sutter2014,Qingqing2016}.
-Methods proposed that are able to probe the volume effect include the number counting of 
-galaxy clusters \citep{PS1974,VL1996} and topology \citep{topology},
+Methods proposed to measure the volume effect include the number counting of 
+galaxy clusters \citep{PS1974,VL1996}, the topology of LSS \citep{topology},
 the BAO scale \citep{EHT1998,BG03,SE03},
 and the shape of 2pCF and power spectrum \citep{Sanchez2006,Sanchez2009}.
-
-%\bibiem[Kazin et al (2012)]{KSB2012}
-%Kazin, E.A., S\'{a}nchez, A.G., Blanton, M.R. 2012, MNRAS, 419, 3223
 
@@
 leading to apparent distortion in the redshift space galaxy distribution \citep{FOG,Kaiser1987,Ballinger1996}.
-This is the major systematic effect limiting our ability to probe the geometry of LSS from galaxy distribution.
-We found its influence is significantly reduced when studying the redshift dependence of the distortion.
+It is the major systematic effects limiting our ability to probe the geometry of LSS from the galaxy distribution.
+However, we found that the influence of RSD is significantly reduced when we consider only the redshift dependence of the distortion.
 
@@
 to characterize the redshift evolution of the LSS distortion. 
-We tested the idea on the Horizon Run 3 (HR3) N-body simulation \citep{horizonrun},
+We tested the idea on the Horizon Run 3 (HR3) N-body simulations \citep{horizonrun},
 showing that the redshift evolution of the gradient field 
@@
 using a slightly modified version of the usual anisotropic galaxy two-point correlation function (2pCF), $\xi(\mu)$, 
-where $\mu\equiv \cos \theta$ and $\theta$ is the direction between the connection of the galaxy pairs and the line of sight.
+where $\mu\equiv \cos \theta$ and $\theta$ is the angle between the connection of the galaxy pairs and the line of sight direction.
 When an incorrect cosmological model is adopted, 
@@
 
-In this paper we continue our exploration of this strategy and presented 
-a new method using the redshift of the shape of the {\it galaxy angular 2pCF} as a function of radial scale, $\omega(r_{\bot})$,
+In this paper we continue our exploration of this strategy and present 
+a new method using the redshift evolution of the shape of the {\it galaxy angular 2pCF} as a function of radial scale, $\omega(r_{\bot})$,
 to constrain cosmology.
@@
 and their sizes are wrongly estimated (volume effect).
-Cosmological models (i,iii) yield to compressed size (in both angular and LOS direction),
+Cosmological models (i,iii) result in compressed volume elements (in both angular and LOS direction),
 and the degree of compression increases with increasing distance;
@@
 %$4.57\times 10^8$, $4.06\times 10^8$, $3.52\times 10^8$, $3.06\times 10^8$ and $2.28 \times 10^8$ mock galaxies,
-we select 457, 406, 352, 206 and 228 million mock galaxies at the five redshifts,
+we select 457, 406, 352, 306 and 228 million mock galaxies at the five redshifts,
 corresponding to a number density of 
@@
    %\includegraphics[width=16cm,natwidth=8,natheight=14]{fig2.pdf}
-   \includegraphics[width=16cm]{fig2.eps}
+   \includegraphics[width=16cm]{fig2_0.eps}
    }
@@
 
-Among different redshifts there is large variation in the amplitude of $\omega(r_\perp)$.
+Among the different redshift bins there is large variation in the amplitude of $\omega(r_\perp)$.
 The amplitude is proportional to the clustering strength, which is affected by the gravitational growth of structures and the galaxy bias.
@@
 the analytical modeling of the shape of the angular 2pCF is relatively well understood;
-one can just fit the 2pCF with the theoretical predictions \citep{Salvador2014,Salvador2016} 
+one can just fit the 2pCF with the theoretical predictions \citep{BCGS2001,Salvador2014,Salvador2016} 
 instead of using our method 
@@
 In order to reliably extract the cosmological information, 
-we just utilize the the redshift evolution of the 2pCF shape, 
+we just utilize the redshift evolution of the 2pCF shape, 
 which is less affected by other factors.
@@
 \subsection{Systematic effects}
-
-In Sec. \ref{sec_2pCF_diffz} we showed that $\hat \omega_{r_\perp}$ measured from the
-constant mass cut samples at different redshifts show good agreement.
-The gravitational growth of structure will not have a large impact on $\hat \omega_{r_\perp}$ on scales $\gtrsim5 h^{-1}$ Mpc,
-yet there are many other factors that may induce redshift evolution
-including galaxy bias, RSD, redshift error, and 
-the redshift evolution of galaxies properties 
-such as mass, morphology, color, concentration. 
-Here we test two ``major'' systematical effects; galaxy bias and the RSD effect.
-
-%The same as \cite{Li2014,Li2015,Li2016} we need to correct for the redshift evolution of $r_\perp\omega$ caused by effects other than the cosmological effect.
-
-%Figure \ref{fig_diffz} already shows that, the growth of structure, especially in low redshift and on non-linear scales, 
-%changes the shape of $r_\perp\omega$ and caused relative enhancement on $r\lesssim2 h^{-1}\rm Mpc$.
-%So we limit the region of scale to $r>5h^{-1}\rm Mpc$ to minimize its effect.
-
-\subsubsection{Galaxy Bias}
-
-Galaxies are biased tracers of the dark matter field;
-more massive galaxies reside in regions with higher density contrast
-and exhibit stronger clustering (i.e. larger bias).
-%In large scale structure surveys, the bias of the galaxy sample is an important fator affecting on the clustering properties of the sample.
-
-We vary the mass cut and check the effect of galaxy bias on $\hat \omega_{r_\perp}$.
-The upper panels of Figure \ref{fig_sys} displays the 2pCF measured from galaxies within a $3175\times3175\times105$ $(h^{-1}\rm Mpc)^3$ volume, taken from the $z=0$ snapshot.
-Four values of minimal mass limits, $3\times 10^{11} M_{\odot}$, $1\times 10^{12} M_{\odot}$, $4\times 10^{12} M_{\odot}$ and $1\times 10^{13} M_{\odot}$,
-are imposed to create samples with different galaxy bias.
-The measured angular 2pCF are displayed.
-
-Different mass cuts result in large variation in the amplitude of the 2pCF (left panel);
-but the shape of the \scr{normalised} 2pCF remains less affected (middle panel).
-Compared with the sample of $M>3\times 10^{11} M_{\odot}$,
-samples with mass limits of $1\times 10^{12} M_{\odot}$, $4\times 10^{12} M_{\odot}$ and $1\times 10^{13} M_{\odot}$
-have amplitude of 2pCFs enhanced by $10\%,\ 50\%$ and $100\%$, 
-while the change in the shape is only $0.5\%,\ 2\%$ and $4\%$, respectively.
-The effect of galaxy bias becomes much less significant by utilizing the shape of the 2pCF rather than the amplitude.
-
-\subsubsection{Redshift Space Distortion}
-
-The galaxy peculiar velocity contaminates the observed redshift and distorts 
-the inferred galaxy radial position.
-It is the major systematic in our previous works \citep{Li2014,Li2015,Li2016}
-of statistical analysis on the 3D galaxy distribution.
-
-The effect of RSD is much milder in this work. 
-The angular positions of galaxies are not shifted by RSD at all;
-the only effect of RSD enter in the procedure of 
-splitting galaxies into redshift shells.
-The galaxies observed in a survey are split into shells of subsamples, 
-with different redshift ranges. So that we can get the 2pCF measurement at different redshfits.
-RSD distorts the galaxy redshift and as a result some galaxies 
-(especially those close to the boundaries of shells) are assigned to the wrong redshift shells.
-
-We shift the radial coordinates of galaxies according to the relation 
-\begin{equation}\label{eq:zvpeu}
-\Delta z = (1+z) \frac{v_{{\rm Z}}}{c},
-\end{equation}
-where $v_{{\rm Z}}$ (Z is the third coordinate of the galaxy in the box, treated as the radial direction in this analysis) 
-is the galaxy peculiar velocity in the LOS direction.
-This lead to {\it misclassification} of some galaxies when we split the box into slices.
-%Then we split the whole box into 30 slices with thickness $105h^{-1}\rm Mpc$, 
-%and measure the angular 2pCF.
-
-The lower panel of Figure \ref{fig_sys} shows how it affects on the 2pCF.
-Comparing this plot with Figure \ref{fig_diffz} one can clearly see the effect of RSD.
-The amplitude of the measured 2pCF is enhanced by $\sim 10\%$ when considering the RSD effect 
-and the slop of $\hat\omega_{r_\perp}$ is suppressed.
-But the redshift evolution of $\hat\omega_{r_\perp}$ is still small, remain $\lesssim4\%$ at $0.5\leq z \leq 2$.
-So RSD should not very affect the application of our method as long as its redshift evolution is small;
-the small effect of RSD can be precisely modeled by simulations and corrected.
-%If looking at the redshift evolution,
-%the curves $\hat{r_\perp\omega} - \hat{r_\perp\omega}(z=0)$ displayed in the right panel,
-%they changed a lot compared with the case of no RSD effect (the right panel of Figure \ref{fig_diffz}),
-%but do not become much larger. %But RSD effect does not introduce large redshfit evolution, although the shape of  is
-
-Similar to RSD, redshift errors of galaxies
-also results in fuzzy boundaries of shells and misclassification of galaxies.
-This effect should be properly quantified when dealing with real observational data.
-
-%In \cite{Li2014,Li2015,Li2016}, the systematic effects contributing to the redshfit evolution of galaxy clusterings 
-%are modeled in mock surveys and subtracted.
-%Similar treatment could be conducted here.
-%One shall construct mock surveys with the above effects included for the correction of systematics.
-
-%The outer boundary of the mock survey becomes fuzzy due to the peculiar velocity effect 
-%on the galaxy redshifts (Eq. (\ref{eq:zvpeu})).
-%A population of galaxies, that are expected to enter the $z<0.7$ region from the outside, is missing.
-%(these $z>0.7$ galaxies have a peculiar velocity toward us and 
-%their observed redshfits become lower than 0.7).
-%To avoid this problem we set the maximal redshift at 0.693, 
-%23.3 $h^{-1}{\rm Mpc}$ away from $z=0.7$.
-
-%3.000e11', '1.000e12', '4.000e12',  '1.000e13
 
@@
 
+In Sec. \ref{sec_2pCF_diffz} we showed that $\hat \omega_{r_\perp}$ measured from the
+constant mass cut samples at different redshifts show good agreement.
+The gravitational growth of structure will not have a large impact on $\hat \omega_{r_\perp}$ on scales $\gtrsim5 h^{-1}$ Mpc,
+yet there are many other factors that may induce redshift evolution
+including galaxy bias, RSD, redshift error, and 
+the redshift evolution of galaxies properties 
+such as mass, morphology, color, concentration. 
+Here we test two ``major'' systematical effects; galaxy bias and the RSD effect.
+
+%The same as \cite{Li2014,Li2015,Li2016} we need to correct for the redshift evolution of $r_\perp\omega$ caused by effects other than the cosmological effect.
+
+%Figure \ref{fig_diffz} already shows that, the growth of structure, especially in low redshift and on non-linear scales, 
+%changes the shape of $r_\perp\omega$ and caused relative enhancement on $r\lesssim2 h^{-1}\rm Mpc$.
+%So we limit the region of scale to $r>5h^{-1}\rm Mpc$ to minimize its effect.
+
+\subsubsection{Galaxy Bias}
+
+\begin{figure*}
+   \centering{
+%   \includegraphics[width=18cm]{fig9_0.eps}
+%   \includegraphics[width=18cm]{fig9_1.eps}
+%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
+%    \includegraphics[height=8cm]{smu.eps}
+    \includegraphics[width=14cm]{fig5.eps}
+   }
+   \caption{\label{fig_cosmo}
+    $\hat{\omega}_{r_\perp}$ (upper panels) and $\hat{\omega}_{r_\perp}(z=z_i) - \hat{\omega}_{r_\perp}(z=0)$ (lower panels) at several redshifts,
+    for four wrong cosmologies.
+    The redshift evolution of the angular 2pCF shape in these wrong cosmologies are detected at high CL.
+   }
+\end{figure*}
+
+Galaxies are biased tracers of the dark matter field;
+more massive galaxies reside in regions with higher density contrast
+and exhibit stronger clustering (i.e. larger bias).
+%In large scale structure surveys, the bias of the galaxy sample is an important fator affecting on the clustering properties of the sample.
+
+We vary the mass cut and check the effect of galaxy bias on $\hat \omega_{r_\perp}$.
+The upper panels of Figure \ref{fig_sys} displays the 2pCF measured from galaxies within a $3175\times3175\times105$ $(h^{-1}\rm Mpc)^3$ volume, taken from the $z=0$ snapshot.
+Four values of minimal mass limits, $3\times 10^{11} M_{\odot}$, $1\times 10^{12} M_{\odot}$, $4\times 10^{12} M_{\odot}$ and $1\times 10^{13} M_{\odot}$,
+are imposed to create samples with different galaxy biases.
+The measured angular 2pCF are displayed.
+
+Different mass cuts result in large variation in the amplitude of the 2pCF (left panel);
+but the shape of the normalised 2pCF remains less affected (middle panel).
+Compared with the sample of $M>3\times 10^{11} M_{\odot}$,
+samples with mass limits of $1\times 10^{12} M_{\odot}$, $4\times 10^{12} M_{\odot}$ and $1\times 10^{13} M_{\odot}$
+have amplitude of 2pCFs enhanced by $10\%,\ 50\%$ and $100\%$, 
+while the change in the shape is only $0.5\%,\ 2\%$ and $4\%$, respectively.
+The effect of galaxy bias becomes much less significant by utilizing the shape of the 2pCF rather than the amplitude.
+
+\subsubsection{Redshift Space Distortion}
+
+\begin{figure*}
+   \centering{
+   %\includegraphics[width=7cm]{Tpcf--contour.eps}
+   %\includegraphics[width=16cm]{Tpcf--contour-others.eps}
+   %\includegraphics[width=16cm,natwidth=52,natheight=40]{fig10.eps}
+   \includegraphics[width=12cm]{fig9.eps}
+   }
+   \caption{\label{fig_contours}
+   Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method, 
+   based on the redshift evolution of the angular 2pCF shape $\hat\omega_{r_\perp}$.
+   Utilizing the HR4 snapshots data of mock galaxies at five redshifts,
+   the method can lead to very tight cosmological constraint.
+   }
+\end{figure*}
+
+The galaxy peculiar velocity contaminates the observed redshift and distorts 
+the inferred galaxy radial position.
+It is the major systematic in our previous works \citep{Li2014,Li2015,Li2016}
+of statistical analysis on the 3D galaxy distribution.
+
+The effect of RSD is much milder in this work. 
+The angular positions of galaxies are not shifted by RSD at all;
+the only effect of RSD enter in the procedure of 
+splitting galaxies into redshift shells.
+The galaxies observed in a survey are split into shells of subsamples, 
+with different redshift ranges. This allows us to obtain 2pCF measurement at various redshifts.
+RSD distorts the galaxy redshift and as a result some galaxies 
+(especially those close to the boundaries of shells) are assigned to the wrong redshift shells.
+
+We shift the radial coordinates of galaxies according to the relation 
+\begin{equation}\label{eq:zvpeu}
+\Delta z = (1+z) \frac{v_{{\rm Z}}}{c},
+\end{equation}
+where $v_{{\rm Z}}$ (Z is the third coordinate of the galaxy in the box, treated as the radial direction in this analysis) 
+is the galaxy peculiar velocity in the LOS direction.
+This lead to {\it misclassification} of some galaxies when we split the box into slices.
+%Then we split the whole box into 30 slices with thickness $105h^{-1}\rm Mpc$, 
+%and measure the angular 2pCF.
+
+The lower panel of Figure \ref{fig_sys} shows how it affects on the 2pCF.
+Comparing this plot with Figure \ref{fig_diffz} one can clearly see the effect of RSD.
+The amplitude of the measured 2pCF is enhanced by $\sim 10\%$ when considering the RSD effect 
+and the slop of $\hat\omega_{r_\perp}$ is suppressed.
+However, the redshift evolution of $\hat\omega_{r_\perp}$ remains small,  $\lesssim4\%$ at $0.5\leq z \leq 2$.
+Therefore RSD should not significantly affect the application of our method, as long as its redshift evolution is small;
+the small effect of RSD can be precisely modelled by simulations and corrected.
+%If looking at the redshift evolution,
+%the curves $\hat{r_\perp\omega} - \hat{r_\perp\omega}(z=0)$ displayed in the right panel,
+%they changed a lot compared with the case of no RSD effect (the right panel of Figure \ref{fig_diffz}),
+%but do not become much larger. %But RSD effect does not introduce large redshfit evolution, although the shape of  is
+
+Similar to RSD, redshift errors of galaxies
+also results in fuzzy boundaries of redshift shells
+Thankfully, there are some methods for mitigating this effect in photometric surveys using pair-center binning \citep{2010MNRAS.407..520N}.
+
+%In \cite{Li2014,Li2015,Li2016}, the systematic effects contributing to the redshfit evolution of galaxy clusterings 
+%are modeled in mock surveys and subtracted.
+%Similar treatment could be conducted here.
+%One shall construct mock surveys with the above effects included for the correction of systematics.
+
+%The outer boundary of the mock survey becomes fuzzy due to the peculiar velocity effect 
+%on the galaxy redshifts (Eq. (\ref{eq:zvpeu})).
+%A population of galaxies, that are expected to enter the $z<0.7$ region from the outside, is missing.
+%(these $z>0.7$ galaxies have a peculiar velocity toward us and 
+%their observed redshfits become lower than 0.7).
+%To avoid this problem we set the maximal redshift at 0.693, 
+%23.3 $h^{-1}{\rm Mpc}$ away from $z=0.7$.
+
+%3.000e11', '1.000e12', '4.000e12',  '1.000e13
+
 \subsection{Likelihood Analysis}
@@
 Adopting the correct cosmological model will resulting in minimal evolution of the normalised 2pCF.
-Thus we proceed to construct a quantitative likelihood estimator.
+Thus we proceed to construct a quantitative likelihood estimator that reflects this property.
 The procedure here is very similar to \cite{Li2014,Li2015,Li2016}.
@@
 For the cosmologies $\Omega_m=0.4,w=-1$ and $\Omega_m=0.26,w=-0.5$,
-the compression shifts the clustering patterns into smaller scales
+the compression shifts the clustering patterns to smaller scales
 at higher redshift and make the 2pCFs steeper.
@@
 %We get 2pCFs with steeper slope and the higher redshift the steeper.
-For cosmologies $\Omega_m=0.15,w=-1$ and $\Omega_m=0.26,w=-1.5$,
-the stretch of structure leads to shallower slope of $\hat{\omega}_{r_\perp}$ at higher redshift.
+For the cosmologies $\Omega_m=0.15,w=-1$ and $\Omega_m=0.26,w=-1.5$,
+the stretch of structure leads to a shallower slope of $\hat{\omega}_{r_\perp}$ at higher redshift.
 %the shallower.
@@
 
-\begin{figure*}
-   \centering{
-%   \includegraphics[width=18cm]{fig9_0.eps}
-%   \includegraphics[width=18cm]{fig9_1.eps}
-%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
-%    \includegraphics[height=8cm]{smu.eps}
-    \includegraphics[width=18cm]{fig5.eps}
-   }
-   \caption{\label{fig_cosmo}
-    $\hat{\omega}_{r_\perp}$ (upper panels) and $\hat{\omega}_{r_\perp}(z=z_i) - \hat{\omega}_{r_\perp}(z=0)$ (lower panels) at several redshifts,
-    for four wrong cosmologies.
-    The redshift evolution of the angular 2pCF shape in these wrong cosmologies are detected at high CL.
-   }
-\end{figure*}
-
 \section{Cosmological constraint}
@@
 We constrain $\Omega_m$ and $w$ through a Bayesian analysis (\cite{Bayesian}; also see \cite{LB2002,Li2016}).
-We assue the likelihood takes the form
+We assume that the likelihood takes the form
 \begin{equation}\label{eq:like}
@@
 \end{equation}
-and scan the parameter space in $\Omega_m-w$ plane to obtain the 68.3\% and 97.4\% CL regions.
+and scan the parameter space in the $\Omega_m-w$ plane to obtain the 68.3\% and 95.4\% CL regions.
 The result is displayed in Figure \ref{fig_contours}.
 
-\begin{figure*}
-   \centering{
-   %\includegraphics[width=7cm]{Tpcf--contour.eps}
-   %\includegraphics[width=16cm]{Tpcf--contour-others.eps}
-   %\includegraphics[width=16cm,natwidth=52,natheight=40]{fig10.eps}
-   \includegraphics[width=16cm]{fig9.eps}
-   }
-   \caption{\label{fig_contours}
-   Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method, 
-   based on the redshfit evolution of the angular 2pCF shape $\hat\omega_{r_\perp}$.
-   Utilizing the HR4 snapshots data of mock galaxies at five redshifts,
-   the method can lead to very tight cosmological constraint.
-   }
-\end{figure*}
-
 We obtain tight constraints on the two parameters.
-The 2$\sigma$ contour lies within the region $0.23<\Omega_m<0.285$, $-1.1<w<-0.9$.
+The 2$\sigma$ contour lies within the region $0.23<\Omega_m<0.29$, $-1.1<w<-0.9$.
 The two parameters are very strongly degenerated with each other,
@@
 The thin shape of the contour implies that, 
-when combining with the another observational data with a different direction of degeneracy (e.g. CMB, BAO),
+when combining with other observational data with a different direction of degeneracy (e.g. CMB, BAO),
 a very tight combined constraint can be obtained.
@@
 In the case of fixing one parameter at its best-fit value and constraining the other,
-one obtains very small 1$\sigma$ uncertainties of $\delta\Omega_m\approx0.002,\delta w\approx0.01$.
+one obtains very small 1$\sigma$ uncertainties of $\delta\Omega_m\approx0.003,\delta w\approx0.01$.
 
@@
 
-We developed a simple method of measuring the redshift of the shape of the galaxy angular correlation function, $\hat \omega_{r_\perp}$, to constrain cosmology.
-A wrongly adopted cosmology results in redshift-dependent mis-scaling in the constructed galaxy distribution,
-which leads to a redshift-dependent rescaling of $\hat \omega_{r_\perp}(r_\perp)$.
-The signal is sensitive to cosmology and relatively insensitive to the gravitational growth of structure,
+We have developed a method for constraining certain cosmological parameters by measuring the redshift evolution of the shape of the galaxy angular correlation function, $\hat \omega_{r_\perp}$.
+We found that a wrongly adopted cosmology results in a redshift-dependent mis-scaling in the constructed galaxy distribution,
+which in turn leads to a redshift-dependent rescaling of $\hat \omega_{r_\perp}(r_\perp)$.
+The redshift dependent effect is sensitive to cosmology while being relatively insensitive to the gravitational growth of structure,
 the galaxy bias, and the RSD effect.
-We test our method on the HR4 mock galaxies having 457, 406, 352, 206 and 228 million galaxies at redshfits 0, 0.5, 1, 1.5, 2.
+We tested our method on the HR4 mock galaxies having 457, 406, 352, 306 and 228 million galaxies at redshifts 0, 0.5, 1, 1.5, 2.
 Analyzing the redshift evolution of $\hat \omega_{r_\perp}(r_\perp)$ 
@@
 One can also use the 2D 2pCF $\xi(s,\mu)$ 
-as a function of both angular and radial scale to fully probe the scaling effect in 3D galaxy distribution.
+as a function of both angular and radial scale to fully probe the scaling effect in the 3D galaxy distribution.
 
@@
 by directly comparing the theoretical 2pCF and the observed one \citep{Salvador2014,Salvador2016}.
-Our method is simpler and simply utilizes the fact in the correct cosmology the angular 2pCF shape
+Our method is simpler and just uses the fact that in the correct cosmology the angular 2pCF shape
 does not exhibit significant redshift evolution.
@@
 \cite{Li2015,Li2016} shows that using the redshift dependence of the AP effect, 
-one can derive very tight cosmological constraint.
+one can derive very tight cosmological constraints.
 The method presented in this paper studies the redshift evolution of the volume effect.
@@
 These two methods probe different information encoded in the 2pCF 
-and can be combined to have a complete geometric probe of LSS galaxy distribution.
+and can be combined to give a complete geometric probe of the LSS galaxy distribution.
 %Or one can also use the redshift evolution of 2D 2pCF xi(s,mu) to have all information included.
@@
 This method is designed to be applied to current and future LSS surveys,
-with a particular emphasis to the {\it photometric surveys}.
+with a particular emphasis on {\it photometric surveys}.
 The galaxy angular 2pCF in redshift shells is much less affected by the large redshift errors compared wit the 3D 2pCF.
@@
 We utilize a statistical pattern which remains constant at all redshifts;
-this invariance is broken if wrong cosmologies are adopted to construct the galaxy distribution
+this invariance is broken when incorrect cosmologies are adopted to construct the galaxy distribution
 and introduces redshift evolution of geometric distortion.
@@
 
-\bibitem[Blake \& Glazebrook (2003)]{BG03};
+\bibitem[Bernardeaua et al.(2002)]{BCGS2001}
+Bernardeaua, F., Colombib, S., Gaztañagac, E., \& Scoccimarro, R. 
+2002, Phys.Rept., 367, 1
+
+\bibitem[Blake \& Glazebrook (2003)]{BG03}
 Blake, C., \& Glazebrook, K. 2003, ApJ, 594, 665
@@
 
+\bibitem[Nock et al.(2010)]{2010MNRAS.407..520N} Nock, K., Percival, W.~J., \& Ross, A.~J.\ 2010, \mnras, 407, 520
+
 %\bibitem[Kitaura et al.(2015)]{MDPATCHY}
@@
 
-\bibitem[Sutter et al.(2014)]{Sutter2014}
-Sutter, P.M., Pisani, A., Wandelt, B.D., \& Weinberg, D.H. 2014, MNRAS, 443, 2983
-
 \bibitem[Salvador et al. (2014)]{Salvador2014}
@@
 
+\bibitem[Sutter et al.(2014)]{Sutter2014}
+Sutter, P.M., Pisani, A., Wandelt, B.D., \& Weinberg, D.H. 2014, MNRAS, 443, 2983
+
 %\bibitem[Speare et al. (2015)]{Speare2015}

### 2017-04-01 draft/draft2.1.tex
updates

--- 2017-04-01 draft/draft1_cris.tex
@@
 \begin{abstract}
+{\bf Let us use 1) angular CF across the line-of-sight 2) $\xi_{\bot}$ rather than $\omega_{r_{\bot}}$}
 We propose to use the redshift dependence of the galaxy angular 2-point correlation function (2pCF)
@@
    \includegraphics[width=16cm]{fig4_b.eps}
+   \includegraphics[width=16cm]{fig4_c.eps}
+   \includegraphics[width=16cm]{fig4_d.eps}
    }
    \caption{\label{fig_sys}
-  Upper panels: $\omega_{r_\perp}$ (left) and $\hat{\omega}_{r_\perp}$ (middle) are shown for four different halo-mass-cuts, $3\times 10^{11},~1\times 10^{12},~4\times 10^{12},~\&~1\times 10^{13}~M_\odot$,
+  First row: $\omega_{r_\perp}$ (left), $\hat{\omega}_{r_\perp}$ (middle), and $\hat\omega_{r_\perp}(z=z_i)-\hat\omega_{r_\perp}(z=0)$ (right) calculated with the RSD effect included.
+  Second row: $\omega_{r_\perp}$ (left) and $\hat{\omega}_{r_\perp}$ (middle) are shown for four different halo-mass-cuts, $3\times 10^{11},~1\times 10^{12},~4\times 10^{12},~\&~1\times 10^{13}~M_\odot$,
   below which we remove from 2pCF calculation. 
   The right panel shows the difference in $\hat{\omega}_{r_\perp}$ between the $3\times 10^{11}~M_\odot$ mass-cut case and the other mass-cut cases. 
-  Lower panels: $\omega_{r_\perp}$ (left), $\hat{\omega}_{r_\perp}$ (middle), and $\hat\omega_{r_\perp}(z=z_i)-\hat\omega_{r_\perp}(z=0)$ (right) calculated with the RSD effect included.
-   }
+  Third row: The same as the second row panels, except that the RSD effect is considered.
+  Fourth row: The redshift evolution in case of using {\it samples with constant number density} $\bar n=7.3\times 10^{-3} {\rm Mpc}^{-3}h^3$, 
+  and the RSD effect is considered. } 
 \end{figure*}
@@
 such as mass, morphology, color, concentration. 
-Here we test two ``major'' systematical effects; galaxy bias and the RSD effect.
+Here we test two ``major'' systematical effects;  the RSD effect and galaxy bias.
 
@@
 
-\subsubsection{Galaxy Bias}
+\subsubsection{Redshift Space Distortion}
 
@@
 
-Galaxies are biased tracers of the dark matter field;
-more massive galaxies reside in regions with higher density contrast
-and exhibit stronger clustering (i.e. larger bias).
-%In large scale structure surveys, the bias of the galaxy sample is an important fator affecting on the clustering properties of the sample.
-
-We vary the mass cut and check the effect of galaxy bias on $\hat \omega_{r_\perp}$.
-The upper panels of Figure \ref{fig_sys} displays the 2pCF measured from galaxies within a $3175\times3175\times105$ $(h^{-1}\rm Mpc)^3$ volume, taken from the $z=0$ snapshot.
-Four values of minimal mass limits, $3\times 10^{11} M_{\odot}$, $1\times 10^{12} M_{\odot}$, $4\times 10^{12} M_{\odot}$ and $1\times 10^{13} M_{\odot}$,
-are imposed to create samples with different galaxy biases.
-The measured angular 2pCF are displayed.
-
-Different mass cuts result in large variation in the amplitude of the 2pCF (left panel);
-but the shape of the normalised 2pCF remains less affected (middle panel).
-Compared with the sample of $M>3\times 10^{11} M_{\odot}$,
-samples with mass limits of $1\times 10^{12} M_{\odot}$, $4\times 10^{12} M_{\odot}$ and $1\times 10^{13} M_{\odot}$
-have amplitude of 2pCFs enhanced by $10\%,\ 50\%$ and $100\%$, 
-while the change in the shape is only $0.5\%,\ 2\%$ and $4\%$, respectively.
-The effect of galaxy bias becomes much less significant by utilizing the shape of the 2pCF rather than the amplitude.
-
-\subsubsection{Redshift Space Distortion}
-
-\begin{figure*}
-   \centering{
-   %\includegraphics[width=7cm]{Tpcf--contour.eps}
-   %\includegraphics[width=16cm]{Tpcf--contour-others.eps}
-   %\includegraphics[width=16cm,natwidth=52,natheight=40]{fig10.eps}
-   \includegraphics[width=12cm]{fig9.eps}
-   }
-   \caption{\label{fig_contours}
-   Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method, 
-   based on the redshift evolution of the angular 2pCF shape $\hat\omega_{r_\perp}$.
-   Utilizing the HR4 snapshots data of mock galaxies at five redshifts,
-   the method can lead to very tight cosmological constraint.
-   }
-\end{figure*}
-
 The galaxy peculiar velocity contaminates the observed redshift and distorts 
@@
 
-The lower panel of Figure \ref{fig_sys} shows how it affects on the 2pCF.
+The upper panel of Figure \ref{fig_sys} shows how it affects on the 2pCF.
 Comparing this plot with Figure \ref{fig_diffz} one can clearly see the effect of RSD.
@@
 Thankfully, there are some methods for mitigating this effect in photometric surveys using pair-center binning \citep{2010MNRAS.407..520N}.
+
+\subsubsection{Galaxy Bias}
+
+\begin{figure*}
+   \centering{
+   %\includegraphics[width=7cm]{Tpcf--contour.eps}
+   %\includegraphics[width=16cm]{Tpcf--contour-others.eps}
+   %\includegraphics[width=16cm,natwidth=52,natheight=40]{fig10.eps}
+   \includegraphics[width=8cm]{fig9_a.eps}
+   \includegraphics[width=8cm]{fig9_b.eps}
+   }
+   \caption{\label{fig_contours}
+   Left: Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method, 
+   based on the redshift evolution of the angular 2pCF shape $\hat\omega_{r_\perp}$.
+   Utilizing the HR4 snapshots data of mock galaxies at five redshifts,
+   the method can lead to very tight cosmological constraint.
+   Right: The constraints in case that one or two high redshift bins are not used. 
+   }
+\end{figure*}
+
+Galaxies are biased tracers of the dark matter field;
+more massive galaxies reside in regions with higher density contrast
+and exhibit stronger clustering (i.e. larger bias).
+%In large scale structure surveys, the bias of the galaxy sample is an important fator affecting on the clustering properties of the sample.
+
+We vary the mass cut and check the effect of galaxy bias on $\hat \omega_{r_\perp}$.
+The second row of Figure \ref{fig_sys} displays the 2pCF measured from galaxies within a $3175\times3175\times105$ $(h^{-1}\rm Mpc)^3$ volume, taken from the $z=0$ snapshot.
+Four values of minimal mass limits, $3\times 10^{11} M_{\odot}$, $1\times 10^{12} M_{\odot}$, $4\times 10^{12} M_{\odot}$ and $1\times 10^{13} M_{\odot}$,
+are imposed to create samples with different galaxy biases.
+The measured angular 2pCF are displayed.
+
+Different mass cuts result in large variation in the amplitude of the 2pCF (left panel);
+but the shape of the normalised 2pCF remains less affected (middle panel).
+Compared with the sample of $M>3\times 10^{11} M_{\odot}$,
+samples with mass limits of $1\times 10^{12} M_{\odot}$, $4\times 10^{12} M_{\odot}$ and $1\times 10^{13} M_{\odot}$
+have amplitude of 2pCFs enhanced by $10\%,\ 50\%$ and $100\%$, 
+while the change in the shape is only $0.5\%,\ 2\%$ and $4\%$, respectively.
+The effect of galaxy bias becomes much less significant by utilizing the shape of the 2pCF rather than the amplitude.
+
+% {\bf 
+The combined effect of galaxy bias and RSD results in larger systematics.
+Galaxies that are more biased predominantly reside within nonlinear, over-dense regions and thus have larger larger peculiar velocities.
+The third row of Figure \ref{fig_sys} shows that, 
+the difference of $\hat \omega_{r_\perp}$ among different mass cut samples reaches $1.5\%,\ 4\%$ and $8\%$ in the case when including the RSD effect.
+
+Finally, the fourth row of the Figure displays the 
+redshift evolution in case of using samples with constant number density $\bar n=7.3\times 10^{-3} {\rm Mpc}^{-3}h^3$, 
+with the RSD effect considered. %(the error bar is a bit larger since for an illustration purpose we only do the computation for 1/30 of the whole sample).
+We see the redshfit evolution of $\hat \omega_{r_\perp}$ is as small as $\lesssim3\%$.
+
+In summary, the effect of RSD and galaxy bias on the shape of galaxy angular correlation function is, not large, but it is still non-negligible.
+When dealing with real observational data, one should construct simulation mocks in which these effects are reliably modelled, 
+so that the systematics are corrected and will not lead to significant bias in the derived cosmological constraints.
 
@@
 and scan the parameter space in the $\Omega_m-w$ plane to obtain the 68.3\% and 95.4\% CL regions.
-The result is displayed in Figure \ref{fig_contours}.
+The result is displayed in the left panel Figure \ref{fig_contours}.
 
@@
 one obtains very small 1$\sigma$ uncertainties of $\delta\Omega_m\approx0.003,\delta w\approx0.01$.
+
+In case that we do not have high redshfit galaxies, the constraint becomes weaker.
+Figure \ref{fig_contours} displays that, 
+in case that we only use the galaxies at $z=$0, 0.5 and 1, 
+the 2$\sigma$ uncertainties of $\delta\Omega_m\approx0.01,\\ \delta w\approx0.1$ (the other parameter fixed at its best-fit value).
+The area of contour is further enlarged by $\approx 50\%$ if we only use galaxies at $z=$0 and 0.5.
 

### 2017-04-01 draft/draft2.1_cris.tex
updates

--- 2017-04-01 draft/draft2.1.tex
@@
 
-\title{Cosmological constraints from the redshift dependence of the volume effect: galaxy angular 2-point correlation function}
-
-%\author{Xiao-Dong~Li\altaffilmark{1}, Changbom~Park\altaffilmark{1}, J.~E.~Forero-Romero\altaffilmark{2} and Juhan Kim%\altaffilmark{3}}
+\title{Cosmological constraints from the redshift dependence of the volume effect using the galaxy 2-point correlation function across the line-of-sight}
+
+%\author{Xiao-Dong~Li\altaffilmark{1}, Changbom~Park\altaffilmark{1}, J.~E.~Forero-Romero\altaffilmangulatark{2} and Juhan Kim%\altaffilmark{3}}
 %\affil{\altaffilmark{1}School of Physics, Korea Institute for Advanced Study, Heogiro 85, Seoul 130-722, Korea }
@@
 \affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
+\affil{Korea Astronomy and Space Science Institute, Daejeon 305-348, Korea}
 
@@
 \begin{abstract}
-{\bf Let us use 1) angular CF across the line-of-sight 2) $\xi_{\bot}$ rather than $\omega_{r_{\bot}}$}
-We propose to use the redshift dependence of the galaxy angular 2-point correlation function (2pCF)
-to constrain cosmological parameters.
+We propose to use the redshift dependence of the galaxy 2-point correlation function across the line-of-sight (2pCF), $\xi(r_{\bot})$, to constrain cosmological parameters.
 When an incorrect set of parameters is assumed for the coordinate transformation from redshift space to comoving space, 
 it produces {\it redshift-dependent mis-scaling} in the constructed galaxy distribution.
-As a result, we observe a redshift-dependent rescaling of the measured galaxy angular 2pCF.
-Using mock galaxy catalogues (containing millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2) from the Horizon Run 4 N-body simulation, we find that the redshift evolution of the angular 2pCF shape, as a function of scale,
+As a result, we observe a redshift-dependent rescaling of the measured $\xi(r_{\bot})$.
+Using mock galaxy catalogues (containing millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2) from the Horizon Run 4 N-body simulation, we find that the redshift evolution of the $\xi(r_{\bot})$ shape, as a function of scale,
 is sensitive to the adopted cosmological parameters. 
@@
 The discovery of cosmic acceleration \citep{Riess1998,Perl1999} implies the existence of a ``dark energy'' component in the Universe 
-or the breakdown of Einstein's gravity theory on cosmological scales.
+or the breakdown of Einstein's gravity theory on cosmological scales \citep[see ][for a recent review]{2012IJMPD..2130002Y}.
 The theoretical explanation and observational probe of cosmic acceleration has attracted 
@@
 Later, with the advent of large observational spectroscopic programs, this was applied to a series of LSS surveys
-\citep{Outram2004,Blake2011,ChuangWang2012,Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, Jeong2014,Sutter2014,2014ApJ...781...96L,Alam2016, Beutler2016, Sanchez2016}.
+\citep{Outram2004,Blake2011,ChuangWang2012,Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, Jeong2014,Sutter2014,2014ApJ...781...96L,Alam2016, Beutler2016, Sanchez2016}, while considering the detailed effect of systematics for unbiased estimates of $D_A(z)$ and $H(z)$ \citep{2014MNRAS.445....2V,2016MNRAS.tmp.1473R,2016arXiv160302389S}.
+
 Although there have also been alternative approaches using the symmetry properties of galaxy pairs \citep{Marinoni2010,Jennings2011,BB2012}
@@
 The method was applied to BOSS DR12 galaxies \citep{Li2016} to probe the redshift dependence of the AP effect, 
-and we arrive at tight cosmological constraints competitive with mainstream probes of SNIa, BAO, CMB.
+and we arrive at tight cosmological constraints competitive with the mainstream probes of SNIa, BAO, and CMB.
 
 In this paper we continue our exploration of this strategy and present 
-a new method using the redshift evolution of the shape of the {\it galaxy angular 2pCF} as a function of radial scale, $\omega(r_{\bot})$,
+a new method using the redshift evolution of the shape of the 2-point correlation function across the line-of-sight as a function of radial scale, $\xi(r_{\bot})$,
 to constrain cosmology.
-A wrongly adopted cosmology result in {\it redshift-dependent mis-scaling} of the galaxy distribution,
-which leads to redshift-evolution of the shape of $\omega(r_{\bot})$.
-The signal is sensitive to the cosmological parameters and relatively insensitive to the other effects such as the gravitational growth of structure,
+A wrongly adopted cosmology results in {\it redshift-dependent mis-scaling} of the galaxy distribution,
+which leads to redshift-evolution of the shape of $\xi(r_{\bot})$.
+The signal is sensitive to the cosmological parameters but relatively insensitive to the other effects such as the gravitational growth of structure,
 the galaxy bias, and the RSD effect.
-We apply our method to HR4 mock galaxies, using hundreds of millions of galaxies at redshifts $0\leq z\leq2$
+We apply our method to HR4 mock catalogues, using hundreds of millions of galaxies at redshifts $0\leq z\leq2$
 and develop the statistical procedure to constrain cosmological parameters.
@@
 %Or one can also use the redshift evolution of 2D 2pCF xi(s,mu) to have all information included.
-%We developed a method measuring the redshift of the shape of galaxy angular correlation function, $\hat \omega_{r_\perp}$, to constrain cosmology.
+%We developed a method measuring the redshift of the shape of galaxy angular correlation function, $\hat \xi_{r_\perp}$, to constrain cosmology.
 %A wrongly adopted cosmology result in redshift-dependent mis-scaling in the constructed galaxy distribution,
@@
    Their true positions and shapes are plotted in blue dashed lines.
-   When the observer adopts the wrong cosmologies to compute the distance from measured redshifts and infer the positions and shapes of the squares,
-   he/she obtains distorted squares shown as the red solid lines.
+   When the observer adopts incorrect cosmologies when computing distances from redshifts and infering the positions and shapes of the squares,
+   they obtain distorted shapes (red solid lines).
    Right panel shows the redshift evolution of the wrongly estimated angular diameter distance (divided by the correct value).
@@
 When incorrect values of $\Omega_m$ and $w$ are adopted, 
-the inferred $\Delta r_{\parallel}$ and $\Delta r_{\perp}$ are also wrong,
-resulting in wrong estimations of the object's shape (AP effect) and size (volume effect).
+the inferred $\Delta r_{\parallel}$ and $\Delta r_{\perp}$ are also incorrect,
+resulting in erroneous estimation of the object's shape (AP effect) and size (volume effect).
 These effects and their cosmological consequences have been studied in \cite{Li2014,Li2015,Li2016}.
@@
 \end{eqnarray}
-then the shapes of the squares appear distorted (AP effect),
-and their sizes are wrongly estimated (volume effect).
-Cosmological models (i,iii) result in compressed volume elements (in both angular and LOS direction),
+then the shapes of the squares would appear distorted (AP effect),
+and their sizes would be wrongly estimated (volume effect).
+Cosmological models (i,iii) result in compressed volume elements (in both angular and LOS directions),
 and the degree of compression increases with increasing distance;
@@
 the size of objects is mis-estimated and the magnitude of mis-estimation depends on the redshift.
-We use the galaxy angular 2pCF to probe the mis-estimation of angular size, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$.
+We use the galaxy 2pCF across the line-of-sight to probe the mis-estimation of angular size, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$.
 
@@
 The imprint of each of these effects on the large scale structure is different and should be distinguishable.
-In the following section we show that they affect the angular correlation function measurements in different ways, 
+In the following section we show that they affect $\xi(r_{\bot})$ measurements in different ways, 
 and thus can be easily separated.
@@
 
-We use the angular 2pCF as a statistical tool to probe the volume effect.
-The galaxy 2pCF as a function of galaxy separation in the angular direction, $\omega(r_\perp)$, is computed for snapshot data of mock galaxies at redshifts 0.5, 1, 1.5 and 2.
+We use the 2pCF across the line-of-sight as a statistical tool to probe the volume effect.
+The galaxy 2pCF as a function of galaxy separation perpendicular to the LOS, $\xi(r_\perp)$, is computed for snapshot data of mock galaxies at redshifts 0.5, 1, 1.5 and 2.
 We adopt the Landy-Szalay estimator~\citep{1993ApJ...412...64L},
 \begin{equation}
-\omega(r_\perp)=\frac{DD-2DR+RR}{RR}\ ,
+\xi(r_\perp)=\frac{DD-2DR+RR}{RR}\ ,
 \end{equation}
@@
 all separated by a distance defined by $r_\perp\pm\Delta_{r_\perp}$ where we choose $\Delta_{r_\perp}=1h^{-1}\rm Mpc$.
-The random catalogue consists of unclustered points uniformly distributed in the same space as the simulated data.. 
+The random catalogue consists of unclustered points uniformly distributed in the same space as the simulated data. 
 In an effort to reduce the statistical variance of the estimator, we use 50 times as many random points as we have galaxies.
@@
 
-\subsection{Galaxy angular 2pCF: at different redshifts}\label{sec_2pCF_diffz}
+\subsection{Galaxy 2pCF across the line-of-sight: at different redshifts}\label{sec_2pCF_diffz}
 
@@
 %    \includegraphics[height=8cm]{smu.eps}
-    \includegraphics[width=18cm]{fig3.eps}
-    \includegraphics[width=18cm]{fig3_b.eps}
+ %   \includegraphics[width=18cm]{fig3.eps}
+%    \includegraphics[width=18cm]{fig3_b.eps}
+    \includegraphics[width=2\columnwidth]{fig3.eps}
+    \includegraphics[width=2\columnwidth]{fig3_b.eps}
    }
    \caption{\label{fig_diffz}
-  The angular 2pCF ($\omega_{r_\perp}$, left panels), the shape of the angular 2pCF ($\hat{\omega}_{r_\perp}$, middle panels),
-  and the evolution with respect to the $z=0$ value ($\hat{\omega}_{r_{\perp}}(z=z_i) - \hat{\omega}_{r_{\perp}}(z=0)$, right panels). 
+  The 2pCF across the line-of-sight, $\xi_{r_\perp}$ (left panels), the shape of $\hat{\xi}_{r_\perp}$ (middle panels),
+  and the evolution with respect to the $z=0$ value, $\hat{\xi}_{r_{\perp}}(z=z_i) - \hat{\xi}_{r_{\perp}}(z=0)$ (right panels). 
   Upper panels show that in the correct cosmology the redshift evolution of the shape of 2pCF is rather small regardless of the large redshfit evolution of the amplitude, 
-  whereas the lower panels show that, in a wrong cosmology $\Omega_m = 0.05,w=-1.5$, the redshift evolution of $\hat{\omega}_{r_\perp}$ is very significant.
+  whereas the lower panels show that, in a wrong cosmology $\Omega_m = 0.05,w=-1.5$, the redshift evolution of $\hat{\xi}_{r_\perp}$ is very significant.
    }
@@
 
-The upper-left panel of Figure \ref{fig_diffz} displays the angular 2pCF measured from HR4 mock galaxies. % (multiplied by scale $r$) in the five snapshot.
-We multiply $\omega$ by the separation $r_\perp$ to have similar size of statistical uncertainty on all scales.
+The upper-left panel of Figure \ref{fig_diffz} displays the 2pCF across the line-of-sight measured from HR4 mock galaxies. % (multiplied by scale $r$) in the five snapshot.
+We multiply $\xi$ by the separation $r_\perp$ to obtain a similar statistical uncertainty on all scales.
 For convenience we will use the denotation
 \begin{equation}
- \hat \omega_{r_{\perp}} \equiv r_{\perp} \omega.
+ \hat \xi_{r_{\perp}} \equiv r_{\perp} \xi.
 \end{equation}
 
-Among the different redshift bins there is large variation in the amplitude of $\omega(r_\perp)$.
+Among the different redshift bins there is large variation in the amplitude of $\xi(r_\perp)$.
 The amplitude is proportional to the clustering strength, which is affected by the gravitational growth of structures and the galaxy bias.
 The amplitude is highest at $z=0$ where the structures experienced the most growth.
-$\omega(r_\perp)$ increases at $z>1$ with increasing redshift 
-as a reason of increasing galaxy bias.
+$\xi(r_\perp)$ increases at $z>1$ with increasing redshift 
+due to the increasing galaxy bias.
 %leading to stronger clustering strength and higher amplitude of 2pCF.
-%On the contrary, at higher redshift we find $\omega(z=2)>\omega(z=1.5)>\omega(z=1)$,
+%On the contrary, at higher redshift we find $\xi(z=2)>\xi(z=1.5)>\xi(z=1)$,
 %The trend is different from $z=1,1.5,2$,
@@
 Although there is large variation in amplitude between the different redshifts bins, 
-%The shape of $r_\perp\omega$ also evolves with redshift.
-the shape of $\omega_{r_{\perp}}$  remains similar at all redshifts;
+%The shape of $r_\perp\xi$ also evolves with redshift.
+the shape of $\xi_{r_{\perp}}$  remains similar at all redshifts;
 in general it peaks at $r\sim9 h^{-1}\rm Mpc$ and monotonically drops or increases at larger or smaller scales.
@@
 in the middle panel of Figure \ref{fig_diffz} 
-we show the $r_\perp\omega$ normalized by the overall amplitude within 
+we show the $r_\perp\xi$ normalized by the overall amplitude within 
 $5h^{-1}{\rm Mpc} < r < 40h^{-1}{\rm Mpc}$
-(here after $\hat \omega_{r_\perp}$):
+(here after $\hat \xi_{r_\perp}$):
 \begin{equation}
- \hat \omega_{ r_\perp} \equiv  \frac{ {r_\perp\omega}(r_{\perp})}{ \int_{r_{\perp, \rm min}}^{r_{\perp, \rm max}}r_{\perp} \omega(r_{\perp}) d r_{\perp} / (r_{\perp,\rm max}-r_{\perp,\rm min}) },
+ \hat \xi_{ r_\perp} \equiv  \frac{ {r_\perp\xi}(r_{\perp})}{ \int_{r_{\perp, \rm min}}^{r_{\perp, \rm max}}r_{\perp} \xi(r_{\perp}) d r_{\perp} / (r_{\perp,\rm max}-r_{\perp,\rm min}) },
 \end{equation}
@@
 On scales larger than $40 h^{-1}$ Mpc,
-the analytical modeling of the shape of the angular 2pCF is relatively well understood;
+the analytical modeling of the shape of $\xi_{r_{\perp}}$ is relatively well understood;
 one can just fit the 2pCF with the theoretical predictions \citep{BCGS2001,Salvador2014,Salvador2016} 
@@
 
-In the upper-middle panel, the overlapping of $\hat\omega_{r_{\perp}}$
+In the upper-middle panel, the overlapping of $\hat\xi_{r_{\perp}}$
 clearly show the minimal redshift evolution of the shape.
@@
 In real observations we may be selecting {\it different} types of galaxies at different redshifts.
-Considering this fact in the comparison of $\hat\omega_{r_\perp}$ 
+Considering this fact in the comparison of $\hat\xi_{r_\perp}$ 
 we compare subsamples of galaxies at {\it different} locations.
-As an example, if at $z=0$ we take $\hat\omega_{r_\perp}$ measured within $0h^{-1}{\rm Mpc}<Z<105 h^{-1}{\rm Mpc}$,
+As an example, if at $z=0$ we take $\hat\xi_{r_\perp}$ measured within $0h^{-1}{\rm Mpc}<Z<105 h^{-1}{\rm Mpc}$,
 at higher redshifts we then adopt measurement within $105h^{-1}{\rm Mpc}<Z<210 h^{-1}{\rm Mpc}$ for a comparison.
-%and take the difference between them to get $\delta \hat{r_\perp\omega}$.
+%and take the difference between them to get $\delta \hat{r_\perp\xi}$.
 %So we are always comparing 2pCF measured from different samples of galaxies.
 If we simply compare the 2pCF of the {\it same} subsample of galaxies at different redshifts, 
-one would significantly underestimate the statistical uncertainty of $\delta \hat{\omega}_{r_\perp}$ by ignoring cosmic variance.
+one would significantly underestimate the statistical uncertainty of $\delta \hat{\xi}_{r_\perp}$ by ignoring cosmic variance.
 %The error bars and covariance are always estimated in this way to take the cosmic variance into consideration.
@@
 
-\subsection{Galaxy angular 2pCF: cosmological effect }
-
-The angular 2pCF of galaxy positions constructed in a wrongly assumed cosmology $\Omega_m=0.05,\ w=-1.5$
+\subsection{Galaxy 2pCF across the line-of-sight: cosmological effect }
+
+The 2pCF across the line-of-sight for galaxy positions constructed in a wrongly assumed cosmology $\Omega_m=0.05,\ w=-1.5$
 is displayed in the lower panels of Figure \ref{fig_diffz}.
 The mis-scaling uniformly shifts the clustering pattern on all scales, 
-leading to a biased $\hat \omega_{r_\perp}$, which is 
-related with the true $\hat \omega$ as
+leading to a biased $\hat \xi_{r_\perp}$, which is 
+related with the true $\hat \xi$ as
 \begin{equation}
- \hat \omega_{r_\perp,\rm wrong}(r) = \hat \omega_{r_\perp, \rm correct}(\alpha_{\perp} r),
+ \hat \xi_{r_\perp,\rm wrong}(r) = \hat \xi_{r_\perp, \rm correct}(\alpha_{\perp} r),
 \end{equation}
@@
 The redshift evolution of $\alpha_{\perp}$ leads to redshift evolution of 
-$\hat \omega_{r_\perp, \rm correct}$,
-%Lower panels of Figure \ref{fig_diffz} shows the $r_\perp\omega$ in five 
+$\hat \xi_{r_\perp, \rm correct}$,
+%Lower panels of Figure \ref{fig_diffz} shows the $r_\perp\xi$ in five 
 %snapshots, in case that the cosmology $\Omega_m=0.05,\ w=-1.5$ 
@@
 the peak location is shifted from $\sim9h^{-1} \rm Mpc$ to $\sim15 h^{-1}\rm Mpc$ at $z=2$,
-as a result of the fact that the angular separation is upscaled by $71.7\%$.
+as a result of the fact that the $\hat\xi_{r_{\perp}}$ separation is upscaled by $71.7\%$.
 Correspondingly, the right panel shows that, 
-compared with $\hat \omega_{r_\perp}$ at $z=0$ there is a 20-40\% change at higher redshifts.
-
-The mis-scaling not only changes the shape of the 2pCF but also modifies its amplitude. %The amplitude of $r_\perp\omega$ is amplified due to the stretch of scale.
+compared with $\hat \xi_{r_\perp}$ at $z=0$ there is a 20-40\% change at higher redshifts.
+
+The mis-scaling not only changes the shape of the 2pCF but also modifies its amplitude. %The amplitude of $r_\perp\xi$ is amplified due to the stretch of scale.
 As is shown in the left panel, due to the stretch of scale the amplitude is enhanced at higher redshifts;
@@
    \centering{
-   \includegraphics[width=16cm]{fig4_a.eps}
-   \includegraphics[width=16cm]{fig4_b.eps}
-   \includegraphics[width=16cm]{fig4_c.eps}
-   \includegraphics[width=16cm]{fig4_d.eps}
+   \includegraphics[width=2\columnwidth]{fig4_a.eps}
+   \includegraphics[width=2\columnwidth]{fig4_b.eps}
+   \includegraphics[width=2\columnwidth]{fig4_c.eps}
+   \includegraphics[width=2\columnwidth]{fig4_d.eps}
    }
    \caption{\label{fig_sys}
-  First row: $\omega_{r_\perp}$ (left), $\hat{\omega}_{r_\perp}$ (middle), and $\hat\omega_{r_\perp}(z=z_i)-\hat\omega_{r_\perp}(z=0)$ (right) calculated with the RSD effect included.
-  Second row: $\omega_{r_\perp}$ (left) and $\hat{\omega}_{r_\perp}$ (middle) are shown for four different halo-mass-cuts, $3\times 10^{11},~1\times 10^{12},~4\times 10^{12},~\&~1\times 10^{13}~M_\odot$,
+  First row: $\xi_{r_\perp}$ (left), $\hat{\xi}_{r_\perp}$ (middle), and $\hat\xi_{r_\perp}(z=z_i)-\hat\xi_{r_\perp}(z=0)$ (right) calculated with the RSD effect included.
+  Second row: $\xi_{r_\perp}$ (left) and $\hat{\xi}_{r_\perp}$ (middle) are shown for four different halo-mass-cuts, $3\times 10^{11},~1\times 10^{12},~4\times 10^{12},~\&~1\times 10^{13}~M_\odot$, 
   below which we remove from 2pCF calculation. 
-  The right panel shows the difference in $\hat{\omega}_{r_\perp}$ between the $3\times 10^{11}~M_\odot$ mass-cut case and the other mass-cut cases. 
+  The right panel shows the difference in $\hat{\xi}_{r_\perp}$ between the $3\times 10^{11}~M_\odot$ mass-cut case and the other mass-cut cases. 
   Third row: The same as the second row panels, except that the RSD effect is considered.
@@
 
-In Sec. \ref{sec_2pCF_diffz} we showed that $\hat \omega_{r_\perp}$ measured from the
+In Sec. \ref{sec_2pCF_diffz} we showed that $\hat \xi_{r_\perp}$ measured from the
 constant mass cut samples at different redshifts show good agreement.
-The gravitational growth of structure will not have a large impact on $\hat \omega_{r_\perp}$ on scales $\gtrsim5 h^{-1}$ Mpc,
+The gravitational growth of structure will not have a large impact on $\hat \xi_{r_\perp}$ on scales $\gtrsim5 h^{-1}$ Mpc,
 yet there are many other factors that may induce redshift evolution
@@
 
-%The same as \cite{Li2014,Li2015,Li2016} we need to correct for the redshift evolution of $r_\perp\omega$ caused by effects other than the cosmological effect.
+%The same as \cite{Li2014,Li2015,Li2016} we need to correct for the redshift evolution of $r_\perp\xi$ caused by effects other than the cosmological effect.
 
 %Figure \ref{fig_diffz} already shows that, the growth of structure, especially in low redshift and on non-linear scales, 
-%changes the shape of $r_\perp\omega$ and caused relative enhancement on $r\lesssim2 h^{-1}\rm Mpc$.
+%changes the shape of $r_\perp\xi$ and caused relative enhancement on $r\lesssim2 h^{-1}\rm Mpc$.
 %So we limit the region of scale to $r>5h^{-1}\rm Mpc$ to minimize its effect.
@@
 %    \includegraphics[height=8cm]{smu.eps}
-    \includegraphics[width=14cm]{fig5.eps}
+    \includegraphics[width=2\columnwidth]{fig5.eps}
    }
    \caption{\label{fig_cosmo}
-    $\hat{\omega}_{r_\perp}$ (upper panels) and $\hat{\omega}_{r_\perp}(z=z_i) - \hat{\omega}_{r_\perp}(z=0)$ (lower panels) at several redshifts,
+    $\hat{\xi}_{r_\perp}$ (upper panels) and $\hat{\xi}_{r_\perp}(z=z_i) - \hat{\xi}_{r_\perp}(z=0)$ (lower panels) at several redshifts,
     for four wrong cosmologies.
-    The redshift evolution of the angular 2pCF shape in these wrong cosmologies are detected at high CL.
+    The redshift evolution of the $\hat\xi_{r_{\perp}}$ shape in these wrong cosmologies are detected at high CL.
    }
@@
 The amplitude of the measured 2pCF is enhanced by $\sim 10\%$ when considering the RSD effect 
-and the slop of $\hat\omega_{r_\perp}$ is suppressed.
-However, the redshift evolution of $\hat\omega_{r_\perp}$ remains small,  $\lesssim4\%$ at $0.5\leq z \leq 2$.
+and the slop of $\hat\xi_{r_\perp}$ is suppressed.
+However, the redshift evolution of $\hat\xi_{r_\perp}$ remains small,  $\lesssim4\%$ at $0.5\leq z \leq 2$.
 Therefore RSD should not significantly affect the application of our method, as long as its redshift evolution is small;
@@
 %If looking at the redshift evolution,
-%the curves $\hat{r_\perp\omega} - \hat{r_\perp\omega}(z=0)$ displayed in the right panel,
+%the curves $\hat{r_\perp\xi} - \hat{r_\perp\xi}(z=0)$ displayed in the right panel,
 %they changed a lot compared with the case of no RSD effect (the right panel of Figure \ref{fig_diffz}),
@@
    Left: Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method, 
-   based on the redshift evolution of the angular 2pCF shape $\hat\omega_{r_\perp}$.
+   based on the redshift evolution of the shape of the 2pCF across the line-of-sight  $\hat\xi_{r_\perp}$.
    Utilizing the HR4 snapshots data of mock galaxies at five redshifts,
@@
 
-We vary the mass cut and check the effect of galaxy bias on $\hat \omega_{r_\perp}$.
+We vary the mass cut and check the effect of galaxy bias on $\hat \xi_{r_\perp}$.
 The second row of Figure \ref{fig_sys} displays the 2pCF measured from galaxies within a $3175\times3175\times105$ $(h^{-1}\rm Mpc)^3$ volume, taken from the $z=0$ snapshot.
@@
 are imposed to create samples with different galaxy biases.
-The measured angular 2pCF are displayed.
+The measured 2pCF across the line-of-sight are displayed.
 
@@
 The third row of Figure \ref{fig_sys} shows that, 
-the difference of $\hat \omega_{r_\perp}$ among different mass cut samples reaches $1.5\%,\ 4\%$ and $8\%$ in the case when including the RSD effect.
+the difference of $\hat \xi_{r_\perp}$ among different mass cut samples reaches $1.5\%,\ 4\%$ and $8\%$ in the case when including the RSD effect.
 
@@
 with the RSD effect considered. %(the error bar is a bit larger since for an illustration purpose we only do the computation for 1/30 of the whole sample).
-We see the redshfit evolution of $\hat \omega_{r_\perp}$ is as small as $\lesssim3\%$.
-
-In summary, the effect of RSD and galaxy bias on the shape of galaxy angular correlation function is, not large, but it is still non-negligible.
+We see the redshfit evolution of $\hat \xi_{r_\perp}$ is as small as $\lesssim3\%$.
+
+In summary, the effect of RSD and galaxy bias on the shape of the galaxy correlation function across the line-of-sight is not large, but is non-negligible.
 When dealing with real observational data, one should construct simulation mocks in which these effects are reliably modelled, 
@@
 
-Adopting the correct cosmological model will resulting in minimal evolution of the normalised 2pCF.
+Adopting the correct cosmological model will result in minimal evolution of the normalised 2pCF.
 Thus we proceed to construct a quantitative likelihood estimator that reflects this property.
 The procedure here is very similar to \cite{Li2014,Li2015,Li2016}.
-We compare the high redshift $\hat\omega_{r_\perp}$ and the lowest redshift measurement,
+We compare the high redshift $\hat\xi_{r_\perp}$ and the lowest redshift measurement,
 \begin{equation}
- \delta \hat{\omega_{r_\perp}}(z_i,z_1) \equiv \hat{\omega_{r_\perp}}(z_i) - \hat{\omega_{r_\perp}}(z_1),
+ \delta \hat{\xi_{r_\perp}}(z_i,z_1) \equiv \hat{\xi_{r_\perp}}(z_i) - \hat{\xi_{r_\perp}}(z_1),
 \end{equation}
 and design the likelihood function to quantify
-the redshift evolution of $\hat\omega_{r_\perp}$:
+the redshift evolution of $\hat\xi_{r_\perp}$:
 \begin{equation}\label{eq:chisq1}
@@
 where $n_z$ is the number of redshifts which is 5 in this analysis, 
-$n_r$ is number of binning in $\hat{\omega}_{r_\perp}(r_\perp)$,
+$n_r$ is number of binning in $\hat{\xi}_{r_\perp}(r_\perp)$,
 which is 35 since we have $r_\perp$ bins 
 with width $1h^{-1}\rm Mpc$ in a range of $5h^{-1}{\rm Mpc}\leq r_\perp\leq 40h^{-1}{\rm Mpc}$.
-${\bf p}(z_i,r_{j})$ is the redshift evolution of the angular correlation function shape with systematic effects subtracted
+${\bf p}(z_i,r_{j})$ is the redshift evolution of the correlation function shape with systematic effects subtracted
 \begin{eqnarray}\label{eq:bfp}
- {\bf p}(z_i,r_{j}) \equiv&\ \delta \hat{\omega_\perp}(z_i,z_1,r_j) - \delta \hat{\omega}_{r_\perp,\rm sys}(z_i,z_1,r_j)
+ {\bf p}(z_i,r_{j}) \equiv&\ \delta \hat{\xi_\perp}(z_i,z_1,r_j) - \delta \hat{\xi}_{r_\perp,\rm sys}(z_i,z_1,r_j)
 \end{eqnarray}
@@
 For the cosmologies $\Omega_m=0.15,w=-1$ and $\Omega_m=0.26,w=-1.5$,
-the stretch of structure leads to a shallower slope of $\hat{\omega}_{r_\perp}$ at higher redshift.
+the stretch of structure leads to a shallower slope of $\hat{\xi}_{r_\perp}$ at higher redshift.
 %the shallower.
@@
 
-We have developed a method for constraining certain cosmological parameters by measuring the redshift evolution of the shape of the galaxy angular correlation function, $\hat \omega_{r_\perp}$.
+We have developed a method for constraining certain cosmological parameters by measuring the redshift evolution of the shape of the galaxy correlation function across the line-of-sight, $\hat \xi_{r_\perp}$.
 We found that a wrongly adopted cosmology results in a redshift-dependent mis-scaling in the constructed galaxy distribution,
-which in turn leads to a redshift-dependent rescaling of $\hat \omega_{r_\perp}(r_\perp)$.
+which in turn leads to a redshift-dependent rescaling of $\hat \xi_{r_\perp}(r_\perp)$.
 The redshift dependent effect is sensitive to cosmology while being relatively insensitive to the gravitational growth of structure,
@@
 We tested our method on the HR4 mock galaxies having 457, 406, 352, 306 and 228 million galaxies at redshifts 0, 0.5, 1, 1.5, 2.
-Analyzing the redshift evolution of $\hat \omega_{r_\perp}(r_\perp)$ 
+Analyzing the redshift evolution of $\hat \xi_{r_\perp}(r_\perp)$ 
 on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
@@
 
-In this analysis we restrict our focus to the rescaling in the angular direction.
+In this analysis we restrict our focus to the rescaling in the direction perpendicular to line-of-sight .
 %The angular correlation function is adopted as a statistical tool to probing the scaling effect in the angular direction.
@@
 by directly comparing the theoretical 2pCF and the observed one \citep{Salvador2014,Salvador2016}.
-Our method is simpler and just uses the fact that in the correct cosmology the angular 2pCF shape
+Our method is simpler and just uses the fact that in the correct cosmology the shape of the 2pCF across the line-of-sight
 does not exhibit significant redshift evolution.
@@
 with a particular emphasis on {\it photometric surveys}.
-The galaxy angular 2pCF in redshift shells is much less affected by the large redshift errors compared wit the 3D 2pCF.
+The galaxy 2pCF across the line-of-sight in redshift shells is much less affected by the large redshift errors compared wit the 3D 2pCF.
 DES will probe hundreds of millions of galaxies at $z\lesssim1.5$, 
@@
 
-\appendix
-
-\
+%\appendix
+%\
 
@@
 
+\bibitem[Ross et al.(2016)]{2016MNRAS.tmp.1473R} Ross, A.~J., Beutler, F., Chuang, C.-H., et al.\ 2016, \mnras,
+
 \bibitem[Ryden(1995)]{Ryden1995}
@@
 %Sanchez, A. G., Kazin, E. A., Beutler, F., et al. 2013, MNRAS, 433, 1202
+
+\bibitem[Sabiu \& Song(2016)]{2016arXiv160302389S} Sabiu, C.~G., \& Song, Y.-S.\ 2016, arXiv:1603.02389
 
@@
 
+\bibitem[Vargas-Maga{\~n}a et al.(2014)]{2014MNRAS.445....2V} Vargas-Maga{\~n}a, M., Ho, S., Xu, X., et al.\ 2014, \mnras, 445, 2
+
 \bibitem[Viana \& Liddle(1996)]{VL1996}
@@
 
+\bibitem[Yoo \& Watanabe(2012)]{2012IJMPD..2130002Y} Yoo, J., \& Watanabe, Y.\ 2012, International Journal of Modern Physics D, 21, 1230002
+
 %\bibitem[York et al.(2000)]{York et al. 2000}

### 2017-04-01 draft/draft2.tex
updates

--- 2017-04-01 draft/draft2.1.tex
@@
 \begin{abstract}
-{\bf Let us use 1) angular CF across the line-of-sight 2) $\xi_{\bot}$ rather than $\omega_{r_{\bot}}$}
 We propose to use the redshift dependence of the galaxy angular 2-point correlation function (2pCF)
@@
   Fourth row: The redshift evolution in case of using {\it samples with constant number density} $\bar n=7.3\times 10^{-3} {\rm Mpc}^{-3}h^3$, 
-  and the RSD effect is considered. } 
+  and the RSD effect is considered (the error bar is a bit larger since for an illustration purpose we only do the computation for 1/30 of the whole sample). } 
 \end{figure*}
@@
    %\includegraphics[width=16cm,natwidth=52,natheight=40]{fig10.eps}
-   \includegraphics[width=8cm]{fig9_a.eps}
-   \includegraphics[width=8cm]{fig9_b.eps}
+   \includegraphics[width=12cm]{fig9.eps}
    }
    \caption{\label{fig_contours}
-   Left: Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method, 
+   Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method, 
    based on the redshift evolution of the angular 2pCF shape $\hat\omega_{r_\perp}$.
@@
    the method can lead to very tight cosmological constraint.
-   Right: The constraints in case that one or two high redshift bins are not used. 
    }
@@
 with the RSD effect considered. %(the error bar is a bit larger since for an illustration purpose we only do the computation for 1/30 of the whole sample).
-We see the redshfit evolution of $\hat \omega_{r_\perp}$ is as small as $\lesssim3\%$.
+We see the redshfit evolution of $\hat \omega_{r_\perp}$ is still as small as $\lesssim5\%$, similar to the case of using constant mass cut sample.
 
@@
 and scan the parameter space in the $\Omega_m-w$ plane to obtain the 68.3\% and 95.4\% CL regions.
-The result is displayed in the left panel Figure \ref{fig_contours}.
+The result is displayed in Figure \ref{fig_contours}.
 
@@
 one obtains very small 1$\sigma$ uncertainties of $\delta\Omega_m\approx0.003,\delta w\approx0.01$.
-
-In case that we do not have high redshfit galaxies, the constraint becomes weaker.
-Figure \ref{fig_contours} displays that, 
-in case that we only use the galaxies at $z=$0, 0.5 and 1, 
-the 2$\sigma$ uncertainties of $\delta\Omega_m\approx0.01,\\ \delta w\approx0.1$ (the other parameter fixed at its best-fit value).
-The area of contour is further enlarged by $\approx 50\%$ if we only use galaxies at $z=$0 and 0.5.
 

### 2017-04-01 draft/draft3.1.tex
updates

--- 2017-04-01 draft/draft2.1_cris.tex
@@
 As a result, we observe a redshift-dependent rescaling of the measured $\xi(r_{\bot})$.
-Using mock galaxy catalogues (containing millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2) from the Horizon Run 4 N-body simulation, we find that the redshift evolution of the $\xi(r_{\bot})$ shape, as a function of scale,
+Using mock galaxy catalogues (containing hundreds of millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2) from the Horizon Run 4 N-body simulation, we find that the redshift evolution of the $\xi(r_{\bot})$ shape, as a function of scale,
 is sensitive to the adopted cosmological parameters. 
@@
 \begin{equation}
- \hat \xi_{r_{\perp}} \equiv r_{\perp} \xi.
+ \xi_{r_{\perp}} \equiv r_{\perp} \xi.
 \end{equation}
@@
 
-The mis-scaling not only changes the shape of the 2pCF but also modifies its amplitude. %The amplitude of $r_\perp\xi$ is amplified due to the stretch of scale.
+The mis-scaling not only changes the shape of the 2pCF but also changes the value of $ \xi_{r_\perp}$. %The amplitude of $r_\perp\xi$ is amplified due to the stretch of scale.
 As is shown in the left panel, due to the stretch of scale the amplitude is enhanced at higher redshifts;
-the higher the redshift, the greater the enhancement.%the amplitude monotonically increases as a function of redshift.
+the higher the redshift, the greater the enhancement
+\footnote{The value of $\xi$ is not affected by the mis-scaling. 
+But since we are using $r_\perp\xi$ rather than $\xi$, the y-axis values are affected. 
+For a 20\% up-rescaling, the peak value of $r_\perp\xi$ is also increased by 20\%.}.%the amplitude monotonically increases as a function of redshift.
 
@@
    \includegraphics[width=8cm]{fig9_b.eps}
+   \includegraphics[width=8cm]{fig9_c.eps}
+   \includegraphics[width=8cm]{fig9_d.eps}
    }
    \caption{\label{fig_contours}
-   Left: Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method, 
-   based on the redshift evolution of the shape of the 2pCF across the line-of-sight  $\hat\xi_{r_\perp}$.
-   Utilizing the HR4 snapshots data of mock galaxies at five redshifts,
-   the method can lead to very tight cosmological constraint.
-   Right: The constraints in case that one or two high redshift bins are not used. 
+   Upper left: Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method, 
+   based on the redshift evolution of the angular 2pCF shape $\hat\omega_{r_\perp}$.
+   The green point denotes our fiducial cosmological model and the contours denote the statistical error.
+   Utilizing the HR4 snapshots data (containing hundreds of millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2),
+   the method lead to very tight cosmological constraint.
+   Upper right: The constraints in case that one or two high redshift bins are not used.
+   Lower left: The 95.4\% likelihood contours using different clustering scales.
+   Lower right: A comparison of the constraint with the cosmological constraints from the current observational data.
    }
@@
 We vary the mass cut and check the effect of galaxy bias on $\hat \xi_{r_\perp}$.
-The second row of Figure \ref{fig_sys} displays the 2pCF measured from galaxies within a $3175\times3175\times105$ $(h^{-1}\rm Mpc)^3$ volume, taken from the $z=0$ snapshot.
+The second row of Figure \ref{fig_sys} displays the 2pCF measured from galaxies within a $3150\times3150\times105$ $(h^{-1}\rm Mpc)^3$ volume, taken from the $z=0$ snapshot.
 Four values of minimal mass limits, $3\times 10^{11} M_{\odot}$, $1\times 10^{12} M_{\odot}$, $4\times 10^{12} M_{\odot}$ and $1\times 10^{13} M_{\odot}$,
@@
 
-In summary, the effect of RSD and galaxy bias on the shape of the galaxy correlation function across the line-of-sight is not large, but is non-negligible.
-When dealing with real observational data, one should construct simulation mocks in which these effects are reliably modelled, 
-so that the systematics are corrected and will not lead to significant bias in the derived cosmological constraints.
+%In summary, the effect of RSD and galaxy bias on the shape of the galaxy correlation function across the line-of-sight is not large, but is non-negligible.
+%When dealing with real observational data, one should construct simulation mocks in which these effects are reliably modelled, 
+%so that the systematics are corrected and will not lead to significant bias in the derived cosmological constraints.
 
@@
 %3.000e11', '1.000e12', '4.000e12',  '1.000e13
+
+\subsubsection{More discussion}
+
+In summary, we aim to minimise the redshift evolution of the shape of the normalised angular 2pcf; 
+the shape change is dramatic when considering a cosmology much deviated from the fiducial model.
+However even in the case of the correct cosmology there remains a small signal, due to growth of structures, RSD and galaxy bias. 
+These systematics are removed with the aid of simulations.
+The procedure of the correction of systematics is similar to what was implemented in our previous papers \cite{Li2014,Li2015,Li2016}.
+
+The systematics are estimated from a simulation conducted using a particular cosmology. 
+There could be a bias in the estimation if the simulation cosmology is different from the truth. 
+The bias would not be serious if the simulation cosmology turns out to be consistent with the best-fit cosmological parameters obtained from the analysis \cite{Li2016}. 
+In the case that there is a large discrepancy between the simulation cosmology and the best-fit cosmology, one needs to adjust the simulation cosmology and re-do the analysis.
+
+A more precise approach would involve estimating the systematic effect from a set of simulations covering the relevant volume of the parameter space. 
+This would remove the remaining uncertainty associated with the cosmological dependence. 
+This approach would also enable the estimation of the $systematic\ error$, 
+which could be important when the sample size is large enough and the systematic error becomes as small as the $statistical\ error$.
+
+The third row of Figure \ref{fig_sys} shows that, 
+if having a large difference in bias between the samples,
+there is a large systematic variation on small scales. 
+This means that an accurate modelling of systematics from simulations is required. 
+To avoid the possible difficulty, one can conduct the analysis using a volume-limited sample, 
+where the redshift evolution of galaxy properties is small and the systematic effect from RSD and galaxy bias is also small,
+as shown by the fourth row of Figure \ref{fig_sys}.
+
+To avoid the large systematics in the nonlinear regime, 
+another solution would be to increase the scale of analysis to larger separations where the non-linear effect is becoming subdominant. 
+Figure \ref{fig_sys} shows that, 
+on scales of $s=20-50 h^{-1} {\rm Mpc}$ the systematic effect is 2-3 times smaller than that of $s=5-20 h^{-1} {\rm Mpc}$. 
+Actually, we tested and found that, using $s = 5-40 h^{-1} {\rm Mpc}$ and $20-40 h^{-1} {\rm Mpc}$, 
+yields cosmological constraints that are pretty close to each other (see \S 4).
+
+We do not consider the systematic effects in case of non-standard cosmological scenarios such as modified gravity and warm dark energy. 
+These topics go beyond the scope of this work, and they are worthy future investigations.
 
@@
 
-In case that we do not have high redshfit galaxies, the constraint becomes weaker.
-Figure \ref{fig_contours} displays that, 
-in case that we only use the galaxies at $z=$0, 0.5 and 1, 
+The simulation sample used in this analysis reaches $z=2$.
+The constraint becomes weaker if we limit the highest redshift of the samples.
+The upper right panel displays that, 
+in case that we exclude the $z=2$ galaxies, 
 the 2$\sigma$ uncertainties of $\delta\Omega_m\approx0.01,\\ \delta w\approx0.1$ (the other parameter fixed at its best-fit value).
-The area of contour is further enlarged by $\approx 50\%$ if we only use galaxies at $z=$0 and 0.5.
+The area of contour is further enlarged by $\approx 50\%$ if we only use galaxies at $z=$0, 0.5 and 1.
+
+So far we simply follow the convention of \cite{Li2016} and adopts $5\hMpc <s< 40\hMpc$. 
+As discussed in the \S 4.3.3, one may want to avoid large systematics in the non-linear regime. 
+In this case one can adopt $20\hMpc<s<40\hMpc$,
+which significantly reduces the systematic effects while not much weaken the power of the final constraints,
+as shown by the lower left panel of Figure \ref{fig_contours}.
+
+The choice of the redshift width $105 \hMpc$ is also slightly little arbitrary. 
+It should be larger than the distance distortion from the RSD and redshift errors.
+The optimistic scheme of clustering scales and redshift width should depend on the specific galaxy sample used in the analysis. 
+One could adjust them to have a good balance between the power of cosmological constraint and the size of systematic effect.
+
+Finally, to be connected with the real observations, 
+the lower right panel displays the constraints from Planck CMB (dotted blue, \cite{Planck2015}),
+the AP analysis using BOSS DR12 galaxies (solid magenta, \cite{Li2016}),
+and the joint constraint $\Omega_m = 0.301 \pm 0.006,\ w=-1.054 \pm 0.025$ 
+obtained using the CMB+SNIa+BAO+AP (dashed black, \cite{6dFGS,MGS,Riess2011,JLA,Anderson2013,Li2016}).
+
+The predicted constraints from this method clearly wins due to the large sample size.
+The total number of galaxies used in this work is 1,749 million,
+which is 1,000 times of the BOSS DR12 sample size.
+So the constrained area is also $\sim 30$ times smaller.
+Such a large sample size will be enabled by LSST (the Large Synoptic Survey Telescope) \footnote{https://www.lsst.org/}, 
+which probe tens of billions of galaxies at $z\lesssim2$.
+
+%combined with an AP analysis using BOSS DR12 galaxies.
+This represents the current scenario of cosmological constraints from observations.
+A new plot is added to compare it with the constraint from our method.
+%the JLA SNIa sample (green area, ),
+%the BAO measurement from BOSS DR11 galaxies (bright yellow, ),
+%\footnote{The CMASS and LOWZ samples from BOSS DR11 have a sky coverage of 8\,377 $\rm deg^2$ and a completeness of 97\%.
+%They are very close to the DR12 samples.},
+%a combination of the BOSS DR11 BAO and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ (dark yellow, ),
+%and the full-mission Planck observations of temperature and polarization anisotropies, released in 2015 (blue, \cite{Planck2015})
 
@@
 
+In our early work of \cite{Li2015,Li2016}, 
+we proposed to use the angular-dependence of the galaxy clustering to apply an AP test and derive cosmological constraints. 
+In contrast, in this work we focus on the scale-dependence of the clustering. 
+The two methods focus on different parts of the clustering information, and the constraints derived from the them should be fairly independent.
+But it is still suggested to have an estimation of the covariance between them in case one is using both methods to do an analysis. 
+An alternative way is to investigate the redshift evolution of the correlation map $\xi(s,\mu)$ as a function of both scale and direction, which captures all the information.
+
 There are already works using the angular 2pCF to constrain cosmology
@@
 The galaxy 2pCF across the line-of-sight in redshift shells is much less affected by the large redshift errors compared wit the 3D 2pCF.
-DES will probe hundreds of millions of galaxies at $z\lesssim1.5$, 
+The Dark Energy Survey will probe hundreds of millions of galaxies at $z\lesssim1.5$
+\footnote{https://www.darkenergysurvey.org/}, 
 and LSST will probe tens of billions of galaxies at $z\lesssim2$.
@@
 and introduces redshift evolution of geometric distortion.
-The systematic effects can be corrected by performing a N-body simulation 
+The systematic effects can be corrected by performing an N-body simulation 
 in a cosmology with values of parameters close enough to the underlying correct one.
@@
 
-%\bibitem[Ade et al. (2015)]{Planck2015}
-%Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. arXiv:1502.01589
+\bibitem[Ade et al. (2015)]{Planck2015}
+Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. arXiv:1502.01589
 
@@
 
-%\bibitem[Anderson et al.(2013)]{Anderson2013}
-%Anderson, L., Aubourg, \'E., \& Bailey, S. et al. 2014, MNRAS, 441, 24
+\bibitem[Anderson et al.(2013)]{Anderson2013}
+Anderson, L., Aubourg, \'E., \& Bailey, S. et al. 2014, MNRAS, 441, 24
 
@@
 
-%\bibitem[Betoule et al.(2014)]{JLA}
-%Betoule, M., Kessler, R., \& Guy, J., et al. 2014, A\&A, 568, 32
-
-%\bibitem[Beutler et al.(2011)]{6dFGS}
+\bibitem[Betoule et al.(2014)]{JLA}
+Betoule, M., Kessler, R., \& Guy, J., et al. 2014, A\&A, 568, 32
+
+\bibitem[Beutler et al.(2011)]{6dFGS}
 Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017
@@
 
-%\bibitem[Riess et al.(2011)]{Riess2011}
-%Riess, A.G., Macri, L., \& Casertano, S., et al. 2011, ApJ, 730, 119
+\bibitem[Riess et al.(2011)]{Riess2011}
+Riess, A.G., Macri, L., \& Casertano, S., et al. 2011, ApJ, 730, 119
 %A 3\% Solution: Determination of the Hubble Constant with the Hubble Space Telescope and Wide Field Camera
@@
 
-%\bibitem[Ross et al.(2015)]{MGS}
-%Ross, A.J., Samushia, L., \& Howlett, C., et al. 2015, MNRAS, 449, 835
+\bibitem[Ross et al.(2015)]{MGS}
+Ross, A.J., Samushia, L., \& Howlett, C., et al. 2015, MNRAS, 449, 835
 

### 2017-04-01 draft/draft3.tex
updates

--- 2017-04-01 draft/draft2.1.tex
@@
 The methodology is presented in \S 4.
-We conclude in \S 5.
+The cosmological constraints from the method is presented in \S 5.
+We conclude in \S 6.
 
@@
 
-The mis-scaling not only changes the shape of the 2pCF but also modifies its amplitude. %The amplitude of $r_\perp\omega$ is amplified due to the stretch of scale.
+The mis-scaling not only changes the shape of the 2pCF but also changes the value of the $y$-axis
+\footnote{}. %The amplitude of $r_\perp\omega$ is amplified due to the stretch of scale.
 As is shown in the left panel, due to the stretch of scale the amplitude is enhanced at higher redshifts;
@@
    based on the redshift evolution of the angular 2pCF shape $\hat\omega_{r_\perp}$.
+   The green point denotes our fiducial cosmological model and the contours denote the statistical error.
    Utilizing the HR4 snapshots data of mock galaxies at five redshifts,
-   the method can lead to very tight cosmological constraint.
+   the method lead to very tight cosmological constraint.
    Right: The constraints in case that one or two high redshift bins are not used. 
@@
 
-In summary, the effect of RSD and galaxy bias on the shape of galaxy angular correlation function is, not large, but it is still non-negligible.
-When dealing with real observational data, one should construct simulation mocks in which these effects are reliably modelled, 
-so that the systematics are corrected and will not lead to significant bias in the derived cosmological constraints.
+%In summary, the effect of RSD and galaxy bias on the shape of galaxy angular correlation function is, not large, but it is still non-negligible.
+%When dealing with real observational data, one should construct simulation mocks in which these effects are reliably modelled, 
+%so that the systematics are corrected and will not lead to significant bias in the derived cosmological constraints.
 
@@
 %3.000e11', '1.000e12', '4.000e12',  '1.000e13
+
+\subsubsection{More discussion}
+
+In summary, we aim to minimise the redshift evolution of the shape of the normalised angular 2pcf; 
+the shape change is dramatic when considering a cosmology much deviated from the fiducial model.
+However even in the case of the correct cosmology there remains a small signal, due to growth of structures, RSD and galaxy bias. 
+These systematics are removed with the aid of simulations.
+The procedure of the correction of systematics is similar to what was implemented in our previous papers \cite{Li2014,Li2015,Li2016}.
+
+The systematics are estimated from a simulation conducted using a particular cosmology. 
+There could be a bias in the estimation if the simulation cosmology is different from the truth. 
+The bias would not be serious if the simulation cosmology turns out to be consistent with the best-fit cosmological parameters obtained from the analysis \cite{Li2016}. 
+In the case that there is a large discrepancy between the simulation cosmology and the best-fit cosmology, one needs to adjust the simulation cosmology and re-do the analysis.
+
+A more precise approach would involve estimating the systematic effect from a set of simulations covering the relevant volume of the parameter space. 
+This would remove the remaining uncertainty associated with the cosmological dependence. 
+This approach would also enable the estimation of the $systematics\ errors$, 
+which could be important when the sample size is large enough and the $systematic\ error$ becomes as small as the $statistical\ error$.
+
+The third row of Figure \ref{fig_sys} shows that, 
+if having a large difference in bias between the samples,
+there is a large systematic variation on small scales. 
+This means that an accurate modelling of systematics from simulations is required. 
+To avoid the possible difficulty, one can conduct the analysis using a volume-limited sample, 
+where the redshift evolution of galaxy properties is small and the systematic effect from RSD and galaxy bias is also small,
+as shown by the fourth row of Figure \ref{fig_sys}.
+
+To avoid the large systematics in the nonlinear regime, 
+another solution would be to increase the scale of analysis to larger separations where the non-linear effect is becoming subdominant. 
+Figure \ref{fig_sys} shows that, 
+on scales of $s=20-50 h^{-1} {\rm Mpc}$ the systematic effect is 2-3 times smaller than that of $s=5-20 h^{-1} {\rm Mpc}$. 
+Actually, we tested and found that, using $s = 5-40 h^{-1} {\rm Mpc}$ and $20-40 h^{-1} {\rm Mpc}$, 
+yields cosmological constraints that are pretty close to each other (see \S 4).
+
+We do not consider the systematic effects in case of non-standard cosmological scenarios such as modified gravity and warm dark energy. 
+These topics go beyond the scope of this work, and they are worthy future investigations.
 
@@
 
-In case that we do not have high redshfit galaxies, the constraint becomes weaker.
-Figure \ref{fig_contours} displays that, 
+In case that we do not have high redshift galaxies, the constraint becomes weaker.
+The upper-right panel of Figure \ref{fig_contours} displays that, 
 in case that we only use the galaxies at $z=$0, 0.5 and 1, 
@@
 The area of contour is further enlarged by $\approx 50\%$ if we only use galaxies at $z=$0 and 0.5.
+
+So far we simply follow the convention of \cite{Li2016} and adopts $5\hMpc <s< 40\hMpc$. 
+As discussed in the \S 4.3.3, one may want to avoid large systematics in the non-linear regime. 
+In this case one can adopt $20\hMpc<s<40\hMpc$,
+which significantly reduces the systematic effects while not much weaken the power of the final constraints,
+as shown by the lower-left panel of Figure \ref{fig_contours}.
+
+The choice of the redshift width $105 \hMpc$ is also slightly little arbitrary. 
+It should be larger than the distance distortion from the RSD and redshift errors.
+The optimistic scheme of clustering scales and redshift width should depend on the specific galaxy sample used in the analysis. 
+One could adjust them to have a good balance between the power of cosmological constraint and the size of systematic effect.
 

### 2017-04-01 105thick/scp.sh

@@ -2,4 +2,8 @@
 #scp xiaodongli@annapurna.kias.re.kr:~/105thick/*.2pcf ./
 #scp xiaodongli@annapurna.kias.re.kr:~/105thick/*.py ./
 #scp xiaodongli@annapurna.kias.re.kr:/home/xiaodongli/105thick/*shiftz*.2pcf ./
-scp xiaodongli@newton.kias.re.kr:/home3/xiaodongli/cpfromanna/*shiftz*.2pcf ./
+#scp xiaodongli@newton.kias.re.kr:/home3/xiaodongli/cpfromanna/*shiftz*.2pcf ./
+#scp xiaodongli@newton.kias.re.kr:/home3/xiaodongli/cpfromanna/*diffmass*.2pcf ./
+#scp xiaodongli@newton.kias.re.kr:/home3/xiaodongli/cpfromanna2/*.2pcf ./
+scp xiaodongli@annapurna.kias.re.kr:~/105thick/J08.dat.z_*.mge3.000e11*ConstNbar*.2pcf ./
+

### 2017-04-03 draft/draft3.1_cris.tex
updates

--- 2017-04-01 draft/draft3.1.tex
@@
 \affil{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
-\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
 \and
@@
 We propose to use the redshift dependence of the galaxy 2-point correlation function across the line-of-sight (2pCF), $\xi(r_{\bot})$, to constrain cosmological parameters.
-When an incorrect set of parameters is assumed for the coordinate transformation from redshift space to comoving space, 
-it produces {\it redshift-dependent mis-scaling} in the constructed galaxy distribution.
-As a result, we observe a redshift-dependent rescaling of the measured $\xi(r_{\bot})$.
+When an incorrect set of cosmological parameters is assumed for transforming galaxy redshifts to comoving distances, 
+it produces {\it redshift-dependent mis-scaling} in the galaxy distribution.
+As a result, we observe a redshift-dependent rescaling in the measured $\xi(r_{\bot})$.
 Using mock galaxy catalogues (containing hundreds of millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2) from the Horizon Run 4 N-body simulation, we find that the redshift evolution of the $\xi(r_{\bot})$ shape, as a function of scale,
@@
 %Our method is complementary to current works using 2pCF to constrain cosmological parameters.
-The method could be applicable to future large scale structure surveys, especially photometric surveys such as DES, LSST, 
+This method could be applicable to future large scale structure surveys, especially photometric surveys such as DES, LSST, 
 to derive tight cosmological constraints.
 This work is a continuation of our previous works \citep{Li2014,Li2015,Li2016}
-as a strategy to constrain cosmological parameters using redshift-invariant physical quantities;
-they are all powerful in constrain cosmology and have a lot of merits,
-e.g., are less affected by the systematic effects introduced by non-linear clustering or RSD,
-does not require accurate modeling of galaxy clustering,
-and are applicable on relative small clustering scales.
+as a strategy to constrain cosmological parameters using redshift-invariant physical quantities.
+They are all powerful in constraining cosmology and have many merits,
+e.g., they are less affected by the systematic effects induced by non-linear clustering or RSD,
+they do not require accurate modeling of galaxy clustering,
+and are applicable on relatively small clustering scales.
 \end{abstract}
@@
 or the breakdown of Einstein's gravity theory on cosmological scales \citep[see ][for a recent review]{2012IJMPD..2130002Y}.
-The theoretical explanation and observational probe of cosmic acceleration has attracted 
-tremendous effort in the last two decades and are still far from well understood or accurately measured \citep{SW1989,Li2011,DHW2013}.
+The theoretical explanation and observational probes of cosmic acceleration have attracted 
+tremendous attention in the last two decades and are still far from being well understood or accurately measured \citep{SW1989,Li2011,DHW2013}.
 %, but its properties still remain far from accurately known and its nature still remains mystery. 
@@
 
-%As one geometrical effect of cosmological parameters on LSS,  
-When an incorrect cosmological model is assumed for the coordinate transformation from redshift space to comoving space,
-geometric distortions are produced in the constructed galaxy distribution. 
-These distortions include the ``volume effect'' which is the mis-scaling of the size of structures,
+When an incorrect cosmological model is assumed when transforming galaxy redshifts to comoving distances,
+geometric distortions are produced in the resultant galaxy distribution. It should be noted that this effect is not related to galaxy peculiar velocities which could cause redshift space distortions.
+The distortions due to coordinate transforms include the ``volume effect'' which is the mis-scaling of the size of structures,
 and the Alcock-Paczynski (AP) effect, the shape distortion induced by the fact that distances along and perpendicular to the line of sight are fundamentally different.
@@
 
-Although there have also been alternative approaches using the symmetry properties of galaxy pairs \citep{Marinoni2010,Jennings2011,BB2012}
+However, there have also been alternative approaches in utilising the AP effect using the symmetry properties of galaxy pairs \citep{Marinoni2010,Jennings2011,BB2012}
 and cosmic voids \citep{Ryden1995,LavausWandelt1995,Sutter2014,Qingqing2016}.
@@
 \cite{Li2014} attempted to use the {\it galaxy density gradient field} 
-to characterize the redshift evolution of the LSS distortion. 
+to characterize the redshift evolution of the large scale galaxy distribution. 
 We tested the idea on the Horizon Run 3 (HR3) N-body simulations \citep{horizonrun},
@@
 In this paper we continue our exploration of this strategy and present 
-a new method using the redshift evolution of the shape of the 2-point correlation function across the line-of-sight as a function of radial scale, $\xi(r_{\bot})$,
+a new method using the redshift evolution of the shape of the galaxy 2pCF across the line-of-sight as a function of radial scale, $\xi(r_{\bot})$,
 to constrain cosmology.
@@
   The growth of structure strengths the clustering and make structures more compact at lower redshift.
-  When the wrong cosmology is adopted, the covmoving distances are mis-scaled and over-estimated by $25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$, respectively,  leading to a clear redshift evolution of the sizes of structures.
+  When the wrong cosmology is adopted, the comoving distances are mis-scaled and over-estimated by $25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$, respectively,  leading to a clear redshift evolution of the sizes of structures.
    }
@@
 than the alteration of shape,
-it is mixed with the other effects; 
+it is mixed with the other effects; i.e.
 the growth of structure and a larger galaxy bias can also lead to a stronger clustering and thus an enhanced amplitude.
@@
 we just utilize the redshift evolution of the 2pCF shape, 
-which is less affected by other factors.
+which is less affected by these complicated factors.
 %which is as a signal suggesting that the assumed cosmological parameters are wrong.
@@
 Similar to RSD, redshift errors of galaxies
-also results in fuzzy boundaries of redshift shells
-Thankfully, there are some methods for mitigating this effect in photometric surveys using pair-center binning \citep{2010MNRAS.407..520N}.
+also results in fuzzy boundaries of redshift shells.
+Thankfully, there are some methods for mitigating this effect in photometric surveys using, for example, pair-center binning \citep{2010MNRAS.407..520N, 2011MNRAS.415.2193R}.
 
@@
 with the RSD effect considered. %(the error bar is a bit larger since for an illustration purpose we only do the computation for 1/30 of the whole sample).
-We see the redshfit evolution of $\hat \xi_{r_\perp}$ is as small as $\lesssim3\%$.
+We see the redshift evolution of $\hat \xi_{r_\perp}$ is as small as $\lesssim3\%$.
 
@@
 
-In summary, we aim to minimise the redshift evolution of the shape of the normalised angular 2pcf; 
-the shape change is dramatic when considering a cosmology much deviated from the fiducial model.
+In summary, we aim to minimise the redshift evolution of the shape of the normalised  2-point correlation function across the line-of-sight; 
+the shape change is dramatic when considering a cosmological model significantly different from the fiducial model.
 However even in the case of the correct cosmology there remains a small signal, due to growth of structures, RSD and galaxy bias. 
@@
 The systematics are estimated from a simulation conducted using a particular cosmology. 
-There could be a bias in the estimation if the simulation cosmology is different from the truth. 
-The bias would not be serious if the simulation cosmology turns out to be consistent with the best-fit cosmological parameters obtained from the analysis \cite{Li2016}. 
+Thus there could be a bias in their estimation if the simulation cosmology is different from the true cosmological model/. 
+The bias would not be serious if the simulation cosmology is consistent with the best-fit cosmological parameters obtained from the analysis \cite{Li2016}. 
 In the case that there is a large discrepancy between the simulation cosmology and the best-fit cosmology, one needs to adjust the simulation cosmology and re-do the analysis.
@@
 The third row of Figure \ref{fig_sys} shows that, 
-if having a large difference in bias between the samples,
+if having a large difference in galaxy bias between the samples,
 there is a large systematic variation on small scales. 
-This means that an accurate modelling of systematics from simulations is required. 
-To avoid the possible difficulty, one can conduct the analysis using a volume-limited sample, 
+This means that accurate modelling of systematics from simulations is required. 
+In an effort to mitigate this problem, one can conduct the analysis using a volume-limited galaxy sample, 
 where the redshift evolution of galaxy properties is small and the systematic effect from RSD and galaxy bias is also small,
@@
 We do not consider the systematic effects in case of non-standard cosmological scenarios such as modified gravity and warm dark energy. 
-These topics go beyond the scope of this work, and they are worthy future investigations.
+These topics go beyond the scope of this work, however they are worthy future investigations.
 
@@
 \end{equation}
-where $n_z$ is the number of redshifts which is 5 in this analysis, 
+where $n_z$ is the number of redshifts bins, which is 5 in this analysis, 
 $n_r$ is number of binning in $\hat{\xi}_{r_\perp}(r_\perp)$,
@@
 
-So far we simply follow the convention of \cite{Li2016} and adopts $5\hMpc <s< 40\hMpc$. 
+So far we simply follow the convention of \cite{Li2016} and adopt $5\hMpc <s< 40\hMpc$ as our analysis scale. 
 As discussed in the \S 4.3.3, one may want to avoid large systematics in the non-linear regime. 
-In this case one can adopt $20\hMpc<s<40\hMpc$,
-which significantly reduces the systematic effects while not much weaken the power of the final constraints,
+In this case one may adopt $20\hMpc<s<40\hMpc$,
+which significantly reduces the systematic effects but does not degrade the power of the parameter constraints,
 as shown by the lower left panel of Figure \ref{fig_contours}.
@@
 
-We have developed a method for constraining certain cosmological parameters by measuring the redshift evolution of the shape of the galaxy correlation function across the line-of-sight, $\hat \xi_{r_\perp}$.
+We have developed a method for constraining certain cosmological parameters by measuring the redshift evolution of the shape of the galaxy 2pCF across the line-of-sight, $\hat \xi_{r_\perp}$.
 We found that a wrongly adopted cosmology results in a redshift-dependent mis-scaling in the constructed galaxy distribution,
@@
 The two methods focus on different parts of the clustering information, and the constraints derived from the them should be fairly independent.
-But it is still suggested to have an estimation of the covariance between them in case one is using both methods to do an analysis. 
+However, it is advisable to have an estimation of the covariance between them in the case there one is using both methods in combination.
 An alternative way is to investigate the redshift evolution of the correlation map $\xi(s,\mu)$ as a function of both scale and direction, which captures all the information.
@@
 %Ross, A.J., Percival, W.J., \& S{\'a}nchez, A.G. et al.\ 2012, MNRAS, 424, 564 
+\bibitem[Ross et al.(2011)]{2011MNRAS.415.2193R} Ross, A.~J., Percival, W.~J., Crocce, M., Cabr{\'e}, A., \& Gazta{\~n}aga, E.\ 2011, \mnras, 415, 2193
 

### 2017-04-03 draft/draft3.2.tex
updates

--- 2017-04-03 draft/draft3.1_cris.tex
@@
 \begin{abstract}
-We propose to use the redshift dependence of the galaxy 2-point correlation function across the line-of-sight (2pCF), $\xi(r_{\bot})$, to constrain cosmological parameters.
-When an incorrect set of cosmological parameters is assumed for transforming galaxy redshifts to comoving distances, 
-it produces {\it redshift-dependent mis-scaling} in the galaxy distribution.
-As a result, we observe a redshift-dependent rescaling in the measured $\xi(r_{\bot})$.
-Using mock galaxy catalogues (containing hundreds of millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2) from the Horizon Run 4 N-body simulation, we find that the redshift evolution of the $\xi(r_{\bot})$ shape, as a function of scale,
-is sensitive to the adopted cosmological parameters. 
-% mock galaxy catalogues having hundreds of millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2.
-However, it is relatively insensitive to the gravitational growth of structure,
-the galaxy bias, and the effect of redshift space distortions.
-Analyzing the 2pCF shape on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
-we derive tight constraints on $\Omega_m$ and $w$ with 68.3\% CL uncertainties of 0.015 and 0.05.
-%Our method is complementary to current works using 2pCF to constrain cosmological parameters.
-This method could be applicable to future large scale structure surveys, especially photometric surveys such as DES, LSST, 
-to derive tight cosmological constraints.
+We develop a methodology to use the redshift dependence of the galaxy 2-point correlation function across the line-of-sight (2pCF), $\xi(r_{\bot})$, as a probe of cosmological parameters. 
+The positions of galaxies in comoving Cartesian space varies under different cosmological parameter choices, 
+inducing a {\it redshift-dependent scaling} in the galaxy distribution. 
+This geometrical distortion can be observed as a redshift-dependent rescaling in the measured $\xi(r_{\bot})$. 
+We test this methodology using a sample of 1.75 billion mock galaxies at redshifts 0, 0.5, 1, 1.5, 2, 
+drawn from the Horizon Run 4 N-body simulation.
+The shape of $\xi(r_{\bot})$ can exhibit a significant redshift evolution when the galaxy sample is 
+analyzed under a cosmology differing from the true, simulated one. 
+Other contributions, including the gravitational growth of structure, 
+galaxy bias, and the redshift space distortions, 
+do not produce large redshift evolution in the shape. 
+We show that one can make use of this geometrical distortion to constrain the values of 
+cosmological parameters governing the expansion history of the universe. 
+This method could be applicable to future large scale structure surveys, 
+especially photometric surveys such as DES, LSST, to derive tight cosmological constraints. 
 This work is a continuation of our previous works \citep{Li2014,Li2015,Li2016} 
 as a strategy to constrain cosmological parameters using redshift-invariant physical quantities.
-They are all powerful in constraining cosmology and have many merits,
-e.g., they are less affected by the systematic effects induced by non-linear clustering or RSD,
-they do not require accurate modeling of galaxy clustering,
-and are applicable on relatively small clustering scales.
+%We propose to use the redshift dependence of the galaxy 2-point correlation function across the line-of-sight (2pCF), $\xi(r_{\bot})$, to constrain cosmological parameters.
+%When an incorrect set of cosmological parameters is assumed for transforming galaxy redshifts to comoving distances, 
+%it produces {\it redshift-dependent mis-scaling} in the galaxy distribution.
+%As a result, we observe a redshift-dependent rescaling in the measured $\xi(r_{\bot})$.
+%We test this idea using a sample of 1.75 billion mock galaxies at redshifts 0, 0.5, 1, 1.5, 2,
+%drawn from the Horizon Run 4 N-body simulation.
+%The shape of $\xi(r_{\bot})$ exhibits redshift evolution when the adopted cosmology is wrong,
+% mock galaxy catalogues having hundreds of millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2.
+%while the other effects, including the gravitational growth of structure,
+%galaxy bias, and the redshift space distortions, do not produce large redshift evolution in the shape.
+%Analyzing the 2pCF shape on scales $20  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
+%we derive tight constraints on $\Omega_m$ and $w$ with 68.3\% CL uncertainties of 0.015 and 0.05.
+%We show that one can make use of this fact to constrain the values of cosmological parameters governing the 
+%expansion history of the universe.
+%Our method is complementary to current works using 2pCF to constrain cosmological parameters.
+%This method could be applicable to future large scale structure surveys, 
+%especially photometric surveys such as DES, LSST, 
+%to derive tight cosmological constraints.
+%This work is a continuation of our previous works \citep{Li2014,Li2015,Li2016}
+%as a strategy to constrain cosmological parameters using redshift-invariant physical quantities.
+%They are all powerful in constraining cosmology and have many merits,
+%e.g., they are less affected by the systematic effects induced by non-linear clustering or RSD,
+%they do not require accurate modeling of galaxy clustering,
+%and are applicable on relatively small clustering scales.
 \end{abstract}
@@
 
-The discovery of cosmic acceleration \citep{Riess1998,Perl1999} implies the existence of a ``dark energy'' component in the Universe 
+The discovery of cosmic acceleration \citep{Riess1998,Perl1999} implies either the existence of a ``dark energy'' component in the Universe 
 or the breakdown of Einstein's gravity theory on cosmological scales \citep[see ][for a recent review]{2012IJMPD..2130002Y}.
@@
 
-In an effort to probe the cosmic expansion history the large scale structure (LSS) surveys enable measurements of two geometrical quantities, 
+In an effort to probe the cosmic expansion history, large scale structure (LSS) surveys are utilized to  measure two key geometrical quantities; 
 the angular diameter distance $D_A$ and the Hubble factor, $H$. 
 If they were precisely measured as a function of redshift, 
-tight constraints can be placed on cosmological parameters, 
+then tight constraints can be placed on cosmological parameters, 
 e.g. the matter density $\Omega_m$ and the equation of state (EoS) of dark energy $w$.
 
-When an incorrect cosmological model is assumed when transforming galaxy redshifts to comoving distances,
-geometric distortions are produced in the resultant galaxy distribution. It should be noted that this effect is not related to galaxy peculiar velocities which could cause redshift space distortions.
+When an incorrect cosmological model is assumed for transforming galaxy redshifts to comoving distances,
+geometric distortions are induced in the resultant galaxy distribution. 
+It should be noted that this effect is not related to the peculiar velocities of galaxies, which cause redshift-space distortions (RSD).
 The distortions due to coordinate transforms include the ``volume effect'' which is the mis-scaling of the size of structures, 
 and the Alcock-Paczynski (AP) effect, the shape distortion induced by the fact that distances along and perpendicular to the line of sight are fundamentally different.
-%Measuring the ratio of galaxy clustering in the radial and transverse directions, provides a probe of the Alcock-Paczynski (AP) effect \citep{AP1979}.
-%There have been a series of works studying the application of the AP test to the LSS
 
@@
 Later, with the advent of large observational spectroscopic programs, this was applied to a series of LSS surveys
-\citep{Outram2004,Blake2011,ChuangWang2012,Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, Jeong2014,Sutter2014,2014ApJ...781...96L,Alam2016, Beutler2016, Sanchez2016}, while considering the detailed effect of systematics for unbiased estimates of $D_A(z)$ and $H(z)$ \citep{2014MNRAS.445....2V,2016MNRAS.tmp.1473R,2016arXiv160302389S}.
-
-However, there have also been alternative approaches in utilising the AP effect using the symmetry properties of galaxy pairs \citep{Marinoni2010,Jennings2011,BB2012}
+\citep{Outram2004,Blake2011,ChuangWang2012,Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, Jeong2014,Sutter2014,2014ApJ...781...96L,Alam2016, Beutler2016, Sanchez2016}, 
+while considering the detailed effect of systematics for unbiased estimates of $D_A(z)$ and $H(z)$ \citep{2014MNRAS.445....2V,2016MNRAS.tmp.1473R,2016arXiv160302389S}.
+Alternative approaches include utilizing the AP effect using the symmetry properties of galaxy pairs \citep{Marinoni2010,Jennings2011,BB2012}
 and cosmic voids \citep{Ryden1995,LavausWandelt1995,Sutter2014,Qingqing2016}.
-Methods proposed to measure the volume effect include the number counting of 
-galaxy clusters \citep{PS1974,VL1996}, the topology of LSS \citep{topology},
-the BAO scale \citep{EHT1998,BG03,SE03},
+
+There have also been studies proposing to measure the volume effect of this geometrical rescaling, 
+these include the number counting of galaxy clusters \citep{PS1974,VL1996}, 
+the topology of LSS \citep{topology}, the BAO scale \citep{EHT1998,BG03,SE03}, 
 and the shape of 2pCF and power spectrum \citep{Sanchez2006,Sanchez2009}.
 
-In \cite{Li2014,Li2015,Li2016} we developed a novel strategy to probe $D_A$ and $H$ from the LSS data.
-%proposed a series of methods to probe the geometric information encoded in the LSS data.
-We found that the AP or volume effect in general introduces a geometric distortion that evolves significantly with redshift;
-this phenomenon can be utilized to distinguish the AP effect from the other effects, such as the redshift-space distortion (RSD).
-The radial distances of galaxies are inferred from the measured redshifts, which are distorted by the peculiar motion of galaxies, 
-leading to apparent distortion in the redshift space galaxy distribution \citep{FOG,Kaiser1987,Ballinger1996}.
-It is the major systematic effects limiting our ability to probe the geometry of LSS from the galaxy distribution.
-However, we found that the influence of RSD is significantly reduced when we consider only the redshift dependence of the distortion.
-
-\cite{Li2014} attempted to use the {\it galaxy density gradient field} 
-to characterize the redshift evolution of the large scale galaxy distribution. 
-We tested the idea on the Horizon Run 3 (HR3) N-body simulations \citep{horizonrun},
-showing that the redshift evolution of the gradient field 
-can be used to infer unbiased constraints on cosmological parameters and that it is, largely, insensitive to RSD.
-The same topic was revisited in \cite{Li2015}, 
-using a slightly modified version of the usual anisotropic galaxy two-point correlation function (2pCF), $\xi(\mu)$, 
-where $\mu\equiv \cos \theta$ and $\theta$ is the angle between the connection of the galaxy pairs and the line of sight direction.
-When an incorrect cosmological model is adopted, 
-the shape of $\xi(\mu)$ is altered due to the anisotropic distortion of the LSS (the AP effect), 
-and the amplitude is shifted due to the change in the comoving volume elements;
-both effects have significant redshift dependence.
-Although the RSD effect significantly distorts $\xi(\mu)$, 
-it exhibits much less redshift evolution.
-The method was applied to BOSS DR12 galaxies \citep{Li2016} to probe the redshift dependence of the AP effect, 
-and we arrive at tight cosmological constraints competitive with the mainstream probes of SNIa, BAO, and CMB.
-
-In this paper we continue our exploration of this strategy and present 
-a new method using the redshift evolution of the shape of the galaxy 2pCF across the line-of-sight as a function of radial scale, $\xi(r_{\bot})$,
-to constrain cosmology.
-A wrongly adopted cosmology results in {\it redshift-dependent mis-scaling} of the galaxy distribution,
-which leads to redshift-evolution of the shape of $\xi(r_{\bot})$.
-The signal is sensitive to the cosmological parameters but relatively insensitive to the other effects such as the gravitational growth of structure,
-the galaxy bias, and the RSD effect.
-We apply our method to HR4 mock catalogues, using hundreds of millions of galaxies at redshifts $0\leq z\leq2$
-and develop the statistical procedure to constrain cosmological parameters.
-
-%In this paper we continue our series of work and probe to use the angular correlation function as a statistical tool to probing the volume effect in the angular direction.
-%The method of redshift dependent AP effect has been shown great power to constrain cosmological parameters \cite{Li2014,Li2015,Li2015}.
-%We hope this method also.
-%The two methods probe different information encoded in the 2pCF and can be combined to fully probe the geometrical effect in LSS.
-%Or one can also use the redshift evolution of 2D 2pCF xi(s,mu) to have all information included.
-%We developed a method measuring the redshift of the shape of galaxy angular correlation function, $\hat \xi_{r_\perp}$, to constrain cosmology.
-%A wrongly adopted cosmology result in redshift-dependent mis-scaling in the constructed galaxy distribution,
-%which shifts apparent scale of the clustering patterns;
-%this manifests itself as a redshift-dependent rescaling of the measured angular correlation function.
-%We find this signal is sensitive to the adopted cosmological parameters and relatively insensitive to the gravitational growth of structure,
-%the galaxy bias, and the RSD effect.
-%We test our method on the HR4 mock galaxies.
-%The method can be applied to current and future LSS surveys,
-%especially, the photometric surveys such as DES and LSST which probe a large amount of galaxies and the large redshift error will not quite affect the angular 2pCF measurement.
+In \cite{Li2014,Li2015} we developed a novel strategy to probe $D_A$ and $H$ from the LSS data. 
+We found that the AP effect introduces a geometric distortion that evolves significantly with redshift;
+this phenomenon can be utilized to distinguish the AP effect from the effect of RSD.
+
+The radial distances of galaxies are inferred from their measured redshifts, 
+which are distorted due to the peculiar motion of galaxies. 
+This leads to an apparent distortion in the redshift-space galaxy distribution \citep{FOG,Kaiser1987,Ballinger1996}. 
+This RSD effect is the main systematic limiting our ability to probe the geometry of LSS from the galaxy distribution. 
+However, we found that the influence of RSD is significantly reduced when focusing on the redshift dependence of galaxy clustering.
+
+In \cite{Li2016}, we analyzed the two-point correlation function (2pCF) of galaxies measured in the Baryon Oscillation Spectroscopic Survey (BOSS). 
+We showed that the redshift dependence of the AP effect leads to tight cosmological constraints that are competitive with mainstream cosmological probes such as type Ia supernovae (SNIa), baryon acoustic oscillations (BAO), and cosmic microwave background (CMB).
+
+In this paper we continue our exploration of redshift invariant galaxy clustering 
+and present a new method for constraining cosmology using the redshift evolution of 
+the galaxy two-point correlation function (2pCF) across the line-of-sight, $\xi(r_{\bot})$. 
+An incorrect choice of cosmology results in {\it redshift-dependent scaling} of the galaxy distribution. 
+This, in turn, results in a significant redshift evolution in the shape of $\xi(r_{\bot})$.
+Of course the correlation function has other contributions factors that may induce redshift evolution, 
+such as the gravitational growth of structure, galaxy bias, and redshift space distortions. 
+However we find that these other contributions do not produce large redshift evolution in the shape of $\xi(r_{\bot})$. 
+We test this methodology using a sample of 1.75 billion mock galaxies at redshifts 0, 0.5, 1, 1.5, 2, drawn from the Horizon Run (HR) 4 N-body simulation.
 
@@
 In \S 2 we briefly review the nature and consequences of the LSS geometric distortion when performing coordinate transforms in a cosmological context. 
-In \S 3 we describe the N-body mock galaxies used to test our method.
-The methodology is presented in \S 4.
-We conclude in \S 5.
+In \S 3 we describe the N-body mock galaxies used in the analysis.
+The methodology is presented in \S 4 and \S 5.
+We conclude in \S 6.
 
@@
 respectively.
+The total number of galaxies is 1.75 billion.
 Applying a uniform mass cut, at higher redshift we obtained a smaller number of galaxies with {\it larger bias}.
@@
 The predicted constraints from this method clearly wins due to the large sample size.
-The total number of galaxies used in this work is 1,749 million,
+The total number of galaxies used in this work is 1.75 billion,
 which is 1,000 times of the BOSS DR12 sample size.

### 2017-04-29 draft/draft3.3.tex
updates

--- 2017-04-03 draft/draft3.2.tex
@@
 \begin{abstract}
-We develop a methodology to use the redshift dependence of the galaxy 2-point correlation function across the line-of-sight (2pCF), $\xi(r_{\bot})$, as a probe of cosmological parameters. 
+We develop a methodology to use the redshift dependence of the galaxy 2-point correlation function (2pCF) across the line-of-sight, $\xi(r_{\bot})$, as a probe of cosmological parameters. 
 The positions of galaxies in comoving Cartesian space varies under different cosmological parameter choices, 
@@
 and present a new method for constraining cosmology using the redshift evolution of 
-the galaxy two-point correlation function (2pCF) across the line-of-sight, $\xi(r_{\bot})$. 
+the galaxy two-point correlation function (2pCF) across the line-of-sight (LOS), $\xi(r_{\bot})$. 
 An incorrect choice of cosmology results in {\it redshift-dependent scaling} of the galaxy distribution. 
@@
    \caption{\label{fig_xyquan}
-   A description of how incorrectly assumed cosmologies can distort the interpretation of observation,
+   An illustrative example of how incorrectly assumed cosmologies can distort a distribution of points,
    assuming $\Omega_m=0.26,w=-1$ is the true cosmology. 
    Left panel shows a series of five regular squares, measured by an observer at the origin.
-   Their true positions and shapes are plotted in blue dashed lines.
-   When the observer adopts incorrect cosmologies when computing distances from redshifts and infering the positions and shapes of the squares,
+   Their true positions and shapes are plotted as blue dashed lines.
+   When the observer adopts incorrect cosmologies when computing distances from redshifts and inferring the positions and shapes of the squares,
    they obtain distorted shapes (red solid lines).
@@
 %Its observed redshift span $\Delta z$ and angular size $\Delta \theta$ are related with the comoving sizes by
-In this section we briefly introduce the scaling effect caused by incorrectly assumed cosmological parameters.
-A more detailed description has been provided in \cite{Li2014,Li2015,Li2016}.
+In this section we briefly discuss the scaling effect in the galaxy clustering statistics caused by assuming incorrect cosmological parameters.
+A more detailed description can be found in \cite{Li2014,Li2015,Li2016}.
 
@@
 and their sizes would be wrongly estimated (volume effect).
-Cosmological models (i,iii) result in compressed volume elements (in both angular and LOS directions),
+Cosmological models (i,iii) result in compressed volume elements (in both the angular and LOS directions),
 and the degree of compression increases with increasing distance;
@@
 
-In sum, as a consequence of incorrect cosmologies 
+In summary, as a consequence of incorrectly assumed cosmologies 
 the size of objects is mis-estimated and the magnitude of mis-estimation depends on the redshift.
-We use the galaxy 2pCF across the line-of-sight to probe the mis-estimation of angular size, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$.
+We thus use the galaxy 2pCF across the LOS to probe the mis-estimation of angular size, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$.
 
@@
 
-We test the method using the mock galaxy samples produced by the Horizon Run 4  (HR4) N-body simulation \citep{hr4,hong2016}.
-
-HR4 was made within a cube of volume $({3.15}\ h^{-1}\rm Gpc)^3$ using  $6300^3$ particles with mass $m_p\simeq 9 \times 10^9 \hMsun$.
+We test the method using the mock galaxies produced by the Horizon Run 4  (HR4) N-body simulation \citep{hr4,hong2016}.
+
+HR4 was made in a $({3.15}\ h^{-1}\rm Gpc)^3$ cube using  $6300^3$ particles with mass $m_p\simeq 9 \times 10^9 \hMsun$.
 The simulation adopted the second order Lagrangian perturbation theory (2LPT) initial conditions at $z_{i}=100$
@@
 
-The resulting mock galaxies were found to reproduce the 2pCF of the SDSS DR7 volume-limited galaxy sample \citep{zehavi2011} very well.
+The resulting mock galaxies were found to well reproduce the 2pCF of the volume-limited galaxy sample from Sloan Digital Sky Survey Data Release 7 (SDSS DR7) \citep{zehavi2011}.
 The mock galaxies shows a similar finger of god (FOG) feature \citep{FOG} as the observation.
@@
 %and a series ({\bf how many?}) of snapshot mock galaxy catalogues at different redshifts.
-We take the snapshot data of the mock galaxies at $z=0,0.5,1,1.5,2$.
+In this analysis, we use five snapshots of mock galaxies at $z=0,0.5,1,1.5,2$.
 %We require subhalos to have at least 30 member particles, 
@@
 respectively.
+At higher redshift, we have smaller number of galaxies, with a {\it larger bias}.
 The total number of galaxies is 1.75 billion.
-Applying a uniform mass cut, at higher redshift we obtained a smaller number of galaxies with {\it larger bias}.
-
-As an illustration, Figure \ref{fig_scatter} displays the 2D distribution of a subsample of mock galaxies in five redshifts,
-with $x$, $y$ coordinates computed using the ``correct'' cosmological parameters $\Omega_m=0.26,\ w=-1$ (left panels) 
+
+As an illustration, Figure \ref{fig_scatter} displays a subsample of galaxies at the five redshifts.
+Their $x$, $y$ coordinates are computed using two sets of cosmological parameters,
+the ``correct'' cosmology $\Omega_m=0.26,\ w=-1$ (left panels),
 and a set of wrong cosmological parameters $\Omega_m=0.05,\ w=-1.5$ (right panels), respectively.
 
-When the correct cosmology is adopted the cosmic scale is correctly estimated,
-the main factor leads to redshift evolution of galaxy distribution is the gravitational growth of structure.
-With decreasing redshift, we clearly see the clusters and filaments form and grow.
-On the other hand, when the wrong cosmology is adopted, there is an artificial scaling of distances in the constructed map.
+When the correct cosmology is adopted, the cosmic scale is correctly estimated,
+and the main factor for the redshift evolution of galaxy distribution is the gravitational growth of structure.
+With decreasing redshift, the clusters and filaments form and grow.
+On the other hand, the wrong cosmology leads to an artificial scaling of distance.
 The separations among galaxies are over-estimated by 
 $25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$,
-leading to a clear redshift evolution of sizes of structures.
+causing a clear redshift evolution of the sizes of structures.
 
@@
 while the volume effect maintains the clustering pattern and uniformly re-scales structures on all scales.
-The imprint of each of these effects on the large scale structure is different and should be distinguishable.
-In the following section we show that they affect $\xi(r_{\bot})$ measurements in different ways, 
+Their imprints are different.
+In the next section, we show that they affect $\xi(r_{\bot})$ measurements in different manners, 
 and thus can be easily separated.
@@
    \caption{\label{fig_scatter}
-  The 2D distribution of a $260\times130\times105 (h^{-1}{\rm Mpc})^3$ subsample of HR4 mock galaxies, 
+  $x$, $y$ coordinates of a $260\times130\times105 (h^{-1}{\rm Mpc})^3$ subsample of HR4 galaxies, 
   at redshifts 0.5, 1, 1.5 and 2.
-  Left and right panels show the $x$, $y$ coordinates computed using the ``correct'' parameters $\Omega_m=0.26,\ w=-1$ 
-  and a set of wrong cosmological parameters $\Omega_m=0.05,\ w=-1.5$, respectively.
+  Left and right panels show the coordinates computed using the ``correct'' parameters $\Omega_m=0.26,\ w=-1$ 
+  and a wrong cosmology $\Omega_m=0.05,\ w=-1.5$, respectively.
   The growth of structure strengths the clustering and make structures more compact at lower redshift.
-  When the wrong cosmology is adopted, the comoving distances are mis-scaled and over-estimated by $25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$, respectively,  leading to a clear redshift evolution of the sizes of structures.
+  When the wrong cosmology is adopted, the comoving distances are upscaled by $25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1,1.5,2$, 
+  respectively, leading to a {\it redshift evolution} in the sizes of structures.
    }
@@
 
-We use the 2pCF across the line-of-sight as a statistical tool to probe the volume effect.
+We use the 2pCF across the LOS as a statistical tool to probe the volume effect.
 The galaxy 2pCF as a function of galaxy separation perpendicular to the LOS, $\xi(r_\perp)$, is computed for snapshot data of mock galaxies at redshifts 0.5, 1, 1.5 and 2.
@@
 
-\subsection{Galaxy 2pCF across the line-of-sight: at different redshifts}\label{sec_2pCF_diffz}
+\subsection{Galaxy 2pCF across the LOS: at different redshifts}\label{sec_2pCF_diffz}
 
@@
    \caption{\label{fig_diffz}
-  The 2pCF across the line-of-sight, $\xi_{r_\perp}$ (left panels), the shape of $\hat{\xi}_{r_\perp}$ (middle panels),
+  The 2pCF across the LOS, $\xi_{r_\perp}$ (left panels), the shape of $\hat{\xi}_{r_\perp}$ (middle panels),
   and the evolution with respect to the $z=0$ value, $\hat{\xi}_{r_{\perp}}(z=z_i) - \hat{\xi}_{r_{\perp}}(z=0)$ (right panels). 
-  Upper panels show that in the correct cosmology the redshift evolution of the shape of 2pCF is rather small regardless of the large redshfit evolution of the amplitude, 
+  Upper panels show that in the correct cosmology the redshift evolution of the shape of 2pCF is rather small regardless of the large redshift evolution of the amplitude, 
   whereas the lower panels show that, in a wrong cosmology $\Omega_m = 0.05,w=-1.5$, the redshift evolution of $\hat{\xi}_{r_\perp}$ is very significant.
@@
 
-The upper-left panel of Figure \ref{fig_diffz} displays the 2pCF across the line-of-sight measured from HR4 mock galaxies. % (multiplied by scale $r$) in the five snapshot.
-We multiply $\xi$ by the separation $r_\perp$ to obtain a similar statistical uncertainty on all scales.
+The upper-left panel of Figure \ref{fig_diffz} displays the 2pCF across the LOS measured from HR4 mock galaxies. % (multiplied by scale $r$) in the five snapshot.
+We multiply $\xi$ by the separation $r_\perp$ to obtain similar statistical uncertainty on all scales.
 For convenience we will use the denotation
@@
 In the upper-middle panel, the overlapping of $\hat\xi_{r_{\perp}}$
-clearly show the minimal redshift evolution of the shape.
+clearly shows that there is minimal redshift evolution of the shape.
 In the upper-right panel, 
@@
 
-\subsection{Galaxy 2pCF across the line-of-sight: cosmological effect }
-
-The 2pCF across the line-of-sight for galaxy positions constructed in a wrongly assumed cosmology $\Omega_m=0.05,\ w=-1.5$
+\subsection{Galaxy 2pCF across the LOS: cosmological effect }
+
+The 2pCF across the LOS for galaxy positions constructed in a wrongly assumed cosmology $\Omega_m=0.05,\ w=-1.5$
 is displayed in the lower panels of Figure \ref{fig_diffz}.
-The mis-scaling uniformly shifts the clustering pattern on all scales, 
+The scaling uniformly shifts the clustering pattern on all scales, 
 leading to a biased $\hat \xi_{r_\perp}$, which is 
@@
 
-The mis-scaling not only changes the shape of the 2pCF but also changes the value of $ \xi_{r_\perp}$. %The amplitude of $r_\perp\xi$ is amplified due to the stretch of scale.
+This scaling not only changes the shape of the 2pCF but also changes the value of $ \xi_{r_\perp}$. %The amplitude of $r_\perp\xi$ is amplified due to the stretch of scale.
 As is shown in the left panel, due to the stretch of scale the amplitude is enhanced at higher redshifts;
@@
 the inferred galaxy radial position.
-It is the major systematic in our previous works \citep{Li2014,Li2015,Li2016}
+It was the major systematic in our previous works \citep{Li2014,Li2015,Li2016}
 of statistical analysis on the 3D galaxy distribution.
@@
 The angular positions of galaxies are not shifted by RSD at all;
-the only effect of RSD enter in the procedure of 
-splitting galaxies into redshift shells.
+the only effect of RSD enter in the redshift distribution of the galaxies in our predefined redshift shell.
 The galaxies observed in a survey are split into shells of subsamples, 
@@
 are imposed to create samples with different galaxy biases.
-The measured 2pCF across the line-of-sight are displayed.
+The measured 2pCF across the LOS are displayed.
 
@@
 
-%In summary, the effect of RSD and galaxy bias on the shape of the galaxy correlation function across the line-of-sight is not large, but is non-negligible.
+%In summary, the effect of RSD and galaxy bias on the shape of the galaxy correlation function across the LOS is not large, but is non-negligible.
 %When dealing with real observational data, one should construct simulation mocks in which these effects are reliably modelled, 
@@
 
-In summary, we aim to minimise the redshift evolution of the shape of the normalised  2-point correlation function across the line-of-sight; 
-the shape change is dramatic when considering a cosmological model significantly different from the fiducial model.
-However even in the case of the correct cosmology there remains a small signal, due to growth of structures, RSD and galaxy bias. 
-These systematics are removed with the aid of simulations.
+In summary, we aim to minimise the redshift evolution of the shape of the normalised  2-point correlation function across the LOS.
+We find that this shape change is dramatic when considering a cosmological model significantly different from the fiducial model.
+However even in the case of the correct cosmology there remains a small signal, due to growth of structures, RSD and galaxy bias. These systematics are removed with the aid of simulations.
 The procedure of the correction of systematics is similar to what was implemented in our previous papers \cite{Li2014,Li2015,Li2016}.
@@
 The systematics are estimated from a simulation conducted using a particular cosmology. 
-Thus there could be a bias in their estimation if the simulation cosmology is different from the true cosmological model/. 
+Thus there could be a bias in their estimation if the simulation cosmology is different from the true cosmological model. 
 The bias would not be serious if the simulation cosmology is consistent with the best-fit cosmological parameters obtained from the analysis \cite{Li2016}. 
@@
 
-To avoid the large systematics in the nonlinear regime, 
-another solution would be to increase the scale of analysis to larger separations where the non-linear effect is becoming subdominant. 
+Another solution, to avoid the large systematics in the nonlinear regime, 
+would be to increase the scale of analysis to larger separations where the non-linear effect becomes subdominant. 
 Figure \ref{fig_sys} shows that, 
@@
 Actually, we tested and found that, using $s = 5-40 h^{-1} {\rm Mpc}$ and $20-40 h^{-1} {\rm Mpc}$, 
-yields cosmological constraints that are pretty close to each other (see \S 4).
+yields cosmological constraints that are similar to each other (see \S 4).
 
 We do not consider the systematic effects in case of non-standard cosmological scenarios such as modified gravity and warm dark energy.
-These topics go beyond the scope of this work, however they are worthy future investigations.
+These topics go beyond the scope of this preliminary work, however they are worthy future investigations.
 
@@
 
-%estimated from the 72 sets of PSB mock galaxies identified from HR3 N-body simulation.
-
 Figure \ref{fig_cosmo} displays the 2pCF and the likelihood values when adopting 
@@
 The 2$\sigma$ contour lies within the region $0.23<\Omega_m<0.29$, $-1.1<w<-0.9$.
-The two parameters are very strongly degenerated with each other,
-and the area of constrained region is quite small.
+The two parameters degenerates strongly with each other,
+and the area of the constrained region is quite small.
 The thin shape of the contour implies that, 
-when combining with other observational data with a different direction of degeneracy (e.g. CMB, BAO),
-a very tight combined constraint can be obtained.
+when combining with other observational data with a different degeneracy directions (e.g. CMB, BAO),
+a very tight combined constraint could be obtained.
 
@@
 
-Finally, to be connected with the real observations, 
+Finally, to put the constraints of our new methodology in perspective, 
 the lower right panel displays the constraints from Planck CMB (dotted blue, \cite{Planck2015}),
@@
 
-The predicted constraints from this method clearly wins due to the large sample size.
+The predicted constraints from this method clearly has an advantage due to the large sample size.
 The total number of galaxies used in this work is 1.75 billion,
@@
 So the constrained area is also $\sim 30$ times smaller.
-Such a large sample size will be enabled by LSST (the Large Synoptic Survey Telescope) \footnote{https://www.lsst.org/}, 
+Such a large sample size will be possible with LSST (the Large Synoptic Survey Telescope) \footnote{https://www.lsst.org/}, 
 which probe tens of billions of galaxies at $z\lesssim2$.
@@
 
-We have developed a method for constraining certain cosmological parameters by measuring the redshift evolution of the shape of the galaxy 2pCF across the line-of-sight, $\hat \xi_{r_\perp}$.
-We found that a wrongly adopted cosmology results in a redshift-dependent mis-scaling in the constructed galaxy distribution,
+We have developed a method for constraining certain cosmological parameters by measuring the redshift evolution of the shape of the galaxy 2pCF across the LOS, $\hat \xi_{r_\perp}$.
+We found that a wrongly adopted cosmology results in a redshift-dependent scaling in the constructed galaxy distribution,
 which in turn leads to a redshift-dependent rescaling of $\hat \xi_{r_\perp}(r_\perp)$.
@@
 the galaxy bias, and the RSD effect.
-We tested our method on the HR4 mock galaxies having 457, 406, 352, 306 and 228 million galaxies at redshifts 0, 0.5, 1, 1.5, 2.
+We tested our method on the HR4 mock galaxies having 457, 406, 352, 306 and 228 million galaxies at redshifts 0, 0.5, 1, 1.5, and 2.
 Analyzing the redshift evolution of $\hat \xi_{r_\perp}(r_\perp)$ 
@@
 
-In this analysis we restrict our focus to the rescaling in the direction perpendicular to line-of-sight .
+In this analysis we restrict our focus to the rescaling in the direction perpendicular to LOS.
 %The angular correlation function is adopted as a statistical tool to probing the scaling effect in the angular direction.
 One can also use the 2D 2pCF $\xi(s,\mu)$ 
-as a function of both angular and radial scale to fully probe the scaling effect in the 3D galaxy distribution.
-
-In our early work of \cite{Li2015,Li2016}, 
-we proposed to use the angular-dependence of the galaxy clustering to apply an AP test and derive cosmological constraints. 
-In contrast, in this work we focus on the scale-dependence of the clustering. 
+as a function of both angular and radial scales to fully probe the scaling effect in the 3D galaxy distribution.
+
+In our early work of \cite{Li2015}, 
+we proposed to use the $\mu$-dependence of the galaxy clustering to apply an AP test. 
+Tight cosmological constraints are derived from the BOSS galaxies \citep{Li2016}. 
+In contrast, in this work we focus on the $s$-dependence of galaxy clustering. 
 The two methods focus on different parts of the clustering information, and the constraints derived from the them should be fairly independent.
-However, it is advisable to have an estimation of the covariance between them in the case there one is using both methods in combination.
-An alternative way is to investigate the redshift evolution of the correlation map $\xi(s,\mu)$ as a function of both scale and direction, which captures all the information.
+However, it is advisable to have an estimation of the covariance between them in the case that one is using both methods in combination
+\footnote{An alternative way is to investigate the redshift evolution of the correlation map $\xi(s,\mu)$ as a function of both scale and direction, which captures all the information.}.
 
@@
 by directly comparing the theoretical 2pCF and the observed one \citep{Salvador2014,Salvador2016}.
-Our method is simpler and just uses the fact that in the correct cosmology the shape of the 2pCF across the line-of-sight
-does not exhibit significant redshift evolution.
+Our method is simpler and just uses the fact that in the correct cosmology the shape of the 2pCF does not exhibit significant redshift evolution.
 %is insensitive to redshift in correct cosmology.
@@
 
-\cite{Li2015,Li2016} shows that using the redshift dependence of the AP effect, 
-one can derive very tight cosmological constraints.
-The method presented in this paper studies the redshift evolution of the volume effect.
+%\cite{Li2015,Li2016} shows that using the redshift dependence of the AP effect, 
+%one can derive very tight cosmological constraints.
+%The method presented in this paper studies the redshift evolution of the volume effect.
 %We hope this method also.
-These two methods probe different information encoded in the 2pCF 
-and can be combined to give a complete geometric probe of the LSS galaxy distribution.
+%These two methods probe different information encoded in the 2pCF 
+%and can be combined to give a complete geometric probe of the LSS galaxy distribution.
 %Or one can also use the redshift evolution of 2D 2pCF xi(s,mu) to have all information included.
@@
 with a particular emphasis on {\it photometric surveys}.
-The galaxy 2pCF across the line-of-sight in redshift shells is much less affected by the large redshift errors compared wit the 3D 2pCF.
+The galaxy 2pCF across the LOS could be less affected by the large redshift errors.
 The Dark Energy Survey will probe hundreds of millions of galaxies at $z\lesssim1.5$
@@
 and also \cite{topology,MS2016},
-are introducing a new strategy to constrain cosmology from galaxy clustering.
-We utilize a statistical pattern which remains constant at all redshifts;
-this invariance is broken when incorrect cosmologies are adopted to construct the galaxy distribution
-and introduces redshift evolution of geometric distortion.
+are introducing a new strategy of galaxy clustering statistics.
+We utilize a statistical pattern which remains constant at all redshifts.
+When incorrect cosmologies are adopted to construct the galaxy distribution, it introduces redshift-dependent geometric distortion,
+and the invariance is broken.
 The systematic effects can be corrected by performing an N-body simulation 
@@
 This avoids the difficulty in the analytical modeling the galaxy clustering, galaxy bias and RSD,
-and enables reliable cosmological constraint on relatively small clustering scales.
+and enables reliable cosmological constraints on relatively small clustering scales.
 We hope these methods play an important role in deriving cosmological constraints from future LSS surveys.
